### 2020-10-27 Draft_V4046Sgr_mnras.tex
Initial Overleaf Import

% mnras_template.tex 
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[letters,usenatbib,times]{mnras}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}

% Allow "Thomas van Noord" and "Simon de Laguarde" and alike to be sorted by "N" and "L" etc. in the bibliography.
% Write the name in the bibliography as "\VAN{Noord}{Van}{van} Noord, Thomas"
\DeclareRobustCommand{\VAN}[3]{#2}
\let\VANthebibliography\thebibliography
\def\thebibliography{\DeclareRobustCommand{\VAN}[3]{##3}\VANthebibliography}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
%% \usepackage{amssymb}	% Extra maths symbols

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.

\title[High-resolution ALMA observations of V4046\,Sgr]{High-resolution ALMA observations of V4046\,Sgr: a circumbinary disc with a thin ring}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[R. Martinez Brunner et al.]{
Rafael Martinez-Brunner,$^{1}$\thanks{E-mail: rmartinezbrunner@gmail.com}
Simon Casassus,$^{1}$
Sebasti\'an P\'erez,$^{2}$
et al. 
\\
% List of institutions
$^{1}$Departamento de Astronom\'{\i}a, Universidad de Chile, Casilla 36-D, Santiago, Chile\\
$^{2}$Universidad de Santiago de Chile, Av. Ecuador 3659, Santiago\\
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2020}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
  The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc known for its wide cavity and dusty ring. We present new high resolution ($\sim$20\,mas) ALMA observations of the 1.3\,mm continuum. The comparison of these observations, combined with SPHERE-IRDIS polarized images and a well-sampled spectral energy distribution (SED), against radiative transfer (RT) predictions carried out with the \textsc{radmc3d} package, allow us to propose a physical model for the source. The new ALMA data reveal a very thin ring at a radius of 13.46$\pm$0.43\,au (Ring13), with a marginally resolved radial width of 3.86$\pm$1.00\,au. Ring13 is surrounded by a $\sim$9\,au-wide gap, and it is flanked by a very bright mm outer ring (Ring24) with a sharp inner edge at 24\,au. The steeply decreasing brightness of Ring24 breaks at $\sim$35\,au into a shallow tail. The RT model requires an inner ring at $\sim$6\,au (Ring6) in small dust grains, hiding under the IRDIS coronagraph, and that surrounds an inner circumbinary disc. Faint mm-continuum close ($\sim0\farcs02$) to the stellar position is picked up by ALMA. ***
  %coincident with Ring6 is picked up by ALMA, whose morphology suggests that Ring6 is lopsided or shadowed by the secondary. 
  The previously reported scattered-light shadow of the secondary star is also reproduced by the RT model. The surprising thin Ring13 is nonetheless roughly 12 times wider than the model scale height, and could thus be long-lived. The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$. 
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
 protoplanetary discs -- submillimetre: planetary systems -- radiative transfer
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

\section{Introduction} \label{sec:Introduction}

Recent observations of young circumstellar discs have transformed current knowledge of planet formation, but the focus of resolved imaging with the Atacama Large Millimetre/submillimetre Array (ALMA) or with 
%VLT/SPHERE 
the current generation of high-contrast images 
has mainly been towards the brighter sources \citep{Andrews2020arXiv200105007A}. The discs around T Tauri Stars (DARTTS) program was first presented in \citet{Avenhaus_2018} with the aim to image eight stars with the Spectro-Polarimeter High-contrast Exoplanet REsearch (SPHERE) \citep{2019A&A...631A.155B}. The sample is not biased towards exceptionally bright and large discs, and consists of only solar-type stars. A second part of the survey increased the number of sources by presenting 21 new images of circumstellar discs \citep{Garufi2020}. The observations revealed diverse structures and morphologies in the scattering surface of these discs. This letter on V4046 Sagittarii (Sgr) is part of the DARTTS survey with ALMA (DARTTS-A) which will present millimetre observations of nine protoplanetary discs previously imaged in polarized scattered light in DARTTS-S.

V4046\,Sgr is a double-lined spectroscopic binary of K-type stars (K5 and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012} in a close ($a \approx 0.041$\,au), circular ($e\leq0.01$) orbit, with an orbital period of 2.42 days \citep{refId0}. It is a member of the $\beta$ Pictoris moving group \citep{Zuckerman_2004}, with an estimated age of 23$\pm$3\,Myr \citep{Mamajek_2014}, and its distance is 72.41$\pm$0.34\,pc \citep{Gaia}. V4046\,Sgr hosts a massive ($\sim$0.1\,M$_{\sun}$) circumbinary disc extending to $\sim$300\,au \citep{Rosenfeld_2013, Rodriguez_2010}, with a rich observable chemical diversity \citep{Kastner_2018}.

The structure of this letter is as follows. The observations, including new 1.3\,mm continuum data, are described in Section~\ref{sec:Observations}. We interpret the data in terms of a parametric model, presented in Section~\ref{sec:model}. Previous models of V4046\,Sgr have been made \citep{Ru_z_Rodr_guez_2019, Rosenfeld_2013, 2019ApJ...882..160Q} but our new ALMA data bring additional information. Our results are discussed in Section~\ref{sec:results} and summarised in Section~\ref{sec:Conclusions}.

\section{Observations} \label{sec:Observations}

%% Disc structures can be explored by means of comparing mm continuum and scattered-light images. These observations allow us to see the distribution of different populations of dust particles, while ALMA traces the millimetre-sized grains settled in the mid-plane of the disc, scattered-light imaging accounts for photons reflected off small micron-sized dust at the disc surface layer, high above the mid-plane. By comparing both, is easier to determine whether asymmetries in scattered light correspond to surface ripples or deep structures intrinsic to the underlying density distribution.

New ALMA observations of V4046\,Sgr were obtained in 2017 as part of the Cycle 5 program 2017.1.01167.S (PI: S. Perez). These were acquired in the context of the DARTTS-A program (Perez et al. {\em in prep}), a larger survey for 9 optically visible TTauri discs at $\sim$50\,mas resolution. The survey simultaneously mapped the 1.3\,mm continuum and the J = 2$-$1 line of $^{12}$CO with the C43-8 array configuration in band 6 (211-275\,GHz). This work focuses exclusively on the data obtained in the 1.3\,mm continuum for our source, acquired with baselines ranging from 92 to 8548\,m, which translate into a synthesized beam of $0\farcs077 \,\times \, 0\farcs051$ (in natural weights).

V4046 Sgr was observed in differential polarization imaging (DPI) mode with SPHERE/IRDIS on March 13, 2016. All the details of this observation can be found in the first DARTTS-S paper \citep{Avenhaus_2018} where the image was first published. Here we use a new reduction of the $H$ band data produced by the IRDAP pipeline \citep{2020A&A...633A..64V}, which can separate stellar and instrumental polarization. The polarized signal is consistent with the previous image in \citet{Avenhaus_2018}. The degree of linear polarization of the central and unresolved signal in V4046 Sgr is only 0.13\%, with a systematic uncertainty of 0.05\% due to time-varying atmospheric conditions during the exposures. The angle of polarization is aligned with the disk major disk, as expected given that the target has Av=0.0 \citep{2016ApJ...828...69M} and the entire polarization is dominated by circum rather than inter-stellar material.

For our analysis of the ALMA image we used an image reconstruction strategy, using the non-parametric image synthesis of the {\tt uvmem} package \citep{2006ApJ...639..951C, 2018A&C....22...16C} it is possible to super-resolve the clean beam, obtaining an effective angular resolution $\sim$3 times finer than natural weights. The model image is obtained by fitting the data using Chi-squared minimisation, with a measure of regularization when required. Here we adopted a $\chi^2$ model image with $\lambda$ = 0.1 for regularization. The resulting {\tt uvmem} image shown in Fig.~\ref{fig:images_vs_simulated} exhibits previously unseen substructure of the disc. This image reveals that the disc features two rings of large dust grains with a broad gap between them, i.e. Ring13 at 13\,au and Ring24 starting at 24\,au. The wide and bright Ring24 reaches its peak intensity at $\sim$30\,au, beyond which it drops steeply before breaking at $\sim$35\,au into a shallow tail. While this is the first observation of Ring13, \citet{Ru_z_Rodr_guez_2019} did anticipate its existence as their ALMA continuum image showed a distinct excess between
$\sim$10 and 17\,au.

\begin{figure*}
  \includegraphics[width=\textwidth]{hot_two_E.pdf}
  \caption{Comparison of observations and simulated images at 1.65\,$\micron$ and 1.3 mm continuum of the circumbinary disc orbiting V4046\,Sgr. From top to bottom: DPI image and ALMA Band 6 observations; simulated images of the parametric model. Top left panel: SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that illustrate the N\_ALC\_YJH\_S coronagraph with a radius of $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc. Top right panel: 1.3\,mm continuum {\tt uvmem} model image. The yellow ellipse shows the size of the natural-weighted beam ($ 0\farcs077 \, \times \, 0\farcs051$), and the small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs026 \, \times \, \sim0\farcs017$). The inset zooms into the central emission, and the green star marks the star positions. Bottom left panel: 1.65\,$\upmu m$ simulated image of the parametric model. Bottom right panel: 1.3\,mm simulated image of the parametric model. The orange ellipse shows the size of the beam: $0\farcs026 \, \times \, 0\farcs017$. For all the images in the figure the colour scale is linear.}
  \label{fig:images_vs_simulated}
\end{figure*}

Ring13 is surprisingly narrow and seems to be off-centred relative to the GAIA stellar position (at the origin of coordinates in Fig.~\ref{fig:images_vs_simulated}). We determined the ring's centre and orientation by minimising the dispersion of the disc radial profiles, from 6\,au to 19\,au, and thus obtained a PA of 74.64$\pm$0.08\,$\degr$, an inclination of 33.90$\pm$0.04\,$\degr$ and a centre at $\Delta \alpha = 9\pm0.05$\,mas $\Delta \delta = 0.06\pm0.04$\,mas, relative to the stars.

The ring width can be measured in polar coordinates by fitting 1-D Gaussians, thus obtaining a width and centroid at each azimuth. On average, we obtained a FWHM of 4.17$\pm$0.94\,au, and a stellocentric radius of 13.46$\pm$0.43\,au (See Fig.~\ref{fig:polarring}). As the {\tt uvmem} model image has an effective angular resolution of $\sim$1/3 that of the natural-weighted beam ($0\farcs077 \,\times \, 0\farcs051$), we see that Ring13 is marginally resolved. After subtraction of the approximate {\tt uvmem} resolution ($\sim0\farcs026 \, \times \, \sim0\farcs016$), the ring width is $\sim$3.86$\pm$1.00\,au.

Repeating the optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.78$\pm$0.03\,$\degr$, with an inclination of 34.01$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 19\pm0.04$\,mas $\Delta \delta = 7\pm0.03$\,mas relative to the stars. We see that both Ring13 and Ring24 both share the same orientation and centre, given the errors, and both are offset from the star. Even though all orientation parameters for Ring13 and Ring24 are consistent within the errors, there are however some hints for a different orientation, as summarised in Fig.~\ref{fig:polarring}, perhaps due to the joint effect of all these small differences.

Interestingly, the ALMA image also detects faint 1.3\,mm continuum emission near the stellar positions (See the inset in Fig.~\ref{fig:images_vs_simulated}). Since this faint central emission is offset from the star, at the origin of coordinates in the figure, it is probably due to large dust grains. This dust structure is at a distance of only $\sim0\farcs02$ from the binary system, and may be part of some inner structure possibly having to do with the small grain ring called Ring6 introduced in the RT model to match the SED (see Sec.\,\ref{sec:model} below). ***
%match the small grain ring called Ring6 introduced in the RT model to match the SED (see Sec.\,\ref{sec:model} below). If so, then given that the binary phase at the time of the observations is PA=347\,$\degr$, so that the secondary lies roughly northwards of the primary, it may be that the northern side of Ring6 is shadowed, resulting in a seemingly lopsided geometry.

The scattered-light image shown in Fig.~\ref{fig:images_vs_simulated} also shows a double ring structure in the micron-
sized dust distribution. The observed morphology presents an inner cavity of $\sim$10\,au in radius and two rings located at 14.10$\pm$0.01, coincident with Ring13, and 24.62$\pm$0.08\,au, coincident with Ring24, with a small gap between them at $\sim$20\,au. The observed second ring matches the inner wall of the 1.3\,mm continuum emission outer ring \citep{Ru_z_Rodr_guez_2019}. Two other important features that are present in the image are: the brightness asymmetry and the shadows projected on the disc produced by the close binary system as they eclipse each other, described in detail by \citet{dOrazi}.

The binary phase reported by \citet{dOrazi} in the scattered-light observation is at a position angle (PA) of 254\,$\degr$, east of north. Using this measurement, the binary phase was calculated at the time of the ALMA observation at a PA of 347\,$\degr$. There is no hint of radio decrements in either Rings13 nor in Ring24 that would match shadowing at this PA, could be explained by inefficient disc cooling compared to the speed of the illumination pattern \citep{Casassus2019MNRAS.486L..58C}.

\begin{figure}
    \includegraphics[width=\columnwidth]{polar_ring_aprox_and_diff_inner.pdf}
    \caption{(a) Polar decomposition of the 1.3\,mm continuum image, using the orientation of Ring24. We trace Ring13 using the centroids (solid line) and width of radial Gaussian fits (blue region between the dotted lines). (b) Centroid of Ring13, for two disc orientations: the orange line corresponds to the same trace as in a), while the blue line is obtained for the inner ring orientation.}
    \label{fig:polarring}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{comp_fig_all_profiles_au.pdf}
    \caption{Comparison of the surface brightness profiles extracted from the deprojected synthetic images and observed \textit{H}-band and 1.3\,mm continuum images. The grey shaded area represents the radius of the artificial coronagraph used in the simulations (i.e., $\sim0\farcs 12$, or $\sim$8.6\,au at 72.4\,pc).}
    \label{fig:radprofiles}
\end{figure}

The observed SED was collected from data in the literature \citep{1988iras....7.....H, 1990A&A...234..230H, Jensen_97, 2000A&A...355L..27H, 2001KFNT...17..409K, 2003yCat.2246....0C, 2007PASJ...59S.369M, 2008PASP..120.1128O, 2010A&A...514A...1I, 2012yCat.2311....0C}, online in \textsc{vizier}, and also using spectrometry data from an archival \textit{Spitzer} IRS spectrum (See Fig.\ref{fig:SED}). The SED will provide us with missing information about the dust population.

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{SED_.png}
    \caption{The observed SED of V4046\,Sgr (black points and solid red curve) compared with the model (blue). The black points represent the measured photometry and the red line shows an archival \textit{Spitzer} IRS spectrum. The dashed silver curve shows the emission of the stellar photosphere model.}
    \label{fig:SED}
\end{figure}

\section{Parametric radiative transfer model} \label{sec:model}

The multi-frequency data can be interpreted in terms of a physical structure using radiative transfer predictions, for which we used the \textsc{radmc3d} package \citep{Dullemond_2012}. The general framework of the parametric model that we used is similar to that in \citet{2018MNRAS.477.5104C} for DoAr\,44, and the initial model values were inspired from those in \citet{Rosenfeld_2013}. Through trial and error, we found a set of values for the parameters that correctly fit the available data. The final structure of the parametric model goes as Fig.~\ref{fig:profiles} shows.

For the representation of the stars, we used two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C} with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of log$\,\dot{\mathrm{M}} = -$9.3\,Myr$^{-1}$ for both cases \citep{10.1111/j.1365-2966.2011.19366.x}. The stars were placed at a mutual separation of 0.041\,au, so that their centre of mass coincides with the origin, and oriented at a PA of 250\,$\degr$, so that the secondary lies to the NWW from the primary, thus casting the same shadow as observed by \citet{dOrazi}.

Reproducing the radial and vertical structure of the V4046\,Sgr disc turned out to be challenging. We built the model in terms of the gas distribution, and with two different dust populations: larger grains that are vertically settled and dominate the total dust mass and a population of smaller grains that are uniformly mixed with the gas and reach larger heights above the mid-plane.

Assuming a three dimensional model in a cylindrical reference frame with coordinates ($r$, $\theta$, $z$), the gas density ($\rho_{\mathrm{gas}}$) distribution follows
\begin{equation}
  \rho_{\mathrm{gas}}(r,z) =\frac{\Sigma(r) \,\delta(r)}{\sqrt{2\pi} \, H(r)} \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{H(r)}\right)^2\right],
\end{equation}
where $\delta(r)$ parameterises the density drops in the gaps and cavities, $H(r)$ is the scale height profile and $\Sigma(r)$ is the surface density profile. $\Sigma(r)$ is defined by
\begin{equation}
  \Sigma(r) = \Sigma_\mathrm{c} \left(\frac{r}{R_\mathrm{c}}\right)^{-\gamma}  \, \mathrm{exp}\left[-\left(\frac{r}{R_\mathrm{c}}\right)^{2-\gamma}\right],
\end{equation}
where $R_c$ is a characteristic radius and $\gamma$ is the surface density gradient. A fixed $\gamma$ = 1 is used as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.

%The $\delta(r)$ function, that account for deviations from the power law, is defined as:
%\begin{align}
%\delta(r) = \left\{ \begin{array}{cc} 
%                 5E-6 & \hspace{5mm} 0.3<r<5 \\
%                 5E-3 & \hspace{5mm} 5<r<8  \\
%                 5E-5 & \hspace{5mm} 8<r<12\\
%                 2.5E-2 & \hspace{5mm} 12<r<19.5 \\
%                 1E-8 & \hspace{5mm} 19.5<r<20.5 \\
%                 1E-4 & \hspace{5mm} 20.5<r<25 \\
%                 1.7E-1 & \hspace{5mm} 25<r<120 \\
%                \end{array} \right.
%\end{align}

The parametric scale height profiles for the gas and for each dust population are 
\begin{equation}
    \label{scale}
  H(r)=\chi \, H_{o}(r) \, [r/r_{o}(r)]^{\psi(r)},
\end{equation}
where $H_\circ$ is the scale height at r = $r_\circ$, $\psi$ is the flaring index and $\chi$ is a scaling factor (in the range $0-1$) that mimics dust settling. For the gas and the small dust grains $\chi$ = 1 and for the millimetre-size dust population we assign a fixed $\chi$ = 1/2 for simplicity, as in \citet{Rosenfeld_2013}.

For the vertical structure, \citet{dOrazi} found flaring angles of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one. explicar que es varphi y como se transforma en psi*** Our model uses the same values, with two different flaring indexes $\psi$. The separation between the two values were set at $r$ = 19\,au with $\psi=0.2$ for Ring6 and Ring13, and $\psi=0.5$ for Ring24. The scale height is $H_\circ = 0.045$ at $r_0 = 19.5$\,au.

The total dust-to-gas mass ratio is taken to be $\zeta = 0.047$ \citep[as in][]{Rosenfeld_2013}. The small dust grains are assumed to only make up for a fraction of $f_\mathrm{sd}=1\%$ of the total dust mass. As small dust is typically tightly coupled to the gas dynamics, its density profile is largely expected to follow the gas density. Then the density of small dust can be calculated as:
\begin{equation}
\rho_{\mathrm{small-dust}}(r,z)=\rho_{\mathrm{gas}}(r,z)\, f_{\mathrm{sd}} \: \zeta .
\end{equation}

Since the large-dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a large inner cavity and scaling factors that account for the larger gap between the rings. For the inner ring, the same profile as the gas is used, but with different values for $R_c$ and $\Sigma_c$. The greatest difference is in the outer ring, where we used a decaying power law modulated by the sum of two Gaussian profiles. In an effort to recreate the break seen in the outer ring between 30.2 and 36.7\,au, we chose a different value for $\gamma$ = -6. For the large dust grains the surface density profile is thus
\begin{multline}
  \Sigma_{\mathrm{large-dust}}(r) = \Sigma_{\mathrm{c}2} \left(\frac{r}{R_{\mathrm{c}2}}\right)^{-\gamma} \\ \, \left\{ \exp\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2-\gamma}\right] + \mathrm{exp}\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2}\right]\right\}.
\end{multline}

The inner part of the outer ring follows a different behaviour. Between $R_\mathrm{in}$ and $R_\mathrm{peak}$, the gas density profile is multiplied by an additional factor
\begin{equation}
    \epsilon(r) = \left(\frac{ r - R_\mathrm{in}}{R_\mathrm{peak} - R_\mathrm{in}}\right)^3,
\end{equation}
where $R_\mathrm{in}$ and $R_\mathrm{peak}$ would depend on the dust population, marking the beginning and the maximum density peak of the outer ring. This parameter allow us to model a smoother inner wall of the outer ring.

The two different populations of dust grains corresponds to the small grains, with radii ranging from 0.4 to 1.5\,$\micron$, and the large dust grains range, with radii from 0.4\,$\micron$ to 10\,mm. We computed the dust opacities using the {\tt bhmie} code provided in the \textsc{radmc3d} package, with a mix composed of 70\% silicate and 30\% graphite.

The observed near-far asymmetry in the DPI image is suggestive of a strongly forward-scattering phase function. In order to reproduce a similar asymmetry, we used much larger grains that typically used in the RT modelling of such near-IR data \citep[e.g.,][]{2018MNRAS.477.5104C}.

The simulated DPI image at 1.65\,$\micron$ in Fig.\,\ref{fig:images_vs_simulated} was obtained with the scattering matrix calculated by the {\tt makeopac.py} script provided in the \textsc{radmc3d} package. As a way of reproducing the \textit{H}-band image, we used a different grain size distribution, where we used a Gaussian distribution centred at 0.4\,$\micron$, and smeared out by 30\% in both directions, and using 20 grain size bins within that range. This distribution applies only to generate the NIR image.

\begin{figure}
	\includegraphics[width=\columnwidth]{allprofiles.png}
        \caption{{\bf Top:} surface density profiles for the gas, the large and small grain populations. {\bf Bottom:} scale height profile $h(r)$. The dashed lines crossing both panels correspond to transition radii in the parametric model.}
    \label{fig:profiles}
\end{figure}

The gas and small dust surface density profiles begin at 0.3\,au, out of the zone expected to be cleared by dynamical interactions with the central binary \citep{Art_Lu}, which is expected to be $\sim$0.1\,au. For the small dust grains, we propose a three ringed structure. The innermost ring of the model is located from 5 to 8\,au, this ring, introduced as Ring6 in Sec.\,\ref{sec:Observations}, is not detectable in the IRDIS observations but was required to account for the SED. Then follow the two rings observed by IRDIS: Ring13, from 12 to 19.5\,au, which is surrounded by very narrow 1\,au-wide gap, and then Ring24, that starts 20.5\,au and has its maximum density peak at 25\,au. The small-dust density then decays exponentially with radius.

On the other hand, in order to reproduce the double-ringed morphology of the millimetre continuum emission, we required a model with a wide central cavity ($r = 11.7$\,au), a narrow 3.7\,au-wide inner ring (which is Ring13) followed by a 8.2\,au gap that separates the outer ring (Ring24), which starts at 22\,au and reaches peak densities at 27.7\,au. This last ring has an observed break between 30.2 and 36.7\,au, which is reproduced in the model with a discontinuity in the exponent $\gamma$, along with the sum of the decaying exponentials. We also truncated the model large-grain density at $\sim$55\,au.

The inner radius of the model grid was set to 0.1\,au and an outer radius of 115\,au, large enough for the dust disc to become undetectable. We set the values of the inclination an the position angle as the same as those obtained from the ALMA observation in Section~\ref{sec:Observations}, so the model has an inclination of i = 33.9\,$\degr$ and a P.A. = 74.6\,$\degr$. Finally, the distance is set at d = 72.4\,pc \citep{Gaia}.

\section{Model results and discussion} \label{sec:results}

Our parametric model is fairly successful in reproducing the available data. The simulated images and the SED of the model are shown in Fig.~\ref{fig:images_vs_simulated} and Fig.~\ref{fig:SED} respectively.

The simulated image at 1.65\,$\micron$ shows a similar radial structure to the one visible in the observations, displaying a two ringed disc, where Ring6 hides under the artificial coronagraph. The visible asymmetry in the SPHERE observations is recreated using grains larger than 0.4\,$\micron$ as smaller grains do not cause a strong forward scattering, meaning that the disc is depleted of very-small grains. Interestingly, the model accurately shows the shadows described by \citet{dOrazi} that are present in the SPHERE-IRDIS image.

The simulated 1.3\,mm continuum image reproduces the two observed rings: the faint Ring13 and the brighter Ring24. As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.~\ref{fig:radprofiles}), we can assume that the model provides an approximation of the disc structure, including the dimensions of Ring13. Accordingly, taking the parametric model values for Ring13 we have that it has a radius of 13.6\,au, a width of 3.7\,au, and a scale height FWHM of the millimetre-size dust ranging from 0.28 to 0.40\,au. The total dust mass of Ring13 is about 3\,M$_{\earth}$ in the model. In turn, in our model Ring24 reaches peak intensity at $\sim$30\,au, then breaks at $\sim$35\,au, as in the observations, and has a total dust mass of $\sim$43\,M$_{\earth}$. The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.14\,au difference in the centroid location of the ring, and a 0.17\,au difference in the width estimation.

As \citet{2018ApJ...869L..46D} explain the stability of a narrow dust ring requires that its height is smaller than its radial extent. Using the parametric model scale height of 0.28\,au at 13.46\,au and the measured width of Ring13 (3.86\,au FWHM, see Section~\ref{sec:Observations}), we have that its width is $\sim$12 times its scale height.

The observed structure may point to the existence of planet-disk interaction within this system, where a giant planet depletes its orbit of gas and dust material. A possible constellation in this scenario is therefore the presence of two giant planets in the disk, one planet between the star and Ring13, and one planet between Ring13 and Ring24. This idea is supported by the similarity to the structure around HD 169142 which \citet{bertrang_avenhaus_2018} reproduced by including several giant planets . We point out that also the disk dispersal by photoevaporative winds \citep{1994ApJ...428..654H} as causation of the inner cavity cannot be ruled out at his stage.

The effective beam size of the presented ALMA observations marginally resolves the width of Ring13 to be $w_\mathrm{d} = 3.86\mathrm{au}$. The most suitable RT model demands a density distribution of small grains and gas that is radially more extended, with an approximate width of $7.5\mathrm{au}$. Although the RT model ascribed step functions to gas and dust densities, in a more physical scenario the density should roughly follow a Gaussian distribution. Assuming that the gas' Ring13-width in the RT model corresponds to the FWHM of a Gaussian structure $w_\mathrm{g} = 7.5\mathrm{au}$, we can see that large dust grains have to be radially converged to explain the discrepancy.

Similarly to \citet{2018ApJ...869L..46D}, the ratio between dust and gas ring width can be linked to important properties:
\begin{equation}\label{eq:ringwidth}
        \frac{w_\mathrm{d}}{w_\mathrm{g}} = \sqrt{\frac{\alpha}{\alpha+\mathrm{St}}}\,,
\end{equation}
where we implicitly assumed the turbulent diffusivity to be equal to the turbulent viscosity. Here, $\alpha$ represents the typical parameter for turbulent viscosity, and $\mathrm{St}$ is the dimensionless Stokes number. Assuming that the most relevant grain size for observed fluxes corresponds to $a = \lambda \mathrm{obs}/(2 \pi)$, and estimating the gas surface density within Ring13 from the RT model to be roughly $20\,\mathrm{g}/\mathrm{cm}^2$, yields $\mathrm{St}\approx 0.03$. With these considerations, equation (\ref{eq:ringwidth}) provides a value of $\alpha \approx 0.01$ for the level of turbulent viscosity. We emphasise that this relies on rough estimates and is additionally restricted to the area within Ring13.

The observed SED is compared with the model in Fig.~\ref{fig:SED}. From the similarity with the data we propose that there has to be a small-grain population close to the stars down to 0.3\,au. The decision of employing the three ringed structure for the small dust grains relies on the fact that the SED needed a ring at a radius smaller than 10\,au to have a proper fit around 10\,$\micron$.
%and we may have detected this ring in the ALMA image, if this ring is lopsided or shadowed by the secondary. 
Ring6 may be just artificial and not a real prediction, as a thin ring like the one needed would have to have millimetre-size dust grains due to dust trapping, and those grains are not present in the ALMA observation. ***

\section{Conclusions} \label{sec:Conclusions}

New ALMA 1.3\,mm continuum imaging of the circumbinary disc around V4046\,Sgr were analysed in the context of the available IR imaging and the observed spectral energy distribution using a RT model. The key conclusions are as follows.
\begin{enumerate}
  \item We report the detection of a narrow ring in the 1.3\,mm continuum, with a radius 13.46$\pm$0.43\,au and an estimated width of 3.86$\pm$1.00\,au. The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes around 3\,M$_{\earth}$ millimetre-sized grains. Using the parametric model scale height value ($h= $ 0.28\,au at 13.46\,au) we have that the ring width is roughly 12 times its estimated height.

  \item The 1.3\,mm outer ring, that starts at $\sim$23\,au and has its peak intensity at $\sim$32\,au, presents a visible break in the surface brightness at $\sim$35\,au.

  \item We interpret the asymmetry observed with SPHERE-IRDIS at 1.65\,$\micron$ as due to strong forward-scattering, which implies that the dust population is depleted of grains smaller than $\sim$0.4\,$\micron$.

  \item Our parametric model, which accounts for the SED of the system, involves the existence of a sub-micron dust population close (<5\,au) to the stars. 
  %We also predict the existence of another thin ring at $\sim$6\,au, about 3\,au-wide and made of small dust grains, and that lies under the coronagraph of the scattered-light image. 
  %The weak central emission at 1.3\,mm could be part of this ring.
\end{enumerate}

 \section*{Acknowledgements}

This paper makes use of the following ALMA data: ADS/JAO.ALMA \#2017.0.01167.S. ALMA is a partnership of ESO (representing its member states), NSF (USA) and NINS (Japan), together with NRC (Canada), MOST and ASIAA (Taiwan), and KASI (Republic of Korea), in cooperation with the Republic of Chile. The Joint ALMA Observatory is operated by ESO, AUI/NRAO and NAOJ. The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.

This research has made use of the VizieR catalogue access tool, CDS, Strasbourg, France (DOI : 10.26093/cds/vizier). The original description of the VizieR service was published in \citet{2000A&AS..143...23O}.

This research has made use of the NASA/IPAC Infrared Science Archive, which is funded by the National Aeronautics and Space Administration and operated by the California Institute of Technology.

\section*{Data Availability}

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

% The best way to enter references is to use BibTeX:

\bibliographystyle{mnras}
\bibliography{bibtex} % if your bibtex file is called example.bib

% Alternatively you could enter them by hand, like this:
% This method is tedious and prone to error if you have lots of references
%\begin{thebibliography}{99}
%\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
%Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
%\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
%Others S., 2012, Journal of Interesting Stuff, 17, 198
%\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

% End of mnras_template.tex

### 2020-10-27 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 For the vertical structure, \citet{dOrazi} found flaring angles of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one.
-explicar que es varphi y como se transforma en psi*** Our model uses the same values, with two different flaring indexes $\psi$.
+Our model uses the same values, with two different flaring indexes $\psi$.
 The separation between the two values were set at $r$ = 19\,au with $\psi=0.2$ for Ring6 and Ring13, and $\psi=0.5$ for Ring24.
@@
 A possible constellation in this scenario is therefore the presence of two giant planets in the disk, one planet between the star and Ring13, and one planet between Ring13 and Ring24.
-This idea is supported by the similarity to the structure around HD 169142 which \citet{bertrang_avenhaus_2018} reproduced by including several giant planets .
+This idea is supported by the similarity to the structure around HD 169142 which \citet{bertrang_avenhaus_2018} reproduced by including several giant planets.
 We point out that also the disk dispersal by photoevaporative winds \citep{1994ApJ...428..654H} as causation of the inner cavity cannot be ruled out at his stage.

### 2020-10-29 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
   The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc known for its wide cavity and dusty ring.
-We present new high resolution ($\sim$20\,mas) ALMA observations of the 1.3\,mm continuum.
+We present new high resolution ($\sim$50\,mas) ALMA observations of the 1.3\,mm continuum.
 The comparison of these observations, combined with SPHERE-IRDIS polarized images and a well-sampled spectral energy distribution (SED), against radiative transfer (RT) predictions carried out with the \textsc{radmc3d} package, allow us to propose a physical model for the source.
@@
   The previously reported scattered-light shadow of the secondary star is also reproduced by the RT model.
-The surprising thin Ring13 is nonetheless roughly 12 times wider than the model scale height, and could thus be long-lived.
+The surprisingly thin Ring13 is nonetheless roughly 12 times wider than the model scale height, and could thus be long-lived.
 The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$.
@@
 
-Recent observations of young circumstellar discs have transformed current knowledge of planet formation, but the focus of resolved imaging with the Atacama Large Millimetre/submillimetre Array (ALMA) or with
+Recent observations of young circumstellar discs have transformed current knowledge of planet formation.
+The focus of resolved imaging with the Atacama Large Millimetre/submillimetre Array (ALMA) or with
 %VLT/SPHERE 
@@
 
-V4046\,Sgr is a double-lined spectroscopic binary of K-type stars (K5 and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012} in a close ($a \approx 0.041$\,au), circular ($e\leq0.01$) orbit, with an orbital period of 2.42 days \citep{refId0}.
+V4046\,Sgr is a double-lined spectroscopic binary of K-type stars (K5 and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012}, on a close ($a \approx 0.041$\,au), circular ($e\leq0.01$) orbit, with an orbital period of 2.42 days \citep{refId0}.
 It is a member of the $\beta$ Pictoris moving group \citep{Zuckerman_2004}, with an estimated age of 23$\pm$3\,Myr \citep{Mamajek_2014}, and its distance is 72.41$\pm$0.34\,pc \citep{Gaia}.
@@
 The degree of linear polarization of the central and unresolved signal in V4046 Sgr is only 0.13\%, with a systematic uncertainty of 0.05\% due to time-varying atmospheric conditions during the exposures.
-The angle of polarization is aligned with the disk major disk, as expected given that the target has Av=0.0 \citep{2016ApJ...828...69M} and the entire polarization is dominated by circum rather than inter-stellar material.
+The angle of polarization is aligned with the disk major disk, as expected given that the target has Av=0.0 \citep{2016ApJ...828...69M} and the entire polarization is dominated by circumstellar rather than inter-stellar material.
 
@@
 Since this faint central emission is offset from the star, at the origin of coordinates in the figure, it is probably due to large dust grains.
-This dust structure is at a distance of only $\sim0\farcs02$ from the binary system, and may be part of some inner structure possibly having to do with the small grain ring called Ring6 introduced in the RT model to match the SED (see Sec.\,\ref{sec:model} below).
+This dust structure is at a distance of only $\sim0\farcs02$ from the binary system, and may be part of some inner structure possibly having to do with the small grain ring called Ring6 introduced in the RT model to match the SED (see Sec.~\ref{sec:model} below).
 ***
@@
 Using this measurement, the binary phase was calculated at the time of the ALMA observation at a PA of 347\,$\degr$.
-There is no hint of radio decrements in either Rings13 nor in Ring24 that would match shadowing at this PA, could be explained by inefficient disc cooling compared to the speed of the illumination pattern \citep{Casassus2019MNRAS.486L..58C}.
+There is no hint of radio decrements in either Rings13 nor in Ring24 that would match shadowing at this PA.
+This could be explained by inefficient disc cooling compared to the speed of the illumination pattern \citep{Casassus2019MNRAS.486L..58C}.
 
@@
 
-\begin{figure}
-	\includegraphics[width=\columnwidth]{comp_fig_all_profiles_au.pdf}
-    \caption{Comparison of the surface brightness profiles extracted from the deprojected synthetic images and observed \textit{H}-band and 1.3\,mm continuum images.
-The grey shaded area represents the radius of the artificial coronagraph used in the simulations (i.e., $\sim0\farcs 12$, or $\sim$8.6\,au at 72.4\,pc).}
-    \label{fig:radprofiles}
-\end{figure}
-
-The observed SED was collected from data in the literature \citep{1988iras....7.....H, 1990A&A...234..230H, Jensen_97, 2000A&A...355L..27H, 2001KFNT...17..409K, 2003yCat.2246....0C, 2007PASJ...59S.369M, 2008PASP..120.1128O, 2010A&A...514A...1I, 2012yCat.2311....0C}, online in \textsc{vizier}, and also using spectrometry data from an archival \textit{Spitzer} IRS spectrum (See Fig.\ref{fig:SED}).
+The observed SED was collected from data in the literature \citep{1988iras....7.....H, 1990A&A...234..230H, Jensen_97, 2000A&A...355L..27H, 2001KFNT...17..409K, 2003yCat.2246....0C, 2007PASJ...59S.369M, 2008PASP..120.1128O, 2010A&A...514A...1I, 2012yCat.2311....0C}, online in \textsc{vizier}, and also using spectrometry data from an archival \textit{Spitzer} IRS spectrum (See Fig.~\ref{fig:SED}).
 The SED will provide us with missing information about the dust population.
@@
 
-For the representation of the stars, we used two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C} with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of log$\,\dot{\mathrm{M}} = -$9.3\,Myr$^{-1}$ for both cases \citep{10.1111/j.1365-2966.2011.19366.x}.
+For the representation of the stars, we used two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C} with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of $\mathrm{log}(\,\dot{\mathrm{M}/(\mathrm{M}_{\sun}\,\mathrm{yr^{-1}})}) = -$9.3 for both cases \citep{10.1111/j.1365-2966.2011.19366.x}.
 The stars were placed at a mutual separation of 0.041\,au, so that their centre of mass coincides with the origin, and oriented at a PA of 250\,$\degr$, so that the secondary lies to the NWW from the primary, thus casting the same shadow as observed by \citet{dOrazi}.
@@
 The separation between the two values were set at $r$ = 19\,au with $\psi=0.2$ for Ring6 and Ring13, and $\psi=0.5$ for Ring24.
-The scale height is $H_\circ = 0.045$ at $r_0 = 19.5$\,au.
+The scale height is $H_\circ = 0.045$\,au at $r_\circ = 19.5$\,au.
 
@@
 
-Since the large-dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a large inner cavity and scaling factors that account for the larger gap between the rings.
+Since the large dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a large inner cavity and scaling factors that account for the larger gap between the rings.
 For the inner ring, the same profile as the gas is used, but with different values for $R_c$ and $\Sigma_c$.
@@
 
-The inner part of the outer ring follows a different behaviour. Between $R_\mathrm{in}$ and $R_\mathrm{peak}$, the gas density profile is multiplied by an additional factor
+The inner part of the outer ring follows a different behaviour.
+Between $R_\mathrm{in}$ and $R_\mathrm{peak}$, marking the beginning and the maximum density peak of the outer ring respectively, the gas density profile is multiplied by an additional factor
 \begin{equation}
-    \epsilon(r) = \left(\frac{ r - R_\mathrm{in}}{R_\mathrm{peak} - R_\mathrm{in}}\right)^3,
+    \epsilon(r) = \left(\frac{ r - R_\mathrm{in}}{R_\mathrm{peak} - R_\mathrm{in}}\right)^3.
 \end{equation}
-where $R_\mathrm{in}$ and $R_\mathrm{peak}$ would depend on the dust population, marking the beginning and the maximum density peak of the outer ring.
+$R_\mathrm{in}$ and $R_\mathrm{peak}$ would depend on the dust population, with $R_\mathrm{in}$ = 20.5\,au and $R_\mathrm{peak}$ = 25\,au for the small dust grains and $R_\mathrm{in}$ = 22\,au and $R_\mathrm{peak}$ = 27.7\,au for the large dust grains.
 This parameter allow us to model a smoother inner wall of the outer ring.
 
-The two different populations of dust grains corresponds to the small grains, with radii ranging from 0.4 to 1.5\,$\micron$, and the large dust grains range, with radii from 0.4\,$\micron$ to 10\,mm.
+The two different populations of dust grains correspond to small grains, with radii ranging from 0.4 to 1.5\,$\micron$, and large dust grains, with radii from 0.4\,$\micron$ to 10\,mm.
 We computed the dust opacities using the {\tt bhmie} code provided in the \textsc{radmc3d} package, with a mix composed of 70\% silicate and 30\% graphite.
@@
 The observed near-far asymmetry in the DPI image is suggestive of a strongly forward-scattering phase function.
-In order to reproduce a similar asymmetry, we used much larger grains that typically used in the RT modelling of such near-IR data \citep[e.g.,][]{2018MNRAS.477.5104C}.
+In order to reproduce a similar asymmetry, we used much larger grains than typically used in the RT modelling of such near-IR data \citep[e.g.,][]{2018MNRAS.477.5104C}.
 
-The simulated DPI image at 1.65\,$\micron$ in Fig.\,\ref{fig:images_vs_simulated} was obtained with the scattering matrix calculated by the {\tt makeopac.py} script provided in the \textsc{radmc3d} package.
+The simulated DPI image at 1.65\,$\micron$ in Fig.~\ref{fig:images_vs_simulated} was obtained with the scattering matrix calculated by the {\tt makeopac.py} script provided in the \textsc{radmc3d} package.
 As a way of reproducing the \textit{H}-band image, we used a different grain size distribution, where we used a Gaussian distribution centred at 0.4\,$\micron$, and smeared out by 30\% in both directions, and using 20 grain size bins within that range.
@@
 For the small dust grains, we propose a three ringed structure.
-The innermost ring of the model is located from 5 to 8\,au, this ring, introduced as Ring6 in Sec.\,\ref{sec:Observations}, is not detectable in the IRDIS observations but was required to account for the SED.
+The innermost ring of the model is located from 5 to 8\,au, this ring, introduced as Ring6 in Sec.~\ref{sec:Observations}, is not detectable in the IRDIS observations but was required to account for the SED.
 Then follow the two rings observed by IRDIS: Ring13, from 12 to 19.5\,au, which is surrounded by very narrow 1\,au-wide gap, and then Ring24, that starts 20.5\,au and has its maximum density peak at 25\,au.
@@
 
+\begin{figure}
+	\includegraphics[width=\columnwidth]{comp_fig_all_profiles_au.pdf}
+    \caption{Comparison of the surface brightness profiles extracted from the deprojected synthetic images and observed \textit{H}-band and 1.3\,mm continuum images.
+The grey shaded area represents the radius of the artificial coronagraph used in the simulations (i.e., $\sim0\farcs 12$, or $\sim$8.6\,au at 72.4\,pc).}
+    \label{fig:radprofiles}
+\end{figure}
+
 The simulated 1.3\,mm continuum image reproduces the two observed rings: the faint Ring13 and the brighter Ring24.
-As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.~\ref{fig:radprofiles}), we can assume that the model provides an approximation of the disc structure, including the dimensions of Ring13.
+As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.~\ref{fig:radprofiles}), we can assume that the model provides a good approximation of the disc structure, including the dimensions of Ring13.
 Accordingly, taking the parametric model values for Ring13 we have that it has a radius of 13.6\,au, a width of 3.7\,au, and a scale height FWHM of the millimetre-size dust ranging from 0.28 to 0.40\,au.
@@
 The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.14\,au difference in the centroid location of the ring, and a 0.17\,au difference in the width estimation.
-
-As \citet{2018ApJ...869L..46D} explain the stability of a narrow dust ring requires that its height is smaller than its radial extent.
-Using the parametric model scale height of 0.28\,au at 13.46\,au and the measured width of Ring13 (3.86\,au FWHM, see Section~\ref{sec:Observations}), we have that its width is $\sim$12 times its scale height.
+%As \citet{2018ApJ...869L..46D} explain the stability of a narrow dust ring requires that its height is smaller than its radial extent. 
+Using the parametric model scale height of 0.33\,au at 13.46\,au and the measured width of Ring13 (3.86\,au FWHM, see Section~\ref{sec:Observations}), we have that its width is $\sim$12 times its scale height.
 
@@
 Here, $\alpha$ represents the typical parameter for turbulent viscosity, and $\mathrm{St}$ is the dimensionless Stokes number.
-Assuming that the most relevant grain size for observed fluxes corresponds to $a = \lambda \mathrm{obs}/(2 \pi)$, and estimating the gas surface density within Ring13 from the RT model to be roughly $20\,\mathrm{g}/\mathrm{cm}^2$, yields $\mathrm{St}\approx 0.03$.
-With these considerations, equation (\ref{eq:ringwidth}) provides a value of $\alpha \approx 0.01$ for the level of turbulent viscosity.
+Assuming that the most relevant grain size for observed fluxes corresponds to $a = \lambda_{\mathrm{obs}}/(2 \pi)$, and estimating the gas surface density within Ring13 from the RT model to be roughly $20\,\mathrm{g}/\mathrm{cm}^2$, yields $\mathrm{St}\approx 0.03$.
+With these considerations, equation~\ref{eq:ringwidth} provides a value of $\alpha \approx 0.01$ for the level of turbulent viscosity.
 We emphasise that this relies on rough estimates and is additionally restricted to the area within Ring13.
@@
 The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes around 3\,M$_{\earth}$ millimetre-sized grains.
-Using the parametric model scale height value ($h= $ 0.28\,au at 13.46\,au) we have that the ring width is roughly 12 times its estimated height.
+Using the parametric model scale height value ($H= $ 0.33\,au at 13.46\,au) we have that the ring width is roughly 12 times its estimated height.
 

### 2020-11-09 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 The comparison of these observations, combined with SPHERE-IRDIS polarized images and a well-sampled spectral energy distribution (SED), against radiative transfer (RT) predictions carried out with the \textsc{radmc3d} package, allow us to propose a physical model for the source.
-The new ALMA data reveal a very thin ring at a radius of 13.46$\pm$0.43\,au (Ring13), with a marginally resolved radial width of 3.86$\pm$1.00\,au.
-Ring13 is surrounded by a $\sim$9\,au-wide gap, and it is flanked by a very bright mm outer ring (Ring24) with a sharp inner edge at 24\,au.
+The new ALMA data reveal a very thin ring at a radius of 13.32$\pm$0.26\,au (Ring13), with a marginally resolved radial width of 1.50$\pm$0.72\,au.
+Ring13 is surrounded by a $\sim$10\,au-wide gap, and it is flanked by a very bright mm outer ring (Ring24) with a sharp inner edge at 24\,au.
 The steeply decreasing brightness of Ring24 breaks at $\sim$35\,au into a shallow tail.
@@
   The previously reported scattered-light shadow of the secondary star is also reproduced by the RT model.
-The surprisingly thin Ring13 is nonetheless roughly 12 times wider than the model scale height, and could thus be long-lived.
+The surprisingly thin Ring13 is nonetheless roughly 5 times wider than the model scale height, and could thus be long-lived.
 The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$.
@@
 The model image is obtained by fitting the data using Chi-squared minimisation, with a measure of regularization when required.
-Here we adopted a $\chi^2$ model image with $\lambda$ = 0.1 for regularization.
+Here we adopted a $\chi^2$ model image with $\lambda$ = 0.01 for regularization (***mem\_lS0.01\_lL0.0\_nogrid/mod\_out.fits).
 The resulting {\tt uvmem} image shown in Fig.~\ref{fig:images_vs_simulated} exhibits previously unseen substructure of the disc.
@@
 The wide and bright Ring24 reaches its peak intensity at $\sim$30\,au, beyond which it drops steeply before breaking at $\sim$35\,au into a shallow tail.
-While this is the first observation of Ring13, \citet{Ru_z_Rodr_guez_2019} did anticipate its existence as their ALMA continuum image showed a distinct excess between
-$\sim$10 and 17\,au.
+While this is the first observation of Ring13, \citet{Ru_z_Rodr_guez_2019} did anticipate its existence as their ALMA continuum image showed a distinct excess between $\sim$10 and 17\,au.
 
@@
 Top right panel: 1.3\,mm continuum {\tt uvmem} model image.
-The yellow ellipse shows the size of the natural-weighted beam ($ 0\farcs077 \, \times \, 0\farcs051$), and the small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs026 \, \times \, \sim0\farcs017$).
+The yellow ellipse shows the size of the natural-weighted beam ($ 0\farcs062 \, \times \, 0\farcs055$), and the small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs035 \, \times \, \sim0\farcs031$).
 The inset zooms into the central emission, and the green star marks the star positions.
@@
 Bottom right panel: 1.3\,mm simulated image of the parametric model.
-The orange ellipse shows the size of the beam: $0\farcs026 \, \times \, 0\farcs017$.
+The orange ellipse shows the size of the beam: $0\farcs035 \, \times \, 0\farcs031$.
 For all the images in the figure the colour scale is linear.}
@@
 Ring13 is surprisingly narrow and seems to be off-centred relative to the GAIA stellar position (at the origin of coordinates in Fig.~\ref{fig:images_vs_simulated}).
-We determined the ring's centre and orientation by minimising the dispersion of the disc radial profiles, from 6\,au to 19\,au, and thus obtained a PA of 74.64$\pm$0.08\,$\degr$, an inclination of 33.90$\pm$0.04\,$\degr$ and a centre at $\Delta \alpha = 9\pm0.05$\,mas $\Delta \delta = 0.06\pm0.04$\,mas, relative to the stars.
+We determined the ring's centre and orientation by minimising the dispersion of the disc radial profiles, from 6\,au to 19\,au, and thus obtained a PA of 77.31$\pm$0.03\,$\degr$, an inclination of 32.96$\pm$0.02\,$\degr$ and a centre at $\Delta \alpha = -4\pm0.02$\,mas $\Delta \delta = 13\pm0.05$\,mas, relative to the stars.
 
 The ring width can be measured in polar coordinates by fitting 1-D Gaussians, thus obtaining a width and centroid at each azimuth.
-On average, we obtained a FWHM of 4.17$\pm$0.94\,au, and a stellocentric radius of 13.46$\pm$0.43\,au (See Fig.~\ref{fig:polarring}).
-As the {\tt uvmem} model image has an effective angular resolution of $\sim$1/3 that of the natural-weighted beam ($0\farcs077 \,\times \, 0\farcs051$), we see that Ring13 is marginally resolved.
-After subtraction of the approximate {\tt uvmem} resolution ($\sim0\farcs026 \, \times \, \sim0\farcs016$), the ring width is $\sim$3.86$\pm$1.00\,au.
+On average, we obtained a FWHM of 2.87$\pm$0.50\,au, and a stellocentric radius of 13.32$\pm$0.26\,au (See Fig.~\ref{fig:polarring}).
+As the {\tt uvmem} model image has an effective angular resolution of $\sim$1/3 that of the natural-weighted beam ($0\farcs062 \,\times \, 0\farcs055$), we see that Ring13 is marginally resolved.
+After subtraction of the approximate {\tt uvmem} resolution ($\sim0\farcs035 \, \times \, \sim0\farcs031$), the ring width is $\sim$1.50$\pm$0.72\,au.
 
-Repeating the optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.78$\pm$0.03\,$\degr$, with an inclination of 34.01$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 19\pm0.04$\,mas $\Delta \delta = 7\pm0.03$\,mas relative to the stars.
+Repeating the optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.86$\pm$0.02\,$\degr$, with an inclination of 33.92$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 2\pm0.02$\,mas $\Delta \delta = 12\pm0.02$\,mas relative to the stars.
 We see that both Ring13 and Ring24 both share the same orientation and centre, given the errors, and both are offset from the star.
@@
 
-The scattered-light image shown in Fig.~\ref{fig:images_vs_simulated} also shows a double ring structure in the micron-
-sized dust distribution.
+The scattered-light image shown in Fig.~\ref{fig:images_vs_simulated} also shows a double ring structure in the micron-sized dust distribution.
 The observed morphology presents an inner cavity of $\sim$10\,au in radius and two rings located at 14.10$\pm$0.01, coincident with Ring13, and 24.62$\pm$0.08\,au, coincident with Ring24, with a small gap between them at $\sim$20\,au.
@@
 
-The binary phase reported by \citet{dOrazi} in the scattered-light observation is at a position angle (PA) of 254\,$\degr$, east of north.
-Using this measurement, the binary phase was calculated at the time of the ALMA observation at a PA of 347\,$\degr$.
+The binary phase reported by \citet{dOrazi} in the scattered-light observation is at a position angle (PA) of 265\,$\degr$, east of north.
+Using this measurement, the binary phase was calculated at the time of the ALMA observation at a PA of $\sim$80\,$\degr$.
 There is no hint of radio decrements in either Rings13 nor in Ring24 that would match shadowing at this PA.
@@
 
-For the representation of the stars, we used two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C} with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of $\mathrm{log}(\,\dot{\mathrm{M}/(\mathrm{M}_{\sun}\,\mathrm{yr^{-1}})}) = -$9.3 for both cases \citep{10.1111/j.1365-2966.2011.19366.x}.
+For the representation of the stars, we used two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C} with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of $\mathrm{log}(\,\dot{\mathrm{M}/(\mathrm{M}_{\sun}\,\mathrm{yr^{-1}})}) = -$9.3 for both cases to include excess UV due to stellar accretion \citep{10.1111/j.1365-2966.2011.19366.x}.
 The stars were placed at a mutual separation of 0.041\,au, so that their centre of mass coincides with the origin, and oriented at a PA of 250\,$\degr$, so that the secondary lies to the NWW from the primary, thus casting the same shadow as observed by \citet{dOrazi}.
@@
 The greatest difference is in the outer ring, where we used a decaying power law modulated by the sum of two Gaussian profiles.
-In an effort to recreate the break seen in the outer ring between 30.2 and 36.7\,au, we chose a different value for $\gamma$ = -6.
+In an effort to recreate the break seen in the outer ring between 29.8 and 37.9\,au, we chose a different value for $\gamma$ = -3.
 For the large dust grains the surface density profile is thus
@@
 \end{equation}
-$R_\mathrm{in}$ and $R_\mathrm{peak}$ would depend on the dust population, with $R_\mathrm{in}$ = 20.5\,au and $R_\mathrm{peak}$ = 25\,au for the small dust grains and $R_\mathrm{in}$ = 22\,au and $R_\mathrm{peak}$ = 27.7\,au for the large dust grains.
+$R_\mathrm{in}$ and $R_\mathrm{peak}$ would depend on the dust population, with $R_\mathrm{in}$ = 19.5\,au and $R_\mathrm{peak}$ = 25\,au for the small dust grains and $R_\mathrm{in}$ = 24.2\,au and $R_\mathrm{peak}$ = 26.6\,au for the large dust grains.
 This parameter allow us to model a smoother inner wall of the outer ring.
@@
 
-The gas and small dust surface density profiles begin at 0.3\,au, out of the zone expected to be cleared by dynamical interactions with the central binary \citep{Art_Lu}, which is expected to be $\sim$0.1\,au.
+The gas and small dust surface density profiles begin at 0.3\,au, out of the zone expected to be cleared by dynamical interactions with the central binary \citep{Art_Lu}, which is expected to be $\sim$0.2\,au.
 For the small dust grains, we propose a three ringed structure.
 The innermost ring of the model is located from 5 to 8\,au, this ring, introduced as Ring6 in Sec.~\ref{sec:Observations}, is not detectable in the IRDIS observations but was required to account for the SED.
-Then follow the two rings observed by IRDIS: Ring13, from 12 to 19.5\,au, which is surrounded by very narrow 1\,au-wide gap, and then Ring24, that starts 20.5\,au and has its maximum density peak at 25\,au.
-The small-dust density then decays exponentially with radius.
+Then follow the two rings observed by IRDIS: Ring13, from 12 to 19.5\,au, %which is surrounded by very narrow 1\,au-wide gap,
+and then Ring24, that starts 19.5\,au and has its maximum density peak at 25\,au. The small-dust density then decays exponentially with radius.
 
@@
 The inner radius of the model grid was set to 0.1\,au and an outer radius of 115\,au, large enough for the dust disc to become undetectable.
-We set the values of the inclination an the position angle as the same as those obtained from the ALMA observation in Section~\ref{sec:Observations}, so the model has an inclination of i = 33.9\,$\degr$ and a P.A.
-= 74.6\,$\degr$.
+We set the values of the inclination an the position angle as the same as those obtained from the ALMA observation in Section~\ref{sec:Observations}, so the model has an inclination of i = 32.96\,$\degr$ and a P.A.
+= 77.31\,$\degr$.
 Finally, the distance is set at d = 72.4\,pc \citep{Gaia}.
@@
 
-Our parametric model is fairly successful in reproducing the available data.
+While certainly not unique, our parametric model is fairly successful in reproducing the available data.
 The simulated images and the SED of the model are shown in Fig.~\ref{fig:images_vs_simulated} and Fig.~\ref{fig:SED} respectively.
@@
 As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.~\ref{fig:radprofiles}), we can assume that the model provides a good approximation of the disc structure, including the dimensions of Ring13.
-Accordingly, taking the parametric model values for Ring13 we have that it has a radius of 13.6\,au, a width of 3.7\,au, and a scale height FWHM of the millimetre-size dust ranging from 0.28 to 0.40\,au.
-The total dust mass of Ring13 is about 3\,M$_{\earth}$ in the model.
+Accordingly, taking the parametric model values for Ring13 we have that it has a radius of 13.35\,au, a width of 2.1\,au, and a scale height FWHM of the millimetre-size dust ranging from 0.30 to 0.36\,au.
+The total dust mass of Ring13 is about 3\,M$_{\earth}$ in the model***.
 In turn, in our model Ring24 reaches peak intensity at $\sim$30\,au, then breaks at $\sim$35\,au, as in the observations, and has a total dust mass of $\sim$43\,M$_{\earth}$.
-The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.14\,au difference in the centroid location of the ring, and a 0.17\,au difference in the width estimation.
+The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.03\,au difference in the centroid location of the ring, and a 0.6\,au difference in the width estimation.
 %As \citet{2018ApJ...869L..46D} explain the stability of a narrow dust ring requires that its height is smaller than its radial extent. 
-Using the parametric model scale height of 0.33\,au at 13.46\,au and the measured width of Ring13 (3.86\,au FWHM, see Section~\ref{sec:Observations}), we have that its width is $\sim$12 times its scale height.
+Using the parametric model scale height of 0.33\,au at 13.32\,au and the measured width of Ring13 (1.50\,au FWHM, see Section~\ref{sec:Observations}), we have that its width is $\sim$4.6 times its scale height.
 
@@
 A possible constellation in this scenario is therefore the presence of two giant planets in the disk, one planet between the star and Ring13, and one planet between Ring13 and Ring24.
+As \citet{Ru_z_Rodr_guez_2019} suggests, the planet between Ring13 and Ring24 may be a Jovian-mass planet with a mass within the range of 0.3$-$1.5\,$\mathrm{M}_{\mathrm{Jup}}$.
 This idea is supported by the similarity to the structure around HD 169142 which \citet{bertrang_avenhaus_2018} reproduced by including several giant planets.
@@
 
-The effective beam size of the presented ALMA observations marginally resolves the width of Ring13 to be $w_\mathrm{d} = 3.86\mathrm{au}$.
+The effective beam size of the presented ALMA observations marginally resolves the width of Ring13 to be $w_\mathrm{d} = 1.50\mathrm{au}$.
 The most suitable RT model demands a density distribution of small grains and gas that is radially more extended, with an approximate width of $7.5\mathrm{au}$.
@@
 Assuming that the most relevant grain size for observed fluxes corresponds to $a = \lambda_{\mathrm{obs}}/(2 \pi)$, and estimating the gas surface density within Ring13 from the RT model to be roughly $20\,\mathrm{g}/\mathrm{cm}^2$, yields $\mathrm{St}\approx 0.03$.
-With these considerations, equation~\ref{eq:ringwidth} provides a value of $\alpha \approx 0.01$ for the level of turbulent viscosity.
+With these considerations, equation~\ref{eq:ringwidth} provides a value of $\alpha \approx 0.001$ for the level of turbulent viscosity.
 We emphasise that this relies on rough estimates and is additionally restricted to the area within Ring13.

### 2020-11-10 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 The model image is obtained by fitting the data using Chi-squared minimisation, with a measure of regularization when required.
-Here we adopted a $\chi^2$ model image with $\lambda$ = 0.01 for regularization (***mem\_lS0.01\_lL0.0\_nogrid/mod\_out.fits).
+Here we adopted a $\chi^2$ model image with $\lambda$ = 0.01 for regularization (***mem\_lS0.01\_lL0.0\_nogrid/mod\_out.fits**).
 The resulting {\tt uvmem} image shown in Fig.~\ref{fig:images_vs_simulated} exhibits previously unseen substructure of the disc.
@@
 Repeating the optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.86$\pm$0.02\,$\degr$, with an inclination of 33.92$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 2\pm0.02$\,mas $\Delta \delta = 12\pm0.02$\,mas relative to the stars.
-We see that both Ring13 and Ring24 both share the same orientation and centre, given the errors, and both are offset from the star.
-Even though all orientation parameters for Ring13 and Ring24 are consistent within the errors, there are however some hints for a different orientation, as summarised in Fig.~\ref{fig:polarring}, perhaps due to the joint effect of all these small differences.
+We see that both Ring13 and Ring24 both share a very similar orientation and centre, given the errors, and both are offset from the star.
+%Even though all orientation parameters for Ring13 and Ring24 are consistent within the errors,
+Perhaps due to the joint effect of all these small differences, we can see that there are some hints for a different orientation, as summarised in Fig.~\ref{fig:polarring}, .
 
@@
     \label{scale}
-  H(r)=\chi \, H_{o}(r) \, [r/r_{o}(r)]^{\psi(r)},
+  H(r)=\chi \, H_{o} \, [r/r_{o}]^{\psi(r)},
 \end{equation}
@@
 The separation between the two values were set at $r$ = 19\,au with $\psi=0.2$ for Ring6 and Ring13, and $\psi=0.5$ for Ring24.
-The scale height is $H_\circ = 0.045$\,au at $r_\circ = 19.5$\,au.
+The scale height is $H_\circ = 0.8775$\,au at $r_\circ = 19.5$\,au.
 
@@
 
-The inner radius of the model grid was set to 0.1\,au and an outer radius of 115\,au, large enough for the dust disc to become undetectable.
+The inner radius of the model grid was set to 0.1\,au and an outer radius of 100\,au, large enough for the dust disc to become undetectable.
 We set the values of the inclination an the position angle as the same as those obtained from the ALMA observation in Section~\ref{sec:Observations}, so the model has an inclination of i = 32.96\,$\degr$ and a P.A.
@@
 Accordingly, taking the parametric model values for Ring13 we have that it has a radius of 13.35\,au, a width of 2.1\,au, and a scale height FWHM of the millimetre-size dust ranging from 0.30 to 0.36\,au.
-The total dust mass of Ring13 is about 3\,M$_{\earth}$ in the model***.
-In turn, in our model Ring24 reaches peak intensity at $\sim$30\,au, then breaks at $\sim$35\,au, as in the observations, and has a total dust mass of $\sim$43\,M$_{\earth}$.
+The total dust mass of Ring13 is about 1\,M$_{\earth}$ in the model.
+In turn, in our model Ring24 reaches peak intensity at $\sim$30\,au, then breaks at $\sim$35\,au, as in the observations, and has a total dust mass of $\sim$32\,M$_{\earth}$.
 The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.03\,au difference in the centroid location of the ring, and a 0.6\,au difference in the width estimation.
 %As \citet{2018ApJ...869L..46D} explain the stability of a narrow dust ring requires that its height is smaller than its radial extent. 
-Using the parametric model scale height of 0.33\,au at 13.32\,au and the measured width of Ring13 (1.50\,au FWHM, see Section~\ref{sec:Observations}), we have that its width is $\sim$4.6 times its scale height.
+Using the large grains scale height of 0.65\,au at Ring13, and a measured width of 1.50\,au, the ring is $\sim$2.3 times more extended in radial than in vertical direction.
 
@@
 A possible constellation in this scenario is therefore the presence of two giant planets in the disk, one planet between the star and Ring13, and one planet between Ring13 and Ring24.
-As \citet{Ru_z_Rodr_guez_2019} suggests, the planet between Ring13 and Ring24 may be a Jovian-mass planet with a mass within the range of 0.3$-$1.5\,$\mathrm{M}_{\mathrm{Jup}}$.
+As \citet{Ru_z_Rodr_guez_2019} suggest, the putative planet between Ring13 and Ring24 may be a giant planet with a mass within the range of 0.3$-$1.5\,$\mathrm{M}_{\mathrm{Jup}}$.
 This idea is supported by the similarity to the structure around HD 169142 which \citet{bertrang_avenhaus_2018} reproduced by including several giant planets.
-We point out that also the disk dispersal by photoevaporative winds \citep{1994ApJ...428..654H} as causation of the inner cavity cannot be ruled out at his stage.
+%We point out that also the disk dispersal by photoevaporative winds \citep{1994ApJ...428..654H} as causation of the inner cavity cannot be ruled out at his stage.
 
@@
 We emphasise that this relies on rough estimates and is additionally restricted to the area within Ring13.
+Yet, its moderate value agrees with the limit \citet{2018ApJ...869L..46D} inferred from multiple dust rings at larger orbital distances ($\alpha \gtrsim 5\times10^{-4}$).
+Further, it is also consistent with the non-detection of non-thermal broadening of CO lines reported by \citet{Flaherty_2020}, from which the authors deduced an upper limit of $\alpha \lesssim 10^{-3}$ at the midplane of V4046\,Sgr.
 

### 2020-11-19 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 %Even though all orientation parameters for Ring13 and Ring24 are consistent within the errors,
-Perhaps due to the joint effect of all these small differences, we can see that there are some hints for a different orientation, as summarised in Fig.~\ref{fig:polarring}, .
+Perhaps due to the joint effect of all these small differences, we can see that there are some hints for a different orientation, as summarised in Fig.~\ref{fig:polarring}.
 
@@
 \end{equation}
-where $\delta(r)$ parameterises the density drops in the gaps and cavities, $H(r)$ is the scale height profile and $\Sigma(r)$ is the surface density profile. $\Sigma(r)$ is defined by
+where $H(r)$ is the scale height profile and $\Sigma(r)$ is the surface density profile.
+$\Sigma(r)$ is defined by a combination of four individual components: the inner disc, Ring6, Ring13 and Ring24.
 \begin{equation}
-  \Sigma(r) = \Sigma_\mathrm{c} \left(\frac{r}{R_\mathrm{c}}\right)^{-\gamma}  \, \mathrm{exp}\left[-\left(\frac{r}{R_\mathrm{c}}\right)^{2-\gamma}\right],
+  \Sigma(r) = \Sigma_{\mathrm{inner\,disc}} + \Sigma_{\mathrm{Ring6}} + \Sigma_{\mathrm{Ring13}} + \Sigma_{\mathrm{Ring24}}
 \end{equation}
-where $R_c$ is a characteristic radius and $\gamma$ is the surface density gradient. A fixed $\gamma$ = 1 is used as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
+
+%$\delta(r)$ parameterises the density drops in the gaps and cavities,
+
+The inner disk follows a power law function defined by
+\begin{equation}
+  \Sigma_{\mathrm{inner\,disc}}(r) =\Sigma_\mathrm{c} \left(\frac{r}{R_\mathrm{c}}\right)^{-\gamma}  \, \mathrm{exp}\left[-\left(\frac{r}{R_\mathrm{c}}\right)^{2-\gamma}\right],
+\end{equation}
+where $R_c$ is a characteristic radius and $\gamma$ is the surface density gradient. We used $R_c$ = 16 and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
+
+We choose to use a Gaussian profiles to parameterize Ring6 and Ring13,
+\begin{equation}
+  \Sigma_{\mathrm{Ring}}(r) = \frac{\Sigma_\circ}{\sqrt{2 \pi} \sigma}
+  \, \mathrm{exp}\left[-\frac{1}{2}\left(\frac{r-\mu}{\sigma}\right)^{2}\right],
+\end{equation}
 
@@
 For the large dust grains the surface density profile is thus
-\begin{multline}
-  \Sigma_{\mathrm{large-dust}}(r) = \Sigma_{\mathrm{c}2} \left(\frac{r}{R_{\mathrm{c}2}}\right)^{-\gamma} \\ \, \left\{ \exp\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2-\gamma}\right] + \mathrm{exp}\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2}\right]\right\}.
-\end{multline}
+
+\begin{equation}
+  \Sigma_{\mathrm{large-dust}}(r) = \Sigma_{\mathrm{c}2} \left(\frac{r}{R_{\mathrm{c}2}}\right)^{-\gamma} \exp\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2-\gamma}\right] .
+\end{equation}
 
@@
         \caption{{\bf Top:} surface density profiles for the gas, the large and small grain populations.
-{\bf Bottom:} scale height profile $h(r)$.
+{\bf Bottom:} Aspect ratio profile $h(r)= H(r)/r$.
 The dashed lines crossing both panels correspond to transition radii in the parametric model.}

### 2020-11-20 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 \end{equation}
-where $H(r)$ is the scale height profile and $\Sigma(r)$ is the surface density profile.
-$\Sigma(r)$ is defined by a combination of four individual components: the inner disc, Ring6, Ring13 and Ring24.
-\begin{equation}
-  \Sigma(r) = \Sigma_{\mathrm{inner\,disc}} + \Sigma_{\mathrm{Ring6}} + \Sigma_{\mathrm{Ring13}} + \Sigma_{\mathrm{Ring24}}
-\end{equation}
-
-%$\delta(r)$ parameterises the density drops in the gaps and cavities,
-
-The inner disk follows a power law function defined by
-\begin{equation}
-  \Sigma_{\mathrm{inner\,disc}}(r) =\Sigma_\mathrm{c} \left(\frac{r}{R_\mathrm{c}}\right)^{-\gamma}  \, \mathrm{exp}\left[-\left(\frac{r}{R_\mathrm{c}}\right)^{2-\gamma}\right],
-\end{equation}
-where $R_c$ is a characteristic radius and $\gamma$ is the surface density gradient. We used $R_c$ = 16 and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
-
-We choose to use a Gaussian profiles to parameterize Ring6 and Ring13,
-\begin{equation}
-  \Sigma_{\mathrm{Ring}}(r) = \frac{\Sigma_\circ}{\sqrt{2 \pi} \sigma}
-  \, \mathrm{exp}\left[-\frac{1}{2}\left(\frac{r-\mu}{\sigma}\right)^{2}\right],
-\end{equation}
-
-%The $\delta(r)$ function, that account for deviations from the power law, is defined as:
-%\begin{align}
-%\delta(r) = \left\{ \begin{array}{cc} 
-%                 5E-6 & \hspace{5mm} 0.3<r<5 \\
-%                 5E-3 & \hspace{5mm} 5<r<8  \\
-%                 5E-5 & \hspace{5mm} 8<r<12\\
-%                 2.5E-2 & \hspace{5mm} 12<r<19.5 \\
-%                 1E-8 & \hspace{5mm} 19.5<r<20.5 \\
-%                 1E-4 & \hspace{5mm} 20.5<r<25 \\
-%                 1.7E-1 & \hspace{5mm} 25<r<120 \\
-%                \end{array} \right.
-%\end{align}
+where $H(r)$ is the scale height profile and $\Sigma(r)$ is the gas surface density profile.
 
@@
     \label{scale}
-  H(r)=\chi \, H_{o} \, [r/r_{o}]^{\psi(r)},
+  H(r)=\chi \, H_{\circ} \, [r/r_{\circ}]^{\psi(r)},
 \end{equation}
@@
 The separation between the two values were set at $r$ = 19\,au with $\psi=0.2$ for Ring6 and Ring13, and $\psi=0.5$ for Ring24.
-The scale height is $H_\circ = 0.8775$\,au at $r_\circ = 19.5$\,au.
+The scale height is $H_\circ = 1$\,au at $r_\circ = 19$\,au.
+
+$\Sigma(r)$ begin at 0.3\,au, out of the zone expected to be cleared by dynamical interactions with the central binary \citep{Art_Lu}, which is expected to be $\sim$0.2\,au.
+We propose a three ringed structure, so we defined the total gas surface density by a combination of four individual components: the inner disc, Ring6, Ring13 and Ring24.
+\begin{equation}
+  \Sigma(r) = \Sigma_{\mathrm{inner\,disc}} + \Sigma_{\mathrm{Ring6}} + \Sigma_{\mathrm{Ring13}} + \Sigma_{\mathrm{Ring24}}
+\end{equation}
+
+The inner disk follows a power law function defined by
+\begin{equation}
+  \Sigma_{\mathrm{inner\,disc}}(r) =\Sigma_\mathrm{c} \left(\frac{r}{R_\mathrm{c}}\right)^{-\gamma}  \, \mathrm{exp}\left[-\left(\frac{r}{R_\mathrm{c}}\right)^{2-\gamma}\right],
+\end{equation}
+where $R_c$ is a characteristic radius and $\gamma$ is the surface density gradient.
+We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =2.6\times10^{-4}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
+We chose to use a Gaussian profiles to parameterize Ring6 and Ring13,
+\begin{equation}
+  \Sigma_{\mathrm{Ring}}(r) = \frac{\Sigma_\circ}{\sqrt{2 \pi} \sigma}
+  \, \mathrm{exp}\left[-\frac{1}{2}\left(\frac{r-\mu}{\sigma}\right)^{2}\right],
+\end{equation}
+where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring6}}=6$\,au, $\mu_{\mathrm{Ring13}}=15$\,au\}, ring widths \{$\sigma_{\mathrm{Ring6}}=1$\,au, $\sigma_{\mathrm{Ring13}}=2.05$\,au\}, and normalizations \{ $\Sigma_{\circ,\mathrm{Ring6}}=1\times10^{13}$, $\Sigma_{\circ,\mathrm{Ring13}}=4.2\times10^{13}$\} for both structure components separately.
+
+For Ring24 we used the same power law than the inner disc but scaled by a $\delta_{\mathrm{sd}}$ factor:
+\begin{equation}
+  \Sigma_{\mathrm{Ring24}} = \Sigma_{\mathrm{inner\,disc}}(r)\, \delta_{\mathrm{sd}},
+\end{equation}
+with $\delta_{\mathrm{sd}}$ = 5.2$\times 10^4$.
+But the inner wall of Ring24 follows a different behaviour.
+Between $R_\mathrm{in}$ and $R_\mathrm{peak}$, marking the beginning and the maximum density peak of the outer ring respectively, the gas density profile is multiplied by an additional factor
+\begin{equation}
+    \epsilon(r) = \left(\frac{ r - R_\mathrm{in}}{R_\mathrm{peak} - R_\mathrm{in}}\right)^3.
+\end{equation}
+This parameter allow us to model a smoother inner wall of the outer ring, with $R_\mathrm{in,gas}$ = 19.\,au and $R_\mathrm{peak,gas}$ = 26.8\,au.
+This factor is also applied to the large dust population with $R_\mathrm{in,ld}$ = 24.6\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$.
 
@@
 
-Since the large dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a large inner cavity and scaling factors that account for the larger gap between the rings.
-For the inner ring, the same profile as the gas is used, but with different values for $R_c$ and $\Sigma_c$.
-The greatest difference is in the outer ring, where we used a decaying power law modulated by the sum of two Gaussian profiles.
-In an effort to recreate the break seen in the outer ring between 29.8 and 37.9\,au, we chose a different value for $\gamma$ = -3.
-For the large dust grains the surface density profile is thus
-
+Since the large dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a large inner cavity, a larger gap between the rings and a break in the outer ring.
+The large-dust surface density profile is defined by the sum of its two components as For the large dust grains the surface density profile is thus
 \begin{equation}
-  \Sigma_{\mathrm{large-dust}}(r) = \Sigma_{\mathrm{c}2} \left(\frac{r}{R_{\mathrm{c}2}}\right)^{-\gamma} \exp\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2-\gamma}\right] .
+  \Sigma_{\mathrm{ld}}(r) = 
+  \Sigma_{\mathrm{Ring13,ld}} + \Sigma_{\mathrm{Ring24,ld}}.
 \end{equation}
 
-The inner part of the outer ring follows a different behaviour.
-Between $R_\mathrm{in}$ and $R_\mathrm{peak}$, marking the beginning and the maximum density peak of the outer ring respectively, the gas density profile is multiplied by an additional factor
+For the inner ring, we chose a Gaussian profile parameterized with centroid radius $\mu_{\mathrm{Ring13, ld}}=13.36$\,au, ring width of $\sigma_{\mathrm{Ring13,ld}}=0.54$\,au and $\Sigma_{\circ,\mathrm{Ring13,ld}}=4.2\times10^{13}$.
+For Ring24 we used the same distribution of the gas, but with the difference that, in an effort to recreate the break seen in the outer ring, between 28.6 and 37\,au we chose a different value for $\gamma$ = -5 and $R_c$ = 38.
+We also truncated the model large-grain density at $\sim$64\,au.
+Thus, the surface density of the outer ring of large grains dust is defined by
 \begin{equation}
-    \epsilon(r) = \left(\frac{ r - R_\mathrm{in}}{R_\mathrm{peak} - R_\mathrm{in}}\right)^3.
+    \Sigma_{\mathrm{Ring24,ld}} = \Sigma_{\mathrm{c}} \left(\frac{r}{R_{\mathrm{c}}}\right)^{-\gamma} \exp\left[-\left(\frac{r}{R_{\mathrm{c}}}\right)^{2-\gamma}\right]\,\delta_{\mathrm{ld}}(r),
 \end{equation}
-$R_\mathrm{in}$ and $R_\mathrm{peak}$ would depend on the dust population, with $R_\mathrm{in}$ = 19.5\,au and $R_\mathrm{peak}$ = 25\,au for the small dust grains and $R_\mathrm{in}$ = 24.2\,au and $R_\mathrm{peak}$ = 26.6\,au for the large dust grains.
-This parameter allow us to model a smoother inner wall of the outer ring.
+where
+\begin{equation}
+  \delta_{\mathrm{ld}}(r) =
+  \begin{cases}
+  0                 & r < 24.6\text{\,au} \\
+  4.37 \times10^{4} & 24.6 < r < 28.6\text{\,au} \\
+  2.04 \times10^{4} & 28.6 < r < 37\text{\,au} \\
+  1.82 \times10^{5} & 37   < r < 64\text{\,au} \\
+  0                 & r > 64\text{\,au.}
+  \end{cases}
+\end{equation}
 
@@
 \end{figure}
-
-The gas and small dust surface density profiles begin at 0.3\,au, out of the zone expected to be cleared by dynamical interactions with the central binary \citep{Art_Lu}, which is expected to be $\sim$0.2\,au.
-For the small dust grains, we propose a three ringed structure.
-The innermost ring of the model is located from 5 to 8\,au, this ring, introduced as Ring6 in Sec.~\ref{sec:Observations}, is not detectable in the IRDIS observations but was required to account for the SED.
-Then follow the two rings observed by IRDIS: Ring13, from 12 to 19.5\,au, %which is surrounded by very narrow 1\,au-wide gap,
-and then Ring24, that starts 19.5\,au and has its maximum density peak at 25\,au. The small-dust density then decays exponentially with radius.
-
-On the other hand, in order to reproduce the double-ringed morphology of the millimetre continuum emission, we required a model with a wide central cavity ($r = 11.7$\,au), a narrow 3.7\,au-wide inner ring (which is Ring13) followed by a 8.2\,au gap that separates the outer ring (Ring24), which starts at 22\,au and reaches peak densities at 27.7\,au.
-This last ring has an observed break between 30.2 and 36.7\,au, which is reproduced in the model with a discontinuity in the exponent $\gamma$, along with the sum of the decaying exponentials.
-We also truncated the model large-grain density at $\sim$55\,au.
 

### 2020-11-23 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 \begin{equation}
-  \rho_{\mathrm{gas}}(r,z) =\frac{\Sigma(r) \,\delta(r)}{\sqrt{2\pi} \, H(r)} \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{H(r)}\right)^2\right],
+  \rho_{\mathrm{gas}}(r,z) =\frac{\Sigma_{\mathrm{gas}}(r)}{\sqrt{2\pi} \, H(r)} \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{H(r)}\right)^2\right],
 \end{equation}
-where $H(r)$ is the scale height profile and $\Sigma(r)$ is the gas surface density profile.
+where $H(r)$ is the scale height profile and $\Sigma_{\mathrm{gas}}(r)$ is the gas surface density profile.
 
@@
 
-$\Sigma(r)$ begin at 0.3\,au, out of the zone expected to be cleared by dynamical interactions with the central binary \citep{Art_Lu}, which is expected to be $\sim$0.2\,au.
-We propose a three ringed structure, so we defined the total gas surface density by a combination of four individual components: the inner disc, Ring6, Ring13 and Ring24.
+We propose a three ringed structure, so we defined the total gas surface density by a combination of four individual components: the inner disc, Ring6, Ring13 and Ring24. Then it is defined by:
 \begin{equation}
-  \Sigma(r) = \Sigma_{\mathrm{inner\,disc}} + \Sigma_{\mathrm{Ring6}} + \Sigma_{\mathrm{Ring13}} + \Sigma_{\mathrm{Ring24}}
+  \Sigma_{\mathrm{gas}}(r) = \Sigma_{\mathrm{inner\,disc}} + \Sigma_{\mathrm{Ring6}} + \Sigma_{\mathrm{Ring13}} + \Sigma_{\mathrm{Ring24}}
 \end{equation}
@@
 We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =2.6\times10^{-4}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
-We chose to use a Gaussian profiles to parameterize Ring6 and Ring13,
+The gas surface density begin at 0.3\,au, out of the zone expected to be cleared by dynamical interactions with the central binary \citep{Art_Lu}, which is expected to be $\sim$0.2\,au.
+
+We chose to use Gaussian profiles to parameterize Ring6 and Ring13,
 \begin{equation}
@@
 Since the large dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a large inner cavity, a larger gap between the rings and a break in the outer ring.
-The large-dust surface density profile is defined by the sum of its two components as For the large dust grains the surface density profile is thus
+We also truncated the model large-grain density at 64\,au.
+The large-dust surface density profile is defined by the sum of its two components
 \begin{equation}
@@
 For the inner ring, we chose a Gaussian profile parameterized with centroid radius $\mu_{\mathrm{Ring13, ld}}=13.36$\,au, ring width of $\sigma_{\mathrm{Ring13,ld}}=0.54$\,au and $\Sigma_{\circ,\mathrm{Ring13,ld}}=4.2\times10^{13}$.
-For Ring24 we used the same distribution of the gas, but with the difference that, in an effort to recreate the break seen in the outer ring, between 28.6 and 37\,au we chose a different value for $\gamma$ = -5 and $R_c$ = 38.
-We also truncated the model large-grain density at $\sim$64\,au.
+For Ring24 we used the same profile of the gas, but with the difference that, in an effort to recreate the break seen in the outer ring, between 28.6 and 37\,au we chose a different value for $\gamma$ = -5 and $R_c$ = 38\,au.
 Thus, the surface density of the outer ring of large grains dust is defined by
@@
   2.04 \times10^{4} & 28.6 < r < 37\text{\,au} \\
-  1.82 \times10^{5} & 37   < r < 64\text{\,au} \\
-  0                 & r > 64\text{\,au.}
+  1.82 \times10^{5} & 37   < r < 64\text{\,au.} \\
   \end{cases}
+\end{equation}
+Then the final density of large dust can be calculated as
+\begin{equation}
+\rho_{\mathrm{large-dust}}(r,z)=
+\frac{\Sigma_{\mathrm{ld}}(r)}{\sqrt{2\pi} \, H(r)} \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{H(r)}\right)^2\right] \, f_{\mathrm{ld}} \: \zeta .
 \end{equation}
@@
 As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.~\ref{fig:radprofiles}), we can assume that the model provides a good approximation of the disc structure, including the dimensions of Ring13.
-Accordingly, taking the parametric model values for Ring13 we have that it has a radius of 13.35\,au, a width of 2.1\,au, and a scale height FWHM of the millimetre-size dust ranging from 0.30 to 0.36\,au.
-The total dust mass of Ring13 is about 1\,M$_{\earth}$ in the model.
-In turn, in our model Ring24 reaches peak intensity at $\sim$30\,au, then breaks at $\sim$35\,au, as in the observations, and has a total dust mass of $\sim$32\,M$_{\earth}$.
-The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.03\,au difference in the centroid location of the ring, and a 0.6\,au difference in the width estimation.
+Accordingly, taking the parametric model values for Ring13 we have that it has a radius of 13.36\,au, a FWHM of 1.30\,au, and a scale height FWHM of the millimetre-size dust of 0.65\,au.
+The total dust mass of Ring13 is about 1.5\,M$_{\earth}$ in the model.
+In turn, in our model Ring24 reaches peak intensity at $\sim$30\,au, then breaks at $\sim$36\,au, as in the observations, and has a total dust mass of $\sim$49\,M$_{\earth}$.
+The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.04\,au difference in the centroid location of the ring, and a 0.2\,au difference in the width estimation.
 %As \citet{2018ApJ...869L..46D} explain the stability of a narrow dust ring requires that its height is smaller than its radial extent. 
-Using the large grains scale height of 0.65\,au at Ring13, and a measured width of 1.50\,au, the ring is $\sim$2.3 times more extended in radial than in vertical direction.
+Using the large grains scale height of 0.66\,au at Ring13, and a measured width of 1.50\,au, the ring is $\sim$2.3 times more extended in radial than in vertical direction.
 
@@
 Although the RT model ascribed step functions to gas and dust densities, in a more physical scenario the density should roughly follow a Gaussian distribution.
-Assuming that the gas' Ring13-width in the RT model corresponds to the FWHM of a Gaussian structure $w_\mathrm{g} = 7.5\mathrm{au}$, we can see that large dust grains have to be radially converged to explain the discrepancy.
+Using that the gas' Ring13-FWHM in the RT model corresponds to $w_\mathrm{g} = 4.83\mathrm{au}$, we can see that large dust grains have to be radially converged to explain the discrepancy.
 
@@
 \begin{enumerate}
-  \item We report the detection of a narrow ring in the 1.3\,mm continuum, with a radius 13.46$\pm$0.43\,au and an estimated width of 3.86$\pm$1.00\,au.
-The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes around 3\,M$_{\earth}$ millimetre-sized grains.
-Using the parametric model scale height value ($H= $ 0.33\,au at 13.46\,au) we have that the ring width is roughly 12 times its estimated height.
+  \item We report the detection of a narrow ring in the 1.3\,mm continuum, with a radius 13.32$\pm$0.26\,au and an estimated width of 1.50$\pm$0.72\,au.
+The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes around 1.5\,M$_{\earth}$ millimetre-sized grains.
+Using the parametric model scale height value ($H= $ 0.66\,au at 13.32\,au) we have that the ring width is roughly 2.3 times its estimated height.
 
-  \item The 1.3\,mm outer ring, that starts at $\sim$23\,au and has its peak intensity at $\sim$32\,au, presents a visible break in the surface brightness at $\sim$35\,au.
+  \item The 1.3\,mm outer ring, that starts at $\sim$24\,au and has its peak intensity at $\sim$30\,au, presents a visible break in the surface brightness at $\sim$35\,au.
 

### 2020-11-26 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 Repeating the optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.86$\pm$0.02\,$\degr$, with an inclination of 33.92$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 2\pm0.02$\,mas $\Delta \delta = 12\pm0.02$\,mas relative to the stars.
-We see that both Ring13 and Ring24 both share a very similar orientation and centre, given the errors, and both are offset from the star.
-%Even though all orientation parameters for Ring13 and Ring24 are consistent within the errors,
+We see that both Ring13 and Ring24 both share a very similar orientation and centre, given the errors, and both are offset from the star.***  %Even though all orientation parameters for Ring13 and Ring24 are consistent within the errors,
 Perhaps due to the joint effect of all these small differences, we can see that there are some hints for a different orientation, as summarised in Fig.~\ref{fig:polarring}.

### 2020-11-27 old_Draft_w-o_ice.tex
Updates from Overleaf

--- 2020-11-26 Draft_V4046Sgr_mnras.tex
@@
 \begin{figure*}
-  \includegraphics[width=\textwidth]{hot_two_E.pdf}
+  \includegraphics[width=\textwidth]{hot_two_E_noice.pdf}
   \caption{Comparison of observations and simulated images at 1.65\,$\micron$ and 1.3 mm continuum of the circumbinary disc orbiting V4046\,Sgr.
@@
 	\centering
-	\includegraphics[width=\columnwidth]{SED_.png}
+	\includegraphics[width=\columnwidth]{SED_noice.png}
     \caption{The observed SED of V4046\,Sgr (black points and solid red curve) compared with the model (blue).
@@
 where $H_\circ$ is the scale height at r = $r_\circ$, $\psi$ is the flaring index and $\chi$ is a scaling factor (in the range $0-1$) that mimics dust settling.
-For the gas and the small dust grains $\chi$ = 1 and for the millimetre-size dust population we assign a fixed $\chi$ = 1/2 for simplicity, as in \citet{Rosenfeld_2013}.
+For the gas and the small dust grains $\chi$ = 1 and for the millimetre-size dust population we assign a fixed $\chi$ = 1/5 for simplicity ***(now is not for simplicity).
 
@@
 Our model uses the same values, with two different flaring indexes $\psi$.
-The separation between the two values were set at $r$ = 19\,au with $\psi=0.2$ for Ring6 and Ring13, and $\psi=0.5$ for Ring24.
-The scale height is $H_\circ = 1$\,au at $r_\circ = 19$\,au.
+The separation between the two values were set at $r$ = 18\,au with $\psi=0.15$ for Ring6 and Ring13, and $\psi=0.5$ for Ring24.
+The scale height is $H_\circ = 0.45$\,au at $r_\circ = 18$\,au.
 
@@
 where $R_c$ is a characteristic radius and $\gamma$ is the surface density gradient.
-We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =2.6\times10^{-4}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
+We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =2.7\times10^{-4}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
 The gas surface density begin at 0.3\,au, out of the zone expected to be cleared by dynamical interactions with the central binary \citep{Art_Lu}, which is expected to be $\sim$0.2\,au.
@@
 \end{equation}
-where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring6}}=6$\,au, $\mu_{\mathrm{Ring13}}=15$\,au\}, ring widths \{$\sigma_{\mathrm{Ring6}}=1$\,au, $\sigma_{\mathrm{Ring13}}=2.05$\,au\}, and normalizations \{ $\Sigma_{\circ,\mathrm{Ring6}}=1\times10^{13}$, $\Sigma_{\circ,\mathrm{Ring13}}=4.2\times10^{13}$\} for both structure components separately.
+where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring6}}=5.5$\,au, $\mu_{\mathrm{Ring13}}=15$\,au\}, ring widths \{$\sigma_{\mathrm{Ring6}}=1$\,au, $\sigma_{\mathrm{Ring13}}=2.05$\,au\}, and normalizations \{ $\Sigma_{\circ,\mathrm{Ring6}}=8\times10^{12}$, $\Sigma_{\circ,\mathrm{Ring13}}=4.2\times10^{13}$\} for both structure components separately.
 
@@
 \end{equation}
-with $\delta_{\mathrm{sd}}$ = 5.2$\times 10^4$.
+with $\delta_{\mathrm{sd}}$ = 5.3$\times 10^4$.
 But the inner wall of Ring24 follows a different behaviour.
@@
 \end{equation}
-This parameter allow us to model a smoother inner wall of the outer ring, with $R_\mathrm{in,gas}$ = 19.\,au and $R_\mathrm{peak,gas}$ = 26.8\,au.
-This factor is also applied to the large dust population with $R_\mathrm{in,ld}$ = 24.6\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$.
+This parameter allow us to model a smoother inner wall of the outer ring, with $R_\mathrm{in,gas}$ = 18.\,au and $R_\mathrm{peak,gas}$ = 26.8\,au.
+This factor is also applied to the large dust population with $R_\mathrm{in,ld}$ = 24.7\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$.
 
@@
 
-For the inner ring, we chose a Gaussian profile parameterized with centroid radius $\mu_{\mathrm{Ring13, ld}}=13.36$\,au, ring width of $\sigma_{\mathrm{Ring13,ld}}=0.54$\,au and $\Sigma_{\circ,\mathrm{Ring13,ld}}=4.2\times10^{13}$.
-For Ring24 we used the same profile of the gas, but with the difference that, in an effort to recreate the break seen in the outer ring, between 28.6 and 37\,au we chose a different value for $\gamma$ = -5 and $R_c$ = 38\,au.
+For the inner ring, we chose a Gaussian profile parameterized with centroid radius $\mu_{\mathrm{Ring13, ld}}=13.38$\,au, ring width of $\sigma_{\mathrm{Ring13,ld}}=0.54$\,au and $\Sigma_{\circ,\mathrm{Ring13,ld}}=3\times10^{13}$.
+For Ring24 we used the same profile of the gas, but with the difference that, in an effort to recreate the break seen in the outer ring, between 28.6 and 35.6\,au we chose a different value for $\gamma$ = -5 and $R_c$ = 38\,au.
 Thus, the surface density of the outer ring of large grains dust is defined by
@@
   0                 & r < 24.6\text{\,au} \\
-  4.37 \times10^{4} & 24.6 < r < 28.6\text{\,au} \\
-  2.04 \times10^{4} & 28.6 < r < 37\text{\,au} \\
-  1.82 \times10^{5} & 37   < r < 64\text{\,au.} \\
+  6.24 \times10^{4} & 24.6 < r < 28.6\text{\,au} \\
+  2.65 \times10^{4} & 28.6 < r < 37\text{\,au} \\
+  2.04 \times10^{5} & 37   < r < 64\text{\,au.} \\
   \end{cases}
@@
 \begin{figure}
-	\includegraphics[width=\columnwidth]{allprofiles.png}
+	\includegraphics[width=\columnwidth]{allprofiles_noice.png}
         \caption{{\bf Top:} surface density profiles for the gas, the large and small grain populations.
@@
 \begin{figure}
-	\includegraphics[width=\columnwidth]{comp_fig_all_profiles_au.pdf}
+	\includegraphics[width=\columnwidth]{comp_fig_all_profiles_au_noice.pdf}
     \caption{Comparison of the surface brightness profiles extracted from the deprojected synthetic images and observed \textit{H}-band and 1.3\,mm continuum images.
@@
 Accordingly, taking the parametric model values for Ring13 we have that it has a radius of 13.36\,au, a FWHM of 1.30\,au, and a scale height FWHM of the millimetre-size dust of 0.65\,au.
-The total dust mass of Ring13 is about 1.5\,M$_{\earth}$ in the model.
-In turn, in our model Ring24 reaches peak intensity at $\sim$30\,au, then breaks at $\sim$36\,au, as in the observations, and has a total dust mass of $\sim$49\,M$_{\earth}$.
-The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.04\,au difference in the centroid location of the ring, and a 0.2\,au difference in the width estimation.
+The total dust mass of Ring13 is about 1.1\,M$_{\earth}$ in the model.
+In turn, in our model Ring24 reaches peak intensity at $\sim$30\,au, then breaks at $\sim$36\,au, as in the observations, and has a total dust mass of $\sim$50\,M$_{\earth}$.
+The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.06\,au difference in the centroid location of the ring, and a 0.2\,au difference in the width estimation.
 %As \citet{2018ApJ...869L..46D} explain the stability of a narrow dust ring requires that its height is smaller than its radial extent. 
-Using the large grains scale height of 0.66\,au at Ring13, and a measured width of 1.50\,au, the ring is $\sim$2.3 times more extended in radial than in vertical direction.
+Using the large grains scale height of 0.31\,au at Ring13, and a measured width of 1.50\,au, the ring is $\sim$4.8 times more extended in radial than in vertical direction.
 
@@
 
-The effective beam size of the presented ALMA observations marginally resolves the width of Ring13 to be $w_\mathrm{d} = 1.50\mathrm{au}$.
-The most suitable RT model demands a density distribution of small grains and gas that is radially more extended, with an approximate width of $7.5\mathrm{au}$.
+*** The effective beam size of the presented ALMA observations marginally resolves the width of Ring13 to be $w_\mathrm{d} = 1.50\mathrm{au}$.
+%The most suitable RT model demands a density distribution of small grains and gas that is radially more extended, with an approximate width of $7.5\mathrm{au}$.
 Although the RT model ascribed step functions to gas and dust densities, in a more physical scenario the density should roughly follow a Gaussian distribution.
@@
 Here, $\alpha$ represents the typical parameter for turbulent viscosity, and $\mathrm{St}$ is the dimensionless Stokes number.
-Assuming that the most relevant grain size for observed fluxes corresponds to $a = \lambda_{\mathrm{obs}}/(2 \pi)$, and estimating the gas surface density within Ring13 from the RT model to be roughly $20\,\mathrm{g}/\mathrm{cm}^2$, yields $\mathrm{St}\approx 0.03$.
+Assuming that the most relevant grain size for observed fluxes corresponds to $a = \lambda_{\mathrm{obs}}/(2 \pi)$, and estimating the gas surface density within Ring13 from the RT model to be roughly $20\,\mathrm{g}/\mathrm{cm}^2$ ***not up to date, yields $\mathrm{St}\approx 0.03$.
 With these considerations, equation~\ref{eq:ringwidth} provides a value of $\alpha \approx 0.001$ for the level of turbulent viscosity.

### 2020-11-27 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
   0                 & r < 24.6\text{\,au} \\
-  4.37 \times10^{4} & 24.6 < r < 28.6\text{\,au} \\
-  2.04 \times10^{4} & 28.6 < r < 37\text{\,au} \\
-  1.82 \times10^{5} & 37   < r < 64\text{\,au.} \\
+  6.24 \times10^{4} & 24.6 < r < 28.6\text{\,au} \\
+  2.78 \times10^{4} & 28.6 < r < 37\text{\,au} \\
+  2.14 \times10^{5} & 37   < r < 64\text{\,au.} \\
   \end{cases}
@@
 The two different populations of dust grains correspond to small grains, with radii ranging from 0.4 to 1.5\,$\micron$, and large dust grains, with radii from 0.4\,$\micron$ to 10\,mm.
-We computed the dust opacities using the {\tt bhmie} code provided in the \textsc{radmc3d} package, with a mix composed of 70\% silicate and 30\% graphite.
+We computed the dust opacities using the {\tt bhmie} code provided in the \textsc{radmc3d} package, with a mix composed of 60\% silicate, 20\% graphite and 20\% ice.
 
@@
   \item We report the detection of a narrow ring in the 1.3\,mm continuum, with a radius 13.32$\pm$0.26\,au and an estimated width of 1.50$\pm$0.72\,au.
-The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes around 1.5\,M$_{\earth}$ millimetre-sized grains.
-Using the parametric model scale height value ($H= $ 0.66\,au at 13.32\,au) we have that the ring width is roughly 2.3 times its estimated height.
+The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes around 1.1\,M$_{\earth}$ millimetre-sized grains.
+Using the parametric model scale height value ($H= $ 0.31\,au at 13.32\,au) we have that the ring width is roughly 4.8 times its estimated height.
 

### 2020-12-01 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 Sebasti\'an P\'erez,$^{2}$
-et al. 
+Antonio Hales,$^{3}$
+Philipp Weber, $^{1,2}$ \newauthor
+Carla Arce-Tord,
+Lucas Cieza,
+Antonio Garufi,
+Sebasti\'an Marino,
+Alice Zurlo
 \\
@@
   The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc known for its wide cavity and dusty ring.
-We present new high resolution ($\sim$50\,mas) ALMA observations of the 1.3\,mm continuum.
-The comparison of these observations, combined with SPHERE-IRDIS polarized images and a well-sampled spectral energy distribution (SED), against radiative transfer (RT) predictions carried out with the \textsc{radmc3d} package, allow us to propose a physical model for the source.
+We present high resolution ($\sim$20--50\,mas) ALMA observations of the 1.3\,mm  continuum which, combined with SPHERE-IRDIS polarized images and a well-sampled spectral energy distribution (SED), allow us to propose a physical model for the source using radiative transfer (RT) predictions.
 The new ALMA data reveal a very thin ring at a radius of 13.32$\pm$0.26\,au (Ring13), with a marginally resolved radial width of 1.50$\pm$0.72\,au.
-Ring13 is surrounded by a $\sim$10\,au-wide gap, and it is flanked by a very bright mm outer ring (Ring24) with a sharp inner edge at 24\,au.
+Ring13 is surrounded by a $\sim$10\,au-wide gap, and it is flanked by a very mm-bright outer ring (Ring24) with a sharp inner edge at 24\,au.
 The steeply decreasing brightness of Ring24 breaks at $\sim$35\,au into a shallow tail.
-The RT model requires an inner ring at $\sim$6\,au (Ring6) in small dust grains, hiding under the IRDIS coronagraph, and that surrounds an inner circumbinary disc.
-Faint mm-continuum close ($\sim0\farcs02$) to the stellar position is picked up by ALMA.
-***
-  %coincident with Ring6 is picked up by ALMA, whose morphology suggests that Ring6 is lopsided or shadowed by the secondary. 
-  The previously reported scattered-light shadow of the secondary star is also reproduced by the RT model.
+In order to reproduce the SED, the model that we propose requires an inner ring at $\sim$6\,au (Ring6) in small dust grains, hiding under the IRDIS coronagraph, and that surrounds an inner circumbinary disc.
+Faint mm-continuum close ($\sim0\farcs02 $ ****GIVE ERRORS***) to the stellar position is picked up by ALMA.
 The surprisingly thin Ring13 is nonetheless roughly 5 times wider than the model scale height, and could thus be long-lived.
 The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$.
+The previously reported scattered-light shadow of the secondary star is also reproduced by the RADMC3D RT package.
 \end{abstract}
@@
 Recent observations of young circumstellar discs have transformed current knowledge of planet formation.
-The focus of resolved imaging with the Atacama Large Millimetre/submillimetre Array (ALMA) or with
-%VLT/SPHERE 
-the current generation of high-contrast images 
-has mainly been towards the brighter sources \citep{Andrews2020arXiv200105007A}.
-The discs around T Tauri Stars (DARTTS) program was first presented in \citet{Avenhaus_2018} with the aim to image eight stars with the Spectro-Polarimeter High-contrast Exoplanet REsearch (SPHERE) \citep{2019A&A...631A.155B}.
-The sample is not biased towards exceptionally bright and large discs, and consists of only solar-type stars.
-A second part of the survey increased the number of sources by presenting 21 new images of circumstellar discs \citep{Garufi2020}.
-The observations revealed diverse structures and morphologies in the scattering surface of these discs.
-This letter on V4046 Sagittarii (Sgr) is part of the DARTTS survey with ALMA (DARTTS-A) which will present millimetre observations of nine protoplanetary discs previously imaged in polarized scattered light in DARTTS-S.
+The focus of resolved imaging with the Atacama Large Millimetre/submillimetre Array (ALMA) or with the current generation of high-contrast cameras has mainly been towards the brighter sources \citep[e.g.][]{2020ARA&A..58..483A}.
+It is to address this bias that the programme called ``Discs Around T Tauri Stars with SPHERE'' (DARTTS-S) collected differential polarization imaging (DPI) data secured with the Spectro-Polarimeter High-contrast Exoplanet REsearch \citep[SPHERE][]{2019A&A...631A.155B} in a total of 29 solar-type stars \citep[][]{Avenhaus_2018,Garufi2020}.
+The sample is not biased towards exceptionally bright and large discs.
+The DARTTS observations revealed diverse structures and morphologies in the scattering surface of these discs.
+This letter on V4046 Sagittarii (Sgr) is part of a companion programme, the DARTTS survey with ALMA (DARTTS-A, Perez et al.
+{\em in prep}), which will present millimetre observations of nine protoplanetary discs previously imaged in polarized scattered light in DARTTS-S.
 
-V4046\,Sgr is a double-lined spectroscopic binary of K-type stars (K5 and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012}, on a close ($a \approx 0.041$\,au), circular ($e\leq0.01$) orbit, with an orbital period of 2.42 days \citep{refId0}.
+V4046\,Sgr is a double-lined spectroscopic binary of K-type stars (K5 and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012}, on a close ($a \approx 0.041$\,au), circular ($e\leq0.01$) orbit, with an orbital period of 2.42 days \citep{2000IAUS..200P..28Q}.
 It is a member of the $\beta$ Pictoris moving group \citep{Zuckerman_2004}, with an estimated age of 23$\pm$3\,Myr \citep{Mamajek_2014}, and its distance is 72.41$\pm$0.34\,pc \citep{Gaia}.
-V4046\,Sgr hosts a massive ($\sim$0.1\,M$_{\sun}$) circumbinary disc extending to $\sim$300\,au \citep{Rosenfeld_2013, Rodriguez_2010}, with a rich observable chemical diversity \citep{Kastner_2018}.
+V4046\,Sgr hosts a massive ($\sim$0.1\,M$_{\sun}$) circumbinary disc extending to $\sim$300\,au \citep{Rosenfeld_2013, Rodriguez_2010},  rich in diverse molecular lines \citep{Kastner_2018}.
 
-The structure of this letter is as follows.
 The observations, including new 1.3\,mm continuum data, are described in Section~\ref{sec:Observations}.
-We interpret the data in terms of a parametric model, presented in Section~\ref{sec:model}.
-Previous models of V4046\,Sgr have been made \citep{Ru_z_Rodr_guez_2019, Rosenfeld_2013, 2019ApJ...882..160Q} but our new ALMA data bring additional information.
+We interpret the data in terms of a parametric model, presented in Section~\ref{sec:model}, which builds up  on the previous models of V4046\,Sgr  \citep{Rosenfeld_2013, Ru_z_Rodr_guez_2019, 2019ApJ...882..160Q} to account for the new  ALMA data.
 Our results are discussed in Section~\ref{sec:results} and summarised in Section~\ref{sec:Conclusions}.
@@
 Perez).
-These were acquired in the context of the DARTTS-A program (Perez et al.
-{\em in prep}), a larger survey for 9 optically visible TTauri discs at $\sim$50\,mas resolution.
-The survey simultaneously mapped the 1.3\,mm continuum and the J = 2$-$1 line of $^{12}$CO with the C43-8 array configuration in band 6 (211-275\,GHz).
-This work focuses exclusively on the data obtained in the 1.3\,mm continuum for our source, acquired with baselines ranging from 92 to 8548\,m, which translate into a synthesized beam of $0\farcs077 \,\times \, 0\farcs051$ (in natural weights).
+The observations  acquired simultaneously the 1.3\,mm continuum and the J = 2$-$1 line of $^{12}$CO with  (i.e.
+with a  band 6 211-275\,GHz correlator setup).
+The ALMA array was in its C43-8 configuration, with baselines ranging from 92 to 8548\,m which translate into a synthesized beam of $0\farcs062 \,\times \, 0\farcs055$, in  natural weights.
+Here we focus on the continuum observations only.
 
-V4046 Sgr was observed in differential polarization imaging (DPI) mode with SPHERE/IRDIS on March 13, 2016.
-All the details of this observation can be found in the first DARTTS-S paper \citep{Avenhaus_2018} where the image was first published.
-Here we use a new reduction of the $H$ band data produced by the IRDAP pipeline \citep{2020A&A...633A..64V}, which can separate stellar and instrumental polarization.
+V4046\,Sgr was observed in differential polarization imaging (DPI) mode with SPHERE/IRDIS on March 13, 2016 \citep[see][for details]{Avenhaus_2018}.
+Here we use a new reduction of the $H$ band data produced with the IRDAP pipeline \citep{2020A&A...633A..64V}, which can separate stellar and instrumental polarization.
 The polarized signal is consistent with the previous image in \citet{Avenhaus_2018}.
-The degree of linear polarization of the central and unresolved signal in V4046 Sgr is only 0.13\%, with a systematic uncertainty of 0.05\% due to time-varying atmospheric conditions during the exposures.
-The angle of polarization is aligned with the disk major disk, as expected given that the target has Av=0.0 \citep{2016ApJ...828...69M} and the entire polarization is dominated by circumstellar rather than inter-stellar material.
+The degree of linear polarization of the central and unresolved signal in V4046\,Sgr is only 0.13\%, with a systematic uncertainty of 0.05\% due to time-varying atmospheric conditions during the exposures.
+The angle of polarization is aligned with the disc major axis, as expected given that the target has Av=0.0 \citep{2016ApJ...828...69M} and the entire polarization is dominated by circumstellar rather than inter-stellar material.
 
-For our analysis of the ALMA image we used an image reconstruction strategy, using the non-parametric image synthesis of the {\tt uvmem} package \citep{2006ApJ...639..951C, 2018A&C....22...16C} it is possible to super-resolve the clean beam, obtaining an effective angular resolution $\sim$3 times finer than natural weights.
-The model image is obtained by fitting the data using Chi-squared minimisation, with a measure of regularization when required.
-Here we adopted a $\chi^2$ model image with $\lambda$ = 0.01 for regularization (***mem\_lS0.01\_lL0.0\_nogrid/mod\_out.fits**).
+Image synthesis of the ALMA continuum was performed with  the {\tt uvmem} package \citep{2006ApJ...639..951C, 2018A&C....22...16C}, which fits a non-parametric model image $I^m_j$ to the data by comparing the  observed  and model visibilities, $V^\circ_k$ and $V^m_k$, using a least-squares figure of merit $L$:
+\begin{equation}
+  L = \sum_{k=1}^N \omega_k  |V^\circ_k - V^m_k|^2 + \lambda S.
+\end{equation}
+The regularization term $S$ depends on the application, and in this case we chose the standard image entropy, or
+\begin{equation}
+S = \sum_{j=1}^M \frac{I_j^m}{M} \ln\left(\frac{I_j^m}{M}\right),
+\end{equation}
+where $M$ is the default pixel intensity value, and is set to $10^{-3}$ times the theoretical noise of the dirty map (as inferred from the visibility weights $\omega_k$).
+Here we set $\lambda = 0.01$.
+Similar applications of {\tt uvmem} in the context of protoplanetary discs can be found, for example,  in \citet{Casassus2013Natur, 2018MNRAS.477.5104C, Casassus2019MNRAS.483.3278C,  Perez2019AJ....158...15P}.
+An  advantage of {\tt uvmem} compared to more traditional imaging strategies, such as provided by the  {\tt tclean}   task in CASA, is that the effective angular resolution of the model image is  $\sim$3 times finer than the natural weights clean beam \citep[][]{2018A&C....22...16C}.
+This angular resolution is comparable to  uniform or super-uniform weights in {\tt tclean}, but it preserves the natural-weights point-source sensitivity.
+
 The resulting {\tt uvmem} image shown in Fig.~\ref{fig:images_vs_simulated} exhibits previously unseen substructure of the disc.
@@
 From top to bottom: DPI image and ALMA Band 6 observations; simulated images of the parametric model.
-Top left panel: SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that illustrate the N\_ALC\_YJH\_S coronagraph with a radius of $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc.
+Top left panel: SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that represents the N\_ALC\_YJH\_S coronagraph with a radius of $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc.
 Top right panel: 1.3\,mm continuum {\tt uvmem} model image.
@@
 The inset zooms into the central emission, and the green star marks the star positions.
-Bottom left panel: 1.65\,$\upmu m$ simulated image of the parametric model.
-Bottom right panel: 1.3\,mm simulated image of the parametric model.
-The orange ellipse shows the size of the beam: $0\farcs035 \, \times \, 0\farcs031$.
+Bottom left panel: synthetic image at 1.65\,$\upmu m$.
+Bottom right panel: synthetic image at 1.3\,mm.
+.
 For all the images in the figure the colour scale is linear.}
@@
 
-Ring13 is surprisingly narrow and seems to be off-centred relative to the GAIA stellar position (at the origin of coordinates in Fig.~\ref{fig:images_vs_simulated}).
-We determined the ring's centre and orientation by minimising the dispersion of the disc radial profiles, from 6\,au to 19\,au, and thus obtained a PA of 77.31$\pm$0.03\,$\degr$, an inclination of 32.96$\pm$0.02\,$\degr$ and a centre at $\Delta \alpha = -4\pm0.02$\,mas $\Delta \delta = 13\pm0.05$\,mas, relative to the stars.
+Ring13 is surprisingly narrow and seems to be off-centred relative to the GAIA stellar position, at the origin of coordinates in Fig.~\ref{fig:images_vs_simulated}.
+We determined the ring's centre and orientation by minimising the dispersion of the disc radial profiles from 6\,au to 19\,au, by using the {\tt MPolarMaps} package described in Casassus et al.
+(2021, in prep).
+The resulting disc orientation is set at a position angle  (PA) of 77.31$\pm$0.03\,$\degr$, with an  inclination of 32.96$\pm$0.02\,$\degr$, and the optimal ring  centre is at $\Delta \alpha = -4\pm0.02$\,mas $\Delta \delta = 13\pm0.05$\,mas relative to the GAIA position of the stars.
+The offset of the center of the cavity and the nominal stellar positions is entirely consistent with a pointing error, since the pointing accuracy of ALMA is usually taken to be 1/10 of the natural-weights beam, at 1\,$\sigma$, or $\sim$6\,mas in this case.
+***ANTONIO PLEASE CONFIRM AND PROVIDE A REFERENCE ****
 
@@
 
-Repeating the optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.86$\pm$0.02\,$\degr$, with an inclination of 33.92$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 2\pm0.02$\,mas $\Delta \delta = 12\pm0.02$\,mas relative to the stars.
-We see that both Ring13 and Ring24 both share a very similar orientation and centre, given the errors, and both are offset from the star.***  %Even though all orientation parameters for Ring13 and Ring24 are consistent within the errors,
-Perhaps due to the joint effect of all these small differences, we can see that there are some hints for a different orientation, as summarised in Fig.~\ref{fig:polarring}.
+In a second optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.86$\pm$0.02\,$\degr$, with an inclination of 33.92$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 2\pm0.02$\,mas $\Delta \delta = 12\pm0.02$\,mas relative to the stars.
+We see that both Ring13 and Ring24 both share a very similar orientation and centre, given the errors.
+However, perhaps due to the joint effect of all these small differences, we can see that there are some hints for a somewhat different orientation, as summarised in Fig.~\ref{fig:polarring}.
 
 Interestingly, the ALMA image also detects faint 1.3\,mm continuum emission near the stellar positions (See the inset in Fig.~\ref{fig:images_vs_simulated}).
-Since this faint central emission is offset from the star, at the origin of coordinates in the figure, it is probably due to large dust grains.
-This dust structure is at a distance of only $\sim0\farcs02$ from the binary system, and may be part of some inner structure possibly having to do with the small grain ring called Ring6 introduced in the RT model to match the SED (see Sec.~\ref{sec:model} below).
-***
+Since this faint central emission is larger than the angular resolution, it is probably stemming from thermal emission from  large dust grains rather directly from the stars.
+The main blob of this dust structure is at a estimate distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.9\,au from the binary system, and may be part of inner disc introduced in the RT model to match the SED (see Sec.~\ref{sec:model} below).
+
 %match the small grain ring called Ring6 introduced in the RT model to match the SED (see Sec.\,\ref{sec:model} below).
@@
 The observed second ring matches the inner wall of the 1.3\,mm continuum emission outer ring \citep{Ru_z_Rodr_guez_2019}.
-Two other important features that are present in the image are: the brightness asymmetry and the shadows projected on the disc produced by the close binary system as they eclipse each other, described in detail by \citet{dOrazi}.
+Two other important features that are present in the image are: the brightness asymmetry and the shadows projected on the disc produced by the close binary system as they eclipse each other, discovered by \citet{dOrazi}.
 
@@
 There is no hint of radio decrements in either Rings13 nor in Ring24 that would match shadowing at this PA.
-This could be explained by inefficient disc cooling compared to the speed of the illumination pattern \citep{Casassus2019MNRAS.486L..58C}.
+This could be explained by inefficient disc cooling compared to the speed of the illumination pattern \citep[see ][ for estimates of this cooling timescale]{Casassus2019MNRAS.486L..58C}.
 
@@
 
-The observed SED was collected from data in the literature \citep{1988iras....7.....H, 1990A&A...234..230H, Jensen_97, 2000A&A...355L..27H, 2001KFNT...17..409K, 2003yCat.2246....0C, 2007PASJ...59S.369M, 2008PASP..120.1128O, 2010A&A...514A...1I, 2012yCat.2311....0C}, online in \textsc{vizier}, and also using spectrometry data from an archival \textit{Spitzer} IRS spectrum (See Fig.~\ref{fig:SED}).
-The SED will provide us with missing information about the dust population.
+The observed SED was collected from data in the literature \citep{1988iras....7.....H, 1990A&A...234..230H, Jensen_97, 2000A&A...355L..27H, 2001KFNT...17..409K, 2003yCat.2246....0C, 2007PASJ...59S.369M, 2008PASP..120.1128O, 2010A&A...514A...1I, 2012yCat.2311....0C}, available online in \textsc{vizier}.
+We also  used  archival \textit{Spitzer} IRS spectroscopic data (see Fig.~\ref{fig:SED}).
 
@@
 Through trial and error, we found a set of values for the parameters that correctly fit the available data.
-The final structure of the parametric model goes as Fig.~\ref{fig:profiles} shows.
+The final structure of the parametric model is summarised in  Fig.~\ref{fig:profiles}.
 
-For the representation of the stars, we used two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C} with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of $\mathrm{log}(\,\dot{\mathrm{M}/(\mathrm{M}_{\sun}\,\mathrm{yr^{-1}})}) = -$9.3 for both cases to include excess UV due to stellar accretion \citep{10.1111/j.1365-2966.2011.19366.x}.
+The stars were modeled using two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C}, with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of $\mathrm{log}(\,\dot{\mathrm{M}/(\mathrm{M}_{\sun}\,\mathrm{yr^{-1}})}) = -$9.3 for both cases to include excess UV due to stellar accretion \citep{10.1111/j.1365-2966.2011.19366.x}.
 The stars were placed at a mutual separation of 0.041\,au, so that their centre of mass coincides with the origin, and oriented at a PA of 250\,$\degr$, so that the secondary lies to the NWW from the primary, thus casting the same shadow as observed by \citet{dOrazi}.
@@
 Reproducing the radial and vertical structure of the V4046\,Sgr disc turned out to be challenging.
-We built the model in terms of the gas distribution, and with two different dust populations: larger grains that are vertically settled and dominate the total dust mass and a population of smaller grains that are uniformly mixed with the gas and reach larger heights above the mid-plane.
+We built the model in terms of the gas distribution, and with two different dust populations: larger grains that are vertically settled and dominate the total dust mass, and a population of smaller grains that are uniformly mixed with the gas and reach larger heights above the mid-plane.
 
@@
 where $H_\circ$ is the scale height at r = $r_\circ$, $\psi$ is the flaring index and $\chi$ is a scaling factor (in the range $0-1$) that mimics dust settling.
-For the gas and the small dust grains $\chi$ = 1 and for the millimetre-size dust population we assign a fixed $\chi$ = 1/5 for simplicity ***(now is not for simplicity).
+The gas and the small dust grains have no settling, so $\chi_{gas}$ = 1.
+The radial spread of Ring13 appears about five times wider in the gas-tracing NIR observations than in the fluxes received from larger grains with ALMA.
+We assume that the same ratio holds in the vertical direction (due to the settling of larger grains towards the disk's midplane), leading to $\chi_{ld}=1/5$.
 
@@
 
-We propose a three ringed structure, so we defined the total gas surface density by a combination of four individual components: the inner disc, Ring6, Ring13 and Ring24. Then it is defined by:
+We propose a three ringed structure, so we defined the total gas surface density by a combination of four individual components: the inner disc, Ring6, Ring13 and Ring24.
+The total gas surface density is then  given  by:
 \begin{equation}
@@
 
-The inner disk follows a power law function defined by
+The inner disc follows a power law function defined by
 \begin{equation}
@@
 \end{equation}
-where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring6}}=5.5$\,au, $\mu_{\mathrm{Ring13}}=15$\,au\}, ring widths \{$\sigma_{\mathrm{Ring6}}=1$\,au, $\sigma_{\mathrm{Ring13}}=2.05$\,au\}, and normalizations \{ $\Sigma_{\circ,\mathrm{Ring6}}=8\times10^{12}$, $\Sigma_{\circ,\mathrm{Ring13}}=4.2\times10^{13}$\} for both structure components separately.
+where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring6}}=5.5$\,au, $\mu_{\mathrm{Ring13}}=15$\,au\}, ring widths \{$\sigma_{\mathrm{Ring6}}=1$\,au, $\sigma_{\mathrm{Ring13}}=2.05$\,au\}, and normalizations \{ $\Sigma_{\circ,\mathrm{Ring6}}=8\times10^{12}$, $\Sigma_{\circ,\mathrm{Ring13}}=4.2\times10^{13}$\} for both components separately.
 
@@
 But the inner wall of Ring24 follows a different behaviour.
-Between $R_\mathrm{in}$ and $R_\mathrm{peak}$, marking the beginning and the maximum density peak of the outer ring respectively, the gas density profile is multiplied by an additional factor
+Between $R_\mathrm{in}$ and $R_\mathrm{peak}$, which respectively mark  the beginning and the maximum density peak of the outer ring, the gas density profile is multiplied by an additional factor
 \begin{equation}
@@
 The small dust grains are assumed to only make up for a fraction of $f_\mathrm{sd}=1\%$ of the total dust mass.
-As small dust is typically tightly coupled to the gas dynamics, its density profile is largely expected to follow the gas density.
+As small dust is typically tightly coupled to the gas dynamics, its density profile is expected to follow the gas density.
 Then the density of small dust can be calculated as:
@@
 For the inner ring, we chose a Gaussian profile parameterized with centroid radius $\mu_{\mathrm{Ring13, ld}}=13.38$\,au, ring width of $\sigma_{\mathrm{Ring13,ld}}=0.54$\,au and $\Sigma_{\circ,\mathrm{Ring13,ld}}=3\times10^{13}$.
-For Ring24 we used the same profile of the gas, but with the difference that, in an effort to recreate the break seen in the outer ring, between 28.6 and 35.6\,au we chose a different value for $\gamma$ = -5 and $R_c$ = 38\,au.
-Thus, the surface density of the outer ring of large grains dust is defined by
+For Ring24 we used the same profile of the gas, but with the difference that, in an effort to recreate the break seen in the outer ring, we chose different values for $\gamma$ = -5 and $R_c$ = 38\,au between 28.6 and 35.6\,au.
+The surface density of the outer ring of large grains dust is thus given by
 \begin{equation}
@@
 The simulated DPI image at 1.65\,$\micron$ in Fig.~\ref{fig:images_vs_simulated} was obtained with the scattering matrix calculated by the {\tt makeopac.py} script provided in the \textsc{radmc3d} package.
-As a way of reproducing the \textit{H}-band image, we used a different grain size distribution, where we used a Gaussian distribution centred at 0.4\,$\micron$, and smeared out by 30\% in both directions, and using 20 grain size bins within that range.
-This distribution applies only to generate the NIR image.
+As a way of reproducing the \textit{H}-band image, we used a different grain size distribution, where we used a Gaussian distribution centred at 0.4\,$\micron$ but  smeared out by 30\%, and with 20 grain size bins within that range.
+This distribution applies only to generate the NIR $Q_\phi$ image.
+To produce this $Q_\phi$ image we performed a linear combination of the two orthogonal linear polarizations \textit{U} and \textit{Q}, following \citet{Avenhaus_2017}, which gives a representation of an unbiased estimate of the polarized intensity image.
 
@@
 
-The inner radius of the model grid was set to 0.1\,au and an outer radius of 100\,au, large enough for the dust disc to become undetectable.
-We set the values of the inclination an the position angle as the same as those obtained from the ALMA observation in Section~\ref{sec:Observations}, so the model has an inclination of i = 32.96\,$\degr$ and a P.A.
+The inner radius of the model grid was set to 0.1\,au,  and the outer radius of 100\,au, which is large enough for the dust disc to become undetectable.
+We set the values of the inclination an disc  position angle as the same as those obtained from the ALMA observation in Section~\ref{sec:Observations}, so the model has an inclination of i = 32.96\,$\degr$ and a P.A.
 = 77.31\,$\degr$.
@@
 The simulated image at 1.65\,$\micron$ shows a similar radial structure to the one visible in the observations, displaying a two ringed disc, where Ring6 hides under the artificial coronagraph.
-The visible asymmetry in the SPHERE observations is recreated using grains larger than 0.4\,$\micron$ as smaller grains do not cause a strong forward scattering, meaning that the disc is depleted of very-small grains.
+The visible asymmetry in the SPHERE observations is reproduced using relative large grains, $\sim$0.4\,$\micron$, as smaller grains did not result in such strong forward scattering.
+As \citet{refId0} states, this forward scattering peak that is present in the observation may indicate that the dust grains in the disk surface are large, suggesting that the disc is depleted of very-small grains.
 Interestingly, the model accurately shows the shadows described by \citet{dOrazi} that are present in the SPHERE-IRDIS image.
@@
 The simulated 1.3\,mm continuum image reproduces the two observed rings: the faint Ring13 and the brighter Ring24.
-As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.~\ref{fig:radprofiles}), we can assume that the model provides a good approximation of the disc structure, including the dimensions of Ring13.
+As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.~\ref{fig:radprofiles}), we can assume that the model provides a possible approximation of the disc structure, including the dimensions of Ring13.
 Accordingly, taking the parametric model values for Ring13 we have that it has a radius of 13.36\,au, a FWHM of 1.30\,au, and a scale height FWHM of the millimetre-size dust of 0.65\,au.
@@
 The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.06\,au difference in the centroid location of the ring, and a 0.2\,au difference in the width estimation.
-%As \citet{2018ApJ...869L..46D} explain the stability of a narrow dust ring requires that its height is smaller than its radial extent. 
-Using the large grains scale height of 0.31\,au at Ring13, and a measured width of 1.50\,au, the ring is $\sim$4.8 times more extended in radial than in vertical direction.
+Using the large grains scale height of 0.31\,au at Ring13, and a measured width of 1.50\,au, the ring is $\sim$4.8 times more extended  radially than vertically.
 
-The observed structure may point to the existence of planet-disk interaction within this system, where a giant planet depletes its orbit of gas and dust material.
-A possible constellation in this scenario is therefore the presence of two giant planets in the disk, one planet between the star and Ring13, and one planet between Ring13 and Ring24.
+The observed structure may point to the existence of planet-disc interactions within this system, where a giant planet depletes its orbit of gas and dust material.
+A possible  constellation in this scenario is therefore the presence of two giant planets in the disc, one planet between the star and Ring13, and one planet between Ring13 and Ring24.
 As \citet{Ru_z_Rodr_guez_2019} suggest, the putative planet between Ring13 and Ring24 may be a giant planet with a mass within the range of 0.3$-$1.5\,$\mathrm{M}_{\mathrm{Jup}}$.
-This idea is supported by the similarity to the structure around HD 169142 which \citet{bertrang_avenhaus_2018} reproduced by including several giant planets.
-%We point out that also the disk dispersal by photoevaporative winds \citep{1994ApJ...428..654H} as causation of the inner cavity cannot be ruled out at his stage.
+This idea is supported by the similarity to the structure around HD\,169142 which \citet{bertrang_avenhaus_2018} reproduced by including several giant planets.
 
-*** The effective beam size of the presented ALMA observations marginally resolves the width of Ring13 to be $w_\mathrm{d} = 1.50\mathrm{au}$.
+*****
+The effective beam size of the presented ALMA observations marginally resolves the width of Ring13 to be $w_\mathrm{d} = 1.50\mathrm{au}$.
 %The most suitable RT model demands a density distribution of small grains and gas that is radially more extended, with an approximate width of $7.5\mathrm{au}$.
@@
 \end{equation}
-where we implicitly assumed the turbulent diffusivity to be equal to the turbulent viscosity.
-Here, $\alpha$ represents the typical parameter for turbulent viscosity, and $\mathrm{St}$ is the dimensionless Stokes number.
-Assuming that the most relevant grain size for observed fluxes corresponds to $a = \lambda_{\mathrm{obs}}/(2 \pi)$, and estimating the gas surface density within Ring13 from the RT model to be roughly $20\,\mathrm{g}/\mathrm{cm}^2$ ***not up to date, yields $\mathrm{St}\approx 0.03$.
-With these considerations, equation~\ref{eq:ringwidth} provides a value of $\alpha \approx 0.001$ for the level of turbulent viscosity.
+where we  assumed the turbulent diffusivity to be equal to the turbulent viscosity $\alpha$, and $\mathrm{St}$ is the dimensionless Stokes number.
+Assuming that the most relevant grain size for observations at a wavelength $\lambda$ corresponds to $a = \lambda_{\mathrm{obs}}/(2 \pi)$, and estimating the gas surface density within Ring13 from the RT model to be roughly $0.5\,\mathrm{g}/\mathrm{cm}^2$, yields $\mathrm{St}\approx 2$.
+With these considerations, equation~\ref{eq:ringwidth} provides a value of $\alpha \approx 0.1$ for the level of turbulent viscosity.
 We emphasise that this relies on rough estimates and is additionally restricted to the area within Ring13.
@@
 Further, it is also consistent with the non-detection of non-thermal broadening of CO lines reported by \citet{Flaherty_2020}, from which the authors deduced an upper limit of $\alpha \lesssim 10^{-3}$ at the midplane of V4046\,Sgr.
+NOT*****
 
@@
 %and we may have detected this ring in the ALMA image, if this ring is lopsided or shadowed by the secondary. 
-Ring6 may be just artificial and not a real prediction, as a thin ring like the one needed would have to have millimetre-size dust grains due to dust trapping, and those grains are not present in the ALMA observation.
-***
+Ring6 may be just artificial and not a real prediction, as a thin ring like the one needed would trap millimetre-size dust grains, while  those grains are not present in the ALMA observation.
 
@@
   \item Our parametric model, which accounts for the SED of the system, involves the existence of a sub-micron dust population close (<5\,au) to the stars.
+
   %We also predict the existence of another thin ring at $\sim$6\,au, about 3\,au-wide and made of small dust grains, and that lies under the coronagraph of the scattered-light image. 

### 2020-12-01 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 As \citet{Ru_z_Rodr_guez_2019} suggest, the putative planet between Ring13 and Ring24 may be a giant planet with a mass within the range of 0.3$-$1.5\,$\mathrm{M}_{\mathrm{Jup}}$.
-This idea is supported by the similarity to the structure around HD\,169142 which \citet{bertrang_avenhaus_2018} reproduced by including several giant planets.
+This idea is supported by the similarity to the structure around HD\,169142 which \citet{2020arXiv200711565B} reproduced by including several giant planets.
 

### 2020-12-04 Draft_V4046_Sgr_mnras.tex
Add files via upload

--- 2020-12-01 Draft_V4046Sgr_mnras.tex
@@
 %% \usepackage{amssymb}	% Extra maths symbols
+\usepackage{soul}
+\usepackage{xcolor}  
+\newcommand{\phil}[1]{\colorbox{yellow}{\bf #1}}
 
@@
 The steeply decreasing brightness of Ring24 breaks at $\sim$35\,au into a shallow tail.
-In order to reproduce the SED, the model that we propose requires an inner ring at $\sim$6\,au (Ring6) in small dust grains, hiding under the IRDIS coronagraph, and that surrounds an inner circumbinary disc.
+In order to reproduce the SED, the model that we propose requires an inner ring at $\sim$6\,au (Ring6) \st{in} \phil{composed of} small dust grains, hiding under the IRDIS coronagraph, and \st{that surrounds} \phil{surrounding} an inner circumbinary disc.
 Faint mm-continuum close ($\sim0\farcs02 $ ****GIVE ERRORS***) to the stellar position is picked up by ALMA.
@@
 
-V4046\,Sgr was observed in differential polarization imaging (DPI) mode with SPHERE/IRDIS on March 13, 2016 \citep[see][for details]{Avenhaus_2018}.
+V4046\,Sgr was observed in differential polarization imaging (DPI) mode with \st{SPHERE/IRDIS} \phil{SPHERE-IRDIS [for consistency]} on March 13, 2016 \citep[see][for details]{Avenhaus_2018}.
 Here we use a new reduction of the $H$ band data produced with the IRDAP pipeline \citep{2020A&A...633A..64V}, which can separate stellar and instrumental polarization.
@@
 
-The resulting {\tt uvmem} image shown in Fig.~\ref{fig:images_vs_simulated} exhibits previously unseen substructure of the disc.
+The resulting {\tt uvmem} image shown in \phil{the top right panel of} Fig.~\ref{fig:images_vs_simulated} exhibits previously unseen substructure of the disc.
 This image reveals that the disc features two rings of large dust grains with a broad gap between them, i.e.
@@
   \includegraphics[width=\textwidth]{hot_two_E.pdf}
-  \caption{Comparison of observations and simulated images at 1.65\,$\micron$ and 1.3 mm continuum of the circumbinary disc orbiting V4046\,Sgr.
-From top to bottom: DPI image and ALMA Band 6 observations; simulated images of the parametric model.
-Top left panel: SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that represents the N\_ALC\_YJH\_S coronagraph with a radius of $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc.
-Top right panel: 1.3\,mm continuum {\tt uvmem} model image.
+  \caption{Comparison of observations \phil{(top)} and simulated images \phil{(bottom)} at 1.65\,$\micron$ \phil{(left)} and 1.3 mm continuum \phil{(right)} of the circumbinary disc orbiting V4046\,Sgr.
+\st{From top to bottom: DPI image and ALMA Band 6 observations; simulated images of the parametric model.} \phil{\textit{Top left panel:}} SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that represents the N\_ALC\_YJH\_S coronagraph with a radius of $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc.
+\phil{\textit{Top right panel:}} 1.3\,mm continuum {\tt uvmem} model image.
 The yellow ellipse shows the size of the natural-weighted beam ($ 0\farcs062 \, \times \, 0\farcs055$), and the small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs035 \, \times \, \sim0\farcs031$).
-The inset zooms into the central emission, and the green star marks the star positions.
-Bottom left panel: synthetic image at 1.65\,$\upmu m$.
-Bottom right panel: synthetic image at 1.3\,mm.
+The inset zooms into the central emission, and the green star marks the \st{star positions} \phil{binary position}.
+\phil{\textit{Bottom left panel:}} synthetic image at 1.65\,$\upmu$\phil{m}.
+\phil{\textit{Bottom right panel:}} synthetic image at 1.3\,mm.
 .
@@
 Since this faint central emission is larger than the angular resolution, it is probably stemming from thermal emission from  large dust grains rather directly from the stars.
-The main blob of this dust structure is at a estimate distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.9\,au from the binary system, and may be part of inner disc introduced in the RT model to match the SED (see Sec.~\ref{sec:model} below).
+The main blob of this dust structure is at a estimate distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.9\,au from the binary system, and may be part of \phil{an} inner disc introduced in the RT model to match the SED (see Sec.~\ref{sec:model} below).
 
@@
 
-The scattered-light image shown in Fig.~\ref{fig:images_vs_simulated} also shows a double ring structure in the micron-sized dust distribution.
+The scattered-light image \st{shown} in \phil{the top left panel of} Fig.~\ref{fig:images_vs_simulated} also shows a double ring structure in the micron-sized dust distribution.
 The observed morphology presents an inner cavity of $\sim$10\,au in radius and two rings located at 14.10$\pm$0.01, coincident with Ring13, and 24.62$\pm$0.08\,au, coincident with Ring24, with a small gap between them at $\sim$20\,au.
@@
 	\includegraphics[width=\columnwidth]{SED_.png}
-    \caption{The observed SED of V4046\,Sgr (black points and solid red curve) compared with the model (blue).
+    \caption{\phil{Change labels in legend: binary instead of stars, RT Model} \phil{Spectroscopy Data, Photometry Data.} The observed SED of V4046\,Sgr (black points and solid red curve) compared with the model (blue).
 The black points represent the measured photometry and the red line shows an archival \textit{Spitzer} IRS spectrum.
@@
 
-The stars were modeled using two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C}, with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of $\mathrm{log}(\,\dot{\mathrm{M}/(\mathrm{M}_{\sun}\,\mathrm{yr^{-1}})}) = -$9.3 for both cases to include excess UV due to stellar accretion \citep{10.1111/j.1365-2966.2011.19366.x}.
+The stars were modeled using two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C}, with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of \st{$\mathrm{log}(\,\dot{\mathrm{M}/(\mathrm{M}_{\sun}\,\mathrm{yr^{-1}})}) = -$9.3} \phil{[replace by:]} $\mathrm{log}(\,\dot{\mathrm{M}}/(\mathrm{M}_{\sun}\,\mathrm{yr^{-1}})) = -$9.3 for both cases to include excess UV due to stellar accretion \citep{10.1111/j.1365-2966.2011.19366.x}.
 The stars were placed at a mutual separation of 0.041\,au, so that their centre of mass coincides with the origin, and oriented at a PA of 250\,$\degr$, so that the secondary lies to the NWW from the primary, thus casting the same shadow as observed by \citet{dOrazi}.
@@
 Reproducing the radial and vertical structure of the V4046\,Sgr disc turned out to be challenging.
-We built the model in terms of the gas distribution, and with two different dust populations: larger grains that are vertically settled and dominate the total dust mass, and a population of smaller grains that are uniformly mixed with the gas and reach larger heights above the mid-plane.
+We built the model in terms of the gas distribution, and with two different dust populations: larger grains that are vertically settled and dominate the total dust mass, and a population of smaller grains that are uniformly mixed with the gas and reach \phil{higher regions} \st{larger heights} above the mid-plane.
 
-Assuming a three dimensional model in a cylindrical reference frame with coordinates ($r$, $\theta$, $z$), the gas density ($\rho_{\mathrm{gas}}$) distribution follows
+Assuming a three dimensional model in a cylindrical reference frame with coordinates ($r$, $\theta$, $z$) \phil{[just for conventional reasons, I would use $\phi$ instead of $\theta$]}, the gas density ($\rho_{\mathrm{gas}}$) distribution follows
 \begin{equation}
@@
 \end{equation}
-where $H_\circ$ is the scale height at r = $r_\circ$, $\psi$ is the flaring index and $\chi$ is a scaling factor (in the range $0-1$) that mimics dust settling.
-The gas and the small dust grains have no settling, so $\chi_{gas}$ = 1.
+where $H_\circ$ is the scale height at \st{r} \phil{$r$}= $r_\circ$, $\psi$ is the flaring index and $\chi$ is a scaling factor (in the range $0-1$) that mimics dust settling.
+The gas and the small dust \phil{(sd)} grains have no settling, so \st{$\chi_{gas}$} \phil{$\chi_{\rm gas}$ = $\chi_{\rm sd}$} = 1.
 The radial spread of Ring13 appears about five times wider in the gas-tracing NIR observations than in the fluxes received from larger grains with ALMA.
-We assume that the same ratio holds in the vertical direction (due to the settling of larger grains towards the disk's midplane), leading to $\chi_{ld}=1/5$.
+We assume that the same ratio holds in the vertical direction (due to the settling of larger grains towards the disk's midplane), leading to \st{$\chi_{ld}=1/5$} \phil{$\chi_{\rm ld}=0.2$ [adapt this in case you changed the model to 0.3]}.
 
-For the vertical structure, \citet{dOrazi} found flaring angles of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one.
-Our model uses the same values, with two different flaring indexes $\psi$.
-The separation between the two values were set at $r$ = 18\,au with $\psi=0.15$ for Ring6 and Ring13, and $\psi=0.5$ for Ring24.
+For the \st{vertical structure} \phil{scattering surfaces}, \citet{dOrazi} found flaring angles of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one.
+Our model uses the same values, with two different flaring \st{indexes} \phil{indices, $\psi_1$ and $\psi_2$} \st{$\psi$}.
+The separation between the two values were set at $r$ = 18\,au with \phil{$\psi_1=0.15$} for Ring6 and Ring13, and \phil{$\psi_2=0.5$} for Ring24.
 The scale height is $H_\circ = 0.45$\,au at $r_\circ = 18$\,au.
 
-We propose a three ringed structure, so we defined the total gas surface density by a combination of four individual components: the inner disc, Ring6, Ring13 and Ring24.
-The total gas surface density is then  given  by:
+We propose a three ringed structure \phil{to reproduce the observations.} \phil{We separate the disk into four individual regions:}\st{, so we defined the total gas surface density by a combination of four individual components:} the inner disc, Ring6, Ring13 and Ring24.
+The \st{total} \phil{combined} gas surface density \phil{profile} is then  given  by:
 \begin{equation}
@@
 \end{equation}
-where $R_c$ is a characteristic radius and $\gamma$ is the surface density gradient.
-We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =2.7\times10^{-4}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
-The gas surface density begin at 0.3\,au, out of the zone expected to be cleared by dynamical interactions with the central binary \citep{Art_Lu}, which is expected to be $\sim$0.2\,au.
+where $R_c$ is a characteristic radius and $\gamma$ is the surface density \st{gradient} \phil{power-law index}.
+We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =2.7\times10^{-4}$\phil{\,$\mathrm{g\,cm^{-3}}$} and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
+\st{The gas surface density begin at 0.3\,au, out of the zone expected to be cleared by dynamical interactions with the central binary} \citep{Art_Lu}, \st{which is expected to be $\sim$0.2\,au.} \phil{Our model extends from 0.3\,au outwards, as the interior is expected to be} \phil{cleared by dynamical effects of the central binary} \citep{Art_Lu}.
 
-We chose to use Gaussian profiles to parameterize Ring6 and Ring13,
+We \st{chose} \phil{choose} to use Gaussian profiles to parameterize Ring6 and Ring13,
 \begin{equation}
@@
 \end{equation}
-where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring6}}=5.5$\,au, $\mu_{\mathrm{Ring13}}=15$\,au\}, ring widths \{$\sigma_{\mathrm{Ring6}}=1$\,au, $\sigma_{\mathrm{Ring13}}=2.05$\,au\}, and normalizations \{ $\Sigma_{\circ,\mathrm{Ring6}}=8\times10^{12}$, $\Sigma_{\circ,\mathrm{Ring13}}=4.2\times10^{13}$\} for both components separately.
+where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring6}}=5.5$\,au, $\mu_{\mathrm{Ring13}}=15$\,au\}, ring widths \{$\sigma_{\mathrm{Ring6}}=1$\,au, $\sigma_{\mathrm{Ring13}}=2.05$\,au\}, and normalizations \phil{[this $\Sigma$ cant be right?
+Also, units for density!]} \{ $\Sigma_{\circ,\mathrm{Ring6}}=8\times10^{12}$, $\Sigma_{\circ,\mathrm{Ring13}}=4.2\times10^{13}$\} for both components separately.
 
-For Ring24 we used the same power law than the inner disc but scaled by a $\delta_{\mathrm{sd}}$ factor:
+For Ring24 we used the same power law \st{than} \phil{as for} the inner disc but scaled by \st{a $\delta_{\mathrm{sd}}$ factor} \phil{an empirically obtained factor, $\delta_{\mathrm{sd}}$= 5.3$\times 10^4$}:
 \begin{equation}
@@
 \end{equation}
-with $\delta_{\mathrm{sd}}$ = 5.3$\times 10^4$.
-But the inner wall of Ring24 follows a different behaviour.
-Between $R_\mathrm{in}$ and $R_\mathrm{peak}$, which respectively mark  the beginning and the maximum density peak of the outer ring, the gas density profile is multiplied by an additional factor
+\st{with $\delta_{\mathrm{sd}}$ = 5.3$\times 10^4$.} \st{But the inner wall} \phil{The inner edge} of Ring24 follows a different \st{behaviour} \phil{profile}.
+Between $R_\mathrm{in}$ and $R_\mathrm{peak}$, which respectively mark  the \st{beginning} \phil{inner edge} and the \phil{location of} maximum density \st{peak} of the outer ring, the gas density profile is multiplied by an additional factor
 \begin{equation}
@@
 \end{equation}
-This parameter allow us to model a smoother inner wall of the outer ring, with $R_\mathrm{in,gas}$ = 18.\,au and $R_\mathrm{peak,gas}$ = 26.8\,au.
+This parameter \st{allow} \phil{allows} us to model a smoother inner \st{wall} \phil{edge} of the outer ring, with $R_\mathrm{in,gas}$ = \st{18.\,au} \phil{18.0\,au} and $R_\mathrm{peak,gas}$ = 26.8\,au.
 This factor is also applied to the large dust population with $R_\mathrm{in,ld}$ = 24.7\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$.
@@
 Since the large dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a large inner cavity, a larger gap between the rings and a break in the outer ring.
-We also truncated the model large-grain density at 64\,au.
-The large-dust surface density profile is defined by the sum of its two components
+We also truncated the \st{model large-grain density} \phil{profile of large dust grains} at 64\,au.
+\st{The large-dust surface density profile is} \phil{It is then} defined by the sum of its two components
 \begin{equation}
@@
 
-For the inner ring, we chose a Gaussian profile parameterized with centroid radius $\mu_{\mathrm{Ring13, ld}}=13.38$\,au, ring width of $\sigma_{\mathrm{Ring13,ld}}=0.54$\,au and $\Sigma_{\circ,\mathrm{Ring13,ld}}=3\times10^{13}$.
-For Ring24 we used the same profile of the gas, but with the difference that, in an effort to recreate the break seen in the outer ring, we chose different values for $\gamma$ = -5 and $R_c$ = 38\,au between 28.6 and 35.6\,au.
-The surface density of the outer ring of large grains dust is thus given by
+For the inner ring, we \st{chose} \phil{choose} a Gaussian profile parameterized with centroid radius $\mu_{\mathrm{Ring13, ld}}=13.38$\,au, ring width of $\sigma_{\mathrm{Ring13,ld}}=0.54$\,au and $\Sigma_{\circ,\mathrm{Ring13,ld}}=3\times10^{13}$.
+For Ring24 we used the same profile \st{of} \phil{as for} the gas, but with the difference that, in an effort to recreate the break seen in the outer ring, we \st{chose} \phil{choose} different values for \st{$\gamma$ = -5} \phil{$\gamma = -5$} and $R_c$ = 38\,au between 28.6 and 35.6\,au.
+The surface density \st{of the outer ring of large grains dust} \phil{for large dust grains in the outer ring} is thus given by
 \begin{equation}
@@
   2.78 \times10^{4} & 28.6 < r < 37\text{\,au} \\
-  2.14 \times10^{5} & 37   < r < 64\text{\,au.} \\
+  2 .14 \times10^{5} & 37   < r < 64\text{\,au.} \\
   \end{cases}
@@
 
-The two different populations of dust grains correspond to small grains, with radii ranging from 0.4 to 1.5\,$\micron$, and large dust grains, with radii from 0.4\,$\micron$ to 10\,mm.
+The two different populations of dust grains correspond to small grains, with radii ranging from 0.4\phil{\,$\micron$} to 1.5\,$\micron$, and large dust grains, with radii from 0.4\,$\micron$ to 10\,mm.
 We computed the dust opacities using the {\tt bhmie} code provided in the \textsc{radmc3d} package, with a mix composed of 60\% silicate, 20\% graphite and 20\% ice.
@@
 The simulated DPI image at 1.65\,$\micron$ in Fig.~\ref{fig:images_vs_simulated} was obtained with the scattering matrix calculated by the {\tt makeopac.py} script provided in the \textsc{radmc3d} package.
-As a way of reproducing the \textit{H}-band image, we used a different grain size distribution, where we used a Gaussian distribution centred at 0.4\,$\micron$ but  smeared out by 30\%, and with 20 grain size bins within that range.
+As a way of reproducing the \textit{H}-band image, we used a different grain size distribution, where we \st{used} \phil{centred} a Gaussian \st{distribution} \st{centred} at 0.4\,$\micron$ \st{but} \phil{,}  smeared out by 30\%, and \phil{distributed over 20 bins within that range} \st{with 20 grain size bins within that range}.
 This distribution applies only to generate the NIR $Q_\phi$ image.
@@
 	\includegraphics[width=\columnwidth]{allprofiles.png}
-        \caption{{\bf Top:} surface density profiles for the gas, the large and small grain populations.
+        \caption{{\bf Top:} surface density profiles for \st{the} gas, \st{the}large and small \phil{dust grains} \st{grain populations}.
 {\bf Bottom:} Aspect ratio profile $h(r)= H(r)/r$.
-The dashed lines crossing both panels correspond to transition radii in the parametric model.}
+The \st{dashed} \phil{dotted} lines crossing both panels correspond to transition radii in the parametric model.}
     \label{fig:profiles}
@@
 
-The inner radius of the model grid was set to 0.1\,au,  and the outer radius of 100\,au, which is large enough for the dust disc to become undetectable.
-We set the values of the inclination an disc  position angle as the same as those obtained from the ALMA observation in Section~\ref{sec:Observations}, so the model has an inclination of i = 32.96\,$\degr$ and a P.A.
+The inner radius of the model grid was set to 0.1\,au,  and the outer radius \st{of} \phil{to} 100\,au, which is large enough for the dust disc to \st{become} \phil{be} undetectable.
+We set the values of the inclination \st{an} \phil{and} disc position angle \phil{to} \st{as} the same as \st{those} obtained from the ALMA observation in Section~\ref{sec:Observations}, \st{so} \phil{such that} the model has an inclination of i = 32.96\,$\degr$ and a P.A.
 = 77.31\,$\degr$.
-Finally, the distance is set at d = 72.4\,pc \citep{Gaia}.
+Finally, the distance is set \st{at} \phil{to} d = 72.4\,pc \citep{Gaia}.
 
@@
 The simulated image at 1.65\,$\micron$ shows a similar radial structure to the one visible in the observations, displaying a two ringed disc, where Ring6 hides under the artificial coronagraph.
-The visible asymmetry in the SPHERE observations is reproduced using relative large grains, $\sim$0.4\,$\micron$, as smaller grains did not result in such strong forward scattering.
-As \citet{refId0} states, this forward scattering peak that is present in the observation may indicate that the dust grains in the disk surface are large, suggesting that the disc is depleted of very-small grains.
+The visible asymmetry in the SPHERE observations is reproduced using \st{relative} \phil{relatively} large grains, $\sim$0.4\,$\micron$, as smaller grains did not result in such strong forward scattering.
+As \citet{refId0} \phil{[This citation looks strange, the T.
+should not be there]} \st{states} \phil{state}, this forward scattering peak \st{that is} present in the observation may indicate that the dust grains in the disk surface are \phil{relatively} large, suggesting that the disc is depleted of very-small grains.
 Interestingly, the model accurately shows the shadows described by \citet{dOrazi} that are present in the SPHERE-IRDIS image.
@@
 As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.~\ref{fig:radprofiles}), we can assume that the model provides a possible approximation of the disc structure, including the dimensions of Ring13.
-Accordingly, taking the parametric model values for Ring13 we have that it has a radius of 13.36\,au, a FWHM of 1.30\,au, and a scale height FWHM of the millimetre-size dust of 0.65\,au.
+Accordingly, taking the parametric model values for Ring13 \st{we have that} \phil{,} it has a radius of 13.36\,au, a FWHM of 1.30\,au, and a scale height FWHM of the millimetre-size dust of 0.65\,au.
 The total dust mass of Ring13 is about 1.1\,M$_{\earth}$ in the model.
-In turn, in our model Ring24 reaches peak intensity at $\sim$30\,au, then breaks at $\sim$36\,au, as in the observations, and has a total dust mass of $\sim$50\,M$_{\earth}$.
+In turn, \st{in} our model \phil{reproduces the observations of} Ring24 \st{reaches} \phil{with} peak intensity at $\sim$30\,au, \st{then breaks} \phil{and break} at $\sim$36\,au\st{, as in the observations, and has}\phil{.
+It contains} a total dust mass of $\sim$50\,M$_{\earth}$.
 The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.06\,au difference in the centroid location of the ring, and a 0.2\,au difference in the width estimation.
-Using the large grains scale height of 0.31\,au at Ring13, and a measured width of 1.50\,au, the ring is $\sim$4.8 times more extended  radially than vertically.
+Using the large \st{grains} \phil{grains'} scale height \phil{at Ring13} of 0.31\,au \st{at Ring13}, and a measured width of 1.50\,au, the ring is $\sim$4.8 times more extended  radially than vertically.
 
@@
 
-*****
 The effective beam size of the presented ALMA observations marginally resolves the width of Ring13 to be $w_\mathrm{d} = 1.50\mathrm{au}$.
@@
 
-Similarly to \citet{2018ApJ...869L..46D}, the ratio between dust and gas ring width can be linked to important properties:
-\begin{equation}\label{eq:ringwidth}
-        \frac{w_\mathrm{d}}{w_\mathrm{g}} = \sqrt{\frac{\alpha}{\alpha+\mathrm{St}}}\,,
-\end{equation}
-where we  assumed the turbulent diffusivity to be equal to the turbulent viscosity $\alpha$, and $\mathrm{St}$ is the dimensionless Stokes number.
-Assuming that the most relevant grain size for observations at a wavelength $\lambda$ corresponds to $a = \lambda_{\mathrm{obs}}/(2 \pi)$, and estimating the gas surface density within Ring13 from the RT model to be roughly $0.5\,\mathrm{g}/\mathrm{cm}^2$, yields $\mathrm{St}\approx 2$.
-With these considerations, equation~\ref{eq:ringwidth} provides a value of $\alpha \approx 0.1$ for the level of turbulent viscosity.
-We emphasise that this relies on rough estimates and is additionally restricted to the area within Ring13.
-Yet, its moderate value agrees with the limit \citet{2018ApJ...869L..46D} inferred from multiple dust rings at larger orbital distances ($\alpha \gtrsim 5\times10^{-4}$).
-Further, it is also consistent with the non-detection of non-thermal broadening of CO lines reported by \citet{Flaherty_2020}, from which the authors deduced an upper limit of $\alpha \lesssim 10^{-3}$ at the midplane of V4046\,Sgr.
-NOT*****
+\textit{Even though the radial spread of large dust grains in Ring13 appears to be quite thin, the width in comparison to the sub-lying gas profile speaks for the presence of non-negligible turbulent diffusion.
+Following a similar ring analysis as in \citet{2018ApJ...869L..46D}, we find that the ratio between the dimensionless diffusion parameter, $\alpha_{\rm diff}$, and the dimensionless Stokes number, St, (which parameterizes the dynamical behaviour of a grain) is roughly, $\alpha_{\rm diff}/{\rm St}\approx 0.1$.
+The observed signal is expected to be dominated by grains of size $a\approx 0.02\,{\rm cm}$, the RT model prescribes a gas density of $\Sigma_{\rm g} \approx 0.5\,{\rm g}{\rm cm}^{-2}$ to the location of Ring13.
+With these values, the relevant Stokes number is estimated to be St$\approx 0.1$.
+This yields an estimated level of diffusivity, $\alpha_{\rm diff}\approx 0.01$, and further provides a value for the level of turbulence, $\alpha$, in Ring13, as it is typically assumed to be equal to the level of diffusion \citep{2007Icar..192..588Y}.
+We note, that the obtained value of $\alpha \approx 0.01$ is larger than typical expectations \citep[e.g.][]{Flaherty_2020} and relies on not very well-constrained estimates of the gas density, as well as the fact that the width of Ring13 is measured at different vertical positions for small and large grains.}
 
@@
 %and we may have detected this ring in the ALMA image, if this ring is lopsided or shadowed by the secondary. 
-Ring6 may be just artificial and not a real prediction, as a thin ring like the one needed would trap millimetre-size dust grains, while  those grains are not present in the ALMA observation.
+Ring6 may be just artificial and not a real prediction, as a thin ring like the one \st{needed} \phil{we implemented} would \phil{be expected to} trap millimetre-size dust grains, while those grains are not present in the ALMA observation.
 

### 2020-12-06 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 The steeply decreasing brightness of Ring24 breaks at $\sim$35\,au into a shallow tail.
-In order to reproduce the SED, the model that we propose requires an inner ring at $\sim$6\,au (Ring6) in small dust grains, hiding under the IRDIS coronagraph, and that surrounds an inner circumbinary disc.
-Faint mm-continuum close ($\sim0\farcs02 $ ****GIVE ERRORS***) to the stellar position is picked up by ALMA.
+In order to reproduce the SED, the model that we propose requires an inner ring at $\sim$6\,au (Ring6) composed of small dust grains, hiding under the IRDIS coronagraph, and surrounding an inner circumbinary disc.
+Faint mm-continuum close ($0\farcs012\pm0\farcs002$) to the stellar position is picked up by ALMA.
 The surprisingly thin Ring13 is nonetheless roughly 5 times wider than the model scale height, and could thus be long-lived.
@@
 
-V4046\,Sgr was observed in differential polarization imaging (DPI) mode with SPHERE/IRDIS on March 13, 2016 \citep[see][for details]{Avenhaus_2018}.
+V4046\,Sgr was observed in differential polarization imaging (DPI) mode with SPHERE-IRDIS on March 13, 2016 \citep[see][for details]{Avenhaus_2018}.
 Here we use a new reduction of the $H$ band data produced with the IRDAP pipeline \citep{2020A&A...633A..64V}, which can separate stellar and instrumental polarization.
@@
 
-The resulting {\tt uvmem} image shown in Fig.~\ref{fig:images_vs_simulated} exhibits previously unseen substructure of the disc.
+The resulting {\tt uvmem} image shown in the top right panel of Fig.~\ref{fig:images_vs_simulated} exhibits previously unseen substructure of the disc.
 This image reveals that the disc features two rings of large dust grains with a broad gap between them, i.e.
@@
   \includegraphics[width=\textwidth]{hot_two_E.pdf}
-  \caption{Comparison of observations and simulated images at 1.65\,$\micron$ and 1.3 mm continuum of the circumbinary disc orbiting V4046\,Sgr.
-From top to bottom: DPI image and ALMA Band 6 observations; simulated images of the parametric model.
-Top left panel: SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that represents the N\_ALC\_YJH\_S coronagraph with a radius of $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc.
-Top right panel: 1.3\,mm continuum {\tt uvmem} model image.
+  \caption{Comparison of observations (top) and simulated images (bottom) at 1.65\,$\micron$ (left) and 1.3\,mm continuum (right) of the circumbinary disc orbiting V4046\,Sgr.
+\textit{Top left panel:} SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that represents the N\_ALC\_YJH\_S coronagraph with a radius of $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc.
+\textit{Top right panel:} 1.3\,mm continuum {\tt uvmem} model image.
 The yellow ellipse shows the size of the natural-weighted beam ($ 0\farcs062 \, \times \, 0\farcs055$), and the small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs035 \, \times \, \sim0\farcs031$).
-The inset zooms into the central emission, and the green star marks the star positions.
-Bottom left panel: synthetic image at 1.65\,$\upmu m$.
-Bottom right panel: synthetic image at 1.3\,mm.
+The inset zooms into the central emission, and the green star marks the binary position.
+\textit{Bottom left panel:} synthetic image at 1.65\,$\micron$.
+\textit{Bottom right panel:} synthetic image at 1.3\,mm.
 .
@@
 The offset of the center of the cavity and the nominal stellar positions is entirely consistent with a pointing error, since the pointing accuracy of ALMA is usually taken to be 1/10 of the natural-weights beam, at 1\,$\sigma$, or $\sim$6\,mas in this case.
-***ANTONIO PLEASE CONFIRM AND PROVIDE A REFERENCE ****
+***ANTONIO PLEASE CONFIRM AND PROVIDE A REFERENCE ***
 
@@
 Since this faint central emission is larger than the angular resolution, it is probably stemming from thermal emission from  large dust grains rather directly from the stars.
-The main blob of this dust structure is at a estimate distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.9\,au from the binary system, and may be part of inner disc introduced in the RT model to match the SED (see Sec.~\ref{sec:model} below).
+The main blob of this dust structure is at a estimate distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.9\,au from the binary system, and may be part of an inner disc introduced in the RT model to match the SED (see Sec.~\ref{sec:model} below).
 
@@
 
-The scattered-light image shown in Fig.~\ref{fig:images_vs_simulated} also shows a double ring structure in the micron-sized dust distribution.
+The scattered-light image in the top left panel of Fig.~\ref{fig:images_vs_simulated} also shows a double ring structure in the micron-sized dust distribution.
 The observed morphology presents an inner cavity of $\sim$10\,au in radius and two rings located at 14.10$\pm$0.01, coincident with Ring13, and 24.62$\pm$0.08\,au, coincident with Ring24, with a small gap between them at $\sim$20\,au.
@@
 
-The stars were modeled using two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C}, with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of $\mathrm{log}(\,\dot{\mathrm{M}/(\mathrm{M}_{\sun}\,\mathrm{yr^{-1}})}) = -$9.3 for both cases to include excess UV due to stellar accretion \citep{10.1111/j.1365-2966.2011.19366.x}.
+The stars were modeled using two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C}, with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of $\mathrm{log}(\,\dot{\mathrm{M}}/(\mathrm{M}_{\sun}\,\mathrm{yr^{-1}}) = -$9.3 for both cases to include excess UV due to stellar accretion \citep{10.1111/j.1365-2966.2011.19366.x}.
 The stars were placed at a mutual separation of 0.041\,au, so that their centre of mass coincides with the origin, and oriented at a PA of 250\,$\degr$, so that the secondary lies to the NWW from the primary, thus casting the same shadow as observed by \citet{dOrazi}.
@@
 Reproducing the radial and vertical structure of the V4046\,Sgr disc turned out to be challenging.
-We built the model in terms of the gas distribution, and with two different dust populations: larger grains that are vertically settled and dominate the total dust mass, and a population of smaller grains that are uniformly mixed with the gas and reach larger heights above the mid-plane.
+We built the model in terms of the gas distribution, and with two different dust populations: larger grains that are vertically settled and dominate the total dust mass, and a population of smaller grains that are uniformly mixed with the gas and reach higher regions above the mid-plane.
 
@@
 \end{equation}
-where $H_\circ$ is the scale height at r = $r_\circ$, $\psi$ is the flaring index and $\chi$ is a scaling factor (in the range $0-1$) that mimics dust settling.
-The gas and the small dust grains have no settling, so $\chi_{gas}$ = 1.
-The radial spread of Ring13 appears about five times wider in the gas-tracing NIR observations than in the fluxes received from larger grains with ALMA.
-We assume that the same ratio holds in the vertical direction (due to the settling of larger grains towards the disk's midplane), leading to $\chi_{ld}=1/5$.
+where $H_\circ$ is the scale height at $r$ = $r_\circ$, $\psi$ is the flaring index and $\chi$ is a scaling factor (in the range $0-1$) that mimics dust settling.
+The gas and the small dust (sd) grains have no settling, so $\chi_{\mathrm{gas}}$ = $\chi_{\mathrm{sd}}$ = 1.
+The radial spread of Ring13 appears about three times wider in the gas-tracing NIR observations than in the fluxes received from larger grains with ALMA.
+We assume that the same ratio holds in the vertical direction (due to the settling of larger grains towards the disk's midplane), leading to $\chi_{\mathrm{ld}}=0.3$.
 
 For the vertical structure, \citet{dOrazi} found flaring angles of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one.
-Our model uses the same values, with two different flaring indexes $\psi$.
-The separation between the two values were set at $r$ = 18\,au with $\psi=0.15$ for Ring6 and Ring13, and $\psi=0.5$ for Ring24.
-The scale height is $H_\circ = 0.45$\,au at $r_\circ = 18$\,au.
+Our model uses the same values, with two different flaring indices, $\psi_1$ and $\psi_2$.
+The separation between the two values were set at $r = 18$\,au with $\psi_1=0.15$ for Ring6 and Ring13, and $\psi_2=0.5$ for Ring24.
+The scale height is $H_\circ = 0.67$\,au at $r_\circ = 18$\,au.
 
-We propose a three ringed structure, so we defined the total gas surface density by a combination of four individual components: the inner disc, Ring6, Ring13 and Ring24.
-The total gas surface density is then  given  by:
+We propose a three ringed structure to reproduce the observations.
+We separate the disk into four individual regions: the inner disc, Ring6, Ring13 and Ring24.
+The combined gas surface density profile is then given by:
 \begin{equation}
@@
 \end{equation}
-where $R_c$ is a characteristic radius and $\gamma$ is the surface density gradient.
-We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =2.7\times10^{-4}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
-The gas surface density begin at 0.3\,au, out of the zone expected to be cleared by dynamical interactions with the central binary \citep{Art_Lu}, which is expected to be $\sim$0.2\,au.
+where $R_c$ is a characteristic radius and $\gamma$ is the surface density power-law index.
+We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =2.8\times10^{-4}$\,$\mathrm{g\,cm^{-3}}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
+Our model extends from 0.3\,au outwards, as the interior is expected to be cleared by dynamical effects of the central binary \citep{Art_Lu}
 
-We chose to use Gaussian profiles to parameterize Ring6 and Ring13,
+We choose to use Gaussian profiles to parameterize Ring6 and Ring13,
 \begin{equation}
@@
 \end{equation}
-where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring6}}=5.5$\,au, $\mu_{\mathrm{Ring13}}=15$\,au\}, ring widths \{$\sigma_{\mathrm{Ring6}}=1$\,au, $\sigma_{\mathrm{Ring13}}=2.05$\,au\}, and normalizations \{ $\Sigma_{\circ,\mathrm{Ring6}}=8\times10^{12}$, $\Sigma_{\circ,\mathrm{Ring13}}=4.2\times10^{13}$\} for both components separately.
+where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring6}}=5.5$\,au, $\mu_{\mathrm{Ring13}}=15$\,au\}, ring widths \{$\sigma_{\mathrm{Ring6}}=1$\,au, $\sigma_{\mathrm{Ring13}}=2.26$\,au\}, and normalizations \{$\Sigma_{\circ,\mathrm{Ring6}}=8\times10^{12}$\,$\mathrm{au\,g\,cm^{-3}}$, $\Sigma_{\circ,\mathrm{Ring13}}=4.2\times10^{13}$\,$\mathrm{au\,g\,cm^{-3}}$\} for both components separately.
 
-For Ring24 we used the same power law than the inner disc but scaled by a $\delta_{\mathrm{sd}}$ factor:
+For Ring24 we used the same power law as for the inner disc but scaled by an empirically obtained factor, $\delta_{\mathrm{sd}}$= 4.9$\times 10^4$:
 \begin{equation}
@@
 \end{equation}
-with $\delta_{\mathrm{sd}}$ = 5.3$\times 10^4$.
-But the inner wall of Ring24 follows a different behaviour.
-Between $R_\mathrm{in}$ and $R_\mathrm{peak}$, which respectively mark  the beginning and the maximum density peak of the outer ring, the gas density profile is multiplied by an additional factor
+The inner edge of Ring24 follows a different profile.
+Between $R_\mathrm{in}$ and $R_\mathrm{peak}$, which respectively mark  the inner edge and the location of maximum density of the outer ring, the gas density profile is multiplied by an additional factor
 \begin{equation}
@@
 \end{equation}
-This parameter allow us to model a smoother inner wall of the outer ring, with $R_\mathrm{in,gas}$ = 18.\,au and $R_\mathrm{peak,gas}$ = 26.8\,au.
+This parameter allows us to model a smoother inner edge of the outer ring, with $R_\mathrm{in,gas}$ = 18.0\,au and $R_\mathrm{peak,gas}$ = 26.8\,au.
 This factor is also applied to the large dust population with $R_\mathrm{in,ld}$ = 24.7\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$.
@@
 Since the large dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a large inner cavity, a larger gap between the rings and a break in the outer ring.
-We also truncated the model large-grain density at 64\,au.
-The large-dust surface density profile is defined by the sum of its two components
+We also truncated the profile of large dust grains at 64\,au.
+It is then defined by the sum of its two components
 \begin{equation}
@@
 
-For the inner ring, we chose a Gaussian profile parameterized with centroid radius $\mu_{\mathrm{Ring13, ld}}=13.38$\,au, ring width of $\sigma_{\mathrm{Ring13,ld}}=0.54$\,au and $\Sigma_{\circ,\mathrm{Ring13,ld}}=3\times10^{13}$.
-For Ring24 we used the same profile of the gas, but with the difference that, in an effort to recreate the break seen in the outer ring, we chose different values for $\gamma$ = -5 and $R_c$ = 38\,au between 28.6 and 35.6\,au.
-The surface density of the outer ring of large grains dust is thus given by
+For the inner ring, we choose a Gaussian profile parameterized with centroid radius $\mu_{\mathrm{Ring13, ld}}=13.38$\,au, ring width of $\sigma_{\mathrm{Ring13,ld}}=0.54$\,au and $\Sigma_{\circ,\mathrm{Ring13,ld}}=3.27\times10^{13}$.
+For Ring24 we used the same profile as for the gas, but with the difference that, in an effort to recreate the break seen in the outer ring, we choose different values for $\gamma = -4$ and $R_c$ = 39\,au between 28.6 and 35.6\,au.
+The surface density for large dust grains in the outer ring is thus given by
 \begin{equation}
@@
   \begin{cases}
-  0                 & r < 24.6\text{\,au} \\
-  6.24 \times10^{4} & 24.6 < r < 28.6\text{\,au} \\
-  2.78 \times10^{4} & 28.6 < r < 37\text{\,au} \\
-  2.14 \times10^{5} & 37   < r < 64\text{\,au.} \\
+  0                 & r < 24.7\text{\,au} \\
+  6.13 \times10^{4} & 24.7 < r < 28.6\text{\,au} \\
+  2.34 \times10^{4} & 28.6 < r < 35.6\text{\,au} \\
+  2.10 \times10^{5} & 35.6 < r < 64\text{\,au.} \\
   \end{cases}
@@
 The simulated DPI image at 1.65\,$\micron$ in Fig.~\ref{fig:images_vs_simulated} was obtained with the scattering matrix calculated by the {\tt makeopac.py} script provided in the \textsc{radmc3d} package.
-As a way of reproducing the \textit{H}-band image, we used a different grain size distribution, where we used a Gaussian distribution centred at 0.4\,$\micron$ but  smeared out by 30\%, and with 20 grain size bins within that range.
+As a way of reproducing the \textit{H}-band image, we used a different grain size distribution, where we centred a Gaussian at 0.4\,$\micron$, smeared out by 30\%, and with distributed over 20 bins within that range.
 This distribution applies only to generate the NIR $Q_\phi$ image.
@@
 	\includegraphics[width=\columnwidth]{allprofiles.png}
-        \caption{{\bf Top:} surface density profiles for the gas, the large and small grain populations.
+        \caption{{\bf Top:} surface density profiles for gas, large and small dust grains.
 {\bf Bottom:} Aspect ratio profile $h(r)= H(r)/r$.
-The dashed lines crossing both panels correspond to transition radii in the parametric model.}
+The dotted lines crossing both panels correspond to transition radii in the parametric model.}
     \label{fig:profiles}
@@
 
-The inner radius of the model grid was set to 0.1\,au,  and the outer radius of 100\,au, which is large enough for the dust disc to become undetectable.
-We set the values of the inclination an disc  position angle as the same as those obtained from the ALMA observation in Section~\ref{sec:Observations}, so the model has an inclination of i = 32.96\,$\degr$ and a P.A.
+The inner radius of the model grid was set to 0.1\,au, and the outer radius to 100\,au, which is large enough for the dust disc to be undetectable.
+We set the values of the inclination and disc position angle to the same as obtained from the ALMA observation in Section~\ref{sec:Observations}, such that the model has an inclination of i = 32.96\,$\degr$ and a P.A.
 = 77.31\,$\degr$.
-Finally, the distance is set at d = 72.4\,pc \citep{Gaia}.
+Finally, the distance is set to d = 72.4\,pc \citep{Gaia}.
 
@@
 The simulated image at 1.65\,$\micron$ shows a similar radial structure to the one visible in the observations, displaying a two ringed disc, where Ring6 hides under the artificial coronagraph.
-The visible asymmetry in the SPHERE observations is reproduced using relative large grains, $\sim$0.4\,$\micron$, as smaller grains did not result in such strong forward scattering.
-As \citet{refId0} states, this forward scattering peak that is present in the observation may indicate that the dust grains in the disk surface are large, suggesting that the disc is depleted of very-small grains.
+The visible asymmetry in the SPHERE observations is reproduced using relatively large grains, $\sim$0.4\,$\micron$, as smaller grains did not result in such strong forward scattering.
+As \citet{refId0} state, this forward scattering peak that is present in the observation may indicate that the dust grains in the disk surface are relatively large, suggesting that the disc is depleted of very-small grains.
 Interestingly, the model accurately shows the shadows described by \citet{dOrazi} that are present in the SPHERE-IRDIS image.
@@
 As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.~\ref{fig:radprofiles}), we can assume that the model provides a possible approximation of the disc structure, including the dimensions of Ring13.
-Accordingly, taking the parametric model values for Ring13 we have that it has a radius of 13.36\,au, a FWHM of 1.30\,au, and a scale height FWHM of the millimetre-size dust of 0.65\,au.
-The total dust mass of Ring13 is about 1.1\,M$_{\earth}$ in the model.
-In turn, in our model Ring24 reaches peak intensity at $\sim$30\,au, then breaks at $\sim$36\,au, as in the observations, and has a total dust mass of $\sim$50\,M$_{\earth}$.
-The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.06\,au difference in the centroid location of the ring, and a 0.2\,au difference in the width estimation.
-Using the large grains scale height of 0.31\,au at Ring13, and a measured width of 1.50\,au, the ring is $\sim$4.8 times more extended  radially than vertically.
+Accordingly, taking the parametric model values for Ring13, it has a radius of 13.38\,au, a FWHM of 1.27\,au, and a scale height FWHM of the millimetre-size dust of 0.48\,au.
+The total dust mass of Ring13 is about 0.9\,M$_{\earth}$ in the model.
+In turn, our model reproduces the observations of Ring24 with peak intensity at $\sim$30\,au, and break at $\sim$36\,au.
+It contains a total dust mass of $\sim$35\,M$_{\earth}$.
+The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.06\,au difference in the centroid location of the ring, and a 0.23\,au difference in the width estimation.
+Using the large grains' scale height at Ring13 of 0.48\,au, and a measured width of 1.50\,au, the ring is $\sim$3.1 times more extended radially than vertically.
 
@@
 
-*****
 The effective beam size of the presented ALMA observations marginally resolves the width of Ring13 to be $w_\mathrm{d} = 1.50\mathrm{au}$.
-%The most suitable RT model demands a density distribution of small grains and gas that is radially more extended, with an approximate width of $7.5\mathrm{au}$.
-Although the RT model ascribed step functions to gas and dust densities, in a more physical scenario the density should roughly follow a Gaussian distribution.
-Using that the gas' Ring13-FWHM in the RT model corresponds to $w_\mathrm{g} = 4.83\mathrm{au}$, we can see that large dust grains have to be radially converged to explain the discrepancy.
+Using that the gas' Ring13-FWHM in the RT model corresponds to $w_\mathrm{g} = 5.32\mathrm{au}$, we can see that large dust grains have to be radially converged to explain the discrepancy.
 
-Similarly to \citet{2018ApJ...869L..46D}, the ratio between dust and gas ring width can be linked to important properties:
-\begin{equation}\label{eq:ringwidth}
-        \frac{w_\mathrm{d}}{w_\mathrm{g}} = \sqrt{\frac{\alpha}{\alpha+\mathrm{St}}}\,,
-\end{equation}
-where we  assumed the turbulent diffusivity to be equal to the turbulent viscosity $\alpha$, and $\mathrm{St}$ is the dimensionless Stokes number.
-Assuming that the most relevant grain size for observations at a wavelength $\lambda$ corresponds to $a = \lambda_{\mathrm{obs}}/(2 \pi)$, and estimating the gas surface density within Ring13 from the RT model to be roughly $0.5\,\mathrm{g}/\mathrm{cm}^2$, yields $\mathrm{St}\approx 2$.
-With these considerations, equation~\ref{eq:ringwidth} provides a value of $\alpha \approx 0.1$ for the level of turbulent viscosity.
-We emphasise that this relies on rough estimates and is additionally restricted to the area within Ring13.
-Yet, its moderate value agrees with the limit \citet{2018ApJ...869L..46D} inferred from multiple dust rings at larger orbital distances ($\alpha \gtrsim 5\times10^{-4}$).
-Further, it is also consistent with the non-detection of non-thermal broadening of CO lines reported by \citet{Flaherty_2020}, from which the authors deduced an upper limit of $\alpha \lesssim 10^{-3}$ at the midplane of V4046\,Sgr.
-NOT*****
+Even though the radial spread of large dust grains in Ring13 appears to be quite thin, the width in comparison to the sub-lying gas profile speaks for the presence of non-negligible turbulent diffusion.
+Following a similar ring analysis as in \citet{2018ApJ...869L..46D}, we find that the ratio between the dimensionless diffusion parameter, $\alpha_{\rm diff}$, and the dimensionless Stokes number, St, (which parameterizes the dynamical behaviour of a grain) is roughly, $\alpha_{\rm diff}/{\rm St}\approx 0.1$.
+The observed signal is expected to be dominated by grains of size $a\approx 0.02\,{\rm cm}$, the RT model prescribes a gas density of $\Sigma_{\rm g} \approx 0.5\,{\rm g}{\rm cm}^{-2}$ to the location of Ring13.
+With these values, the relevant Stokes number is estimated to be St$\approx 0.1$.
+This yields an estimated level of diffusivity, $\alpha_{\rm diff}\approx 0.01$, and further provides a value for the level of turbulence, $\alpha$, in Ring13, as it is typically assumed to be equal to the level of diffusion \citep{2007Icar..192..588Y}.
+We note, that the obtained value of $\alpha \approx 0.01$ is larger than typical expectations \citep[e.g.][]{Flaherty_2020} and relies on not very well-constrained estimates of the gas density, as well as the fact that the width of Ring13 is measured at different vertical positions for small and large grains.
 
@@
 %and we may have detected this ring in the ALMA image, if this ring is lopsided or shadowed by the secondary. 
-Ring6 may be just artificial and not a real prediction, as a thin ring like the one needed would trap millimetre-size dust grains, while  those grains are not present in the ALMA observation.
+Ring6 may be just artificial and not a real prediction, as a thin ring like the one we implemented would be expected to trap millimetre-size dust grains, while those grains are not present in the ALMA observation.
 
@@
   \item We report the detection of a narrow ring in the 1.3\,mm continuum, with a radius 13.32$\pm$0.26\,au and an estimated width of 1.50$\pm$0.72\,au.
-The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes around 1.1\,M$_{\earth}$ millimetre-sized grains.
-Using the parametric model scale height value ($H= $ 0.31\,au at 13.32\,au) we have that the ring width is roughly 4.8 times its estimated height.
+The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes around 0.9\,M$_{\earth}$ millimetre-sized grains.
+Using the parametric model scale height value ($H= $ 0.48\,au at 13.32\,au) we have that the ring width is roughly 3.1 times its estimated height.
 
-  \item The 1.3\,mm outer ring, that starts at $\sim$24\,au and has its peak intensity at $\sim$30\,au, presents a visible break in the surface brightness at $\sim$35\,au.
+  \item The 1.3\,mm outer ring, that starts at $\sim$24\,au and has its peak intensity at $\sim$30\,au, presents a visible break in the surface brightness at $\sim$36\,au.
 
@@
 
-\section*{Data Availability}
+%\section*{Data Availability}
 

### 2020-12-07 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 
-Even though the radial spread of large dust grains in Ring13 appears to be quite thin, the width in comparison to the sub-lying gas profile speaks for the presence of non-negligible turbulent diffusion.
-Following a similar ring analysis as in \citet{2018ApJ...869L..46D}, we find that the ratio between the dimensionless diffusion parameter, $\alpha_{\rm diff}$, and the dimensionless Stokes number, St, (which parameterizes the dynamical behaviour of a grain) is roughly, $\alpha_{\rm diff}/{\rm St}\approx 0.1$.
+Even though the radial spread of large dust grains in Ring13 appears to be quite thin, the width in comparison to the sub-lying gas profile speaks for the presence of considerable turbulent diffusion.
+Following a similar ring analysis as in \citet{2018ApJ...869L..46D}, we find that the ratio between the dimensionless diffusion parameter, $D$, and the dimensionless Stokes number, St, (which parameterizes the dynamical behaviour of a grain) is roughly, $D/{\rm St}\approx 0.1$.
 The observed signal is expected to be dominated by grains of size $a\approx 0.02\,{\rm cm}$, the RT model prescribes a gas density of $\Sigma_{\rm g} \approx 0.5\,{\rm g}{\rm cm}^{-2}$ to the location of Ring13.
-With these values, the relevant Stokes number is estimated to be St$\approx 0.1$.
-This yields an estimated level of diffusivity, $\alpha_{\rm diff}\approx 0.01$, and further provides a value for the level of turbulence, $\alpha$, in Ring13, as it is typically assumed to be equal to the level of diffusion \citep{2007Icar..192..588Y}.
-We note, that the obtained value of $\alpha \approx 0.01$ is larger than typical expectations \citep[e.g.][]{Flaherty_2020} and relies on not very well-constrained estimates of the gas density, as well as the fact that the width of Ring13 is measured at different vertical positions for small and large grains.
+With these values, the relevant Stokes number is approximated to be St$\approx 0.1$.
+This yields an estimate for the level of diffusivity of $D\approx 0.01$.
+It further provides a value for the level of turbulence in Ring13, $\alpha_{\rm turb}\approx 0.01$, assuming turbulence to be equal to the level of diffusion \citep{2007Icar..192..588Y}.
+We note, that the obtained value for $\alpha_{\rm turb}$ is larger than typical expectations \citep[e.g.][for V4046 Sgr]{Flaherty_2020} and carries uncertainties originating from estimates of the local gas density, as well as the fact that the width of Ring13 is measured at different vertical positions for small and large grains in the observations.
 

### 2021-01-18 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 We present high resolution ($\sim$20--50\,mas) ALMA observations of the 1.3\,mm  continuum which, combined with SPHERE-IRDIS polarized images and a well-sampled spectral energy distribution (SED), allow us to propose a physical model for the source using radiative transfer (RT) predictions.
-The new ALMA data reveal a very thin ring at a radius of 13.32$\pm$0.26\,au (Ring13), with a marginally resolved radial width of 1.50$\pm$0.72\,au.
+The new ALMA data reveal a very thin ring at a radius of 13.15$\pm$0.26\,au (Ring13), with a marginally resolved radial width of 2.46$\pm$0.56\,au.
 Ring13 is surrounded by a $\sim$10\,au-wide gap, and it is flanked by a very mm-bright outer ring (Ring24) with a sharp inner edge at 24\,au.
 The steeply decreasing brightness of Ring24 breaks at $\sim$35\,au into a shallow tail.
-In order to reproduce the SED, the model that we propose requires an inner ring at $\sim$6\,au (Ring6) composed of small dust grains, hiding under the IRDIS coronagraph, and surrounding an inner circumbinary disc.
+In order to reproduce the SED, the model that we propose requires an inner ring at $\sim$6\,au (Ring5) composed mainly of small dust grains, hiding under the IRDIS coronagraph, and surrounding an inner circumbinary disc.
 Faint mm-continuum close ($0\farcs012\pm0\farcs002$) to the stellar position is picked up by ALMA.
-The surprisingly thin Ring13 is nonetheless roughly 5 times wider than the model scale height, and could thus be long-lived.
+The surprisingly thin Ring13 is nonetheless roughly 4 times wider than the model scale height, and could thus be long-lived.
 The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$.
@@
 V4046\,Sgr is a double-lined spectroscopic binary of K-type stars (K5 and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012}, on a close ($a \approx 0.041$\,au), circular ($e\leq0.01$) orbit, with an orbital period of 2.42 days \citep{2000IAUS..200P..28Q}.
-It is a member of the $\beta$ Pictoris moving group \citep{Zuckerman_2004}, with an estimated age of 23$\pm$3\,Myr \citep{Mamajek_2014}, and its distance is 72.41$\pm$0.34\,pc \citep{Gaia}.
+It is a member of the $\beta$ Pictoris moving group \citep{Zuckerman_2004}, with an estimated age of 23$\pm$3\,Myr \citep{Mamajek_2014}, and its distance is 71.48$\pm$0.11\,pc \citep{gaiacollaboration2020gaia}.
 V4046\,Sgr hosts a massive ($\sim$0.1\,M$_{\sun}$) circumbinary disc extending to $\sim$300\,au \citep{Rosenfeld_2013, Rodriguez_2010},  rich in diverse molecular lines \citep{Kastner_2018}.
@@
   \caption{Comparison of observations (top) and simulated images (bottom) at 1.65\,$\micron$ (left) and 1.3\,mm continuum (right) of the circumbinary disc orbiting V4046\,Sgr.
-\textit{Top left panel:} SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that represents the N\_ALC\_YJH\_S coronagraph with a radius of $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc.
+\textit{Top left panel:} SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that represents the N\_ALC\_YJH\_S coronagraph with a radius of $\sim0\farcs12$, or $\sim$8.6\,au at 71.48\,pc.
 \textit{Top right panel:} 1.3\,mm continuum {\tt uvmem} model image.
-The yellow ellipse shows the size of the natural-weighted beam ($ 0\farcs062 \, \times \, 0\farcs055$), and the small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs035 \, \times \, \sim0\farcs031$).
+The small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs021 \, \times \, \sim0\farcs018$).
 The inset zooms into the central emission, and the green star marks the binary position.
@@
 The ring width can be measured in polar coordinates by fitting 1-D Gaussians, thus obtaining a width and centroid at each azimuth.
-On average, we obtained a FWHM of 2.87$\pm$0.50\,au, and a stellocentric radius of 13.32$\pm$0.26\,au (See Fig.~\ref{fig:polarring}).
+On average, we obtained a FWHM of 2.83$\pm$0.50\,au, and a stellocentric radius of 13.15$\pm$0.26\,au (See Fig.~\ref{fig:polarring}).
 As the {\tt uvmem} model image has an effective angular resolution of $\sim$1/3 that of the natural-weighted beam ($0\farcs062 \,\times \, 0\farcs055$), we see that Ring13 is marginally resolved.
-After subtraction of the approximate {\tt uvmem} resolution ($\sim0\farcs035 \, \times \, \sim0\farcs031$), the ring width is $\sim$1.50$\pm$0.72\,au.
+After subtraction of the approximate {\tt uvmem} resolution ($\sim0\farcs021 \,\times \,\sim0\farcs018$), the ring width is $\sim$2.46$\pm$0.56\,au.
 
@@
 Since this faint central emission is larger than the angular resolution, it is probably stemming from thermal emission from  large dust grains rather directly from the stars.
-The main blob of this dust structure is at a estimate distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.9\,au from the binary system, and may be part of an inner disc introduced in the RT model to match the SED (see Sec.~\ref{sec:model} below).
-
-%match the small grain ring called Ring6 introduced in the RT model to match the SED (see Sec.\,\ref{sec:model} below).
-If so, then given that the binary phase at the time of the observations is PA=347\,$\degr$, so that the secondary lies roughly northwards of the primary, it may be that the northern side of Ring6 is shadowed, resulting in a seemingly lopsided geometry.
+The main blob of this dust structure is at a estimate distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.85$\pm$0.14\,au from the binary system, and, estimating its form as a Gaussian ellipse, it has a FWHM of $\sim$1.43\,au.
+If this feature is caused by the presence of millimeter-size dust, its estimated mass would be around 0.12\,M$_{\earth}$.
+%and may be part of an inner disc introduced in the RT model to match the SED (see Sec.~\ref{sec:model} below).
 
@@
 The gas and the small dust (sd) grains have no settling, so $\chi_{\mathrm{gas}}$ = $\chi_{\mathrm{sd}}$ = 1.
-The radial spread of Ring13 appears about three times wider in the gas-tracing NIR observations than in the fluxes received from larger grains with ALMA.
-We assume that the same ratio holds in the vertical direction (due to the settling of larger grains towards the disk's midplane), leading to $\chi_{\mathrm{ld}}=0.3$.
+The radial spread of Ring13 appears two to three times wider in the gas-tracing NIR observations than in the fluxes received from larger grains with ALMA.
+We assume that the same ratio holds in the vertical direction (due to the settling of larger grains towards the disc's midplane), leading to $\chi_{\mathrm{ld}}=0.4$.
 
@@
 Our model uses the same values, with two different flaring indices, $\psi_1$ and $\psi_2$.
-The separation between the two values were set at $r = 18$\,au with $\psi_1=0.15$ for Ring6 and Ring13, and $\psi_2=0.5$ for Ring24.
-The scale height is $H_\circ = 0.67$\,au at $r_\circ = 18$\,au.
+The separation between the two values were set at $r = 18$\,au with $\psi_1=0.2$ for Ring5 and Ring13, and $\psi_2=0.5$ for Ring24.
+The scale height is $H_\circ = 0.88$\,au at $r_\circ = 18$\,au.
 
 We propose a three ringed structure to reproduce the observations.
-We separate the disk into four individual regions: the inner disc, Ring6, Ring13 and Ring24.
+We separate the disc into four individual regions: the inner disc, Ring5, Ring13 and Ring24.
 The combined gas surface density profile is then given by:
 \begin{equation}
-  \Sigma_{\mathrm{gas}}(r) = \Sigma_{\mathrm{inner\,disc}} + \Sigma_{\mathrm{Ring6}} + \Sigma_{\mathrm{Ring13}} + \Sigma_{\mathrm{Ring24}}
+  \Sigma_{\mathrm{gas}}(r) = \Sigma_{\mathrm{inner\,disc}} + \Sigma_{\mathrm{Ring5}} + \Sigma_{\mathrm{Ring13}} + \Sigma_{\mathrm{Ring24}}
 \end{equation}
@@
 where $R_c$ is a characteristic radius and $\gamma$ is the surface density power-law index.
-We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =2.8\times10^{-4}$\,$\mathrm{g\,cm^{-3}}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
+We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =3.26\times10^{-4}$\,$\mathrm{g\,cm^{-3}}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
 Our model extends from 0.3\,au outwards, as the interior is expected to be cleared by dynamical effects of the central binary \citep{Art_Lu}
 
-We choose to use Gaussian profiles to parameterize Ring6 and Ring13,
+We choose to use Gaussian profiles to parameterize Ring5 and Ring13,
 \begin{equation}
-  \Sigma_{\mathrm{Ring}}(r) = \frac{\Sigma_\circ}{\sqrt{2 \pi} \sigma}
+  \Sigma_{\mathrm{ring}}(r) = \frac{\Sigma_\circ}{\sqrt{2 \pi} \sigma}
   \, \mathrm{exp}\left[-\frac{1}{2}\left(\frac{r-\mu}{\sigma}\right)^{2}\right],
 \end{equation}
-where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring6}}=5.5$\,au, $\mu_{\mathrm{Ring13}}=15$\,au\}, ring widths \{$\sigma_{\mathrm{Ring6}}=1$\,au, $\sigma_{\mathrm{Ring13}}=2.26$\,au\}, and normalizations \{$\Sigma_{\circ,\mathrm{Ring6}}=8\times10^{12}$\,$\mathrm{au\,g\,cm^{-3}}$, $\Sigma_{\circ,\mathrm{Ring13}}=4.2\times10^{13}$\,$\mathrm{au\,g\,cm^{-3}}$\} for both components separately.
+where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring5}}=5.5$\,au, $\mu_{\mathrm{Ring13}}=14.9$\,au\}, ring widths \{$\sigma_{\mathrm{Ring5}}=1$\,au, $\sigma_{\mathrm{Ring13}}=2.3$\,au\}, and normalizations \{$\Sigma_{\circ,\mathrm{Ring5}}=3.28$\,$\mathrm{au\,g\,cm^{-3}}$, $\Sigma_{\circ,\mathrm{Ring13}}=6 \times 10^{-1}$\,$\mathrm{au\,g\,cm^{-3}}$\} for both components separately.
 
-For Ring24 we used the same power law as for the inner disc but scaled by an empirically obtained factor, $\delta_{\mathrm{sd}}$= 4.9$\times 10^4$:
+For Ring24 we used the same power law as for the inner disc but scaled by an empirically obtained factor, $\delta_{\mathrm{sd}}$= 4.2$\times 10^4$:
 \begin{equation}
-  \Sigma_{\mathrm{Ring24}} = \Sigma_{\mathrm{inner\,disc}}(r)\, \delta_{\mathrm{sd}},
+  \Sigma_{\mathrm{Ring24}}(r) = \Sigma_{\mathrm{inner\,disc}}(r)\, \delta_{\mathrm{sd}},
 \end{equation}
@@
 \end{equation}
-This parameter allows us to model a smoother inner edge of the outer ring, with $R_\mathrm{in,gas}$ = 18.0\,au and $R_\mathrm{peak,gas}$ = 26.8\,au.
-This factor is also applied to the large dust population with $R_\mathrm{in,ld}$ = 24.7\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$.
+This parameter allows us to model a smoother inner edge of the outer ring, with $R_\mathrm{in,gas}$ = 18.0\,au and $R_\mathrm{peak,gas}$ = 26.4\,au.
+This factor is also applied to the large dust population with $R_\mathrm{in,ld}$ = 24.2\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$.
 
@@
 
-Since the large dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a large inner cavity, a larger gap between the rings and a break in the outer ring.
-We also truncated the profile of large dust grains at 64\,au.
-It is then defined by the sum of its two components
+Since the large dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a larger inner cavity, a larger gap between Ring13 and Ring24, and a break in the outer ring.
+To be consistent with the theory, Ring5 should have a small large-dust population too, but, as this ring is not visible in the ALMA observation, we added just the right mass to be undetectable by the ALMA observation.
+We also truncated the profile of large dust grains at 63\,au.
+It is then defined by the sum of its three components
 \begin{equation}
-  \Sigma_{\mathrm{ld}}(r) = 
+  \Sigma_{\mathrm{ld}}(r) = \Sigma_{\mathrm{Ring5,ld}} + 
   \Sigma_{\mathrm{Ring13,ld}} + \Sigma_{\mathrm{Ring24,ld}}.
@@
 
-For the inner ring, we choose a Gaussian profile parameterized with centroid radius $\mu_{\mathrm{Ring13, ld}}=13.38$\,au, ring width of $\sigma_{\mathrm{Ring13,ld}}=0.54$\,au and $\Sigma_{\circ,\mathrm{Ring13,ld}}=3.27\times10^{13}$.
-For Ring24 we used the same profile as for the gas, but with the difference that, in an effort to recreate the break seen in the outer ring, we choose different values for $\gamma = -4$ and $R_c$ = 39\,au between 28.6 and 35.6\,au.
+For Ring5 and Ring13, we choose Gaussian profiles parameterized with centroid radii $\mu_{\mathrm{Ring5, ld}}=5.5$\,au and $\mu_{\mathrm{Ring13, ld}}=13.22$\,au, ring widths of $\sigma_{\mathrm{Ring5,ld}}=0.4$\,au and $\sigma_{\mathrm{Ring13,ld}}=0.85$\,au, and normalizations $\Sigma_{\circ,\mathrm{Ring5,ld}}=1.34\times10^{-4}\,\mathrm{au\,g\,cm^{-3}}$ and $\Sigma_{\circ,\mathrm{Ring13,ld}}=2.41\,\mathrm{au\,g\,cm^{-3}}$.
+For Ring24 we used the same profile as for the gas, but with the difference that, in an effort to recreate the break seen in the outer ring, we choose different values for $\gamma = -3.5$ and $R_c$ = 39\,au between 27.9 and 35.3\,au.
 The surface density for large dust grains in the outer ring is thus given by
 \begin{equation}
-    \Sigma_{\mathrm{Ring24,ld}} = \Sigma_{\mathrm{c}} \left(\frac{r}{R_{\mathrm{c}}}\right)^{-\gamma} \exp\left[-\left(\frac{r}{R_{\mathrm{c}}}\right)^{2-\gamma}\right]\,\delta_{\mathrm{ld}}(r),
+    \Sigma_{\mathrm{Ring24,ld}}(r) = \Sigma_{\mathrm{c}} \left(\frac{r}{R_{\mathrm{c}}}\right)^{-\gamma} \exp\left[-\left(\frac{r}{R_{\mathrm{c}}}\right)^{2-\gamma}\right]\,\delta_{\mathrm{ld}}(r),
 \end{equation}
@@
   \begin{cases}
-  0                 & r < 24.7\text{\,au} \\
-  6.13 \times10^{4} & 24.7 < r < 28.6\text{\,au} \\
-  2.34 \times10^{4} & 28.6 < r < 35.6\text{\,au} \\
-  2.10 \times10^{5} & 35.6 < r < 64\text{\,au.} \\
+  0                 & r < 24.6\text{\,au} \\
+  7.19 \times10^{4} & 24.6 < r < 27.9\text{\,au} \\
+  3.17 \times10^{4} & 27.9 < r < 35.3\text{\,au} \\
+  2.65 \times10^{5} & 35.3 < r < 64\text{\,au.} \\
   \end{cases}
@@
 \begin{equation}
-\rho_{\mathrm{large-dust}}(r,z)=
+\rho_{\mathrm{large\,dust}}(r,z)=
 \frac{\Sigma_{\mathrm{ld}}(r)}{\sqrt{2\pi} \, H(r)} \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{H(r)}\right)^2\right] \, f_{\mathrm{ld}} \: \zeta .
@@
 
-The two different populations of dust grains correspond to small grains, with radii ranging from 0.4 to 1.5\,$\micron$, and large dust grains, with radii from 0.4\,$\micron$ to 10\,mm.
+The two different populations of dust grains correspond to small grains, with radii ranging from 0.3 to 1.5\,$\micron$, and large dust grains, with radii from 0.3\,$\micron$ to 10\,mm.
 We computed the dust opacities using the {\tt bhmie} code provided in the \textsc{radmc3d} package, with a mix composed of 60\% silicate, 20\% graphite and 20\% ice.
@@
 {\bf Bottom:} Aspect ratio profile $h(r)= H(r)/r$.
+The dashed brown line indicates the undetectable large grains in Ring5.
 The dotted lines crossing both panels correspond to transition radii in the parametric model.}
@@
 = 77.31\,$\degr$.
-Finally, the distance is set to d = 72.4\,pc \citep{Gaia}.
+Finally, the distance is set to d = 71.48\,pc \citep{gaiacollaboration2020gaia}.
 
@@
 
-The simulated image at 1.65\,$\micron$ shows a similar radial structure to the one visible in the observations, displaying a two ringed disc, where Ring6 hides under the artificial coronagraph.
+The simulated image at 1.65\,$\micron$ shows a similar radial structure to the one visible in the observations, displaying a two ringed disc, where Ring5 hides under the artificial coronagraph.
 The visible asymmetry in the SPHERE observations is reproduced using relatively large grains, $\sim$0.4\,$\micron$, as smaller grains did not result in such strong forward scattering.
-As \citet{refId0} state, this forward scattering peak that is present in the observation may indicate that the dust grains in the disk surface are relatively large, suggesting that the disc is depleted of very-small grains.
+As \citet{refId0} state, this forward scattering peak that is present in the observation may indicate that the dust grains in the disc surface are relatively large, suggesting that the disc is depleted of very-small grains.
 Interestingly, the model accurately shows the shadows described by \citet{dOrazi} that are present in the SPHERE-IRDIS image.
@@
     \caption{Comparison of the surface brightness profiles extracted from the deprojected synthetic images and observed \textit{H}-band and 1.3\,mm continuum images.
-The grey shaded area represents the radius of the artificial coronagraph used in the simulations (i.e., $\sim0\farcs 12$, or $\sim$8.6\,au at 72.4\,pc).}
+The grey shaded area represents the radius of the artificial coronagraph used in the simulations (i.e., $\sim0\farcs 1$, or $\sim$7.1\,au at 71.48\,pc).}
     \label{fig:radprofiles}
@@
 The simulated 1.3\,mm continuum image reproduces the two observed rings: the faint Ring13 and the brighter Ring24.
+The introduced Ring5 is not visible at the simulated image as its peak predicted intensities are around three times the noise in the ALMA image ($\sim1\times10^{-7}$\,Jy\,$\mathrm{beam}^{-1}$).
 As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.~\ref{fig:radprofiles}), we can assume that the model provides a possible approximation of the disc structure, including the dimensions of Ring13.
-Accordingly, taking the parametric model values for Ring13, it has a radius of 13.38\,au, a FWHM of 1.27\,au, and a scale height FWHM of the millimetre-size dust of 0.48\,au.
-The total dust mass of Ring13 is about 0.9\,M$_{\earth}$ in the model.
+Accordingly, taking the parametric model values for Ring13, it has a radius of 13.22\,au, a FWHM of 2.00\,au, and a scale height FWHM of the millimetre-size dust of 0.61\,au.
+The total dust mass of Ring13 is about 0.7\,M$_{\earth}$ in the model.
 In turn, our model reproduces the observations of Ring24 with peak intensity at $\sim$30\,au, and break at $\sim$36\,au.
-It contains a total dust mass of $\sim$35\,M$_{\earth}$.
-The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.06\,au difference in the centroid location of the ring, and a 0.23\,au difference in the width estimation.
-Using the large grains' scale height at Ring13 of 0.48\,au, and a measured width of 1.50\,au, the ring is $\sim$3.1 times more extended radially than vertically.
+It contains a total dust mass of $\sim$44\,M$_{\earth}$.
+The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.07\,au difference in the centroid location of the ring, and a 0.46\,au difference in the width estimation.
+Using the large grains' scale height at Ring13 of 0.61\,au, and a measured width of 2.46\,au, the ring is $\sim$4.1 times more extended radially than vertically.
 
@@
 
-The effective beam size of the presented ALMA observations marginally resolves the width of Ring13 to be $w_\mathrm{d} = 1.50\mathrm{au}$.
-Using that the gas' Ring13-FWHM in the RT model corresponds to $w_\mathrm{g} = 5.32\mathrm{au}$, we can see that large dust grains have to be radially converged to explain the discrepancy.
+The effective beam size of the presented ALMA observations marginally resolves the width of Ring13 to be $w_\mathrm{d} = 2.46\mathrm{au}$.
+Using that the gas' Ring13-FWHM in the RT model corresponds to $w_\mathrm{g} = 5.42\mathrm{au}$, we can see that large dust grains have to be radially converged to explain the discrepancy.
 
@@
 Following a similar ring analysis as in \citet{2018ApJ...869L..46D}, we find that the ratio between the dimensionless diffusion parameter, $D$, and the dimensionless Stokes number, St, (which parameterizes the dynamical behaviour of a grain) is roughly, $D/{\rm St}\approx 0.1$.
-The observed signal is expected to be dominated by grains of size $a\approx 0.02\,{\rm cm}$, the RT model prescribes a gas density of $\Sigma_{\rm g} \approx 0.5\,{\rm g}{\rm cm}^{-2}$ to the location of Ring13.
+The observed signal is expected to be dominated by grains of size $a\approx 0.02\,{\rm cm}$.
+The RT model, together with the dust-to-gas ratio of 0.05, prescribe a gas density of $\Sigma_{\rm g} \approx 0.5\,{\rm g}{\rm cm}^{-2}$ to the location of Ring13.
 With these values, the relevant Stokes number is approximated to be St$\approx 0.1$.
 This yields an estimate for the level of diffusivity of $D\approx 0.01$.
-It further provides a value for the level of turbulence in Ring13, $\alpha_{\rm turb}\approx 0.01$, assuming turbulence to be equal to the level of diffusion \citep{2007Icar..192..588Y}.
-We note, that the obtained value for $\alpha_{\rm turb}$ is larger than typical expectations \citep[e.g.][for V4046 Sgr]{Flaherty_2020} and carries uncertainties originating from estimates of the local gas density, as well as the fact that the width of Ring13 is measured at different vertical positions for small and large grains in the observations.
+It further provides a value for the level of turbulent viscosity in Ring13, $\alpha_{\rm turb}\approx 0.01$, assuming viscosity to be equal to the level of diffusion \citep{2007Icar..192..588Y}.
+We note that an observation of molecular line broadening has found no evidence for turbulent contributions, suggesting $\alpha_{\rm turb}<0.01$ (Flaherty et al.
+2020).
+The value inferred from our model is just within this limit.
+It is linearly proportional to the local dust-to-gas ratio (by our definition of the gas surface density profile) -- a standard ISM  value of 0.01 for the dust-to-gas ratio would thus lead to an expected level of turbulent viscosity of $\alpha_{\rm turb}\approx 5\times10^{-3}$.
+While the exact value for $\alpha_{\rm turb}$ is not well constrained, the presence of turbulence is a robust detection, as it is required to explain the radial spread of the resolved Ring13.
 
@@
 From the similarity with the data we propose that there has to be a small-grain population close to the stars down to 0.3\,au.
-The decision of employing the three ringed structure for the small dust grains relies on the fact that the SED needed a ring at a radius smaller than 10\,au to have a proper fit around 10\,$\micron$.
-%and we may have detected this ring in the ALMA image, if this ring is lopsided or shadowed by the secondary. 
-Ring6 may be just artificial and not a real prediction, as a thin ring like the one we implemented would be expected to trap millimetre-size dust grains, while those grains are not present in the ALMA observation.
+The observed blob in the ALMA observation can not be explained using a millimeter-sized dust population following the mass estimation in Section\,\ref{sec:Observations}, as it creates a larger excess in the 10$\,\micron$ that does not match the data.
+The decision of employing the three ringed structure (i.e.
+add Ring5 to the observed structure) relies on the fact that the SED needed a ring at a radius around 5--7\,au to have a proper fit around 10\,$\micron$.
+
+%Ring5 may be just artificial and not a real prediction, as a thin ring like the one we implemented would be expected to trap millimetre-size dust grains, while those grains are not present in the ALMA observation.
 
@@
 \begin{enumerate}
-  \item We report the detection of a narrow ring in the 1.3\,mm continuum, with a radius 13.32$\pm$0.26\,au and an estimated width of 1.50$\pm$0.72\,au.
-The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes around 0.9\,M$_{\earth}$ millimetre-sized grains.
-Using the parametric model scale height value ($H= $ 0.48\,au at 13.32\,au) we have that the ring width is roughly 3.1 times its estimated height.
+  \item We report the detection of a narrow ring in the 1.3\,mm continuum, with a radius 13.15$\pm$0.26\,au and an estimated width of 2.46$\pm$0.56\,au.
+The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes around 0.7\,M$_{\earth}$ millimetre-sized grains.
+Using the parametric model scale height value ($H= $ 0.60\,au at 13.15\,au) we have that the ring width is roughly 4 times its estimated height.
 
@@
 
-  \item Our parametric model, which accounts for the SED of the system, involves the existence of a sub-micron dust population close (<5\,au) to the stars.
+  \item Our parametric model, which accounts for the SED of the system, involves the existence of a sub-micron dust population close (<5\,au) to the stars and predicts the presence of an inner ring at $\sim$5\,au made mainly of small dust grains.
+
+  \item The resolved radial width of Ring13 speaks for the presence of a considerable level of turbulent viscosity.
 
@@
 This research has made use of the NASA/IPAC Infrared Science Archive, which is funded by the National Aeronautics and Space Administration and operated by the California Institute of Technology.
+
+S.P. acknowledges support from the Joint Committee of ESO and the Government of Chile and Fondecyt Regular grant 1191934.
 

### 2021-01-18 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 
-  \item Our parametric model, which accounts for the SED of the system, involves the existence of a sub-micron dust population close (<5\,au) to the stars and predicts the presence of an inner ring at $\sim$5\,au made mainly of small dust grains.
+  \item Our parametric model, which accounts for the SED of the system, involves the existence of a sub-micron dust population close (<5\,au) to the stars, and predicts the presence of another inner ring at $\sim$5\,au made mainly of small dust grains.
 

### 2021-01-18 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 The simulated 1.3\,mm continuum image reproduces the two observed rings: the faint Ring13 and the brighter Ring24.
-The introduced Ring5 is not visible at the simulated image as its peak predicted intensities are around three times the noise in the ALMA image ($\sim1\times10^{-7}$\,Jy\,$\mathrm{beam}^{-1}$).
+The introduced Ring5 is not visible at the simulated image as its peak predicted intensities are around two times the noise in the ALMA image ($\sim1\times10^{-7}$\,Jy\,$\mathrm{beam}^{-1}$).
+This gives us an upper limit for the total millimeter-sized dust mass present in Ring5 of $\sim2\times10^{-5}$\,M$_{\earth}$.
+
 As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.~\ref{fig:radprofiles}), we can assume that the model provides a possible approximation of the disc structure, including the dimensions of Ring13.

### 2021-01-20 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

--- 2021-01-18 Draft_V4046Sgr_mnras.tex
@@
 The simulated 1.3\,mm continuum image reproduces the two observed rings: the faint Ring13 and the brighter Ring24.
-The introduced Ring5 is not visible at the simulated image as its peak predicted intensities are around three times the noise in the ALMA image ($\sim1\times10^{-7}$\,Jy\,$\mathrm{beam}^{-1}$).
+The introduced Ring5 is not visible at the simulated image as its peak predicted intensities are around two times the noise in the ALMA image ($\sim$1$\times10^{-7}$\,Jy\,$\mathrm{beam}^{-1}$).
+This gives us an upper limit for the total millimeter-sized dust mass present in Ring5 of $\sim$2$\times10^{-5}$\,M$_{\earth}$.
+
 As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.~\ref{fig:radprofiles}), we can assume that the model provides a possible approximation of the disc structure, including the dimensions of Ring13.

### 2021-01-23 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 % Basic setup. Most papers should leave these options alone.
-\documentclass[letters,usenatbib,times]{mnras}
+\documentclass[usenatbib,times]{mnras}
 
@@
 \author[R. Martinez Brunner et al.]{
-Rafael Martinez-Brunner,$^{1}$\thanks{E-mail: rmartinezbrunner@gmail.com}
+Rafael Martinez--Brunner,$^{1}$\thanks{E-mail: rmartinezbrunner@gmail.com}
 Simon Casassus,$^{1}$
 Sebasti\'an P\'erez,$^{2}$
-Antonio Hales,$^{3}$
+Antonio Hales,
 Philipp Weber, $^{1,2}$ \newauthor
-Carla Arce-Tord,
+Miguel Carcamo,
+Carla Arce-Tord,$^{1}$
 Lucas Cieza,
 Antonio Garufi,
-Sebasti\'an Marino,
+Sebasti\'an Marino,$^{3}$
 Alice Zurlo
@@
 $^{2}$Universidad de Santiago de Chile, Av. Ecuador 3659, Santiago\\
+$^{3}$Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
 }
@@
     The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc known for its wide cavity and dusty ring.
-We present high resolution ($\sim$20--50\,mas) ALMA observations of the 1.3\,mm  continuum which, combined with SPHERE-IRDIS polarized images and a well-sampled spectral energy distribution (SED), allow us to propose a physical model for the source using radiative transfer (RT) predictions.
+We present high resolution ($\sim$20--50\,mas) ALMA observations of the 1.3\,mm  continuum which, combined with SPHERE--IRDIS polarized images and a well-sampled spectral energy distribution (SED), allow us to propose a physical model for the source using radiative transfer (RT) predictions.
 The new ALMA data reveal a very thin ring at a radius of 13.15$\pm$0.26\,au (Ring13), with a marginally resolved radial width of 2.46$\pm$0.56\,au.
@@
 The steeply decreasing brightness of Ring24 breaks at $\sim$35\,au into a shallow tail.
-In order to reproduce the SED, the model that we propose requires an inner ring at $\sim$6\,au (Ring5) composed mainly of small dust grains, hiding under the IRDIS coronagraph, and surrounding an inner circumbinary disc.
-Faint mm-continuum close ($0\farcs012\pm0\farcs002$) to the stellar position is picked up by ALMA.
+In order to reproduce the SED, the model that we propose requires an inner ring at $\sim$5\,au (Ring5) composed mainly of small dust grains, hiding under the IRDIS coronagraph, and surrounding an inner circumbinary disc.
 The surprisingly thin Ring13 is nonetheless roughly 4 times wider than the model scale height, and could thus be long-lived.
@@
 The DARTTS observations revealed diverse structures and morphologies in the scattering surface of these discs.
-This letter on V4046 Sagittarii (Sgr) is part of a companion programme, the DARTTS survey with ALMA (DARTTS-A, Perez et al.
+This article on V4046 Sagittarii (Sgr) is part of a companion programme, the DARTTS survey with ALMA (DARTTS-A, Perez et al.
 {\em in prep}), which will present millimetre observations of nine protoplanetary discs previously imaged in polarized scattered light in DARTTS-S.
@@
 V4046\,Sgr is a double-lined spectroscopic binary of K-type stars (K5 and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012}, on a close ($a \approx 0.041$\,au), circular ($e\leq0.01$) orbit, with an orbital period of 2.42 days \citep{2000IAUS..200P..28Q}.
-It is a member of the $\beta$ Pictoris moving group \citep{Zuckerman_2004}, with an estimated age of 23$\pm$3\,Myr \citep{Mamajek_2014}, and its distance is 71.48$\pm$0.11\,pc \citep{gaiacollaboration2020gaia}.
+It is a member of the $\beta$ Pictoris moving group \citep{Zuckerman_2004}, with an estimated age of 18.5$^{+2.0}_{-2.4}$\,Myr \citep{2020A&A...642A.179M}, and its distance is 71.48$\pm$0.11\,pc \citep{gaiacollaboration2020gaia}.
 V4046\,Sgr hosts a massive ($\sim$0.1\,M$_{\sun}$) circumbinary disc extending to $\sim$300\,au \citep{Rosenfeld_2013, Rodriguez_2010},  rich in diverse molecular lines \citep{Kastner_2018}.
@@
 
-V4046\,Sgr was observed in differential polarization imaging (DPI) mode with SPHERE-IRDIS on March 13, 2016 \citep[see][for details]{Avenhaus_2018}.
+V4046\,Sgr was observed in differential polarization imaging (DPI) mode with SPHERE--IRDIS on March 13, 2016 \citep[see][for details]{Avenhaus_2018}.
 Here we use a new reduction of the $H$ band data produced with the IRDAP pipeline \citep{2020A&A...633A..64V}, which can separate stellar and instrumental polarization.
@@
   \caption{Comparison of observations (top) and simulated images (bottom) at 1.65\,$\micron$ (left) and 1.3\,mm continuum (right) of the circumbinary disc orbiting V4046\,Sgr.
-\textit{Top left panel:} SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that represents the N\_ALC\_YJH\_S coronagraph with a radius of $\sim0\farcs12$, or $\sim$8.6\,au at 71.48\,pc.
+\textit{Top left panel:} SPHERE--IRDIS \textit{H}-band image with a yellow filled circle that represents the N\_ALC\_YJH\_S coronagraph with a radius of $\sim0\farcs12$, or $\sim$8.6\,au at 71.48\,pc.
 \textit{Top right panel:} 1.3\,mm continuum {\tt uvmem} model image.
@@
 \textit{Bottom left panel:} synthetic image at 1.65\,$\micron$.
-\textit{Bottom right panel:} synthetic image at 1.3\,mm.
-.
+\textit{Bottom right panel:} synthetic image at 1.3\,mm convolved with the {\tt uvmem} beam.
 For all the images in the figure the colour scale is linear.}
@@
 Since this faint central emission is larger than the angular resolution, it is probably stemming from thermal emission from  large dust grains rather directly from the stars.
-The main blob of this dust structure is at a estimate distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.85$\pm$0.14\,au from the binary system, and, estimating its form as a Gaussian ellipse, it has a FWHM of $\sim$1.43\,au.
-If this feature is caused by the presence of millimeter-size dust, its estimated mass would be around 0.12\,M$_{\earth}$.
+The main blob of this dust structure is at estimated distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.85$\pm$0.14\,au from the binary system, and, estimating its form as a Gaussian ellipse, it has a FWHM of $\sim$1.43\,au.
+If this feature is caused by the presence of millimeter-size dust, assuming optically thin emission, its estimated mass would be around 0.12\,M$_{\earth}$.
 %and may be part of an inner disc introduced in the RT model to match the SED (see Sec.~\ref{sec:model} below).
@@
 The observed second ring matches the inner wall of the 1.3\,mm continuum emission outer ring \citep{Ru_z_Rodr_guez_2019}.
-Two other important features that are present in the image are: the brightness asymmetry and the shadows projected on the disc produced by the close binary system as they eclipse each other, discovered by \citet{dOrazi}.
+Two other important features that are present in the image are: the near-far brightness asymmetry, and the shadows projected on the disc by the close binary system as they eclipse each other, discovered by \citet{dOrazi}.
 
@@
     \label{scale}
-  H(r)=\chi \, H_{\circ} \, [r/r_{\circ}]^{\psi(r)},
+  H(r)=\chi \, H_{\circ} \,\left( \frac{r}{r_{\circ}}\right)^{1+\psi(r)},
 \end{equation}
@@
 The radial spread of Ring13 appears two to three times wider in the gas-tracing NIR observations than in the fluxes received from larger grains with ALMA.
-We assume that the same ratio holds in the vertical direction (due to the settling of larger grains towards the disc's midplane), leading to $\chi_{\mathrm{ld}}=0.4$.
+We assume that the same ratio holds in the vertical direction (due to the settling of larger grains towards the midplane of the disc), leading to $\chi_{\mathrm{ld}}=0.4$.
+This is analogous to assuming equal radial and vertical turbulent diffusions.
 
-For the vertical structure, \citet{dOrazi} found flaring angles of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one.
-Our model uses the same values, with two different flaring indices, $\psi_1$ and $\psi_2$.
+For the vertical structure, \citet{dOrazi} found flaring angles, i.e.
+$H/r$, of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one.
+Our model aims to reproduce those values by using two different flaring indices, $\psi_1$ and $\psi_2$.
 The separation between the two values were set at $r = 18$\,au with $\psi_1=0.2$ for Ring5 and Ring13, and $\psi_2=0.5$ for Ring24.
-The scale height is $H_\circ = 0.88$\,au at $r_\circ = 18$\,au.
+The scale height is $H_\circ = 2.2$\,au at $r_\circ = 18$\,au.
+This is summarized in Fig.\ref{fig:profiles} bottom panel that shows the aspect ratio profile $h(r)=H(r)/r$.
 
@@
 
-The inner disc follows a power law function defined by
+The inner disc follows a power-law function defined by
 \begin{equation}
@@
 where $R_c$ is a characteristic radius and $\gamma$ is the surface density power-law index.
-We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =3.26\times10^{-4}$\,$\mathrm{g\,cm^{-3}}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
+We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =3.3\times10^{-4}$\,$\mathrm{g\,cm^{-3}}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
 Our model extends from 0.3\,au outwards, as the interior is expected to be cleared by dynamical effects of the central binary \citep{Art_Lu}
@@
 \end{equation}
-where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring5}}=5.5$\,au, $\mu_{\mathrm{Ring13}}=14.9$\,au\}, ring widths \{$\sigma_{\mathrm{Ring5}}=1$\,au, $\sigma_{\mathrm{Ring13}}=2.3$\,au\}, and normalizations \{$\Sigma_{\circ,\mathrm{Ring5}}=3.28$\,$\mathrm{au\,g\,cm^{-3}}$, $\Sigma_{\circ,\mathrm{Ring13}}=6 \times 10^{-1}$\,$\mathrm{au\,g\,cm^{-3}}$\} for both components separately.
+where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring5}}=5.5$\,au, $\mu_{\mathrm{Ring13}}=14.9$\,au\}, ring widths \{$\sigma_{\mathrm{Ring5}}=1$\,au, $\sigma_{\mathrm{Ring13}}=2.3$\,au\}, and normalizations \{$\Sigma_{\circ,\mathrm{Ring5}}=3.3$\,$\mathrm{au\,g\,cm^{-3}}$, $\Sigma_{\circ,\mathrm{Ring13}}=6.
+\times 10^{-1}$\,$\mathrm{au\,g\,cm^{-3}}$\} for both components separately.
 
-For Ring24 we used the same power law as for the inner disc but scaled by an empirically obtained factor, $\delta_{\mathrm{sd}}$= 4.2$\times 10^4$:
+For Ring24 we used the same power-law as for the inner disc but scaled by an empirically obtained factor, $\delta_{\mathrm{sd}}(r)$= 4.2$\times 10^4$ for $r>18$\,au and $\delta_{\mathrm{sd}}(r)$= 0 for $r<18$\,au:
 \begin{equation}
-  \Sigma_{\mathrm{Ring24}}(r) = \Sigma_{\mathrm{inner\,disc}}(r)\, \delta_{\mathrm{sd}},
+  \Sigma_{\mathrm{Ring24}}(r) = \Sigma_{\mathrm{inner\,disc}}(r)\, \delta_{\mathrm{sd}}(r),
 \end{equation}
@@
 
-For Ring5 and Ring13, we choose Gaussian profiles parameterized with centroid radii $\mu_{\mathrm{Ring5, ld}}=5.5$\,au and $\mu_{\mathrm{Ring13, ld}}=13.22$\,au, ring widths of $\sigma_{\mathrm{Ring5,ld}}=0.4$\,au and $\sigma_{\mathrm{Ring13,ld}}=0.85$\,au, and normalizations $\Sigma_{\circ,\mathrm{Ring5,ld}}=1.34\times10^{-4}\,\mathrm{au\,g\,cm^{-3}}$ and $\Sigma_{\circ,\mathrm{Ring13,ld}}=2.41\,\mathrm{au\,g\,cm^{-3}}$.
-For Ring24 we used the same profile as for the gas, but with the difference that, in an effort to recreate the break seen in the outer ring, we choose different values for $\gamma = -3.5$ and $R_c$ = 39\,au between 27.9 and 35.3\,au.
+For Ring5 and Ring13, we choose Gaussian profiles parameterized with centroid radii $\mu_{\mathrm{Ring5, ld}}=5.5$\,au and $\mu_{\mathrm{Ring13, ld}}=13.22$\,au, ring widths of $\sigma_{\mathrm{Ring5,ld}}=0.4$\,au and $\sigma_{\mathrm{Ring13,ld}}=0.85$\,au, and normalizations $\Sigma_{\circ,\mathrm{Ring5,ld}}=1.3\times10^{-4}\,\mathrm{au\,g\,cm^{-3}}$ and $\Sigma_{\circ,\mathrm{Ring13,ld}}=2.4\,\mathrm{au\,g\,cm^{-3}}$.
+For Ring24 we used a similar profile as for the gas --a power-law function--, but with the difference that, in an effort to recreate the break seen in the outer ring, we choose different values for $\gamma = -3.5$ and $R_c$ = 39\,au between 27.9 and 35.3\,au.
 The surface density for large dust grains in the outer ring is thus given by
 \begin{equation}
-    \Sigma_{\mathrm{Ring24,ld}}(r) = \Sigma_{\mathrm{c}} \left(\frac{r}{R_{\mathrm{c}}}\right)^{-\gamma} \exp\left[-\left(\frac{r}{R_{\mathrm{c}}}\right)^{2-\gamma}\right]\,\delta_{\mathrm{ld}}(r),
+    \Sigma_{\mathrm{Ring24,ld}}(r) = \Sigma_{\mathrm{c}} \left(\frac{r}{R_{\mathrm{c}}(r)}\right)^{-\gamma(r)} \exp\left[-\left(\frac{r}{R_{\mathrm{c}}(r)}\right)^{2-\gamma}\right]\,\delta_{\mathrm{ld}}(r),
 \end{equation}
-where
+where $\delta_{\mathrm{ld}}(r)$ ensures continuity
 \begin{equation}
@@
 The simulated DPI image at 1.65\,$\micron$ in Fig.~\ref{fig:images_vs_simulated} was obtained with the scattering matrix calculated by the {\tt makeopac.py} script provided in the \textsc{radmc3d} package.
-As a way of reproducing the \textit{H}-band image, we used a different grain size distribution, where we centred a Gaussian at 0.4\,$\micron$, smeared out by 30\%, and with distributed over 20 bins within that range.
+As a way of reproducing the \textit{H}-band image, we used a different grain size distribution, where we centred a Gaussian at 0.4\,$\micron$, smeared out by 30\% ($\sigma$ = 0.12\,$\micron$), and with distributed over 20 bins within that range.
 This distribution applies only to generate the NIR $Q_\phi$ image.
@@
 {\bf Bottom:} Aspect ratio profile $h(r)= H(r)/r$.
-The dashed brown line indicates the undetectable large grains in Ring5.
+The dashed brown line depicts an upper limit for large dust grains within Ring5, inferred from its non-detection in ALMA data.
 The dotted lines crossing both panels correspond to transition radii in the parametric model.}
@@
 As \citet{refId0} state, this forward scattering peak that is present in the observation may indicate that the dust grains in the disc surface are relatively large, suggesting that the disc is depleted of very-small grains.
-Interestingly, the model accurately shows the shadows described by \citet{dOrazi} that are present in the SPHERE-IRDIS image.
+Or it may suggest that grains are not spherical as assumed by Mie Theory.
+Interestingly, the model accurately shows the shadows described by \citet{dOrazi} that are present in the SPHERE--IRDIS image.
 
@@
 This gives us an upper limit for the total millimeter-sized dust mass present in Ring5 of $\sim$2$\times10^{-5}$\,M$_{\earth}$.
+The depletion of large dust grains in Ring5 is consistent with efficient dust trapping in Ring13.
+A zone of radially increasing gas pressure can entirely filter out large dust grains from inner regions, while smaller grains can be able to overcome this barrier due to their strong frictional coupling to the gas accretion flow \citep[studied in the context of planetary gaps,][]{Rice2006,Zhu2012,Weber2018}.
+Still, the strong depletion of large particles demands that within Ring5 dust evolution is very inefficient or limited, or that large particles are very rapidly removed.
+Otherwise, the present small grains should quickly coagulate to form detectable grain sizes in the ALMA observation in Fig.\ref{fig:images_vs_simulated}  \citep{Drazkowska2019}.
 
@@
 The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.07\,au difference in the centroid location of the ring, and a 0.46\,au difference in the width estimation.
-Using the large grains' scale height at Ring13 of 0.61\,au, and a measured width of 2.46\,au, the ring is $\sim$4.1 times more extended radially than vertically.
+Since  the  scale height of the large grains in Ring13 is  0.61\,au, and has a  measured width of 2.46$\pm$0.56\,au, the ring is $\sim$4.1$\pm$0.9 times more extended radially than vertically.
 
@@
 
-The effective beam size of the presented ALMA observations marginally resolves the width of Ring13 to be $w_\mathrm{d} = 2.46\mathrm{au}$.
+The effective beam size of the presented ALMA observations marginally resolves the FWHM of Ring13 to be $w_\mathrm{d} = 2.46\pm$0.56\,au.
 Using that the gas' Ring13-FWHM in the RT model corresponds to $w_\mathrm{g} = 5.42\mathrm{au}$, we can see that large dust grains have to be radially converged to explain the discrepancy.
@@
 It further provides a value for the level of turbulent viscosity in Ring13, $\alpha_{\rm turb}\approx 0.01$, assuming viscosity to be equal to the level of diffusion \citep{2007Icar..192..588Y}.
-We note that an observation of molecular line broadening has found no evidence for turbulent contributions, suggesting $\alpha_{\rm turb}<0.01$ (Flaherty et al.
-2020).
+We note that an observation of molecular line broadening has found no evidence for turbulent contributions, suggesting $\alpha_{\rm turb}<0.01$ \citep{Flaherty_2020}.
 The value inferred from our model is just within this limit.
@@
 From the similarity with the data we propose that there has to be a small-grain population close to the stars down to 0.3\,au.
-The observed blob in the ALMA observation can not be explained using a millimeter-sized dust population following the mass estimation in Section\,\ref{sec:Observations}, as it creates a larger excess in the 10$\,\micron$ that does not match the data.
+The observed central and compact signal  in the ALMA observation cannot be explained using  millimeter-sized dust, following the mass estimates in Section\,\ref{sec:Observations}, as it reaches $\sim$18 times large surface densities than in the gas.
+Also, the hypothesis of thermal emission from large grains in the inner disc results in  a large excess at 10$\,\micron$ that does not match the data.
 The decision of employing the three ringed structure (i.e.
@@
 The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes around 0.7\,M$_{\earth}$ millimetre-sized grains.
-Using the parametric model scale height value ($H= $ 0.60\,au at 13.15\,au) we have that the ring width is roughly 4 times its estimated height.
+Using the parametric model scale height value ($H=$ 0.60\,au at 13.15\,au) we have that the ring width is roughly 4 times its estimated height.
 
@@
 
-  \item We interpret the asymmetry observed with SPHERE-IRDIS at 1.65\,$\micron$ as due to strong forward-scattering, which implies that the dust population is depleted of grains smaller than $\sim$0.4\,$\micron$.
+  \item We interpret the asymmetry observed with SPHERE--IRDIS at 1.65\,$\micron$ as due to strong forward-scattering, which implies that the dust population is depleted of grains smaller than $\sim$0.4\,$\micron$.
 
@@
 
-S.P. acknowledges support from the Joint Committee of ESO and the Government of Chile and Fondecyt Regular grant 1191934.
+S.C. acknowledges support from FONDECYT grant 1171624. S.P. acknowledges support from the Joint Committee of ESO and the Government of Chile and FONDECYT grant 1191934.
 

### 2021-01-24 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[R. Martinez Brunner et al.]{
-Rafael Martinez--Brunner,$^{1}$\thanks{E-mail: rmartinezbrunner@gmail.com}
+\author[R. Martinez Brunner et al.]{Rafael Martinez--Brunner,$^{1}$
+\thanks{E-mail: rmartinezbrunner@gmail.com}
 Simon Casassus,$^{1}$
 Sebasti\'an P\'erez,$^{2}$
-Antonio Hales,
+Antonio Hales,$^{7,8}$
 Philipp Weber, $^{1,2}$ \newauthor
@@
 Sebasti\'an Marino,$^{3}$
-Alice Zurlo
+Alice Zurlo$^{4,5,6}$
 \\
 % List of institutions
-$^{1}$Departamento de Astronom\'{\i}a, Universidad de Chile, Casilla 36-D, Santiago, Chile\\
-$^{2}$Universidad de Santiago de Chile, Av. Ecuador 3659, Santiago\\
+$^{1}$Departamento de Astronom\'ia, Universidad de Chile, Casilla 36-D, Santiago, Chile\\
+$^{2}$Departamento de F\'isica, Universidad de Santiago de Chile, Av. Ecuador 3659, Santiago\\
 $^{3}$Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
+$^{4}$N\'ucleo de Astronom\'ia, Facultad de Ingenier\'ia y Ciencias, Universidad Diego Portales, Av. Ejercito 441, Santiago, Chile\\
+$^{5}$Escuela de Ingenier\'ia Industrial, Facultad de Ingenier\'ia y Ciencias, Universidad Diego Portales, Av. Ejercito 441, Santiago, Chile \\
+$^{6}$Aix Marseille Universit\'e, CNRS, LAM - Laboratoire d'Astrophysique de Marseille, UMR 7326, 13388, Marseille, France  \\
+$^{7}$Joint ALMA Observatory, Avenida Alonso de C\'ordova 3107, Vitacura 7630355, Santiago, Chile \\
+$^{8}$National Radio Astronomy Observatory, 520 Edgemont Road, Charlottesville, VA 22903-2475, United States of America \\
 }
@@
 Our model aims to reproduce those values by using two different flaring indices, $\psi_1$ and $\psi_2$.
-The separation between the two values were set at $r = 18$\,au with $\psi_1=0.2$ for Ring5 and Ring13, and $\psi_2=0.5$ for Ring24.
+The separation between the two values was set at $r = 18$\,au with $\psi_1=0.2$ for Ring5 and Ring13, and $\psi_2=0.5$ for Ring24.
 The scale height is $H_\circ = 2.2$\,au at $r_\circ = 18$\,au.
@@
 
-For Ring24 we used the same power-law as for the inner disc but scaled by an empirically obtained factor, $\delta_{\mathrm{sd}}(r)$= 4.2$\times 10^4$ for $r>18$\,au and $\delta_{\mathrm{sd}}(r)$= 0 for $r<18$\,au:
+For Ring24 we used the same power-law as for the inner disc but scaled by an empirically obtained factor, $\delta_{\mathrm{sd}}(r)$:
 \begin{equation}
   \Sigma_{\mathrm{Ring24}}(r) = \Sigma_{\mathrm{inner\,disc}}(r)\, \delta_{\mathrm{sd}}(r),
+\end{equation}
+with
+\begin{equation}
+  \delta_{\mathrm{sd}}(r) =
+  \begin{cases}
+  0    & r < 18\text{\,au} \\
+  4.2\times 10^4 & r > 18\text{\,au}.
+  \end{cases}
 \end{equation}
@@
 For Ring5 and Ring13, we choose Gaussian profiles parameterized with centroid radii $\mu_{\mathrm{Ring5, ld}}=5.5$\,au and $\mu_{\mathrm{Ring13, ld}}=13.22$\,au, ring widths of $\sigma_{\mathrm{Ring5,ld}}=0.4$\,au and $\sigma_{\mathrm{Ring13,ld}}=0.85$\,au, and normalizations $\Sigma_{\circ,\mathrm{Ring5,ld}}=1.3\times10^{-4}\,\mathrm{au\,g\,cm^{-3}}$ and $\Sigma_{\circ,\mathrm{Ring13,ld}}=2.4\,\mathrm{au\,g\,cm^{-3}}$.
-For Ring24 we used a similar profile as for the gas --a power-law function--, but with the difference that, in an effort to recreate the break seen in the outer ring, we choose different values for $\gamma = -3.5$ and $R_c$ = 39\,au between 27.9 and 35.3\,au.
+For Ring24 we used a similar profile as for the gas --a power-law function-- but with the difference that, in an effort to recreate the break seen in the outer ring, we choose different values for $\gamma = -3.5$ and $R_c$ = 39\,au between 27.9 and 35.3\,au.
 The surface density for large dust grains in the outer ring is thus given by
@@
 \end{equation}
-where $\delta_{\mathrm{ld}}(r)$ ensures continuity
+where
 \begin{equation}
@@
   0                 & r < 24.6\text{\,au} \\
-  7.19 \times10^{4} & 24.6 < r < 27.9\text{\,au} \\
-  3.17 \times10^{4} & 27.9 < r < 35.3\text{\,au} \\
-  2.65 \times10^{5} & 35.3 < r < 64\text{\,au.} \\
+  7.2 \times10^{4} & 24.6 < r < 27.9\text{\,au} \\
+  3.2 \times10^{4} & 27.9 < r < 35.3\text{\,au} \\
+  2.7 \times10^{5} & 35.3 < r < 64\text{\,au.} \\
   \end{cases}
@@
 Otherwise, the present small grains should quickly coagulate to form detectable grain sizes in the ALMA observation in Fig.\ref{fig:images_vs_simulated}  \citep{Drazkowska2019}.
+The central emission is not present in the 1.3\,mm continuum image as it was impossible to achieve a bright blob without disrupting the SED fit (read below).
 
@@
 The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.07\,au difference in the centroid location of the ring, and a 0.46\,au difference in the width estimation.
-Since  the  scale height of the large grains in Ring13 is  0.61\,au, and has a  measured width of 2.46$\pm$0.56\,au, the ring is $\sim$4.1$\pm$0.9 times more extended radially than vertically.
+Since  the  scale height of the large grains in Ring13 is  0.61\,au, and has a  measured width of 2.46$\pm$0.56\,au, the ring is 4.1$\pm$0.9 times more extended radially than vertically.
 
@@
 The value inferred from our model is just within this limit.
-It is linearly proportional to the local dust-to-gas ratio (by our definition of the gas surface density profile) -- a standard ISM  value of 0.01 for the dust-to-gas ratio would thus lead to an expected level of turbulent viscosity of $\alpha_{\rm turb}\approx 5\times10^{-3}$.
+It is linearly proportional to the local dust-to-gas ratio (by our definition of the gas surface density profile) a standard ISM  value of 0.01 for the dust-to-gas ratio would thus lead to an expected level of turbulent viscosity of $\alpha_{\rm turb}\approx 5\times10^{-3}$.
 While the exact value for $\alpha_{\rm turb}$ is not well constrained, the presence of turbulence is a robust detection, as it is required to explain the radial spread of the resolved Ring13.
@@
 From the similarity with the data we propose that there has to be a small-grain population close to the stars down to 0.3\,au.
-The observed central and compact signal  in the ALMA observation cannot be explained using  millimeter-sized dust, following the mass estimates in Section\,\ref{sec:Observations}, as it reaches $\sim$18 times large surface densities than in the gas.
-Also, the hypothesis of thermal emission from large grains in the inner disc results in  a large excess at 10$\,\micron$ that does not match the data.
-The decision of employing the three ringed structure (i.e.
+The observed central and compact signal in the ALMA observation cannot be explained with the hypothesis of thermal emission from large grains in the inner disc.
+Following the mass estimates in Section\,\ref{sec:Observations}, the millimeter-sized dust needed reaches $\sim$18 times larger surface densities than in the gas, resulting in a large excess at 10$\,\micron$ that does not match the data.
+On the other hand, the decision of employing the three ringed structure (i.e.
 add Ring5 to the observed structure) relies on the fact that the SED needed a ring at a radius around 5--7\,au to have a proper fit around 10\,$\micron$.
-
-%Ring5 may be just artificial and not a real prediction, as a thin ring like the one we implemented would be expected to trap millimetre-size dust grains, while those grains are not present in the ALMA observation.
 
@@
 
-S.C. acknowledges support from FONDECYT grant 1171624. S.P. acknowledges support from the Joint Committee of ESO and the Government of Chile and FONDECYT grant 1191934.
+S.C. acknowledges support from FONDECYT grant 1171624.
+
+S.P. acknowledges support from the Joint Committee of ESO and the Government of Chile and FONDECYT grant 1191934.
+
+A.Z. acknowledges support from the FONDECYT Iniciaci\'on en investigaci\'on project number 11190837
 

### 2021-01-28 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 % Basic setup. Most papers should leave these options alone.
-\documentclass[usenatbib,times]{mnras}
+\documentclass[fleqn,usenatbib,useAMS]{mnras}
 
@@
 Sebasti\'an P\'erez,$^{2}$
-Antonio Hales,$^{7,8}$
+Antonio Hales,$^{3,4}$
 Philipp Weber, $^{1,2}$ \newauthor
-Miguel Carcamo,
+Miguel Carcamo,$^{5,6}$
 Carla Arce-Tord,$^{1}$
-Lucas Cieza,
-Antonio Garufi,
-Sebasti\'an Marino,$^{3}$
-Alice Zurlo$^{4,5,6}$
+Lucas Cieza,$^{7}$
+Antonio Garufi,$^{8}$
+Sebasti\'an Marino,$^{9}$
+Alice Zurlo$^{7,10,11}$
 \\
@@
 $^{2}$Departamento de F\'isica, Universidad de Santiago de Chile, Av. Ecuador 3659, Santiago\\
-$^{3}$Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
-$^{4}$N\'ucleo de Astronom\'ia, Facultad de Ingenier\'ia y Ciencias, Universidad Diego Portales, Av. Ejercito 441, Santiago, Chile\\
-$^{5}$Escuela de Ingenier\'ia Industrial, Facultad de Ingenier\'ia y Ciencias, Universidad Diego Portales, Av. Ejercito 441, Santiago, Chile \\
-$^{6}$Aix Marseille Universit\'e, CNRS, LAM - Laboratoire d'Astrophysique de Marseille, UMR 7326, 13388, Marseille, France  \\
-$^{7}$Joint ALMA Observatory, Avenida Alonso de C\'ordova 3107, Vitacura 7630355, Santiago, Chile \\
-$^{8}$National Radio Astronomy Observatory, 520 Edgemont Road, Charlottesville, VA 22903-2475, United States of America \\
+$^{3}$Joint ALMA Observatory, Avenida Alonso de C\'ordova 3107, Vitacura 7630355, Santiago, Chile \\
+$^{4}$National Radio Astronomy Observatory, 520 Edgemont Road, Charlottesville, VA 22903-2475, United States of America \\
+$^{5}$Departamento de Ingenier\'ia Inform´atica, Universidad de Santiago de Chile, Av. Ecuador, 3659, Santiago, Chile\\
+$^{6}$Jodrell Bank Centre for Astrophysics, Alan Turing Building, Department of Physics and Astronomy, Alan Turing Building,\\ University of Manchester, Oxford Road, Manchester, M13 9PL, UK \\
+$^{7}$N\'ucleo de Astronom\'ia, Facultad de Ingenier\'ia y Ciencias, Universidad Diego Portales, Av. Ejercito 441, Santiago, Chile\\
+$^{8}$INAF, Osservatorio Astrofisico di Arcetri, Largo Enrico Fermi 5, I-50125, Firenze, Italy\\
+$^{9}$Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
+$^{10}$Escuela de Ingenier\'ia Industrial, Facultad de Ingenier\'ia y Ciencias, Universidad Diego Portales, Av. Ejercito 441, Santiago, Chile \\
+$^{11}$Aix Marseille Universit\'e, CNRS, LAM - Laboratoire d'Astrophysique de Marseille, UMR 7326, 13388, Marseille, France  \\
 }
@@
 % Enter the current year, for the copyright statements etc.
-\pubyear{2020}
+\pubyear{2021}
 
@@
     The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc known for its wide cavity and dusty ring.
-We present high resolution ($\sim$20--50\,mas) ALMA observations of the 1.3\,mm  continuum which, combined with SPHERE--IRDIS polarized images and a well-sampled spectral energy distribution (SED), allow us to propose a physical model for the source using radiative transfer (RT) predictions.
+We present high resolution ($\sim$20--50\,mas) ALMA observations of the 1.3\,mm  continuum which, combined with SPHERE--IRDIS polarized images and well-sampled spectral energy distribution (SED), allow us to propose a physical model for the source using radiative transfer (RT) predictions.
 The new ALMA data reveal a very thin ring at a radius of 13.15$\pm$0.26\,au (Ring13), with a marginally resolved radial width of 2.46$\pm$0.56\,au.
@@
 In order to reproduce the SED, the model that we propose requires an inner ring at $\sim$5\,au (Ring5) composed mainly of small dust grains, hiding under the IRDIS coronagraph, and surrounding an inner circumbinary disc.
-The surprisingly thin Ring13 is nonetheless roughly 4 times wider than the model scale height, and could thus be long-lived.
+The surprisingly thin Ring13 is nonetheless roughly 4 times wider than the model scale height.
 The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$.
@@
 \end{equation}
-where $M$ is the default pixel intensity value, and is set to $10^{-3}$ times the theoretical noise of the dirty map (as inferred from the visibility weights $\omega_k$).
+where $M$ is the default pixel intensity value and is set to $10^{-3}$ times the theoretical noise of the dirty map (as inferred from the visibility weights $\omega_k$).
 Here we set $\lambda = 0.01$.
@@
 The offset of the center of the cavity and the nominal stellar positions is entirely consistent with a pointing error, since the pointing accuracy of ALMA is usually taken to be 1/10 of the natural-weights beam, at 1\,$\sigma$, or $\sim$6\,mas in this case.
-***ANTONIO PLEASE CONFIRM AND PROVIDE A REFERENCE ***
 
@@
 In a second optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.86$\pm$0.02\,$\degr$, with an inclination of 33.92$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 2\pm0.02$\,mas $\Delta \delta = 12\pm0.02$\,mas relative to the stars.
-We see that both Ring13 and Ring24 both share a very similar orientation and centre, given the errors.
+We see that both Ring13 and Ring24 share a very similar orientation and centre, given the errors.
 However, perhaps due to the joint effect of all these small differences, we can see that there are some hints for a somewhat different orientation, as summarised in Fig.~\ref{fig:polarring}.
@@
 Interestingly, the ALMA image also detects faint 1.3\,mm continuum emission near the stellar positions (See the inset in Fig.~\ref{fig:images_vs_simulated}).
-Since this faint central emission is larger than the angular resolution, it is probably stemming from thermal emission from  large dust grains rather directly from the stars.
+Since this faint central emission is larger than the angular resolution, it is probably stemming from thermal emission from  large dust grains rather than directly from the stars.
 The main blob of this dust structure is at estimated distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.85$\pm$0.14\,au from the binary system, and, estimating its form as a Gaussian ellipse, it has a FWHM of $\sim$1.43\,au.
-If this feature is caused by the presence of millimeter-size dust, assuming optically thin emission, its estimated mass would be around 0.12\,M$_{\earth}$.
+If this feature is caused by the presence of millimetre-sized dust, assuming optically thin emission, its estimated mass would be around 0.12\,M$_{\earth}$.
 %and may be part of an inner disc introduced in the RT model to match the SED (see Sec.~\ref{sec:model} below).
@@
 
-We propose a three ringed structure to reproduce the observations.
-We separate the disc into four individual regions: the inner disc, Ring5, Ring13 and Ring24.
+We propose a three-ringed structure to reproduce the observations.
+We separate the disc into four individual regions: the inner disc, Ring5, Ring13, and Ring24.
 The combined gas surface density profile is then given by:
@@
 The introduced Ring5 is not visible at the simulated image as its peak predicted intensities are around two times the noise in the ALMA image ($\sim$1$\times10^{-7}$\,Jy\,$\mathrm{beam}^{-1}$).
-This gives us an upper limit for the total millimeter-sized dust mass present in Ring5 of $\sim$2$\times10^{-5}$\,M$_{\earth}$.
+This gives us an upper limit for the total millimetre-sized dust mass present in Ring5 of $\sim$2$\times10^{-5}$\,M$_{\earth}$.
 The depletion of large dust grains in Ring5 is consistent with efficient dust trapping in Ring13.
@@
 As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.~\ref{fig:radprofiles}), we can assume that the model provides a possible approximation of the disc structure, including the dimensions of Ring13.
-Accordingly, taking the parametric model values for Ring13, it has a radius of 13.22\,au, a FWHM of 2.00\,au, and a scale height FWHM of the millimetre-size dust of 0.61\,au.
+Accordingly, taking the parametric model values for Ring13, it has a radius of 13.22\,au, a FWHM of 2.00\,au, and a scale height FWHM of the millimetre-sized dust of 0.61\,au.
 The total dust mass of Ring13 is about 0.7\,M$_{\earth}$ in the model.
@@
 It contains a total dust mass of $\sim$44\,M$_{\earth}$.
-The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.07\,au difference in the centroid location of the ring, and a 0.46\,au difference in the width estimation.
+The model predictions for the millimetre-sized dust population in Ring13 are close to the measurements, with only a 0.07\,au difference in the centroid location of the ring, and a 0.46\,au difference in the width estimation.
 Since  the  scale height of the large grains in Ring13 is  0.61\,au, and has a  measured width of 2.46$\pm$0.56\,au, the ring is 4.1$\pm$0.9 times more extended radially than vertically.
@@
 The observed structure may point to the existence of planet-disc interactions within this system, where a giant planet depletes its orbit of gas and dust material.
-A possible  constellation in this scenario is therefore the presence of two giant planets in the disc, one planet between the star and Ring13, and one planet between Ring13 and Ring24.
+A possible  constellation in this scenario is, therefore, the presence of two giant planets in the disc, one planet between the star and Ring13, and one planet between Ring13 and Ring24.
 As \citet{Ru_z_Rodr_guez_2019} suggest, the putative planet between Ring13 and Ring24 may be a giant planet with a mass within the range of 0.3$-$1.5\,$\mathrm{M}_{\mathrm{Jup}}$.
@@
 The observed SED is compared with the model in Fig.~\ref{fig:SED}.
-From the similarity with the data we propose that there has to be a small-grain population close to the stars down to 0.3\,au.
+From the similarity with the data, we propose that there has to be a small-grain population close to the stars down to 0.3\,au.
 The observed central and compact signal in the ALMA observation cannot be explained with the hypothesis of thermal emission from large grains in the inner disc.
-Following the mass estimates in Section\,\ref{sec:Observations}, the millimeter-sized dust needed reaches $\sim$18 times larger surface densities than in the gas, resulting in a large excess at 10$\,\micron$ that does not match the data.
-On the other hand, the decision of employing the three ringed structure (i.e.
+Following the mass estimates in Section\,\ref{sec:Observations}, the millimetre-sized dust needed reaches $\sim$18 times larger surface densities than in the gas, resulting in a large excess at 10$\,\micron$ that does not match the data.
+On the other hand, the decision of employing the three-ringed structure (i.e.
 add Ring5 to the observed structure) relies on the fact that the SED needed a ring at a radius around 5--7\,au to have a proper fit around 10\,$\micron$.
@@
 
-New ALMA 1.3\,mm continuum imaging of the circumbinary disc around V4046\,Sgr were analysed in the context of the available IR imaging and the observed spectral energy distribution using a RT model.
+New ALMA 1.3\,mm continuum imaging of the circumbinary disc around V4046\,Sgr were analysed in the context of the available IR imaging and the observed spectral energy distribution using an RT model.
 The key conclusions are as follows.
@@
 
-  \item Our parametric model, which accounts for the SED of the system, involves the existence of a sub-micron dust population close (<5\,au) to the stars, and predicts the presence of another inner ring at $\sim$5\,au made mainly of small dust grains.
+  \item Our parametric model, which accounts for the SED of the system, involves the existence of a sub-micron dust population close (<5\,au) to the stars, and predicts the presence of another inner ring at $\sim$5\,au, made mainly of small dust grains.
 
@@
 A.Z. acknowledges support from the FONDECYT Iniciaci\'on en investigaci\'on project number 11190837
+
+MC acknowledges support from ANID PFCHA/DOCTORADO BECAS CHILE/2018-72190574.
 

### 2021-03-05 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
     The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc known for its wide cavity and dusty ring.
-We present high resolution ($\sim$20--50\,mas) ALMA observations of the 1.3\,mm  continuum which, combined with SPHERE--IRDIS polarized images and well-sampled spectral energy distribution (SED), allow us to propose a physical model for the source using radiative transfer (RT) predictions.
+We present high resolution ($\sim$20--50\,mas) ALMA observations of the 1.3\,mm  continuum of V4046\,Sgr which, combined with SPHERE--IRDIS polarized images and well-sampled spectral energy distribution (SED), allow us to propose a physical model using radiative transfer (RT) predictions.
 The new ALMA data reveal a very thin ring at a radius of 13.15$\pm$0.26\,au (Ring13), with a marginally resolved radial width of 2.46$\pm$0.56\,au.
@@
 The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$.
-The previously reported scattered-light shadow of the secondary star is also reproduced by the RADMC3D RT package.
+The previously reported scattered-light shadow of the secondary star is also reproduced by our physical model.
 \end{abstract}
@@
 
+Disc structures can be explored by means of comparing mm continuum and scattered-light images.
+These observations allow us to see the distribution of different populations of dust particles, while ALMA traces the millimetre-sized grains settled in the mid-plane of the disc, scattered-light imaging accounts for photons reflected off small micron-sized dust at the disc surface layer, high above the mid-plane.
+By comparing both, is easier to determine whether asymmetries in scattered light correspond to surface ripples or deep structures intrinsic to the underlying density distribution.
+
+From previous analysis of radio wavelength observations taken with Sub-millimeter Array (SMA) \citep{Rapson_2015} and subsequently with ALMA \citep{Guzman_2017,Huang_2017,Bergner_2018,Kastner_2018}, it was detected that the millimeter dust configuration of the circumbinary disc had a large inner hole of $\sim$30\,au, featuring a narrow ring centred around 37\,au that accounted for most of the dust mass.
+Later on, \citet{Avenhaus_2018} using DPI in the J and H bands confirmed the double-ring morphology presented by \citet{Rapson_2015}, where the micron-size dust disc presented an $\sim$10\,au-wide inner cavity, a narrow ring at $\sim$14\,au and the outer ring centred at $\sim$27\,au.
+
+The pursuit of creating high-fidelity parametric simulations that resolve NIR scattered-light and millimeter continuum observations simultaneously is something only few have ventured into \citep[e.g.][]{Dong_2018,2019MNRAS.486..304B, Ru_z_Rodr_guez_2019}.
+A model that achieves this quest can serve as a convenient sample to interpret real data in terms of a physical model.
+In this paper we aim to reproduce the protoplanetary disc around V4046\,Sgr with a 3D model using as guidance previous NIR images, the spectral energy distribution (SED) and a new high definition 1.3\,mm continuum ALMA image, as a way to throw light on its complex structure and the processes that are occurring in it.
+
 The observations, including new 1.3\,mm continuum data, are described in Section~\ref{sec:Observations}.
-We interpret the data in terms of a parametric model, presented in Section~\ref{sec:model}, which builds up  on the previous models of V4046\,Sgr  \citep{Rosenfeld_2013, Ru_z_Rodr_guez_2019, 2019ApJ...882..160Q} to account for the new  ALMA data.
+The parametric model is presented in Section~\ref{sec:model}, which builds up on the previous models of V4046\,Sgr  \citep{Rosenfeld_2013, Ru_z_Rodr_guez_2019, 2019ApJ...882..160Q}.
 Our results are discussed in Section~\ref{sec:results} and summarised in Section~\ref{sec:Conclusions}.
@@
 \section{Observations} \label{sec:Observations}
-
-%% Disc structures can be explored by means of comparing mm continuum and scattered-light images.
-These observations allow us to see the distribution of different populations of dust particles, while ALMA traces the millimetre-sized grains settled in the mid-plane of the disc, scattered-light imaging accounts for photons reflected off small micron-sized dust at the disc surface layer, high above the mid-plane.
-By comparing both, is easier to determine whether asymmetries in scattered light correspond to surface ripples or deep structures intrinsic to the underlying density distribution.
+\subsection{ALMA}
 
@@
 Perez).
-The observations  acquired simultaneously the 1.3\,mm continuum and the J = 2$-$1 line of $^{12}$CO with  (i.e.
+The observations acquired simultaneously the 1.3\,mm continuum and the J = 2$-$1 line of $^{12}$CO (i.e.
 with a band 6 211-275\,GHz correlator setup).
@@
 Here we focus on the continuum observations only.
-
-V4046\,Sgr was observed in differential polarization imaging (DPI) mode with SPHERE--IRDIS on March 13, 2016 \citep[see][for details]{Avenhaus_2018}.
-Here we use a new reduction of the $H$ band data produced with the IRDAP pipeline \citep{2020A&A...633A..64V}, which can separate stellar and instrumental polarization.
-The polarized signal is consistent with the previous image in \citet{Avenhaus_2018}.
-The degree of linear polarization of the central and unresolved signal in V4046\,Sgr is only 0.13\%, with a systematic uncertainty of 0.05\% due to time-varying atmospheric conditions during the exposures.
-The angle of polarization is aligned with the disc major axis, as expected given that the target has Av=0.0 \citep{2016ApJ...828...69M} and the entire polarization is dominated by circumstellar rather than inter-stellar material.
+The line data will be presented in the main DARTTS-A paper.
 
@@
 \begin{equation}
-  L = \sum_{k=1}^N \omega_k  |V^\circ_k - V^m_k|^2 + \lambda S.
+  L = \sum_{k=1}^N \omega_k  |V^\circ_k - V^m_k|^2 + \lambda S,
 \end{equation}
-The regularization term $S$ depends on the application, and in this case we chose the standard image entropy, or
+where $\omega_k$ are the visibility weights and $\lambda$ is a dimensionless parameter that controls the relative importance of the regularization term $S$.
+
+The chosen regularization term $S$ for this case was the standard image entropy, or
 \begin{equation}
@@
 Here we set $\lambda = 0.01$.
-Similar applications of {\tt uvmem} in the context of protoplanetary discs can be found, for example,  in \citet{Casassus2013Natur, 2018MNRAS.477.5104C, Casassus2019MNRAS.483.3278C,  Perez2019AJ....158...15P}.
-An  advantage of {\tt uvmem} compared to more traditional imaging strategies, such as provided by the  {\tt tclean}   task in CASA, is that the effective angular resolution of the model image is  $\sim$3 times finer than the natural weights clean beam \citep[][]{2018A&C....22...16C}.
+Similar applications of {\tt uvmem} in the context of protoplanetary discs can be found, for example, in \citet{Casassus2013Natur, 2018MNRAS.477.5104C, Casassus2019MNRAS.483.3278C,  Perez2019AJ....158...15P} and in \citet{2020ApJ...889L..24P} using long baseline data.
+An advantage of {\tt uvmem} compared to more traditional imaging strategies, such as provided by the  {\tt tclean} task in CASA, is that the effective angular resolution of the model image is $\sim$3 times finer than the natural weights clean beam \citep[][]{2018A&C....22...16C}, giving us a new approximate {\tt uvmem} resolution of $\sim0\farcs021 \,\times \,\sim0\farcs018$.
 This angular resolution is comparable to uniform or super-uniform weights in {\tt tclean}, but it preserves the natural-weights point-source sensitivity.
@@
 While this is the first observation of Ring13, \citet{Ru_z_Rodr_guez_2019} did anticipate its existence as their ALMA continuum image showed a distinct excess between $\sim$10 and 17\,au.
+The {\tt uvmem} map has a resolution of 21$\times$18\,mas and an RMS noise of 26$\micron$Jy per resolution beam, at a frequency of 237 GHz.
+
+Ring13 is surprisingly narrow and seems to be off-centred relative to the Gaia stellar position, at the origin of coordinates in Fig.~\ref{fig:images_vs_simulated}.
+We determined the ring's centre and orientation by minimising the dispersion of the disc radial profiles from 6\,au to 19\,au, by using the {\tt MPolarMaps} package described in Casassus et al.
+(2021, in prep).
+The resulting disc orientation is set at a position angle (PA) of 77.31$\pm$0.03\,$\degr$ (east of north), with an  inclination of 32.96$\pm$0.02\,$\degr$, and the optimal ring centre is at $\Delta \alpha = -4\pm0.02$\,mas $\Delta \delta = 13\pm0.05$\,mas relative to the Gaia position of the stars.
+The offset of the center of the cavity and the nominal stellar positions is entirely consistent with a pointing error, since the pointing accuracy of ALMA is $\sim$5\,mas for the signal to noise ratio of our image (calculated using the ALMA Technical Handbook).
+
+The ring width can be measured in polar coordinates by fitting 1-D Gaussians, thus obtaining a width and centroid at each azimuth (see Fig.~\ref{fig:polarring}).
+On average, we obtained a FWHM of 2.83$\pm$0.50\,au, and a stellocentric radius of 13.15$\pm$0.26\,au.
+As the {\tt uvmem} model image has an approximate {\tt uvmem} beam of $\sim0\farcs021 \,\times \,\sim0\farcs018$, we see that Ring13 is marginally resolved.
+After subtraction of the {\tt uvmem} beam, the ring width is $\sim$2.46$\pm$0.56\,au.
+
+In a second optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.86$\pm$0.02\,$\degr$, with an inclination of 33.92$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 2\pm0.02$\,mas $\Delta \delta = 12\pm0.02$\,mas relative to the stars.
+We see that both Ring13 and Ring24 share a very similar orientation and centre, given the errors.
+However, perhaps due to the joint effect of all these small differences, we can see that there are some hints for a somewhat different orientation, as summarised in Fig.~\ref{fig:polarring}.
+
+Interestingly, the ALMA image also detects faint 1.3\,mm continuum emission near the stellar positions (see the inset in Fig.~\ref{fig:images_vs_simulated}).
+Since this faint central emission is larger than the angular resolution, it is probably stemming from thermal emission from  large dust grains rather than directly from the stars.
+The main blob of this dust structure is at estimated distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.85$\pm$0.14\,au from the binary system, and, estimating its form as a Gaussian ellipse, it has a mean FWHM of $\sim$1.43\,au.
+If this feature is caused by the presence of millimetre-sized dust, assuming optically thin emission, its estimated mass would be around 0.12\,M$_{\earth}$.
+%and may be part of an inner disc introduced in the RT model to match the SED (see Sec.~\ref{sec:model} below).
+
+\subsection{SPHERE--IRDIS}
+
+V4046\,Sgr was observed in DPI mode with SPHERE--IRDIS on March 13, 2016 \citep[see][for details]{Avenhaus_2018}.
+Here we use a new reduction of the $H$ band data produced with the IRDAP pipeline \citep{2020A&A...633A..64V}, which can separate stellar and instrumental polarization.
+The polarized signal is consistent with the previous image in \citet{Avenhaus_2018}.
+The degree of linear polarization of the central and unresolved signal in V4046\,Sgr is only 0.13\%, with a systematic uncertainty of 0.05\% due to time-varying atmospheric conditions during the exposures.
+The angle of polarization is aligned with the disc major axis, as expected given that the target has an extinction of Av=0.0 \citep{2016ApJ...828...69M} and the entire polarization is dominated by circumstellar rather than inter-stellar material.
 
@@
 
-Ring13 is surprisingly narrow and seems to be off-centred relative to the GAIA stellar position, at the origin of coordinates in Fig.~\ref{fig:images_vs_simulated}.
-We determined the ring's centre and orientation by minimising the dispersion of the disc radial profiles from 6\,au to 19\,au, by using the {\tt MPolarMaps} package described in Casassus et al.
-(2021, in prep).
-The resulting disc orientation is set at a position angle  (PA) of 77.31$\pm$0.03\,$\degr$, with an  inclination of 32.96$\pm$0.02\,$\degr$, and the optimal ring  centre is at $\Delta \alpha = -4\pm0.02$\,mas $\Delta \delta = 13\pm0.05$\,mas relative to the GAIA position of the stars.
-The offset of the center of the cavity and the nominal stellar positions is entirely consistent with a pointing error, since the pointing accuracy of ALMA is usually taken to be 1/10 of the natural-weights beam, at 1\,$\sigma$, or $\sim$6\,mas in this case.
-
-The ring width can be measured in polar coordinates by fitting 1-D Gaussians, thus obtaining a width and centroid at each azimuth.
-On average, we obtained a FWHM of 2.83$\pm$0.50\,au, and a stellocentric radius of 13.15$\pm$0.26\,au (See Fig.~\ref{fig:polarring}).
-As the {\tt uvmem} model image has an effective angular resolution of $\sim$1/3 that of the natural-weighted beam ($0\farcs062 \,\times \, 0\farcs055$), we see that Ring13 is marginally resolved.
-After subtraction of the approximate {\tt uvmem} resolution ($\sim0\farcs021 \,\times \,\sim0\farcs018$), the ring width is $\sim$2.46$\pm$0.56\,au.
-
-In a second optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.86$\pm$0.02\,$\degr$, with an inclination of 33.92$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 2\pm0.02$\,mas $\Delta \delta = 12\pm0.02$\,mas relative to the stars.
-We see that both Ring13 and Ring24 share a very similar orientation and centre, given the errors.
-However, perhaps due to the joint effect of all these small differences, we can see that there are some hints for a somewhat different orientation, as summarised in Fig.~\ref{fig:polarring}.
-
-Interestingly, the ALMA image also detects faint 1.3\,mm continuum emission near the stellar positions (See the inset in Fig.~\ref{fig:images_vs_simulated}).
-Since this faint central emission is larger than the angular resolution, it is probably stemming from thermal emission from  large dust grains rather than directly from the stars.
-The main blob of this dust structure is at estimated distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.85$\pm$0.14\,au from the binary system, and, estimating its form as a Gaussian ellipse, it has a FWHM of $\sim$1.43\,au.
-If this feature is caused by the presence of millimetre-sized dust, assuming optically thin emission, its estimated mass would be around 0.12\,M$_{\earth}$.
-%and may be part of an inner disc introduced in the RT model to match the SED (see Sec.~\ref{sec:model} below).
-
 The scattered-light image in the top left panel of Fig.~\ref{fig:images_vs_simulated} also shows a double ring structure in the micron-sized dust distribution.
-The observed morphology presents an inner cavity of $\sim$10\,au in radius and two rings located at 14.10$\pm$0.01, coincident with Ring13, and 24.62$\pm$0.08\,au, coincident with Ring24, with a small gap between them at $\sim$20\,au.
+The observed morphology presents an inner cavity of $\sim$10\,au in radius and two rings located at 14.10$\pm$0.01\,au, coincident with Ring13, and 24.62$\pm$0.08\,au, coincident with Ring24, with a small gap between them at $\sim$20\,au.
 The observed second ring matches the inner wall of the 1.3\,mm continuum emission outer ring \citep{Ru_z_Rodr_guez_2019}.
@@
 
-The binary phase reported by \citet{dOrazi} in the scattered-light observation is at a position angle (PA) of 265\,$\degr$, east of north.
+The binary phase reported by \citet{dOrazi} in the scattered-light observation is at a PA of 265\,$\degr$, east of north.
 Using this measurement, the binary phase was calculated at the time of the ALMA observation at a PA of $\sim$80\,$\degr$.
-There is no hint of radio decrements in either Rings13 nor in Ring24 that would match shadowing at this PA.
+There is no hint of radio decrements in either Ring13 nor in Ring24 that would match shadowing at this PA.
 This could be explained by inefficient disc cooling compared to the speed of the illumination pattern \citep[see ][ for estimates of this cooling timescale]{Casassus2019MNRAS.486L..58C}.
@@
 
+\subsection{Spectral energy distribution}
+
 The observed SED was collected from data in the literature \citep{1988iras....7.....H, 1990A&A...234..230H, Jensen_97, 2000A&A...355L..27H, 2001KFNT...17..409K, 2003yCat.2246....0C, 2007PASJ...59S.369M, 2008PASP..120.1128O, 2010A&A...514A...1I, 2012yCat.2311....0C}, available online in \textsc{vizier}.
-We also  used  archival \textit{Spitzer} IRS spectroscopic data (see Fig.~\ref{fig:SED}).
+We also  used  archival \textit{Spitzer} IRS spectroscopic data available in the CASSIS database \citep{Lebouteiller_2015} (see Fig.~\ref{fig:SED}).
+
+The SED features the standard signature of a transition disk, with a distinctive “dip” in the continuum near 10 $\micron$m suggesting that small, warm dust is preferentially depleted (although not absent; see Section 4.2.1) near the central binary.
+although the very weak excess
+in the near-infrared makes it clear that the dust optical depths
+must be significantly diminished within at least a few AU of the
+central stars*** \citep{Rosenfeld_2013}.
 
@@
 Through trial and error, we found a set of values for the parameters that correctly fit the available data.
-The final structure of the parametric model is summarised in  Fig.~\ref{fig:profiles}.
+The final structure of the parametric model is summarised in  Fig.~\ref{fig:profiles}, where we show on the top panel surface density profiles for gas, large and small dust grains, and in the bottom panel the aspect ratio profile.
 
 The stars were modeled using two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C}, with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of $\mathrm{log}(\,\dot{\mathrm{M}}/(\mathrm{M}_{\sun}\,\mathrm{yr^{-1}}) = -$9.3 for both cases to include excess UV due to stellar accretion \citep{10.1111/j.1365-2966.2011.19366.x}.
-The stars were placed at a mutual separation of 0.041\,au, so that their centre of mass coincides with the origin, and oriented at a PA of 250\,$\degr$, so that the secondary lies to the NWW from the primary, thus casting the same shadow as observed by \citet{dOrazi}.
+The stars were placed at a mutual separation of 0.041\,au, so that their centre of mass coincides with the origin, and oriented at a PA of 250\,$\degr$, so that the secondary lies to the NW from the primary, thus casting the same shadow as observed by \citet{dOrazi}.
 
@@
 
-New ALMA 1.3\,mm continuum imaging of the circumbinary disc around V4046\,Sgr were analysed in the context of the available IR imaging and the observed spectral energy distribution using an RT model.
+We presented new ALMA 1.3\,mm continuum imaging of the circumbinary disc around V4046\,Sgr.
+We analysed the 1.3\,mm map in combination with the available IR imaging and the observed spectral energy distribution using an RT model.
 The key conclusions are as follows.
@@
 The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes around 0.7\,M$_{\earth}$ millimetre-sized grains.
-Using the parametric model scale height value ($H=$ 0.60\,au at 13.15\,au) we have that the ring width is roughly 4 times its estimated height.
+Using the parametric model scale height value for the large grains ($H=$ 0.60\,au at 13.15\,au) we have that the ring width is roughly 4 times its estimated height.
 
@@
 
+S.C.
+acknowledges support from FONDECYT grant 1171624.
+S.P.
+acknowledges support from the Joint Committee of ESO and the Government of Chile and FONDECYT grant 1191934.
+A.Z.
+acknowledges support from the FONDECYT Iniciaci\'on en investigaci\'on project number 11190837.
+MC acknowledges support from ANID PFCHA/DOCTORADO BECAS CHILE/2018-72190574.
 This paper makes use of the following ALMA data: ADS/JAO.ALMA \#2017.0.01167.S.
@@
 The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.
-
 This research has made use of the VizieR catalogue access tool, CDS, Strasbourg, France (DOI : 10.26093/cds/vizier).
 The original description of the VizieR service was published in \citet{2000A&AS..143...23O}.
-
 This research has made use of the NASA/IPAC Infrared Science Archive, which is funded by the National Aeronautics and Space Administration and operated by the California Institute of Technology.
 
-S.C. acknowledges support from FONDECYT grant 1171624.
+\section*{Data Availability}
 
-S.P. acknowledges support from the Joint Committee of ESO and the Government of Chile and FONDECYT grant 1191934.
-
-A.Z. acknowledges support from the FONDECYT Iniciaci\'on en investigaci\'on project number 11190837
-
-MC acknowledges support from ANID PFCHA/DOCTORADO BECAS CHILE/2018-72190574.
-
-%\section*{Data Availability}
+The data used in this article are presented in Figure 1.
+The final images can be found in FITS format in supplementary materials while the original raw data can be downloaded directly from the ALMA archive using project code 2017.1.01167.S.
+The SPHERE/IRDIS data can be downloaded from the ESO archive using project code 096.C-0523(A).
 

### 2021-03-05 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 If this feature is caused by the presence of millimetre-sized dust, assuming optically thin emission, its estimated mass would be around 0.12\,M$_{\earth}$.
-%and may be part of an inner disc introduced in the RT model to match the SED (see Sec.~\ref{sec:model} below).
+
+\begin{multline}
+      M_{blob} = 0.03 M_{\sun} \left(\frac{F}{1\,\mathrm{Jy}}\right) \left(\frac{D}{100\,\mathrm{pc}}\right)^2 \left(\frac{\lambda}{1.3\,\mathrm{mm}}\right)^3 
+      \\
+      \left(\frac{50\,\mathrm{K}}{T}\right)    \left(\frac{0.02\,\mathrm{cm^2/g}}{\kappa_{1.3\,\mathrm{mm}}}\right)
+\end{multline}
 
@@
 
-The SED features the standard signature of a transition disk, with a distinctive “dip” in the continuum near 10 $\micron$m suggesting that small, warm dust is preferentially depleted (although not absent; see Section 4.2.1) near the central binary.
-although the very weak excess
-in the near-infrared makes it clear that the dust optical depths
-must be significantly diminished within at least a few AU of the
-central stars*** \citep{Rosenfeld_2013}.
+%The SED features the standard signature of a transition disk, with a distinctive “dip” in the continuum near 10 $\micron$m suggesting that small, warm dust is preferentially depleted (although not absent; see Section 4.2.1) near the central binary.
+although the very weak excess in the near-infrared makes it clear that the dust optical depths must be significantly diminished within at least a few AU of the central stars*** \citep{Rosenfeld_2013}.
 

### 2021-04-06 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

--- 2021-03-05 Draft_V4046Sgr_mnras.tex
@@
 
-The ring width can be measured in polar coordinates by fitting 1-D Gaussians, thus obtaining a width and centroid at each azimuth (see Fig.~\ref{fig:polarring}).
+The ring width can be measured in polar coordinates by fitting 1-D Gaussians at each azimuth, thus obtaining a width and centroid.
+In Fig.~\ref{fig:polarring}) is shown the positions of the obtained centroids and widths over the polar decomposition of the ALMA image.
 On average, we obtained a FWHM of 2.83$\pm$0.50\,au, and a stellocentric radius of 13.15$\pm$0.26\,au.
@@
 We see that both Ring13 and Ring24 share a very similar orientation and centre, given the errors.
-However, perhaps due to the joint effect of all these small differences, we can see that there are some hints for a somewhat different orientation, as summarised in Fig.~\ref{fig:polarring}.
+However, very likely due to the joint effect of all these small differences, we can see that there are some hints for a somewhat different orientation.
+This is summarised in the second panel of Fig.~\ref{fig:polarring}, where is showing the difference between the Gaussian fitting at each azimuth for both optimization.
+Both fitted centroids follow a curve almost entirely within the errors of the other one, leaving the window open to the discussion of if this differences might be just a consequence of the pointing error or are they a real notable feature of the disc.
 
@@
 The main blob of this dust structure is at estimated distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.85$\pm$0.14\,au from the binary system, and, estimating its form as a Gaussian ellipse, it has a mean FWHM of $\sim$1.43\,au.
-If this feature is caused by the presence of millimetre-sized dust, assuming optically thin emission, its estimated mass would be around 0.12\,M$_{\earth}$.
-%and may be part of an inner disc introduced in the RT model to match the SED (see Sec.~\ref{sec:model} below).
+If this feature is caused by the presence of millimetre-sized dust, assuming optically thin emission, i.e.
+following
+\begin{multline}
+    \label{optically_thin_equation}
+      M_{blob} = 0.03 M_{\sun} \left(\frac{F}{1\,\mathrm{Jy}}\right) \left(\frac{d}{100\,\mathrm{pc}}\right)^2 \left(\frac{\lambda}{1.3\,\mathrm{mm}}\right)^3 
+      \\
+      \left(\frac{50\,\mathrm{K}}{T}\right)    \left(\frac{0.02\,\mathrm{cm^2/g}}{\kappa_{1.3\,\mathrm{mm}}}\right),
+\end{multline}
+where $F$ is the total flux of the blob, $d$ the distance of 71.4\,pc , $\lambda$ the wavelength, $\kappa_{1.3\,\mathrm{mm}}$ the opacity at 1.3\,mm and the temperature set at $T=500\,\mathrm{K}$.
+Then, its estimated mass would be around 0.12\,M$_{\earth}$.
 
@@
 
-\subsection{Spectral energy distribution}
+\subsection{Spectral energy distribution} \label{subsec:SED}
 
@@
 We also  used  archival \textit{Spitzer} IRS spectroscopic data available in the CASSIS database \citep{Lebouteiller_2015} (see Fig.~\ref{fig:SED}).
-
-The SED features the standard signature of a transition disk, with a distinctive “dip” in the continuum near 10 $\micron$m suggesting that small, warm dust is preferentially depleted (although not absent; see Section 4.2.1) near the central binary.
-although the very weak excess
-in the near-infrared makes it clear that the dust optical depths
-must be significantly diminished within at least a few AU of the
-central stars*** \citep{Rosenfeld_2013}.
+The SED describe the characteristic “dip” near 10 $\micron$, a common element of transition disk, as described by \citet{Rosenfeld_2013}.
+\citet{Jensen_97} concluded that these data matched that of a extended circumbinary disk truncated at $\sim$0.3\,au, as the interior would also be expected to be cleared by dynamical effects of the central binary \citep{Art_Lu}.
 
@@
 where $H_\circ$ is the scale height at $r$ = $r_\circ$, $\psi$ is the flaring index and $\chi$ is a scaling factor (in the range $0-1$) that mimics dust settling.
+In hydrostatical equilibrium dust diffusion and settling are expected to balance each other, leading to a settling factor of $\chi = \sqrt{D_{\rm d}/(D_{\rm d} + St)}$ \citep{Dubrulle1995}.
+Here, $D_{\rm d}$ is a dimensionless parameter that informs about the level of diffusivity (it is typically assumed to be similar to the level of turbulence for the particle sizes regarded here \citep{2007Icar..192..588Y}.
+The Stokes number,
+\begin{equation}
+    {\rm St} := 0.5 \,\pi a \rho_{\rm mat} \, \Sigma_{\rm gas}^{-1}, 
+\end{equation}
+summarises a particle's dynamical behaviour in a given environment (where $\rho_{\rm mat}$ represents a dust particle's material density)..
+By definition, the gas has no settling, and the small dust grain's settling is negligible.
+As we do not know the level of diffusivity in the disc (this will be a topic of interest in Section~\ref{sec:results}), nor the exact value of $\Sigma_{\rm gas}$, we infer the scaling factor for large dust, $\chi_{\rm ld}$, from the width of Ring13.
+In the radial profile this ring is observed two to three times wider in the gas-tracing NIR than in the fluxes received from larger grains by ALMA.
 The gas and the small dust (sd) grains have no settling, so $\chi_{\mathrm{gas}}$ = $\chi_{\mathrm{sd}}$ = 1.
@@
 We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =3.3\times10^{-4}$\,$\mathrm{g\,cm^{-3}}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
-Our model extends from 0.3\,au outwards, as the interior is expected to be cleared by dynamical effects of the central binary \citep{Art_Lu}
+Our model extends from 0.3\,au outwards, consistent with the inner edge radius inferred from the SED data (See sec.
+\ref{subsec:SED}).
 
@@
 The simulated DPI image at 1.65\,$\micron$ in Fig.~\ref{fig:images_vs_simulated} was obtained with the scattering matrix calculated by the {\tt makeopac.py} script provided in the \textsc{radmc3d} package.
-As a way of reproducing the \textit{H}-band image, we used a different grain size distribution, where we centred a Gaussian at 0.4\,$\micron$, smeared out by 30\% ($\sigma$ = 0.12\,$\micron$), and with distributed over 20 bins within that range.
-This distribution applies only to generate the NIR $Q_\phi$ image.
+As a way of reproducing the \textit{H}-band image, we used a different grain size distribution, where we centred a Gaussian at $\mathrm{a}$ = 0.4\,$\micron$ with $\sigma_{\mathrm{a}}$ = 0.12\,$\micron$ (smeared out by 30\%), and distributed the dust over 20 bins within the range of $\pm \sigma$.
+This distribution applies only to generate the NIR $Q_\phi$ image and not the ALMA image or the SED.
 To produce this $Q_\phi$ image we performed a linear combination of the two orthogonal linear polarizations \textit{U} and \textit{Q}, following \citet{Avenhaus_2017}, which gives a representation of an unbiased estimate of the polarized intensity image.
@@
 The simulated images and the SED of the model are shown in Fig.~\ref{fig:images_vs_simulated} and Fig.~\ref{fig:SED} respectively.
+The model presented here is a solution of a very degenerative problem, ergo, as a way of computing a measure of goodness of our model, we calculated a chi--square optimization to find the uncertainties of the some relevant parameters that will be useful for the discussion.
+Thus, we found that the width of Ring13 is $w_\mathrm{g} = 5.42^{+0.01}_{-1.15}$\,au, the scale height is $H_\circ = 2.2^{+0.01}_{-0.03}$\,au at $r_\circ = 18$\,au, the location of Ring6 is.
 
@@
 
-The effective beam size of the presented ALMA observations marginally resolves the FWHM of Ring13 to be $w_\mathrm{d} = 2.46\pm$0.56\,au.
-Using that the gas' Ring13-FWHM in the RT model corresponds to $w_\mathrm{g} = 5.42\mathrm{au}$, we can see that large dust grains have to be radially converged to explain the discrepancy.
+The effective beam size of the presented ALMA observations marginally resolves the FWHM of Ring13 to be $w_\mathrm{d} = 2.46\pm0.56$\,au.
+Using that the gas' Ring13-FWHM in the RT model corresponds to $w_\mathrm{g} = 5.42^{+0.01}_{-1.15}$\,au, we can see that large dust grains have to be radially converged to explain the discrepancy.
 
 Even though the radial spread of large dust grains in Ring13 appears to be quite thin, the width in comparison to the sub-lying gas profile speaks for the presence of considerable turbulent diffusion.
-Following a similar ring analysis as in \citet{2018ApJ...869L..46D}, we find that the ratio between the dimensionless diffusion parameter, $D$, and the dimensionless Stokes number, St, (which parameterizes the dynamical behaviour of a grain) is roughly, $D/{\rm St}\approx 0.1$.
+Following a similar ring analysis as in \citet{2018ApJ...869L..46D}, we find that the ratio between the dimensionless diffusion parameter, $D_{\rm d}$, and the dimensionless Stokes number, St, (which parameterizes the dynamical behaviour of a grain) is roughly, $D_{\rm d}/{\rm St}\approx 0.1$.
 The observed signal is expected to be dominated by grains of size $a\approx 0.02\,{\rm cm}$.
@@
 With these values, the relevant Stokes number is approximated to be St$\approx 0.1$.
-This yields an estimate for the level of diffusivity of $D\approx 0.01$.
-It further provides a value for the level of turbulent viscosity in Ring13, $\alpha_{\rm turb}\approx 0.01$, assuming viscosity to be equal to the level of diffusion \citep{2007Icar..192..588Y}.
+This yields an estimate for the level of diffusivity of $D_{\rm d}\approx 0.01$.
+It further provides a value for the level of turbulent viscosity in Ring13, $\alpha_{\rm turb}\approx 0.01$, assuming the level of turbulence to be equal to the level of diffusion \citep{2007Icar..192..588Y}.
 We note that an observation of molecular line broadening has found no evidence for turbulent contributions, suggesting $\alpha_{\rm turb}<0.01$ \citep{Flaherty_2020}.
 The value inferred from our model is just within this limit.
-It is linearly proportional to the local dust-to-gas ratio (by our definition of the gas surface density profile) a standard ISM  value of 0.01 for the dust-to-gas ratio would thus lead to an expected level of turbulent viscosity of $\alpha_{\rm turb}\approx 5\times10^{-3}$.
-While the exact value for $\alpha_{\rm turb}$ is not well constrained, the presence of turbulence is a robust detection, as it is required to explain the radial spread of the resolved Ring13.
+By our definition of the gas surface density profile, the value inferred for the level of turbulence is linearly proportional to the local dust-to-gas ratio.
+Lower values than the chosen ratio of 0.05 would, therefore, lead to an equally lower level of turbulence in the assessment.
+While the exact value for $\alpha_{\rm turb}$ is not well constrained, a certain level of turbulence is required to explain the radial spread of the resolved Ring13.
 

### 2021-04-06 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 \end{equation}
-where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring5}}=5.5$\,au, $\mu_{\mathrm{Ring13}}=14.9$\,au\}, ring widths \{$\sigma_{\mathrm{Ring5}}=1$\,au, $\sigma_{\mathrm{Ring13}}=2.3$\,au\}, and normalizations \{$\Sigma_{\circ,\mathrm{Ring5}}=3.3$\,$\mathrm{au\,g\,cm^{-3}}$, $\Sigma_{\circ,\mathrm{Ring13}}=6.
+where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring5}}=5.1$\,au, $\mu_{\mathrm{Ring13}}=14.9$\,au\}, ring widths \{$\sigma_{\mathrm{Ring5}}=0.35$\,au, $\sigma_{\mathrm{Ring13}}=2.1$\,au\}, and normalizations \{$\Sigma_{\circ,\mathrm{Ring5}}=3.3$\,$\mathrm{au\,g\,cm^{-3}}$, $\Sigma_{\circ,\mathrm{Ring13}}=6.
 \times 10^{-1}$\,$\mathrm{au\,g\,cm^{-3}}$\} for both components separately.
@@
 
-For Ring5 and Ring13, we choose Gaussian profiles parameterized with centroid radii $\mu_{\mathrm{Ring5, ld}}=5.5$\,au and $\mu_{\mathrm{Ring13, ld}}=13.22$\,au, ring widths of $\sigma_{\mathrm{Ring5,ld}}=0.4$\,au and $\sigma_{\mathrm{Ring13,ld}}=0.85$\,au, and normalizations $\Sigma_{\circ,\mathrm{Ring5,ld}}=1.3\times10^{-4}\,\mathrm{au\,g\,cm^{-3}}$ and $\Sigma_{\circ,\mathrm{Ring13,ld}}=2.4\,\mathrm{au\,g\,cm^{-3}}$.
+For Ring5 and Ring13, we choose Gaussian profiles parameterized with centroid radii $\mu_{\mathrm{Ring5, ld}}=5.1$\,au and $\mu_{\mathrm{Ring13, ld}}=13.22$\,au, ring widths of $\sigma_{\mathrm{Ring5,ld}}=0.14$\,au and $\sigma_{\mathrm{Ring13,ld}}=0.85$\,au, and normalizations $\Sigma_{\circ,\mathrm{Ring5,ld}}=1.3\times10^{-4}\,\mathrm{au\,g\,cm^{-3}}$ and $\Sigma_{\circ,\mathrm{Ring13,ld}}=2.4\,\mathrm{au\,g\,cm^{-3}}$.
 For Ring24 we used a similar profile as for the gas --a power-law function-- but with the difference that, in an effort to recreate the break seen in the outer ring, we choose different values for $\gamma = -3.5$ and $R_c$ = 39\,au between 27.9 and 35.3\,au.
@@
 The simulated images and the SED of the model are shown in Fig.~\ref{fig:images_vs_simulated} and Fig.~\ref{fig:SED} respectively.
-The model presented here is a solution of a very degenerative problem, ergo, as a way of computing a measure of goodness of our model, we calculated a chi--square optimization to find the uncertainties of the some relevant parameters that will be useful for the discussion.
-Thus, we found that the width of Ring13 is $w_\mathrm{g} = 5.42^{+0.01}_{-1.15}$\,au, the scale height is $H_\circ = 2.2^{+0.01}_{-0.03}$\,au at $r_\circ = 18$\,au, the location of Ring6 is.
+The model presented here is a solution of a very degenerative problem, ergo, as a way of computing a measure of goodness of our model, we calculated a chi-square optimization to find the uncertainties of the some relevant parameters that will be useful for the discussion.
+Thus, we found that the width of Ring13 is $w_\mathrm{g} = 4.95^{+0.18}_{-0.33}$\,au, the scale height is $H_\circ = 2.2^{+0.01}_{-0.03}$\,au at $r_\circ = 18$\,au, the location of Ring5 is $r=5.1^{+0.2}_{-0.1}$\,au and its width is $w_\mathrm{Ring5} = 0.82^{+0.16}_{-0.13}$\,au.
 
@@
 The observed SED is compared with the model in Fig.~\ref{fig:SED}.
-From the similarity with the data, we propose that there has to be a small-grain population close to the stars down to 0.3\,au.
-The observed central and compact signal in the ALMA observation cannot be explained with the hypothesis of thermal emission from large grains in the inner disc.
+From the similarity with the data, we propose that there has to be a small-grain population close to the stars down to 0.3\,au, i.e.
+an inner disc.
+On the other hand, the observed central and compact signal in the ALMA observation cannot be explained with the hypothesis of thermal emission from large grains in the inner disc.
 Following the mass estimates in Section\,\ref{sec:Observations}, the millimetre-sized dust needed reaches $\sim$18 times larger surface densities than in the gas, resulting in a large excess at 10$\,\micron$ that does not match the data.
-On the other hand, the decision of employing the three-ringed structure (i.e.
-add Ring5 to the observed structure) relies on the fact that the SED needed a ring at a radius around 5--7\,au to have a proper fit around 10\,$\micron$.
+Meanwhile, the decision of employing the three-ringed structure (i.e.
+add Ring5 to the observed structure) relies on the fact that the SED needed a ring at a radius around 4--6\,au to have a proper fit around 10\,$\micron$.
 
@@
 
-We presented new ALMA 1.3\,mm continuum imaging of the circumbinary disc around V4046\,Sgr.
-We analysed the 1.3\,mm map in combination with the available IR imaging and the observed spectral energy distribution using an RT model.
-The key conclusions are as follows.
+Observing the same source at different wavelengths, or employing more than one instrument, will tell different stories about the same physical phenomena.
+Using radiative transfer simulations let us find a common plot that may explain all this diverse results.
+For V4046\,Sgr, there was a missing piece for an accurate representation of the system: a thin ring of millimeter-sized dust grains at a distance of $\sim$13\,au.
+We presented new ALMA 1.3\,mm continuum imaging of this circumbinary disc at an unprecedented definition ($\sim0\farcs021 \, \times \, \sim0\farcs018$).
+The new observed feature gives us some insights of the dynamics that are driving the formation of this unique morphology.
+Together with the analysis of SPHERE--IRDIS polarized images and a well-sampled SED, the radiative transfer modeling came as a useful tool for increasing the scope of our investigation.
+
+The key conclusions of this multi-layered analysis are as follows.
 \begin{enumerate}
-  \item We report the detection of a narrow ring in the 1.3\,mm continuum, with a radius 13.15$\pm$0.26\,au and an estimated width of 2.46$\pm$0.56\,au.
+  \item We report the detection of a two-ringed disc structure.
+The narrow ring in the 1.3\,mm continuum, has a radius of 13.15$\pm$0.26\,au and an estimated width of 2.46$\pm$0.56\,au.
 The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes around 0.7\,M$_{\earth}$ millimetre-sized grains.
 Using the parametric model scale height value for the large grains ($H=$ 0.60\,au at 13.15\,au) we have that the ring width is roughly 4 times its estimated height.
+The 1.3\,mm outer ring, that starts at $\sim$24\,au and has its peak intensity at $\sim$30\,au, presents a visible break in the surface brightness at $\sim$36\,au.
 
-  \item The 1.3\,mm outer ring, that starts at $\sim$24\,au and has its peak intensity at $\sim$30\,au, presents a visible break in the surface brightness at $\sim$36\,au.
+  \item The resolved radial width of Ring13 speaks for the presence of a considerable level of turbulent viscosity.
 
@@
   \item Our parametric model, which accounts for the SED of the system, involves the existence of a sub-micron dust population close (<5\,au) to the stars, and predicts the presence of another inner ring at $\sim$5\,au, made mainly of small dust grains.
-
-  \item The resolved radial width of Ring13 speaks for the presence of a considerable level of turbulent viscosity.
 

### 2021-04-06 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 
-Disc structures can be explored by means of comparing mm continuum and scattered-light images.
-These observations allow us to see the distribution of different populations of dust particles, while ALMA traces the millimetre-sized grains settled in the mid-plane of the disc, scattered-light imaging accounts for photons reflected off small micron-sized dust at the disc surface layer, high above the mid-plane.
+Disc structures can be explored by means of comparing millimetre continuum and scattered-light images.
+These observations allow us to see the distribution of different populations of dust particles: while ALMA traces the millimetre-sized grains settled in the mid-plane of the disc, scattered-light imaging accounts for photons reflected off micron-sized dust at the disc surface layer, high above the mid-plane.
 By comparing both, is easier to determine whether asymmetries in scattered light correspond to surface ripples or deep structures intrinsic to the underlying density distribution.
 
-From previous analysis of radio wavelength observations taken with Sub-millimeter Array (SMA) \citep{Rapson_2015} and subsequently with ALMA \citep{Guzman_2017,Huang_2017,Bergner_2018,Kastner_2018}, it was detected that the millimeter dust configuration of the circumbinary disc had a large inner hole of $\sim$30\,au, featuring a narrow ring centred around 37\,au that accounted for most of the dust mass.
+From previous analysis of radio wavelength observations taken with Sub-millimeter Array (SMA) \citep{Rosenfeld_2013} and subsequently with ALMA \citep{Guzman_2017,Huang_2017,Bergner_2018,Kastner_2018}, it was detected that the millimeter dust configuration of the circumbinary disc had a large inner hole of $\sim$30\,au, featuring a narrow ring centred around 37\,au that accounted for most of the dust mass.
 Later on, \citet{Avenhaus_2018} using DPI in the J and H bands confirmed the double-ring morphology presented by \citet{Rapson_2015}, where the micron-size dust disc presented an $\sim$10\,au-wide inner cavity, a narrow ring at $\sim$14\,au and the outer ring centred at $\sim$27\,au.
@@
 The small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs021 \, \times \, \sim0\farcs018$).
-The inset zooms into the central emission, and the green star marks the binary position.
+The inset zooms into the central emission, and the green star marks the center of the inner ring.
 \textit{Bottom left panel:} synthetic image at 1.65\,$\micron$.
@@
 	\centering
-	\includegraphics[width=\columnwidth]{SED_.png}
+	\includegraphics[width=\columnwidth]{SED_.pdf}
     \caption{The observed SED of V4046\,Sgr (black points and solid red curve) compared with the model (blue).
@@
 
-We choose to use Gaussian profiles to parameterize Ring5 and Ring13,
+We choose to use Gaussian profiles to parametrize Ring5 and Ring13,
 \begin{equation}

### 2021-05-10 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 Ring13 is surrounded by a $\sim$10\,au-wide gap, and it is flanked by a very mm-bright outer ring (Ring24) with a sharp inner edge at 24\,au.
-The steeply decreasing brightness of Ring24 breaks at $\sim$35\,au into a shallow tail.
+Between 25\,au and $\sim$35\,au the brightness of Ring24 is relatively flat and then breaks into a steeper tail that reaches out to $\sim$60\,au.
 In order to reproduce the SED, the model that we propose requires an inner ring at $\sim$5\,au (Ring5) composed mainly of small dust grains, hiding under the IRDIS coronagraph, and surrounding an inner circumbinary disc.
-The surprisingly thin Ring13 is nonetheless roughly 4 times wider than the model scale height.
+The surprisingly thin Ring13 is nonetheless roughly 4 times wider than its expected vertical extent.
 The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$.
@@
 Recent observations of young circumstellar discs have transformed current knowledge of planet formation.
-The focus of resolved imaging with the Atacama Large Millimetre/submillimetre Array (ALMA) or with the current generation of high-contrast cameras has mainly been towards the brighter sources \citep[e.g.][]{2020ARA&A..58..483A}.
+The focus of resolved imaging with the Atacama Large Millimeter/submillimeter Array (ALMA) or with the current generation of high-contrast cameras has mainly been towards the brighter sources \citep[e.g.][]{2020ARA&A..58..483A}.
 It is to address this bias that the programme called ``Discs Around T Tauri Stars with SPHERE'' (DARTTS-S) collected differential polarization imaging (DPI) data secured with the Spectro-Polarimeter High-contrast Exoplanet REsearch \citep[SPHERE][]{2019A&A...631A.155B} in a total of 29 solar-type stars \citep[][]{Avenhaus_2018,Garufi2020}.
@@
 The DARTTS observations revealed diverse structures and morphologies in the scattering surface of these discs.
-This article on V4046 Sagittarii (Sgr) is part of a companion programme, the DARTTS survey with ALMA (DARTTS-A, Perez et al.
-{\em in prep}), which will present millimetre observations of nine protoplanetary discs previously imaged in polarized scattered light in DARTTS-S.
+This article on V4046 Sagittarii (Sgr) is the first installment of a companion programme, the DARTTS survey with ALMA (DARTTS-A), which will present millimetre observations of nine protoplanetary discs previously imaged in polarized scattered light in DARTTS-S.
+
+Disc structures can be explored by means of comparing millimetre continuum and scattered-light images.
+These observations allow us to see the distribution of different populations of dust particles: while ALMA traces the millimetre-sized grains settled in the mid-plane of the disc, scattered-light imaging accounts for photons reflected off micron-sized dust at the disc surface layer, high above the mid-plane.
+Therefore, the comparison of both allows to trace the dynamics present at different vertical heights in the disc.
 
@@
 
-Disc structures can be explored by means of comparing millimetre continuum and scattered-light images.
-These observations allow us to see the distribution of different populations of dust particles: while ALMA traces the millimetre-sized grains settled in the mid-plane of the disc, scattered-light imaging accounts for photons reflected off micron-sized dust at the disc surface layer, high above the mid-plane.
-By comparing both, is easier to determine whether asymmetries in scattered light correspond to surface ripples or deep structures intrinsic to the underlying density distribution.
+From previous analysis of radio wavelength observations taken with Sub-millimeter Array (SMA) \citep{Rosenfeld_2013} and subsequently with ALMA \citep{Guzman_2017,Huang_2017,Bergner_2018,Kastner_2018}, it was detected that the millimetre dust configuration of the circumbinary disc had a large inner hole of $\sim$30\,au, featuring a narrow ring centred around 37\,au that accounted for most of the dust mass.
+By using DPI in the J- and H-band, \citet{Avenhaus_2018} confirmed the double-ring morphology previously presented in \citet{Rapson_2015}, where the observed brightness presented a $\sim$10\,au-wide inner cavity, a narrow ring at $\sim$14\,au and the outer ring centred at $\sim$27\,au.
 
-From previous analysis of radio wavelength observations taken with Sub-millimeter Array (SMA) \citep{Rosenfeld_2013} and subsequently with ALMA \citep{Guzman_2017,Huang_2017,Bergner_2018,Kastner_2018}, it was detected that the millimeter dust configuration of the circumbinary disc had a large inner hole of $\sim$30\,au, featuring a narrow ring centred around 37\,au that accounted for most of the dust mass.
-Later on, \citet{Avenhaus_2018} using DPI in the J and H bands confirmed the double-ring morphology presented by \citet{Rapson_2015}, where the micron-size dust disc presented an $\sim$10\,au-wide inner cavity, a narrow ring at $\sim$14\,au and the outer ring centred at $\sim$27\,au.
+The suggestion of a parametric model that simultaneously fits the NIR scattered-light and millimetre continuum brightness is challenging and has been attempted in only few previous studies \citep[e.g.][]{Dong_2018,2019MNRAS.486..304B, Ru_z_Rodr_guez_2019}.
+A successful model can serve as a convenient sample to link the observations to the structure of the underlying dust density distribution.
 
-The pursuit of creating high-fidelity parametric simulations that resolve NIR scattered-light and millimeter continuum observations simultaneously is something only few have ventured into \citep[e.g.][]{Dong_2018,2019MNRAS.486..304B, Ru_z_Rodr_guez_2019}.
-A model that achieves this quest can serve as a convenient sample to interpret real data in terms of a physical model.
-In this paper we aim to reproduce the protoplanetary disc around V4046\,Sgr with a 3D model using as guidance previous NIR images, the spectral energy distribution (SED) and a new high definition 1.3\,mm continuum ALMA image, as a way to throw light on its complex structure and the processes that are occurring in it.
+In this paper we present new observations of the continuum emission at 1.3 mm of V4046 Sgr which reveal previously undiscovered structures.
+This work also aims to reproduce the observations of the protoplanetary disc around V4046\,Sgr with a 3D model using as guidance previous NIR images, the spectral energy distribution (SED) and a new high definition 1.3\,mm continuum ALMA image, as a way to throw light on its complex structure and the processes that are occurring in it.
 
-The observations, including new 1.3\,mm continuum data, are described in Section~\ref{sec:Observations}.
-The parametric model is presented in Section~\ref{sec:model}, which builds up on the previous models of V4046\,Sgr  \citep{Rosenfeld_2013, Ru_z_Rodr_guez_2019, 2019ApJ...882..160Q}.
-Our results are discussed in Section~\ref{sec:results} and summarised in Section~\ref{sec:Conclusions}.
+The details of the observations taken into account are described in Section~\ref{sec:Observations}.
+The parametric model is presented in Section~\ref{sec:model}, the results are discussed in Section~\ref{sec:results} and in Section~\ref{sec:Conclusions} we present our conclusions.
 
 \section{Observations} \label{sec:Observations}
-\subsection{ALMA}
+\subsection{ALMA}  \label{subsec:ALMA}
 
@@
 The ring width can be measured in polar coordinates by fitting 1-D Gaussians at each azimuth, thus obtaining a width and centroid.
-In Fig.~\ref{fig:polarring}) is shown the positions of the obtained centroids and widths over the polar decomposition of the ALMA image.
-On average, we obtained a FWHM of 2.83$\pm$0.50\,au, and a stellocentric radius of 13.15$\pm$0.26\,au.
+The top panel of Fig.~\ref{fig:polarring}) shows the positions of the obtained centroids and widths over the polar decomposition of the ALMA image.
+On average, we obtained a FWHM of 2.83$\pm$0.25\,au, and a stellocentric radius of 13.15$\pm$0.42\,au.
 As the {\tt uvmem} model image has an approximate {\tt uvmem} beam of $\sim0\farcs021 \,\times \,\sim0\farcs018$, we see that Ring13 is marginally resolved.
-After subtraction of the {\tt uvmem} beam, the ring width is $\sim$2.46$\pm$0.56\,au.
+After subtraction of the {\tt uvmem} beam, the ring width is $\sim$2.46$\pm$0.40\,au.
 
@@
 However, very likely due to the joint effect of all these small differences, we can see that there are some hints for a somewhat different orientation.
-This is summarised in the second panel of Fig.~\ref{fig:polarring}, where is showing the difference between the Gaussian fitting at each azimuth for both optimization.
-Both fitted centroids follow a curve almost entirely within the errors of the other one, leaving the window open to the discussion of if this differences might be just a consequence of the pointing error or are they a real notable feature of the disc.
+This is summarised in the second panel of Fig.~\ref{fig:polarring}, where it shows the centroids of the Gaussian fitting at each azimuth for both optimization.
+The curve that follows these fitted centroids for each of the optimizations goes almost entirely within the errors of the other one, leaving the window open to the discussion of if this differences are just a consequence of the pointing error or are they a real notable feature of the disc.
 
@@
 
-\subsection{SPHERE--IRDIS}
+\subsection{SPHERE--IRDIS}  \label{subsec:SPHERE}
 
@@
     \includegraphics[width=\columnwidth]{polar_ring_aprox_and_diff_inner.pdf}
-    \caption{(a) Polar decomposition of the 1.3\,mm continuum image, using the orientation of Ring24.
+    \caption{{\bf (a)} Polar decomposition of the 1.3\,mm continuum image, using the orientation of Ring24.
 We trace Ring13 using the centroids (solid line) and width of radial Gaussian fits (blue region between the dotted lines).
-(b) Centroid of Ring13, for two disc orientations: the orange line corresponds to the same trace as in a), while the blue line is obtained for the inner ring orientation.}
+{\bf (b)} Centroid of Ring13, for two disc orientations: the orange line corresponds to the same trace as in (a), while the blue line is obtained for the inner ring orientation.}
     \label{fig:polarring}
@@
 
-The multi-frequency data can be interpreted in terms of a physical structure using radiative transfer predictions, for which we used the \textsc{radmc3d} package \citep{Dullemond_2012}.
-The general framework of the parametric model that we used is similar to that in \citet{2018MNRAS.477.5104C} for DoAr\,44, and the initial model values were inspired from those in \citet{Rosenfeld_2013}.
-Through trial and error, we found a set of values for the parameters that correctly fit the available data.
+The multi-frequency data can be interpreted in terms of a physical structure using radiative transfer predictions, for which we used the \textsc{radmc3d} package \citep[version 2.0,][]{Dullemond_2012}.
+The general framework of the parametric model that we developed is similar to that in \citet{2018MNRAS.477.5104C} for DoAr\,44, and the initial model values were inspired from those in \citet{Rosenfeld_2013}, \citet{Ru_z_Rodr_guez_2019} and \citet{2019ApJ...882..160Q}.
+Computing a high-resolution radiative transfer model that succeeds in the reproduction of multi-frequency imaging and the SED, is finding a solution to a very degenerative problem, so obtaining an ideal model with a full parameter exploration requires a level of computation and time that exceeds our capabilities.
+Consequently, our approach was to find through trial and error a set of values for the parameters that closely fit the available data.
+Then, we improved this fit implementing one dimensional chi squared optimizations for some key parameters (more on this in sec.~\ref{sec:results}).
 The final structure of the parametric model is summarised in Fig.~\ref{fig:profiles}, where we show on the top panel surface density profiles for gas, large and small dust grains, and in the bottom panel the aspect ratio profile.
 
-The stars were modeled using two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C}, with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of $\mathrm{log}(\,\dot{\mathrm{M}}/(\mathrm{M}_{\sun}\,\mathrm{yr^{-1}}) = -$9.3 for both cases to include excess UV due to stellar accretion \citep{10.1111/j.1365-2966.2011.19366.x}.
-The stars were placed at a mutual separation of 0.041\,au, so that their centre of mass coincides with the origin, and oriented at a PA of 250\,$\degr$, so that the secondary lies to the NW from the primary, thus casting the same shadow as observed by \citet{dOrazi}.
+The stars were modeled using two Kurucz photosphere models \citep{1979ApJS...40....1K, 1997A&A...318..841C}, with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$, respectively and with an accretion rate of $\mathrm{log}(\,\dot{\mathrm{M}}/(\mathrm{M}_{\sun}\,\mathrm{yr^{-1}})) = -$9.3 for both cases to include excess UV due to stellar accretion \citep{10.1111/j.1365-2966.2011.19366.x}.
+The stars were placed at a mutual separation of 0.041\,au, so that their centre of mass coincides with the origin.
+Their PA was set to 250\,$\degr$, so that the secondary lies to the NW from the primary, thus casting the same shadow as observed by \citet{dOrazi}.
 
@@
 \begin{equation}
-    {\rm St} := 0.5 \,\pi a \rho_{\rm mat} \, \Sigma_{\rm gas}^{-1}, 
+    {\rm St} := \frac{1}{2} \,\frac{\pi a \rho_{\rm mat}}{\Sigma_{\rm gas}}, 
 \end{equation}
-summarises a particle's dynamical behaviour in a given environment (where $\rho_{\rm mat}$ represents a dust particle's material density)..
-By definition, the gas has no settling, and the small dust grain's settling is negligible.
+summarises a particle's dynamical behaviour in a given environment (where $\rho_{\rm mat}$ represents a dust particle's material density).
+By definition, the gas has no settling, and the small dust grains settling is negligible, so that $\chi_{\rm gas}=\chi_{\rm sd}=1$.
 As we do not know the level of diffusivity in the disc (this will be a topic of interest in Section~\ref{sec:results}), nor the exact value of $\Sigma_{\rm gas}$, we infer the scaling factor for large dust, $\chi_{\rm ld}$, from the width of Ring13.
 In the radial profile this ring is observed two to three times wider in the gas-tracing NIR than in the fluxes received from larger grains by ALMA.
-The gas and the small dust (sd) grains have no settling, so $\chi_{\mathrm{gas}}$ = $\chi_{\mathrm{sd}}$ = 1.
-The radial spread of Ring13 appears two to three times wider in the gas-tracing NIR observations than in the fluxes received from larger grains with ALMA.
-We assume that the same ratio holds in the vertical direction (due to the settling of larger grains towards the midplane of the disc), leading to $\chi_{\mathrm{ld}}=0.4$.
+We assume that the same ratio holds in the vertical direction (due to the settling of larger grains towards the mid-plane of the disc), leading to $\chi_{\mathrm{ld}}=0.4$.
 This is analogous to assuming equal radial and vertical turbulent diffusions.
 
-For the vertical structure, \citet{dOrazi} found flaring angles, i.e.
-$H/r$, of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one.
+For the vertical structure, \citet{dOrazi} found flaring angles (i.e.
+height of the ring over the disk midplane divided by the radius of the ring), of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one.
 Our model aims to reproduce those values by using two different flaring indices, $\psi_1$ and $\psi_2$.
 The separation between the two values was set at $r = 18$\,au with $\psi_1=0.2$ for Ring5 and Ring13, and $\psi_2=0.5$ for Ring24.
-The scale height is $H_\circ = 2.2$\,au at $r_\circ = 18$\,au.
-This is summarized in Fig.\ref{fig:profiles} bottom panel that shows the aspect ratio profile $h(r)=H(r)/r$.
+The scale height is set to $H_\circ = 0.94$\,au at $r_\circ = 18$\,au.
+This is summarized in bottom panel of Fig.~\ref{fig:profiles} that shows the aspect ratio profile $h(r)=H(r)/r$.
 
-We propose a three-ringed structure to reproduce the observations.
+Although both ALMA and SPHERE--IRDIS images display two-ringed morphologies, we propose a three-ringed structure plus an inner disc to reproduce the observations.
+This bold decision is due the major fit improvement in the SED (more on this in sec.~\ref{sec:results}).
 We separate the disc into four individual regions: the inner disc, Ring5, Ring13, and Ring24.
@@
 
-The inner disc follows a power-law function defined by
+The inner disc model follows a power-law function defined by
 \begin{equation}
@@
 We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =3.3\times10^{-4}$\,$\mathrm{g\,cm^{-3}}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
-Our model extends from 0.3\,au outwards, consistent with the inner edge radius inferred from the SED data (See sec.
-\ref{subsec:SED}).
+Our model extends from 0.3\,au outwards, consistent with the inner edge radius inferred from the SED data (See sec.~\ref{subsec:SED}).
 
-We choose to use Gaussian profiles to parametrize Ring5 and Ring13,
+We chose to use Gaussian profiles to parametrize Ring5 and Ring13,
 \begin{equation}
@@
 \end{equation}
-where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring5}}=5.1$\,au, $\mu_{\mathrm{Ring13}}=14.9$\,au\}, ring widths \{$\sigma_{\mathrm{Ring5}}=0.35$\,au, $\sigma_{\mathrm{Ring13}}=2.1$\,au\}, and normalizations \{$\Sigma_{\circ,\mathrm{Ring5}}=3.3$\,$\mathrm{au\,g\,cm^{-3}}$, $\Sigma_{\circ,\mathrm{Ring13}}=6.
-\times 10^{-1}$\,$\mathrm{au\,g\,cm^{-3}}$\} for both components separately.
+where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring5}}=5.2$\,au, $\mu_{\mathrm{Ring13}}=14.9$\,au\}, ring widths \{$\sigma_{\mathrm{Ring5}}=0.25$\,au, $\sigma_{\mathrm{Ring13}}=2.2$\,au\}, and normalizations \{$\Sigma_{\circ,\mathrm{Ring5}}=3.3$\,$\mathrm{g\,cm^{-3}}$, $\Sigma_{\circ,\mathrm{Ring13}}=6.0 \times 10^{-1}$\,$\mathrm{g\,cm^{-3}}$\} for both components separately.
 
-For Ring24 we used the same power-law as for the inner disc but scaled by an empirically obtained factor, $\delta_{\mathrm{sd}}(r)$:
+For Ring24 we used the same power-law as for the inner disc but scaled by an empirically obtained factor, $\delta_{\mathrm{sd}}(r)$ and by $\epsilon(r)$, a parameter that allows us model a smoother inner edge of the outer ring:
 \begin{equation}
-  \Sigma_{\mathrm{Ring24}}(r) = \Sigma_{\mathrm{inner\,disc}}(r)\, \delta_{\mathrm{sd}}(r),
+  \Sigma_{\mathrm{Ring24}}(r) = \Sigma_{\mathrm{inner\,disc}}(r)\, \delta_{\mathrm{sd}}(r)\,\epsilon(r),
 \end{equation}
@@
   0    & r < 18\text{\,au} \\
-  4.2\times 10^4 & r > 18\text{\,au}.
+  4.2\times 10^4 & r > 18\text{\,au},
   \end{cases}
 \end{equation}
-The inner edge of Ring24 follows a different profile.
-Between $R_\mathrm{in}$ and $R_\mathrm{peak}$, which respectively mark  the inner edge and the location of maximum density of the outer ring, the gas density profile is multiplied by an additional factor
+and 
 \begin{equation}
-    \epsilon(r) = \left(\frac{ r - R_\mathrm{in}}{R_\mathrm{peak} - R_\mathrm{in}}\right)^3.
+    \epsilon(r) = 
+    \begin{cases}
+  0    & r < R_\mathrm{in} \,\, {\rm and} \,\, R_\mathrm{peak} < r \\
+  \left(\frac{ r - R_\mathrm{in}}{R_\mathrm{peak} - R_\mathrm{in}}\right)^3 & R_\mathrm{in} < r < R_\mathrm{peak},
+    \end{cases}
 \end{equation}
-This parameter allows us to model a smoother inner edge of the outer ring, with $R_\mathrm{in,gas}$ = 18.0\,au and $R_\mathrm{peak,gas}$ = 26.4\,au.
-This factor is also applied to the large dust population with $R_\mathrm{in,ld}$ = 24.2\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$.
+where $R_\mathrm{in}$ and $R_\mathrm{peak}$ respectively mark the inner edge and the location of maximum density of the outer ring.
+We used $R_\mathrm{in,gas}$ = 18.0\,au and $R_\mathrm{peak,gas}$ = 26.4\,au.
 
@@
 Since the large dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a larger inner cavity, a larger gap between Ring13 and Ring24, and a break in the outer ring.
-To be consistent with the theory, Ring5 should have a small large-dust population too, but, as this ring is not visible in the ALMA observation, we added just the right mass to be undetectable by the ALMA observation.
-We also truncated the profile of large dust grains at 63\,au.
+We only included a low density of large grains within Ring5, just underneath the detection limit of the ALMA observation, as it does not show any visible signature.We also truncated the profile of large dust grains at 63\,au.
 It is then defined by the sum of its three components
@@
 
-For Ring5 and Ring13, we choose Gaussian profiles parameterized with centroid radii $\mu_{\mathrm{Ring5, ld}}=5.1$\,au and $\mu_{\mathrm{Ring13, ld}}=13.22$\,au, ring widths of $\sigma_{\mathrm{Ring5,ld}}=0.14$\,au and $\sigma_{\mathrm{Ring13,ld}}=0.85$\,au, and normalizations $\Sigma_{\circ,\mathrm{Ring5,ld}}=1.3\times10^{-4}\,\mathrm{au\,g\,cm^{-3}}$ and $\Sigma_{\circ,\mathrm{Ring13,ld}}=2.4\,\mathrm{au\,g\,cm^{-3}}$.
-For Ring24 we used a similar profile as for the gas --a power-law function-- but with the difference that, in an effort to recreate the break seen in the outer ring, we choose different values for $\gamma = -3.5$ and $R_c$ = 39\,au between 27.9 and 35.3\,au.
+For Ring5 and Ring13, we chose Gaussian profiles parameterized with centroid radii $\mu_{\mathrm{Ring5, ld}}=5.2$\,au and $\mu_{\mathrm{Ring13, ld}}=13.22$\,au, ring widths of $\sigma_{\mathrm{Ring5,ld}}=0.1$\,au and $\sigma_{\mathrm{Ring13,ld}}=0.85$\,au, and normalizations $\Sigma_{\circ,\mathrm{Ring5,ld}}=1.3\times10^{-4}\,\mathrm{g\,cm^{-3}}$ and $\Sigma_{\circ,\mathrm{Ring13,ld}}=2.4\,\mathrm{g\,cm^{-3}}$.
+For Ring24 we used a similar profile as for the gas (a power-law function).
 The surface density for large dust grains in the outer ring is thus given by
 \begin{equation}
-    \Sigma_{\mathrm{Ring24,ld}}(r) = \Sigma_{\mathrm{c}} \left(\frac{r}{R_{\mathrm{c}}(r)}\right)^{-\gamma(r)} \exp\left[-\left(\frac{r}{R_{\mathrm{c}}(r)}\right)^{2-\gamma}\right]\,\delta_{\mathrm{ld}}(r),
+    \Sigma_{\mathrm{Ring24,ld}}(r) = \Sigma_{\mathrm{c}} \left(\frac{r}{R_{\mathrm{c}}(r)}\right)^{-\gamma_{\mathrm{ld}}} \exp\left[-\left(\frac{r}{R_{\mathrm{c}}(r)}\right)^{2-\gamma_{\mathrm{ld}}}\right]\,\delta_{\mathrm{ld}}(r) \,\epsilon(r),
 \end{equation}
@@
 \end{equation}
+and for $\epsilon(r)$ we used $R_\mathrm{in,ld}$ = 24.2\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$. In an effort to recreate the break seen in the outer ring, we used
+\begin{equation}
+  \gamma_{\mathrm{ld}}(r) =
+  \begin{cases}
+  3.5 & 27.9\text{\,au} < r < 35.3\text{\,au} \\
+    1                 &  {\rm elsewhere} \\
+
+  \end{cases}
+\end{equation}
+
 Then the final density of large dust can be calculated as
@@
 
-The observed near-far asymmetry in the DPI image is suggestive of a strongly forward-scattering phase function.
-In order to reproduce a similar asymmetry, we used much larger grains than typically used in the RT modelling of such near-IR data \citep[e.g.,][]{2018MNRAS.477.5104C}.
+The observed asymmetry between the near side and the far side of the disc in the DPI image is suggestive of a strongly forward-scattering phase function.
+In order to reproduce a similar asymmetry, we used much larger grains than typically used in the RT modelling of such NIR data \citep[e.g.,][]{2018MNRAS.477.5104C}.
 
@@
 
-While certainly not unique, our parametric model is fairly successful in reproducing the available data.
+While certainly not unique, our parametric model is fairly successful in reproducing the available data, so it became  a useful tool to discuss the real disc.
 The simulated images and the SED of the model are shown in Fig.~\ref{fig:images_vs_simulated} and Fig.~\ref{fig:SED} respectively.
-The model presented here is a solution of a very degenerative problem, ergo, as a way of computing a measure of goodness of our model, we calculated a chi-square optimization to find the uncertainties of the some relevant parameters that will be useful for the discussion.
-Thus, we found that the width of Ring13 is $w_\mathrm{g} = 4.95^{+0.18}_{-0.33}$\,au, the scale height is $H_\circ = 2.2^{+0.01}_{-0.03}$\,au at $r_\circ = 18$\,au, the location of Ring5 is $r=5.1^{+0.2}_{-0.1}$\,au and its width is $w_\mathrm{Ring5} = 0.82^{+0.16}_{-0.13}$\,au.
 
-The simulated image at 1.65\,$\micron$ shows a similar radial structure to the one visible in the observations, displaying a two ringed disc, where Ring5 hides under the artificial coronagraph.
+As mentioned before, the model presented here gives a solution to a very degenerative problem.
+Nevertheless, as a way to improve and obtain a rough measure of the accuracy of our model, we made one dimensional explorations of the parameter space and found uncertainties of some relevant parameters that will be useful for the discussion.
+Varying the value for one parameter and calculating chi-square for each new value, given $\chi^2_m$ the model chi squared value, the uncertainties (up and down) will be those with $\chi^2=\chi^2_m+1$.
+Assuming a quadratic behavior for the curve fitting, we can estimate that the scale height at $r_\circ$= 18\,au is $H_\circ = 0.92^{+0.01}_{-0.01}$\,au, the width of Ring13 is $w_\mathrm{g} = 5.18^{+0.42}_{-0.16}$\,au for the gas and $w_\mathrm{g} = 2.00^{+0.08}_{-1.4}$\,au, the location of Ring5 is $r=5.2^{+0.05}_{-0.7}$\,au and its width is $w_\mathrm{Ring5} = 0.59^{+0.08}_{-0.36}$\,au.
+
+\begin{figure*}
+	\includegraphics[width=\textwidth]{plot_chi_all.pdf}
+        \caption{one dimensional explorations of the chi squared space of our parametric model. {\it Top:} scale height at $r_\circ$=18\,au, width of }
+    \label{fig:chi}
+\end{figure*}
+
+Given those uncertainties for the width of Ring13 and the , one thought that arise is that the inner ring could be much thinner than our ALMA measurements The intrinsic error of the {\tt uvmem} correction can not be known with high accuracy, so the approximate beam may not be $1/3$ of the beam in natural weights but higher.
+Any change in this factor would translate to into a narrower Ring13.
+With a $2/5$ factor, the width of Ring13 is 2.28$\pm$0.51\,au, resulting in a marginally resolve ring.
+T
+
+The simulated image at 1.65\,$\micron$ matches the radial structure of the corresponding observation to a high degree, displaying a two ringed disc, where Ring5 hides under the artificial coronagraph.
 The visible asymmetry in the SPHERE observations is reproduced using relatively large grains, $\sim$0.4\,$\micron$, as smaller grains did not result in such strong forward scattering.
-As \citet{refId0} state, this forward scattering peak that is present in the observation may indicate that the dust grains in the disc surface are relatively large, suggesting that the disc is depleted of very-small grains.
-Or it may suggest that grains are not spherical as assumed by Mie Theory.
+As \citet{refId0} state, the strong forward scattering that is present in the observation may indicate that the dust grains in the disc surface are relatively large, suggesting that the disc is depleted of very small grains.
+Alternatively, it may suggest that grains are not spherical as assumed in the calculations of opacities using Mie theory.
 Interestingly, the model accurately shows the shadows described by \citet{dOrazi} that are present in the SPHERE--IRDIS image.
@@
 The simulated 1.3\,mm continuum image reproduces the two observed rings: the faint Ring13 and the brighter Ring24.
-The introduced Ring5 is not visible at the simulated image as its peak predicted intensities are around two times the noise in the ALMA image ($\sim$1$\times10^{-7}$\,Jy\,$\mathrm{beam}^{-1}$).
+The introduced Ring5 is not visible in the simulated image as its predicted peak intensity is around two times the noise in the ALMA image ($\sim$1$\times10^{-7}$\,Jy\,$\mathrm{beam}^{-1}$).
 This gives us an upper limit for the total millimetre-sized dust mass present in Ring5 of $\sim$2$\times10^{-5}$\,M$_{\earth}$.
@@
 Still, the strong depletion of large particles demands that within Ring5 dust evolution is very inefficient or limited, or that large particles are very rapidly removed.
-Otherwise, the present small grains should quickly coagulate to form detectable grain sizes in the ALMA observation in Fig.\ref{fig:images_vs_simulated}  \citep{Drazkowska2019}.
-The central emission is not present in the 1.3\,mm continuum image as it was impossible to achieve a bright blob without disrupting the SED fit (read below).
+Otherwise, the present small grains should quickly coagulate to form detectable grain sizes in the ALMA observation in Fig.~\ref{fig:images_vs_simulated} \citep{Drazkowska2019}.
+The central emission is not present in the simulated 1.3 mm continuum image as it was impossible to achieve a bright blob without disrupting the SED fit (read below).
 
 As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.~\ref{fig:radprofiles}), we can assume that the model provides a possible approximation of the disc structure, including the dimensions of Ring13.
-Accordingly, taking the parametric model values for Ring13, it has a radius of 13.22\,au, a FWHM of 2.00\,au, and a scale height FWHM of the millimetre-sized dust of 0.61\,au.
+Accordingly, taking the parametric model values for Ring13, it has a radius of 13.22\,au, a FWHM of 2.00\,au, and a scale height FWHM of the millimetre-sized dust of 0.6\,au.
 The total dust mass of Ring13 is about 0.7\,M$_{\earth}$ in the model.
@@
 The model predictions for the millimetre-sized dust population in Ring13 are close to the measurements, with only a 0.07\,au difference in the centroid location of the ring, and a 0.46\,au difference in the width estimation.
-Since the scale height of the large grains in Ring13 is 0.61\,au, and has a measured width of 2.46$\pm$0.56\,au, the ring is 4.1$\pm$0.9 times more extended radially than vertically.
+Since the scale height FWHM of the large grains in Ring13 is 0.6\,au, and has a measured width of 2.46$\pm$0.40\,au (See sec.~\ref{subsec:ALMA}), the ring is 4.1$\pm$0.9 times more extended radially than vertically.
 
@@
 
-The effective beam size of the presented ALMA observations marginally resolves the FWHM of Ring13 to be $w_\mathrm{d} = 2.46\pm0.56$\,au.
+The effective beam size of the presented ALMA observations marginally resolves the FWHM of Ring13 to be $w_\mathrm{d} = 2.46\pm0.40$\,au.
 Using that the gas' Ring13-FWHM in the RT model corresponds to $w_\mathrm{g} = 5.42^{+0.01}_{-1.15}$\,au, we can see that large dust grains have to be radially converged to explain the discrepancy.
@@
 From the similarity with the data, we propose that there has to be a small-grain population close to the stars down to 0.3\,au, i.e.
-an inner disc.
+an inner disc, as it was crucial to fit the 5--10\,$\micron$ range.
 On the other hand, the observed central and compact signal in the ALMA observation cannot be explained with the hypothesis of thermal emission from large grains in the inner disc.
-Following the mass estimates in Section\,\ref{sec:Observations}, the millimetre-sized dust needed reaches $\sim$18 times larger surface densities than in the gas, resulting in a large excess at 10$\,\micron$ that does not match the data.
+Following the mass estimates in Section~\ref{sec:Observations}, the millimetre-sized dust needed reaches $\sim$18 times larger surface densities than in the gas, resulting in a large excess at 10$\,\micron$ that does not match the data.
 Meanwhile, the decision of employing the three-ringed structure (i.e.
-add Ring5 to the observed structure) relies on the fact that the SED needed a ring at a radius around 4--6\,au to have a proper fit around 10\,$\micron$.
+add Ring5 to the observed structure) relies on the fact that the SED needed a ring at a radius around 4--6\,au to have a proper fit around 10\,$\micron$, otherwise, instead of the distinct bump that is present, there would be a gap.
 
@@
 Using radiative transfer simulations let us find a common plot that may explain all this diverse results.
-For V4046\,Sgr, there was a missing piece for an accurate representation of the system: a thin ring of millimeter-sized dust grains at a distance of $\sim$13\,au.
-We presented new ALMA 1.3\,mm continuum imaging of this circumbinary disc at an unprecedented definition ($\sim0\farcs021 \, \times \, \sim0\farcs018$).
+For V4046\,Sgr, there was a missing piece for an accurate representation of the system: a thin ring of millimetre-sized dust grains at a distance of $\sim$13\,au.
+We presented new ALMA 1.3\,mm continuum imaging of this circumbinary disc at an unprecedented definition ($\sim0\farcs021 \, \times \, \sim0\farcs018$) were this new ring becomes visible for the first time.
 The new observed feature gives us some insights of the dynamics that are driving the formation of this unique morphology.
@@
   \item We report the detection of a two-ringed disc structure.
-The narrow ring in the 1.3\,mm continuum, has a radius of 13.15$\pm$0.26\,au and an estimated width of 2.46$\pm$0.56\,au.
+The narrow ring in the 1.3\,mm continuum, has a radius of 13.15$\pm$0.26\,au and an estimated width of 2.46$\pm$0.40\,au.
 The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes around 0.7\,M$_{\earth}$ millimetre-sized grains.
-Using the parametric model scale height value for the large grains ($H=$ 0.60\,au at 13.15\,au) we have that the ring width is roughly 4 times its estimated height.
+Using the parametric model scale height FWHM value for the large grains ($H=$ 0.6\,au at 13.15\,au) we find that the ring width is roughly 4 times its estimated height.
 The 1.3\,mm outer ring, that starts at $\sim$24\,au and has its peak intensity at $\sim$30\,au, presents a visible break in the surface brightness at $\sim$36\,au.
@@
 
-  \item Our parametric model, which accounts for the SED of the system, involves the existence of a sub-micron dust population close (<5\,au) to the stars, and predicts the presence of another inner ring at $\sim$5\,au, made mainly of small dust grains.
+  \item Our parametric model, which accounts for the SED of the system, involves the existence of a sub-micron dust population close (<5\,au) to the stars, and predicts the presence of another inner ring at $\sim$5\,au, mainly consisting of small dust grains.
 
@@
 
-The data used in this article are presented in Figure 1.
+The data used in this article are presented in Fig.~\ref{fig:images_vs_simulated}.
 The final images can be found in FITS format in supplementary materials while the original raw data can be downloaded directly from the ALMA archive using project code 2017.1.01167.S.

### 2021-05-27 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 We see that both Ring13 and Ring24 share a very similar orientation and centre, given the errors.
-However, very likely due to the joint effect of all these small differences, we can see that there are some hints for a somewhat different orientation.
+However, quite likely due to the joint effect of all these small differences, we can see that there are some hints for a somewhat different orientation.
 This is summarised in the second panel of Fig.~\ref{fig:polarring}, where it shows the centroids of the Gaussian fitting at each azimuth for both optimization.
@@
 The main blob of this dust structure is at estimated distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.85$\pm$0.14\,au from the binary system, and, estimating its form as a Gaussian ellipse, it has a mean FWHM of $\sim$1.43\,au.
-If this feature is caused by the presence of millimetre-sized dust, assuming optically thin emission, i.e.
-following
-\begin{multline}
-    \label{optically_thin_equation}
-      M_{blob} = 0.03 M_{\sun} \left(\frac{F}{1\,\mathrm{Jy}}\right) \left(\frac{d}{100\,\mathrm{pc}}\right)^2 \left(\frac{\lambda}{1.3\,\mathrm{mm}}\right)^3 
-      \\
-      \left(\frac{50\,\mathrm{K}}{T}\right)    \left(\frac{0.02\,\mathrm{cm^2/g}}{\kappa_{1.3\,\mathrm{mm}}}\right),
-\end{multline}
-where $F$ is the total flux of the blob, $d$ the distance of 71.4\,pc , $\lambda$ the wavelength, $\kappa_{1.3\,\mathrm{mm}}$ the opacity at 1.3\,mm and the temperature set at $T=500\,\mathrm{K}$.
+\citet{Francis_2020} also did some measurements of this central emission by assuming a power--law profile for an inner disk that goes from 0.1 to 4\,au, and has a total dust mass of 0.013$\pm$0.002\,M$_{\earth}$.
+They stated that the inner radius of the disk is well beyond the sublimation radius as the system shows a low--NIR excess but a clear millimetre emission.
+
+%If this feature is caused by the presence of millimetre-sized dust, assuming optically thin emission, i.e. following
+%\begin{multline}
+%    \label{optically_thin_equation}
+%      M_{blob} = 0.03 M_{\sun} \left(\frac{F}{1\,\mathrm{Jy}}\right) \left(\frac{d}{100\,\mathrm{pc}}\right)^2 \left(\frac{\lambda}{1.3\,\mathrm{mm}}\right)^3 
+%      \\
+ %     \left(\frac{50\,\mathrm{K}}{T}\right)    %\left(\frac{0.02\,\mathrm{cm^2/g}}{\kappa_{1.3\,\mathrm{mm}}}\right),
+%\end{multline}
+%where $F$ is the total flux of the blob, $d$ the distance of 71.4\,pc , $\lambda$ the wavelength, $\kappa_{1.3\,\mathrm{mm}}$ the opacity at 1.3\,mm and the temperature set at $T=500\,\mathrm{K}$.
 Then, its estimated mass would be around 0.12\,M$_{\earth}$.
@@
 We also used archival \textit{Spitzer} IRS spectroscopic data available in the CASSIS database \citep{Lebouteiller_2015} (see Fig.~\ref{fig:SED}).
-The SED describe the characteristic “dip” near 10 $\micron$, a common element of transition disk, as described by \citet{Rosenfeld_2013}.
-\citet{Jensen_97} concluded that these data matched that of a extended circumbinary disk truncated at $\sim$0.3\,au, as the interior would also be expected to be cleared by dynamical effects of the central binary \citep{Art_Lu}.
+The SED describe the characteristic “dip” near 10 $\micron$, a common element of transition disc, as described by \citet{Rosenfeld_2013}.
+\citet{Jensen_97} concluded that these data matched that of a extended circumbinary disc truncated at $\sim$0.3\,au, as the interior would also be expected to be cleared by dynamical effects of the central binary \citep{Art_Lu}.
 
@@
 The general framework of the parametric model that we developed is similar to that in \citet{2018MNRAS.477.5104C} for DoAr\,44, and the initial model values were inspired from those in \citet{Rosenfeld_2013}, \citet{Ru_z_Rodr_guez_2019} and \citet{2019ApJ...882..160Q}.
-Computing a high-resolution radiative transfer model that succeeds in the reproduction of multi-frequency imaging and the SED, is finding a solution to a very degenerative problem, so obtaining an ideal model with a full parameter exploration requires a level of computation and time that exceeds our capabilities.
-Consequently, our approach was to find through trial and error a set of values for the parameters that closely fit the available data.
-Then, we improved this fit implementing one dimensional chi squared optimizations for some key parameters (more on this in sec.~\ref{sec:results}).
-The final structure of the parametric model is summarised in Fig.~\ref{fig:profiles}, where we show on the top panel surface density profiles for gas, large and small dust grains, and in the bottom panel the aspect ratio profile.
+Computing a high-resolution radiative transfer model that succeeds in the reproduction of multi-frequency imaging and the SED, is finding a solution to a highly degenerative problem, so obtaining an ideal model with a full parameter exploration requires a level of computation and time that exceeds our capabilities and the scope of this paper.
+Consequently, our approach was to find through trial and error a set of values for the parameters that closely fit the available data, and then, improve this fit by implementing one dimensional chi squared optimizations for some key parameters (more on this in sec.~\ref{sec:results}).
+The final structure of the parametric model is summarised in Fig.~\ref{fig:profiles}, where we show on the top panel surface density profiles for gas, large and small dust grains, and in the bottom panel the respective aspect ratio profile.
 
@@
 Reproducing the radial and vertical structure of the V4046\,Sgr disc turned out to be challenging.
-We built the model in terms of the gas distribution, and with two different dust populations: larger grains that are vertically settled and dominate the total dust mass, and a population of smaller grains that are uniformly mixed with the gas and reach higher regions above the mid-plane.
+We built the model in terms of the gas distribution, and with two main dust populations: larger grains that are vertically settled and dominate the total dust mass, and a population of smaller grains that are uniformly mixed with the gas and reach higher regions above the mid-plane.
+And we also added a third dust population of large grains and with a tightly confined distribution and a special size range just to account for the central emission.
 
@@
 For the vertical structure, \citet{dOrazi} found flaring angles (i.e.
-height of the ring over the disk midplane divided by the radius of the ring), of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one.
+height of the ring over the disc midplane divided by the radius of the ring), of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one.
 Our model aims to reproduce those values by using two different flaring indices, $\psi_1$ and $\psi_2$.
@@
 The scale height is set to $H_\circ = 0.94$\,au at $r_\circ = 18$\,au.
+This vertical structure is consistent with the measurements made by \citet{dOrazi}, as the model flaring angles are $\varphi_{\mathrm{inner}}$ = 6.5\,$\degr$ and $\varphi_{\mathrm{outer}}$ = 7.9\,$\degr$.
 This is summarized in bottom panel of Fig.~\ref{fig:profiles} that shows the aspect ratio profile $h(r)=H(r)/r$.
@@
 Although both ALMA and SPHERE--IRDIS images display two-ringed morphologies, we propose a three-ringed structure plus an inner disc to reproduce the observations.
-This bold decision is due the major fit improvement in the SED (more on this in sec.~\ref{sec:results}).
+This bold decision is due the major fit improvement in the SED and the polarize image (more on this in sec.~\ref{sec:results}).
 We separate the disc into four individual regions: the inner disc, Ring5, Ring13, and Ring24.
@@
 \end{equation}
-with
-\begin{equation}
-  \delta_{\mathrm{sd}}(r) =
-  \begin{cases}
-  0    & r < 18\text{\,au} \\
-  4.2\times 10^4 & r > 18\text{\,au},
-  \end{cases}
-\end{equation}
-and 
+with $\delta_{\mathrm{sd}}(r) = 4.2\times 10^4$ for $r > 18$\,au and zero for lower radii, and
+%\begin{equation}
+%  \delta_{\mathrm{sd}}(r) =
+%  \begin{cases}
+%  0    & r < 18\text{\,au} \\
+%  4.2\times 10^4 & r > 18\text{\,au},
+%  \end{cases}
+%\end{equation}
 \begin{equation}
@@
     \begin{cases}
-  0    & r < R_\mathrm{in} \,\, {\rm and} \,\, R_\mathrm{peak} < r \\
+  1    & r < R_\mathrm{in} \,\, {\rm and} \,\, R_\mathrm{peak} < r \\
   \left(\frac{ r - R_\mathrm{in}}{R_\mathrm{peak} - R_\mathrm{in}}\right)^3 & R_\mathrm{in} < r < R_\mathrm{peak},
@@
 Since the large dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a larger inner cavity, a larger gap between Ring13 and Ring24, and a break in the outer ring.
-We only included a low density of large grains within Ring5, just underneath the detection limit of the ALMA observation, as it does not show any visible signature.We also truncated the profile of large dust grains at 63\,au.
+We only included a low density of large grains within Ring5, just underneath the detection limit of the ALMA observation, as it does not show any visible signature.
+We also truncated the profile of large dust grains at 63\,au.
 It is then defined by the sum of its three components
@@
 \end{equation}
-and for $\epsilon(r)$ we used $R_\mathrm{in,ld}$ = 24.2\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$. In an effort to recreate the break seen in the outer ring, we used
+and for the smoothing factor $\epsilon(r)$ we used $R_\mathrm{in,ld}$ = 24.2\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$. In an effort to recreate the break seen in the outer ring, we used
 \begin{equation}
@@
     1                 &  {\rm elsewhere} \\
-
   \end{cases}
@@
 \rho_{\mathrm{large\,dust}}(r,z)=
-\frac{\Sigma_{\mathrm{ld}}(r)}{\sqrt{2\pi} \, H(r)} \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{H(r)}\right)^2\right] \, f_{\mathrm{ld}} \: \zeta .
+\frac{\Sigma_{\mathrm{ld}}(r)}{\sqrt{2\pi} \, H(r)} \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{H(r)}\right)^2\right] \, f_{\mathrm{ld}} \: \zeta.
 \end{equation}
 
-The two different populations of dust grains correspond to small grains, with radii ranging from 0.3 to 1.5\,$\micron$, and large dust grains, with radii from 0.3\,$\micron$ to 10\,mm.
+These two different populations of dust grains correspond to small grains, with radii ranging from 0.3 to 1.5\,$\micron$, and large dust grains, with radii from 0.3\,$\micron$ to 10\,mm.
 We computed the dust opacities using the {\tt bhmie} code provided in the \textsc{radmc3d} package, with a mix composed of 60\% silicate, 20\% graphite and 20\% ice.
@@
 To produce this $Q_\phi$ image we performed a linear combination of the two orthogonal linear polarizations \textit{U} and \textit{Q}, following \citet{Avenhaus_2017}, which gives a representation of an unbiased estimate of the polarized intensity image.
+
+For the reproduction of central emission we introduce a special dust population that is distributed only on a very close Gaussian ring parameterized by $\mu_{\mathrm{central\,blob}}=1.1$\,au, $\sigma_{\mathrm{central\,blob}}=0.4$\,au and $\Sigma_{\circ,\mathrm{central\,blob}}=2.4\,\mathrm{g\,cm^{-3}}$, and following the argument of \citet{Francis_2020}, it goes in past the sublimation radius until it reaches the grid boundary.
+This dust population has grains with radii ranging from 0.8 to 10\,mm, same upper limit as the large dust but is depleted of small grains.
+This different size range is a way to avoid creating excess NIR in the SED and to be consistent with previous mass estimates (see Appendix~\ref{sec:Appendix}).
+As the ring is extremely proximate to the binary system the dust will not have any traces of ice, so we used a composition mix of 70\% silicate and 30\% graphite.
 
@@
 
-As mentioned before, the model presented here gives a solution to a very degenerative problem.
-Nevertheless, as a way to improve and obtain a rough measure of the accuracy of our model, we made one dimensional explorations of the parameter space and found uncertainties of some relevant parameters that will be useful for the discussion.
-Varying the value for one parameter and calculating chi-square for each new value, given $\chi^2_m$ the model chi squared value, the uncertainties (up and down) will be those with $\chi^2=\chi^2_m+1$.
-Assuming a quadratic behavior for the curve fitting, we can estimate that the scale height at $r_\circ$= 18\,au is $H_\circ = 0.92^{+0.01}_{-0.01}$\,au, the width of Ring13 is $w_\mathrm{g} = 5.18^{+0.42}_{-0.16}$\,au for the gas and $w_\mathrm{g} = 2.00^{+0.08}_{-1.4}$\,au, the location of Ring5 is $r=5.2^{+0.05}_{-0.7}$\,au and its width is $w_\mathrm{Ring5} = 0.59^{+0.08}_{-0.36}$\,au.
-
-\begin{figure*}
-	\includegraphics[width=\textwidth]{plot_chi_all.pdf}
-        \caption{one dimensional explorations of the chi squared space of our parametric model. {\it Top:} scale height at $r_\circ$=18\,au, width of }
-    \label{fig:chi}
-\end{figure*}
+As mentioned before, the model presented here gives a solution to a highly degenerative problem.
+Nevertheless, as a way to improve and obtain a rough measure of the accuracy of our model, we made one dimensional explorations of the parameter space and found uncertainties of some relevant parameters that will be useful for the discussion (see Appendix.~\ref{sec:Appendix}).
+We can estimate that the scale height at $r_\circ$= 18\,au is $H_\circ = 0.92^{+0.01}_{-0.01}$\,au, the width of Ring13 is $w_\mathrm{g} = 5.18^{+0.42}_{-0.16}$\,au for the gas and $w_\mathrm{g} = 2.00^{+0.08}_{-1.4}$\,au, the location of Ring5 is $r=5.2^{+0.05}_{-0.7}$\,au and its width is $w_\mathrm{Ring5} = 0.59^{+0.08}_{-0.36}$\,au.
 
@@
 A zone of radially increasing gas pressure can entirely filter out large dust grains from inner regions, while smaller grains can be able to overcome this barrier due to their strong frictional coupling to the gas accretion flow \citep[studied in the context of planetary gaps,][]{Rice2006,Zhu2012,Weber2018}.
-Still, the strong depletion of large particles demands that within Ring5 dust evolution is very inefficient or limited, or that large particles are very rapidly removed.
+Still, the strong depletion of large particles demands that within Ring5 dust evolution is extremely inefficient or limited, or that large particles are rapidly removed.
 Otherwise, the present small grains should quickly coagulate to form detectable grain sizes in the ALMA observation in Fig.~\ref{fig:images_vs_simulated} \citep{Drazkowska2019}.
@@
 In turn, our model reproduces the observations of Ring24 with peak intensity at $\sim$30\,au, and break at $\sim$36\,au.
-It contains a total dust mass of $\sim$44\,M$_{\earth}$.
+It contains a total dust mass of $\sim$45\,M$_{\earth}$, that stands under the lower limit of 60\,M$_{\earth}$ inferred by \citet{Ru_z_Rodr_guez_2019} from a previous 860\,$\micron$ continuum ALMA image.
 The model predictions for the millimetre-sized dust population in Ring13 are close to the measurements, with only a 0.07\,au difference in the centroid location of the ring, and a 0.46\,au difference in the width estimation.
 Since the scale height FWHM of the large grains in Ring13 is 0.6\,au, and has a measured width of 2.46$\pm$0.40\,au (See sec.~\ref{subsec:ALMA}), the ring is 4.1$\pm$0.9 times more extended radially than vertically.
+The central emission radial profile is also well reproduced, and the lack of a high NIR excess indicate that the dust in this blob must be at least bigger than 0.5\,mm (see Appendix~\ref{sec:Appendix}).
+In addition, our interpretation of a Gaussian close ring agrees with the mass estimates of \citet{Francis_2020} with a dust mass of 0.012\,M$_{\earth}$, implying a slightly higher lower limit for the dust population around the central region.
 
@@
 The effective beam size of the presented ALMA observations marginally resolves the FWHM of Ring13 to be $w_\mathrm{d} = 2.46\pm0.40$\,au.
-Using that the gas' Ring13-FWHM in the RT model corresponds to $w_\mathrm{g} = 5.42^{+0.01}_{-1.15}$\,au, we can see that large dust grains have to be radially converged to explain the discrepancy.
+Using that the FWHM of the gas in Ring13 in the RT model corresponds to $w_\mathrm{g} = 5.42^{+0.01}_{-1.15}$\,au, we can see that large dust grains have to be radially converged to explain the discrepancy.
 
@@
   \item The resolved radial width of Ring13 speaks for the presence of a considerable level of turbulent viscosity.
+
+  \item The central emission observed by ALMA might be by
 
@@
 %%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
+\appendix
+
+\section{Parameter--space exploitation} \label{sec:Appendix}
+
+The model presented here has many degrees of freedom and each model requires a high level of computational power and time, so a MCMC optimization or similar methods of parameter exploration are impossible to acquire.
+But as a way to compute a measure of goodness of fit and to try to quantify the improvements we did a partial exploration of the parameter space.
+Varying the value for one parameter and calculating chi-square for each new value, given $\chi^2_m$ the model chi squared value, the uncertainties (up and down) will be those with $\chi^2=\chi^2_m+1$.
+Assuming a quadratic behavior for the curve fitting,
+\begin{figure*}
+	\includegraphics[width=\textwidth]{plot_chi_all.pdf}
+        \caption{one dimensional explorations of the chi squared space of our parametric model. {\it Top:} scale height at $r_\circ$=18\,au, width of }
+    \label{fig:chi}
+\end{figure*}
+
+The
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2021-05-27 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 Nevertheless, as a way to improve and obtain a rough measure of the accuracy of our model, we made one dimensional explorations of the parameter space and found uncertainties of some relevant parameters that will be useful for the discussion (see Appendix.~\ref{sec:Appendix}).
-We can estimate that the scale height at $r_\circ$= 18\,au is $H_\circ = 0.92^{+0.01}_{-0.01}$\,au, the width of Ring13 is $w_\mathrm{g} = 5.18^{+0.42}_{-0.16}$\,au for the gas and $w_\mathrm{g} = 2.00^{+0.08}_{-1.4}$\,au, the location of Ring5 is $r=5.2^{+0.05}_{-0.7}$\,au and its width is $w_\mathrm{Ring5} = 0.59^{+0.08}_{-0.36}$\,au.
+We can estimate confidence intervals for the scale height at $r_\circ$= 18\,au with $H_\circ = 0.92^{+0.01}_{-0.01}$\,au, for the location of Ring5 with $r=5.2^{+0.14}_{-0.36}$\,au, and for the width of gas Ring13 of $w_\mathrm{g} = 5.18^{+0.33}_{-0.20}$\,au.
 
-Given those uncertainties for the width of Ring13 and the , one thought that arise is that the inner ring could be much thinner than our ALMA measurements The intrinsic error of the {\tt uvmem} correction can not be known with high accuracy, so the approximate beam may not be $1/3$ of the beam in natural weights but higher.
+%Given those uncertainties for the width of Ring13 and the , one thought that arise is that the inner ring could be much thinner than our ALMA measurements The intrinsic error of the {\tt uvmem} correction can not be known with high accuracy, so the approximate beam may not be $1/3$ of the beam in natural weights but higher.
 Any change in this factor would translate to into a narrower Ring13.
@@
 But as a way to compute a measure of goodness of fit and to try to quantify the improvements we did a partial exploration of the parameter space.
-Varying the value for one parameter and calculating chi-square for each new value, given $\chi^2_m$ the model chi squared value, the uncertainties (up and down) will be those with $\chi^2=\chi^2_m+1$.
-Assuming a quadratic behavior for the curve fitting,
+We explore $\chi^2$ space in the vicinity of the model values for the scale height at $r_\circ$, the location of Ring5, the width of the gas component of Ring13, the width of the gas part of Ring5, the width of the large dust portion of Ring13 and around the lower limit of the grain sizes in the blob.
+The parameter space exploration is shown in Figure~\ref{fig:chi}.
+Our model fits the SED and two images, so the total $\chi^2$ value for a given model is composed of the sum of the $\chi^2$ values for each of the three fits.
+
+For the first three parameters, we find that the value of the parameter in our model is almost at a minimum in its one dimensional $\chi^2$ space, so given $\chi^2_m$ the total chi squared value for the model, the uncertainties (up and down) will be those with $\chi^2=\chi^2_m+1$.
+As the values are around a local minimum, we can as assume a quadratic equation for the curve fitting.
+
+For the the other three parameters, we found that although our chosen values are close to a minimum, the geometries are more suggestive of different border conditions.
+These exploration allow us to support the idea of Ring5, as it is clear that the absence of it creates a great increment in the total $\chi^2$ value, but also that the ring must be quite thin.
+For the case of the lower limit of the central blob, it is evident that there is a threshold around 500\,$\micron$, where the SED start to deviate far away from a minimum, that point represent where the NIR excess becomes significant.
+
 \begin{figure*}
-	\includegraphics[width=\textwidth]{plot_chi_all.pdf}
-        \caption{one dimensional explorations of the chi squared space of our parametric model. {\it Top:} scale height at $r_\circ$=18\,au, width of }
+	\includegraphics[width=\textwidth]{plot_chi_squared_all800.pdf}
+        \caption{one dimensional explorations of the chi squared space of our parametric model.
+Each panel display at the bottom the $\chi^2$ values for the SED and for the two images separately, and on top the total $\chi^2$ value in terms of the parameter value.
+{\it Top:} scale height at $r_\circ$=18\,au, location of Ring5, width of the gas component of Ring13.
+{\it Bottom:} Width of the gas part of Ring5, width of the large dust section of Ring13, lower limit of the grain sizes in the blob.}
     \label{fig:chi}
 \end{figure*}
-
-The
 

### 2021-05-27 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 The introduced Ring5 is not visible in the simulated image as its predicted peak intensity is around two times the noise in the ALMA image ($\sim$1$\times10^{-7}$\,Jy\,$\mathrm{beam}^{-1}$).
-This gives us an upper limit for the total millimetre-sized dust mass present in Ring5 of $\sim$2$\times10^{-5}$\,M$_{\earth}$.
+This gives us an upper limit for the total millimetre--sized dust mass present in Ring5 of $\sim$2$\times10^{-5}$\,M$_{\earth}$.
 The depletion of large dust grains in Ring5 is consistent with efficient dust trapping in Ring13.
@@
 Otherwise, the present small grains should quickly coagulate to form detectable grain sizes in the ALMA observation in Fig.~\ref{fig:images_vs_simulated} \citep{Drazkowska2019}.
-The central emission is not present in the simulated 1.3 mm continuum image as it was impossible to achieve a bright blob without disrupting the SED fit (read below).
+The central emission is also well reproduced with the inclusion of a Gaussian close ring, resulting in the observed central blob.
+The lack of a high NIR excess in the SED indicate that the dust in this blob must be at least bigger than 0.5\,mm (see Appendix~\ref{sec:Appendix}), but we choose to use 0.8\,mm as the lower limit for the dust population that composes this feature because this predicts a dust mass of 0.012\,M$_{\earth}$, that is in agreement with the mass estimate of \citet{Francis_2020} (0.013$\pm$0.002\,M$_{\earth}$).
 
 As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.~\ref{fig:radprofiles}), we can assume that the model provides a possible approximation of the disc structure, including the dimensions of Ring13.
-Accordingly, taking the parametric model values for Ring13, it has a radius of 13.22\,au, a FWHM of 2.00\,au, and a scale height FWHM of the millimetre-sized dust of 0.6\,au.
-The total dust mass of Ring13 is about 0.7\,M$_{\earth}$ in the model.
-In turn, our model reproduces the observations of Ring24 with peak intensity at $\sim$30\,au, and break at $\sim$36\,au.
-It contains a total dust mass of $\sim$45\,M$_{\earth}$, that stands under the lower limit of 60\,M$_{\earth}$ inferred by \citet{Ru_z_Rodr_guez_2019} from a previous 860\,$\micron$ continuum ALMA image.
+The FWHM of the gas in Ring13 in the RT model corresponds to $w_\mathrm{g} = 5.18^{+0.32}_{-0.20}$\,au, but the  large dust grains have to be radially converged to explain the ALMA image.
+Accordingly, taking the parametric model values for the large dust in Ring13, it has a FWHM of 2.00\,au, a radius of 13.22\,au, and a scale height FWHM of the millimetre-sized dust of 0.25\,au.
+The total dust mass of Ring13 would be about 0.7\,M$_{\earth}$.
 The model predictions for the millimetre-sized dust population in Ring13 are close to the measurements, with only a 0.07\,au difference in the centroid location of the ring, and a 0.46\,au difference in the width estimation.
-Since the scale height FWHM of the large grains in Ring13 is 0.6\,au, and has a measured width of 2.46$\pm$0.40\,au (See sec.~\ref{subsec:ALMA}), the ring is 4.1$\pm$0.9 times more extended radially than vertically.
-The central emission radial profile is also well reproduced, and the lack of a high NIR excess indicate that the dust in this blob must be at least bigger than 0.5\,mm (see Appendix~\ref{sec:Appendix}).
-In addition, our interpretation of a Gaussian close ring agrees with the mass estimates of \citet{Francis_2020} with a dust mass of 0.012\,M$_{\earth}$, implying a slightly higher lower limit for the dust population around the central region.
+Since the scale height FWHM of the large grains in Ring13 is 0.25\,au, and that from the ALMA observation we can resolve a width of 2.46$\pm$0.40\,au (See sec.~\ref{subsec:ALMA}), the ring is 9.7$\pm$1.5 times more extended radially than vertically.
+Looking at the rest of the disc, in turn, our model reproduces the observations of Ring24 with peak intensity at $\sim$30\,au, and breaks at $\sim$36\,au.
+It contains a total dust mass of $\sim$45\,M$_{\earth}$.%, that stands under the lower limit of 60\,M$_{\earth}$ inferred by \citet{Ru_z_Rodr_guez_2019} from a previous 860\,$\micron$ continuum ALMA image.
 
@@
 This idea is supported by the similarity to the structure around HD\,169142 which \citet{2020arXiv200711565B} reproduced by including several giant planets.
-
-The effective beam size of the presented ALMA observations marginally resolves the FWHM of Ring13 to be $w_\mathrm{d} = 2.46\pm0.40$\,au.
-Using that the FWHM of the gas in Ring13 in the RT model corresponds to $w_\mathrm{g} = 5.42^{+0.01}_{-1.15}$\,au, we can see that large dust grains have to be radially converged to explain the discrepancy.
 
@@
 The model presented here has many degrees of freedom and each model requires a high level of computational power and time, so a MCMC optimization or similar methods of parameter exploration are impossible to acquire.
-But as a way to compute a measure of goodness of fit and to try to quantify the improvements we did a partial exploration of the parameter space.
+But as a way to compute a measure of goodness of fit and to try to quantify the improvements, we did a partial exploration of the parameter space.
 We explore $\chi^2$ space in the vicinity of the model values for the scale height at $r_\circ$, the location of Ring5, the width of the gas component of Ring13, the width of the gas part of Ring5, the width of the large dust portion of Ring13 and around the lower limit of the grain sizes in the blob.
@@
 Our model fits the SED and two images, so the total $\chi^2$ value for a given model is composed of the sum of the $\chi^2$ values for each of the three fits.
+\begin{equation}
+    \chi^2_{\mathrm{total}}=\chi^2_{\mathrm{SED}}+\chi^2_{\mathrm{ALMA}}+\chi^2_{\mathrm{SPHERE}}
+\end{equation}
 
@@
 These exploration allow us to support the idea of Ring5, as it is clear that the absence of it creates a great increment in the total $\chi^2$ value, but also that the ring must be quite thin.
-For the case of the lower limit of the central blob, it is evident that there is a threshold around 500\,$\micron$, where the SED start to deviate far away from a minimum, that point represent where the NIR excess becomes significant.
+For the case of the lower limit of the central blob, it is evident that there is a threshold around 500\,$\micron$ where the SED start to deviate far away from the typical value.
+That point represent where the NIR excess becomes significant.
 

### 2021-05-27 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 The narrow ring in the 1.3\,mm continuum, has a radius of 13.15$\pm$0.26\,au and an estimated width of 2.46$\pm$0.40\,au.
-The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes around 0.7\,M$_{\earth}$ millimetre-sized grains.
-Using the parametric model scale height FWHM value for the large grains ($H=$ 0.6\,au at 13.15\,au) we find that the ring width is roughly 4 times its estimated height.
+The location of this ring is coincident with the inner ring observed in the scattered-light image.
+From our RT modeling we can predict that the ring includes around 0.7\,M$_{\earth}$ of millimetre-sized grains.
+Using the parametric model scale height FWHM value for the large grains ($H=$ 0.25\,au at 13.15\,au) we find that the ring width is roughly 10 times its estimated height.
 The 1.3\,mm outer ring, that starts at $\sim$24\,au and has its peak intensity at $\sim$30\,au, presents a visible break in the surface brightness at $\sim$36\,au.
+
+  \item The central emission present in the ALMA image might be a close inner ring made up of dust grains larger than 0.5\,mm, or it would create a NIR excess higher than the one inferred from the SED.
+Our model agrees with the mass estimation for this feature made by \citet{Francis_2020} with a mass of 0.012\,M$_{\earth}$.
 
@@
 
-  \item The central emission observed by ALMA might be by
-
   \item We interpret the asymmetry observed with SPHERE--IRDIS at 1.65\,$\micron$ as due to strong forward-scattering, which implies that the dust population is depleted of grains smaller than $\sim$0.4\,$\micron$.
 
-  \item Our parametric model, which accounts for the SED of the system, involves the existence of a sub-micron dust population close (<5\,au) to the stars, and predicts the presence of another inner ring at $\sim$5\,au, mainly consisting of small dust grains.
-
-  %We also predict the existence of another thin ring at $\sim$6\,au, about 3\,au-wide and made of small dust grains, and that lies under the coronagraph of the scattered-light image. 
-  %The weak central emission at 1.3\,mm could be part of this ring.
+  \item Our parametric model, which accounts for the SED of the system, involves the existence of a sub-micron dust population close to the stars (inner disc).
+Also predicts the presence of another inner ring at $\sim$5\,au, mainly consisting of small dust grains.
+The depletion of large dust is consistent with efficient dust trapping in Ring13.
+This additional ring lies under the coronagraph of the scattered-light image and is to faint to be detected by the ALMA observation.
 \end{enumerate}

### 2021-05-27 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
     The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc known for its wide cavity and dusty ring.
-We present high resolution ($\sim$20--50\,mas) ALMA observations of the 1.3\,mm continuum of V4046\,Sgr which, combined with SPHERE--IRDIS polarized images and well-sampled spectral energy distribution (SED), allow us to propose a physical model using radiative transfer (RT) predictions.
-The new ALMA data reveal a very thin ring at a radius of 13.15$\pm$0.26\,au (Ring13), with a marginally resolved radial width of 2.46$\pm$0.56\,au.
-Ring13 is surrounded by a $\sim$10\,au-wide gap, and it is flanked by a very mm-bright outer ring (Ring24) with a sharp inner edge at 24\,au.
+We present high resolution ($\sim$20--50\,mas) ALMA observations of the 1.3\,mm continuum of V4046\,Sgr which, that combined with SPHERE--IRDIS polarized images and well-sampled spectral energy distribution (SED), allow us to propose a physical model using radiative transfer (RT) predictions.
+The new ALMA data reveal a impressively thin ring at a radius of 13.15$\pm$0.26\,au (Ring13), with a marginally resolved radial width of 2.46$\pm$0.40\,au.
+Ring13 is surrounded by a $\sim$10\,au-wide gap, and it is flanked by a mm-bright outer ring (Ring24) with a sharp inner edge at 24\,au.
 Between 25\,au and $\sim$35\,au the brightness of Ring24 is relatively flat and then breaks into a steeper tail that reaches out to $\sim$60\,au.
+The observation also detects a central emission that we interpret as a tight ring made of dust grains with a lower size limit of 0.5\,mm.
 In order to reproduce the SED, the model that we propose requires an inner ring at $\sim$5\,au (Ring5) composed mainly of small dust grains, hiding under the IRDIS coronagraph, and surrounding an inner circumbinary disc.
-The surprisingly thin Ring13 is nonetheless roughly 4 times wider than its expected vertical extent.
+The surprisingly thin Ring13 is nonetheless roughly 10 times wider than its expected vertical extent.
 The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$.
@@
 The main blob of this dust structure is at estimated distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.85$\pm$0.14\,au from the binary system, and, estimating its form as a Gaussian ellipse, it has a mean FWHM of $\sim$1.43\,au.
-\citet{Francis_2020} also did some measurements of this central emission by assuming a power--law profile for an inner disk that goes from 0.1 to 4\,au, and has a total dust mass of 0.013$\pm$0.002\,M$_{\earth}$.
-They stated that the inner radius of the disk is well beyond the sublimation radius as the system shows a low--NIR excess but a clear millimetre emission.
+\citet{Francis_2020} also did some measurements of this central emission by assuming a power--law profile for an inner disc that goes from 0.1 to 4\,au, and has a total dust mass of 0.013$\pm$0.002\,M$_{\earth}$.
+They stated that the inner radius of the disc is well beyond the sublimation radius as the system shows a low--NIR excess but a clear millimetre emission.
 

### 2021-05-27 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 We present high resolution ($\sim$20--50\,mas) ALMA observations of the 1.3\,mm continuum of V4046\,Sgr which, that combined with SPHERE--IRDIS polarized images and well-sampled spectral energy distribution (SED), allow us to propose a physical model using radiative transfer (RT) predictions.
-The new ALMA data reveal a impressively thin ring at a radius of 13.15$\pm$0.26\,au (Ring13), with a marginally resolved radial width of 2.46$\pm$0.40\,au.
+The new ALMA data reveal a impressively thin ring at a radius of 13.15$\pm$0.42\,au (Ring13), with a marginally resolved radial width of 2.46$\pm$0.20\,au.
 Ring13 is surrounded by a $\sim$10\,au-wide gap, and it is flanked by a mm-bright outer ring (Ring24) with a sharp inner edge at 24\,au.
@@
 Ring13 is surprisingly narrow and seems to be off-centred relative to the Gaia stellar position, at the origin of coordinates in Fig.~\ref{fig:images_vs_simulated}.
-We determined the ring's centre and orientation by minimising the dispersion of the disc radial profiles from 6\,au to 19\,au, by using the {\tt MPolarMaps} package described in Casassus et al.
+We determined the ring's centre and orientation by minimising the dispersion of the disc radial profiles from 6 to 18\,au, by using the {\tt MPolarMaps} package described in Casassus et al.
 (2021, in prep).
@@
 The ring width can be measured in polar coordinates by fitting 1-D Gaussians at each azimuth, thus obtaining a width and centroid.
-The top panel of Fig.~\ref{fig:polarring}) shows the positions of the obtained centroids and widths over the polar decomposition of the ALMA image.
-On average, we obtained a FWHM of 2.83$\pm$0.25\,au, and a stellocentric radius of 13.15$\pm$0.42\,au.
+The top panel of Fig.~\ref{fig:polarring} shows the positions of the obtained centroids and widths over the polar decomposition of the ALMA image.
+On average, we obtained a FWHM of 2.83$\pm$0.16\,au, and a stellocentric radius of 13.15$\pm$0.42\,au.
 As the {\tt uvmem} model image has an approximate {\tt uvmem} beam of $\sim0\farcs021 \,\times \,\sim0\farcs018$, we see that Ring13 is marginally resolved.
-After subtraction of the {\tt uvmem} beam, the ring width is $\sim$2.46$\pm$0.40\,au.
+After subtraction of the {\tt uvmem} beam, the ring width is $\sim$2.46$\pm$0.20\,au.
 
 In a second optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.86$\pm$0.02\,$\degr$, with an inclination of 33.92$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 2\pm0.02$\,mas $\Delta \delta = 12\pm0.02$\,mas relative to the stars.
-We see that both Ring13 and Ring24 share a very similar orientation and centre, given the errors.
+We see that both Ring13 and Ring24 share a very similar orientation and centre, given the errors and the pointing error.
 However, quite likely due to the joint effect of all these small differences, we can see that there are some hints for a somewhat different orientation.
@@
 The model predictions for the millimetre-sized dust population in Ring13 are close to the measurements, with only a 0.07\,au difference in the centroid location of the ring, and a 0.46\,au difference in the width estimation.
-Since the scale height FWHM of the large grains in Ring13 is 0.25\,au, and that from the ALMA observation we can resolve a width of 2.46$\pm$0.40\,au (See sec.~\ref{subsec:ALMA}), the ring is 9.7$\pm$1.5 times more extended radially than vertically.
+Since the scale height FWHM of the large grains in Ring13 is 0.25\,au, and that from the ALMA observation we can resolve a width of 2.46$\pm$0.20\,au (See sec.~\ref{subsec:ALMA}), the ring is 9.7$\pm$1.5 times more extended radially than vertically.
 Looking at the rest of the disc, in turn, our model reproduces the observations of Ring24 with peak intensity at $\sim$30\,au, and breaks at $\sim$36\,au.
@@
   \item We report the detection of a two-ringed disc structure.
-The narrow ring in the 1.3\,mm continuum, has a radius of 13.15$\pm$0.26\,au and an estimated width of 2.46$\pm$0.40\,au.
+The narrow ring in the 1.3\,mm continuum, has a radius of 13.15$\pm$0.42\,au and an estimated width of 2.46$\pm$0.20\,au.
 The location of this ring is coincident with the inner ring observed in the scattered-light image.

### 2021-05-27 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
     The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc known for its wide cavity and dusty ring.
-We present high resolution ($\sim$20--50\,mas) ALMA observations of the 1.3\,mm continuum of V4046\,Sgr which, that combined with SPHERE--IRDIS polarized images and well-sampled spectral energy distribution (SED), allow us to propose a physical model using radiative transfer (RT) predictions.
+We present high resolution ($\sim$20--50\,mas) ALMA observations of the 1.3\,mm continuum of V4046\,Sgr which, combined with SPHERE--IRDIS polarized images and well-sampled spectral energy distribution (SED), allow us to propose a physical model using radiative transfer (RT) predictions.
 The new ALMA data reveal a impressively thin ring at a radius of 13.15$\pm$0.42\,au (Ring13), with a marginally resolved radial width of 2.46$\pm$0.20\,au.
 Ring13 is surrounded by a $\sim$10\,au-wide gap, and it is flanked by a mm-bright outer ring (Ring24) with a sharp inner edge at 24\,au.
-Between 25\,au and $\sim$35\,au the brightness of Ring24 is relatively flat and then breaks into a steeper tail that reaches out to $\sim$60\,au.
+Between 25 and $\sim$35\,au the brightness of Ring24 is relatively flat and then breaks into a steeper tail that reaches out to $\sim$60\,au.
 The observation also detects a central emission that we interpret as a tight ring made of dust grains with a lower size limit of 0.5\,mm.
@@
 
-Recent observations of young circumstellar discs have transformed current knowledge of planet formation.
+Recent observations of young circumstellar discs have transformed the current knowledge on planet formation.
 The focus of resolved imaging with the Atacama Large Millimeter/submillimeter Array (ALMA) or with the current generation of high-contrast cameras has mainly been towards the brighter sources \citep[e.g.][]{2020ARA&A..58..483A}.
@@
 These observations allow us to see the distribution of different populations of dust particles: while ALMA traces the millimetre-sized grains settled in the mid-plane of the disc, scattered-light imaging accounts for photons reflected off micron-sized dust at the disc surface layer, high above the mid-plane.
-Therefore, the comparison of both allows to trace the dynamics present at different vertical heights in the disc.
+Therefore, the comparison between them allows to trace the dynamics present at different vertical heights in the disc.
 
-V4046\,Sgr is a double-lined spectroscopic binary of K-type stars (K5 and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012}, on a close ($a \approx 0.041$\,au), circular ($e\leq0.01$) orbit, with an orbital period of 2.42 days \citep{2000IAUS..200P..28Q}.
+V4046\,Sgr is a double-lined spectroscopic binary of K-type stars (K5 and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012}, on a close ($a \approx 0.041$\,au), circular ($e\leq0.01$) orbit, with an orbital period of 2.42\,days \citep{2000IAUS..200P..28Q}.
 It is a member of the $\beta$ Pictoris moving group \citep{Zuckerman_2004}, with an estimated age of 18.5$^{+2.0}_{-2.4}$\,Myr \citep{2020A&A...642A.179M}, and its distance is 71.48$\pm$0.11\,pc \citep{gaiacollaboration2020gaia}.
@@
 
-In this paper we present new observations of the continuum emission at 1.3 mm of V4046 Sgr which reveal previously undiscovered structures.
-This work also aims to reproduce the observations of the protoplanetary disc around V4046\,Sgr with a 3D model using as guidance previous NIR images, the spectral energy distribution (SED) and a new high definition 1.3\,mm continuum ALMA image, as a way to throw light on its complex structure and the processes that are occurring in it.
+In this paper we present new observations of the continuum emission at 1.3\,mm of V4046\,Sgr which reveal previously undiscovered structures.
+This work also aims to reproduce the observations of the protoplanetary disc around V4046\,Sgr with a 3D model using as guidance previous NIR images, the spectral energy distribution (SED) and the new high definition 1.3\,mm continuum ALMA image, as a way of throwing light on its complex structure and the processes that shaped it.
 
@@
 Similar applications of {\tt uvmem} in the context of protoplanetary discs can be found, for example, in \citet{Casassus2013Natur, 2018MNRAS.477.5104C, Casassus2019MNRAS.483.3278C, Perez2019AJ....158...15P} and in \citet{2020ApJ...889L..24P} using long baseline data.
-An advantage of {\tt uvmem} compared to more traditional imaging strategies, such as provided by the {\tt tclean} task in CASA, is that the effective angular resolution of the model image is $\sim$3 times finer than the natural weights clean beam \citep[][]{2018A&C....22...16C}, giving us a new approximate {\tt uvmem} resolution of $\sim0\farcs021 \,\times \,\sim0\farcs018$.
+An advantage of {\tt uvmem} compared to more traditional imaging strategies, such as provided by the {\tt tclean} task in CASA, is that the effective angular resolution of the model image is $\sim$3 times finer than the natural weights clean beam \citep[][]{2018A&C....22...16C}, giving us a new approximate {\tt uvmem} resolution of $\sim$0$\farcs021 \,\times \,\sim$0$\farcs018$.
 This angular resolution is comparable to uniform or super-uniform weights in {\tt tclean}, but it preserves the natural-weights point-source sensitivity.
@@
 On average, we obtained a FWHM of 2.83$\pm$0.16\,au, and a stellocentric radius of 13.15$\pm$0.42\,au.
-As the {\tt uvmem} model image has an approximate {\tt uvmem} beam of $\sim0\farcs021 \,\times \,\sim0\farcs018$, we see that Ring13 is marginally resolved.
+As the {\tt uvmem} model image has an approximate {\tt uvmem} beam of $\sim$0$\farcs021 \,\times \,\sim$0$\farcs018$, we see that Ring13 is marginally resolved.
 After subtraction of the {\tt uvmem} beam, the ring width is $\sim$2.46$\pm$0.20\,au.
@@
 Since this faint central emission is larger than the angular resolution, it is probably stemming from thermal emission from large dust grains rather than directly from the stars.
-The main blob of this dust structure is at estimated distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.85$\pm$0.14\,au from the binary system, and, estimating its form as a Gaussian ellipse, it has a mean FWHM of $\sim$1.43\,au.
+The peak intensity of this dust structure is at an estimated distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.85$\pm$0.14\,au, from the binary system, and, estimating its form as a Gaussian ellipse, it has a mean FWHM of $\sim$1.43\,au.
 \citet{Francis_2020} also did some measurements of this central emission by assuming a power--law profile for an inner disc that goes from 0.1 to 4\,au, and has a total dust mass of 0.013$\pm$0.002\,M$_{\earth}$.
@@
 
-For Ring5 and Ring13, we chose Gaussian profiles parameterized with centroid radii $\mu_{\mathrm{Ring5, ld}}=5.2$\,au and $\mu_{\mathrm{Ring13, ld}}=13.22$\,au, ring widths of $\sigma_{\mathrm{Ring5,ld}}=0.1$\,au and $\sigma_{\mathrm{Ring13,ld}}=0.85$\,au, and normalizations $\Sigma_{\circ,\mathrm{Ring5,ld}}=1.3\times10^{-4}\,\mathrm{g\,cm^{-3}}$ and $\Sigma_{\circ,\mathrm{Ring13,ld}}=2.4\,\mathrm{g\,cm^{-3}}$.
+For Ring5 and Ring13, we chose Gaussian profiles parameterized with centroid radii $\mu_{\mathrm{Ring5, ld}}=5.2$\,au and $\mu_{\mathrm{Ring13, ld}}=13.22$\,au, ring widths of $\sigma_{\mathrm{Ring5,ld}}=0.1$\,au and $\sigma_{\mathrm{Ring13,ld}}=0.85$\,au, and normalizations $\Sigma_{\circ,\mathrm{Ring5,ld}}=1.3\times10^{-4}\,\mathrm{g\,cm^{-3}}$ and $\Sigma_{\circ,\mathrm{Ring13,ld}}=2.3\,\mathrm{g\,cm^{-3}}$.
 For Ring24 we used a similar profile as for the gas (a power-law function).
@@
 
-For the reproduction of central emission we introduce a special dust population that is distributed only on a very close Gaussian ring parameterized by $\mu_{\mathrm{central\,blob}}=1.1$\,au, $\sigma_{\mathrm{central\,blob}}=0.4$\,au and $\Sigma_{\circ,\mathrm{central\,blob}}=2.4\,\mathrm{g\,cm^{-3}}$, and following the argument of \citet{Francis_2020}, it goes in past the sublimation radius until it reaches the grid boundary.
+For the reproduction of central emission we introduce a special dust population that is distributed only on a very close Gaussian ring parameterized by $\mu_{\mathrm{central\,blob}}=1.1$\,au, $\sigma_{\mathrm{central\,blob}}=0.4$\,au and $\Sigma_{\circ,\mathrm{central\,blob}}=58.8\,\mathrm{g\,cm^{-3}}$, and following the argument of \citet{Francis_2020}, it goes in past the sublimation radius until it reaches the grid boundary.
 This dust population has grains with radii ranging from 0.8 to 10\,mm, same upper limit as the large dust but is depleted of small grains.

### 2021-05-27 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
   \caption{Comparison of observations (top) and simulated images (bottom) at 1.65\,$\micron$ (left) and 1.3\,mm continuum (right) of the circumbinary disc orbiting V4046\,Sgr.
-\textit{Top left panel:} SPHERE--IRDIS \textit{H}-band image with a yellow filled circle that represents the N\_ALC\_YJH\_S coronagraph with a radius of $\sim0\farcs12$, or $\sim$8.6\,au at 71.48\,pc.
+\textit{Top left panel:} SPHERE--IRDIS \textit{H}-band image with a yellow filled circle that represents the N\_ALC\_YJH\_S coronagraph with a radius of $\sim$0$\farcs12$, or $\sim$8.6\,au at 71.48\,pc.
 \textit{Top right panel:} 1.3\,mm continuum {\tt uvmem} model image.
-The small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs021 \, \times \, \sim0\farcs018$).
+The small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim$0$\farcs021 \, \times \, \sim$0$\farcs018$).
 The inset zooms into the central emission, and the green star marks the center of the inner ring.
@@
     \caption{Comparison of the surface brightness profiles extracted from the deprojected synthetic images and observed \textit{H}-band and 1.3\,mm continuum images.
-The grey shaded area represents the radius of the artificial coronagraph used in the simulations (i.e., $\sim0\farcs 1$, or $\sim$7.1\,au at 71.48\,pc).}
+The grey shaded area represents the radius of the artificial coronagraph used in the simulations (i.e., $\sim$0$\farcs 1$, or $\sim$7.1\,au at 71.48\,pc).}
     \label{fig:radprofiles}
@@
 The model predictions for the millimetre-sized dust population in Ring13 are close to the measurements, with only a 0.07\,au difference in the centroid location of the ring, and a 0.46\,au difference in the width estimation.
-Since the scale height FWHM of the large grains in Ring13 is 0.25\,au, and that from the ALMA observation we can resolve a width of 2.46$\pm$0.20\,au (See sec.~\ref{subsec:ALMA}), the ring is 9.7$\pm$1.5 times more extended radially than vertically.
+Since the scale height FWHM of the large grains in Ring13 is 0.25\,au, and that from the ALMA observation we can resolve a width of 2.46$\pm$0.20\,au (see sec.~\ref{subsec:ALMA}), the ring is 9.7$\pm$1.5 times more extended radially than vertically.
 Looking at the rest of the disc, in turn, our model reproduces the observations of Ring24 with peak intensity at $\sim$30\,au, and breaks at $\sim$36\,au.
@@
 For V4046\,Sgr, there was a missing piece for an accurate representation of the system: a thin ring of millimetre-sized dust grains at a distance of $\sim$13\,au.
-We presented new ALMA 1.3\,mm continuum imaging of this circumbinary disc at an unprecedented definition ($\sim0\farcs021 \, \times \, \sim0\farcs018$) were this new ring becomes visible for the first time.
+We presented new ALMA 1.3\,mm continuum imaging of this circumbinary disc at an unprecedented definition ($\sim$0$\farcs021 \, \times \, \sim$0$\farcs018$) were this new ring becomes visible for the first time.
 The new observed feature gives us some insights of the dynamics that are driving the formation of this unique morphology.
@@
 But as a way to compute a measure of goodness of fit and to try to quantify the improvements, we did a partial exploration of the parameter space.
-We explore $\chi^2$ space in the vicinity of the model values for the scale height at $r_\circ$, the location of Ring5, the width of the gas component of Ring13, the width of the gas part of Ring5, the width of the large dust portion of Ring13 and around the lower limit of the grain sizes in the blob.
-The parameter space exploration is shown in Figure~\ref{fig:chi}.
+We explore $\chi^2$ space in the vicinity of the model values for the scale height at $r_\circ$ ($H_\circ$), the location of Ring5 $r_5$, the width of the gas component of Ring13 $w_{\mathrm{g13}}$, the width of the gas part of Ring5 $w_{\mathrm{g5}}$, the width of the large dust portion of Ring13 $w_{\mathrm{ld13}}$ and around the lower limit of the grain sizes in the central blob.
+The parameter space exploration is shown in Fig.~\ref{fig:chi}.
 Our model fits the SED and two images, so the total $\chi^2$ value for a given model is composed of the sum of the $\chi^2$ values for each of the three fits.
 \begin{equation}
-    \chi^2_{\mathrm{total}}=\chi^2_{\mathrm{SED}}+\chi^2_{\mathrm{ALMA}}+\chi^2_{\mathrm{SPHERE}}
+    \chi^2_{\mathrm{total}}=\chi^2_{\mathrm{SED}}+\chi^2_{\mathrm{ALMA}}+\chi^2_{\mathrm{SPHERE}}.
 \end{equation}
 
-For the first three parameters, we find that the value of the parameter in our model is almost at a minimum in its one dimensional $\chi^2$ space, so given $\chi^2_m$ the total chi squared value for the model, the uncertainties (up and down) will be those with $\chi^2=\chi^2_m+1$.
+For the first three parameters, we find that the values of the parameters in our model are almost at a minimum in each one dimensional $\chi^2$ space, so given $\chi^2_\mathrm{m}$ the total chi squared value for the model, the uncertainties (up and down) will be those with $\chi^2=\chi^2_\mathrm{m}+1$.
 As the values are around a local minimum, we can as assume a quadratic equation for the curve fitting.
@@
 For the the other three parameters, we found that although our chosen values are close to a minimum, the geometries are more suggestive of different border conditions.
-These exploration allow us to support the idea of Ring5, as it is clear that the absence of it creates a great increment in the total $\chi^2$ value, but also that the ring must be quite thin.
+These exploration allow us to support the idea of Ring5, as it is clear that the absence of it creates a great increment in the total $\chi^2$ value, but also requires the ring to be quite thin.
 For the case of the lower limit of the central blob, it is evident that there is a threshold around 500\,$\micron$ where the SED start to deviate far away from the typical value.

### 2021-05-27 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
     The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc known for its wide cavity and dusty ring.
-We present high resolution ($\sim$20--50\,mas) ALMA observations of the 1.3\,mm continuum of V4046\,Sgr which, combined with SPHERE--IRDIS polarized images and well-sampled spectral energy distribution (SED), allow us to propose a physical model using radiative transfer (RT) predictions.
-The new ALMA data reveal a impressively thin ring at a radius of 13.15$\pm$0.42\,au (Ring13), with a marginally resolved radial width of 2.46$\pm$0.20\,au.
+We present high resolution ($\sim$20\,mas or 1.4\,au) ALMA observations of the 1.3\,mm continuum of V4046\,Sgr which, combined with SPHERE--IRDIS polarized images and well-sampled spectral energy distribution (SED), allow us to propose a physical model using radiative transfer (RT) predictions.
+The new ALMA data reveal a thin ring at a radius of 13.15$\pm$0.42\,au (Ring13), with a radial width of 2.46$\pm$0.20\,au.
 Ring13 is surrounded by a $\sim$10\,au-wide gap, and it is flanked by a mm-bright outer ring (Ring24) with a sharp inner edge at 24\,au.
 Between 25 and $\sim$35\,au the brightness of Ring24 is relatively flat and then breaks into a steeper tail that reaches out to $\sim$60\,au.
-The observation also detects a central emission that we interpret as a tight ring made of dust grains with a lower size limit of 0.5\,mm.
-In order to reproduce the SED, the model that we propose requires an inner ring at $\sim$5\,au (Ring5) composed mainly of small dust grains, hiding under the IRDIS coronagraph, and surrounding an inner circumbinary disc.
+In addition, central emission is detected close to the star which we interpret as a tight ring made of dust grains with a lower size limit of 0.5\,mm.
+In order to reproduce the SED, the model also requires an inner ring at $\sim$5\,au (Ring5) composed mainly of small dust grains, hiding under the IRDIS coronagraph, and surrounding an inner circumbinary disc.
 The surprisingly thin Ring13 is nonetheless roughly 10 times wider than its expected vertical extent.
 The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$.
-The previously reported scattered-light shadow of the secondary star is also reproduced by our physical model.
+The previously reported scattered light shadow of the secondary star is also reproduced by our model.
 \end{abstract}
@@
 Recent observations of young circumstellar discs have transformed the current knowledge on planet formation.
-The focus of resolved imaging with the Atacama Large Millimeter/submillimeter Array (ALMA) or with the current generation of high-contrast cameras has mainly been towards the brighter sources \citep[e.g.][]{2020ARA&A..58..483A}.
-It is to address this bias that the programme called ``Discs Around T Tauri Stars with SPHERE'' (DARTTS-S) collected differential polarization imaging (DPI) data secured with the Spectro-Polarimeter High-contrast Exoplanet REsearch \citep[SPHERE][]{2019A&A...631A.155B} in a total of 29 solar-type stars \citep[][]{Avenhaus_2018,Garufi2020}.
+Among the main recent findings of resolved observations of discs is the discovery of substructures in the form of gaps, rings, cavities, and spirals, to name a few \citep[see,][and references there in]{Andrews_2020_aug}.
+***EXPAND on rings as radial dust traps***.
+
+The focus of resolved imaging with the Atacama Large Millimeter/submillimeter Array (ALMA) or with the current generation of high-contrast cameras has mainly been towards the brighter sources.
+It is to address this bias that the ``Discs Around T Tauri Stars with SPHERE'' (DARTTS-S) programme collected differential polarization imaging (DPI) data with the Spectro-Polarimeter High-contrast Exoplanet REsearch \citep[SPHERE][]{2019A&A...631A.155B} for a total of 29 solar-type stars \citep[][]{Avenhaus_2018,Garufi2020}.
 The sample is not biased towards exceptionally bright and large discs.
@@
 This article on V4046 Sagittarii (Sgr) is the first installment of a companion programme, the DARTTS survey with ALMA (DARTTS-A), which will present millimetre observations of nine protoplanetary discs previously imaged in polarized scattered light in DARTTS-S.
-
-Disc structures can be explored by means of comparing millimetre continuum and scattered-light images.
-These observations allow us to see the distribution of different populations of dust particles: while ALMA traces the millimetre-sized grains settled in the mid-plane of the disc, scattered-light imaging accounts for photons reflected off micron-sized dust at the disc surface layer, high above the mid-plane.
-Therefore, the comparison between them allows to trace the dynamics present at different vertical heights in the disc.
 
@@
 
-From previous analysis of radio wavelength observations taken with Sub-millimeter Array (SMA) \citep{Rosenfeld_2013} and subsequently with ALMA \citep{Guzman_2017,Huang_2017,Bergner_2018,Kastner_2018}, it was detected that the millimetre dust configuration of the circumbinary disc had a large inner hole of $\sim$30\,au, featuring a narrow ring centred around 37\,au that accounted for most of the dust mass.
-By using DPI in the J- and H-band, \citet{Avenhaus_2018} confirmed the double-ring morphology previously presented in \citet{Rapson_2015}, where the observed brightness presented a $\sim$10\,au-wide inner cavity, a narrow ring at $\sim$14\,au and the outer ring centred at $\sim$27\,au.
+Previous analysis of radio observations taken with the Sub-Millimeter Array (SMA) \citep{Rosenfeld_2013} and later with ALMA \citep{Guzman_2017,Huang_2017,Bergner_2018,Kastner_2018}, showed that the millimetre dust of the V4046 Sgr circumbinary disc features a large inner hole of $\sim$30\,au and a narrow ring centred around 37\,au that account for most of the dust mass.
+On the other hand, by using SPHERE polarized light observations in the J- and H-band, \citet{Avenhaus_2018} confirmed the double-ring morphology previously reported by \citet{Rapson_2015} using GPI data.
+In these polarized light observations, the surface brightness presents a $\sim$10\,au-wide inner cavity, a narrow ring at $\sim$14\,au, and an outer ring centred at $\sim$27\,au.
 
-The suggestion of a parametric model that simultaneously fits the NIR scattered-light and millimetre continuum brightness is challenging and has been attempted in only few previous studies \citep[e.g.][]{Dong_2018,2019MNRAS.486..304B, Ru_z_Rodr_guez_2019}.
-A successful model can serve as a convenient sample to link the observations to the structure of the underlying dust density distribution.
+Finding a parametric model that simultaneously fits the near-IR scattered light and millimetre continuum emission is challenging and has been attempted in a few previous studies \citep[e.g.][]{Dong_2018,2019MNRAS.486..304B, Ru_z_Rodr_guez_2019}.
+Such model can provide a way to link the observations to the structures in the underlying dust and gas density distributions, and shed light on the complex processes that shaped them.
 
-In this paper we present new observations of the continuum emission at 1.3\,mm of V4046\,Sgr which reveal previously undiscovered structures.
-This work also aims to reproduce the observations of the protoplanetary disc around V4046\,Sgr with a 3D model using as guidance previous NIR images, the spectral energy distribution (SED) and the new high definition 1.3\,mm continuum ALMA image, as a way of throwing light on its complex structure and the processes that shaped it.
-
-The details of the observations taken into account are described in Section~\ref{sec:Observations}.
-The parametric model is presented in Section~\ref{sec:model}, the results are discussed in Section~\ref{sec:results} and in Section~\ref{sec:Conclusions} we present our conclusions.
+In this paper, we present new ALMA observations of the continuum emission at 1.3\,mm of V4046\,Sgr which reveal previously undiscovered structures.
+This work also aims to reproduce these observations with a 3D parametric model that fits all available data, including the polarized scattered light SPHERE image, the spectral energy distribution (SED), as well as the new high definition 1.3\,mm continuum map.
+Section~\ref{sec:Observations} describes the available observations that we aim to model.
+Section~\ref{sec:model} describes the structural parameters of our model.
+A description of our parameter space exploration can be found in Appendix~\ref{sec:Appendix}.
+The results of our modelling are presented in Section~\ref{sec:results}, including a discussion of the main findings.
+Finally, in Section~\ref{sec:Conclusions} we present our conclusions.
 
@@
 
-\subsection{SPHERE--IRDIS}  \label{subsec:SPHERE}
+\subsection{VLT/SPHERE--IRDIS}  \label{subsec:SPHERE}
 
@@
 
-The scattered-light image in the top left panel of Fig.~\ref{fig:images_vs_simulated} also shows a double ring structure in the micron-sized dust distribution.
+The scattered light image in the top left panel of Fig.~\ref{fig:images_vs_simulated} also shows a double ring structure in the micron-sized dust distribution.
 The observed morphology presents an inner cavity of $\sim$10\,au in radius and two rings located at 14.10$\pm$0.01\,au, coincident with Ring13, and 24.62$\pm$0.08\,au, coincident with Ring24, with a small gap between them at $\sim$20\,au.
@@
 
-The binary phase reported by \citet{dOrazi} in the scattered-light observation is at a PA of 265\,$\degr$, east of north.
+The binary phase reported by \citet{dOrazi} in the scattered light observation is at a PA of 265\,$\degr$, east of north.
 Using this measurement, the binary phase was calculated at the time of the ALMA observation at a PA of $\sim$80\,$\degr$.
@@
 The narrow ring in the 1.3\,mm continuum, has a radius of 13.15$\pm$0.42\,au and an estimated width of 2.46$\pm$0.20\,au.
-The location of this ring is coincident with the inner ring observed in the scattered-light image.
+The location of this ring is coincident with the inner ring observed in the scattered light image.
 From our RT modeling we can predict that the ring includes around 0.7\,M$_{\earth}$ of millimetre-sized grains.
@@
 The depletion of large dust is consistent with efficient dust trapping in Ring13.
-This additional ring lies under the coronagraph of the scattered-light image and is to faint to be detected by the ALMA observation.
+This additional ring lies under the coronagraph of the scattered light image and is to faint to be detected by the ALMA observation.
 \end{enumerate}

### 2021-05-30 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 We present high resolution ($\sim$20\,mas or 1.4\,au) ALMA observations of the 1.3\,mm continuum of V4046\,Sgr which, combined with SPHERE--IRDIS polarized images and well-sampled spectral energy distribution (SED), allow us to propose a physical model using radiative transfer (RT) predictions.
-The new ALMA data reveal a thin ring at a radius of 13.15$\pm$0.42\,au (Ring13), with a radial width of 2.46$\pm$0.20\,au.
+The new ALMA data reveal a thin ring at a radius of 13.15$\pm$0.42\,au (Ring13), with a radial width of 2.46$\pm$0.56\,au.
 Ring13 is surrounded by a $\sim$10\,au-wide gap, and it is flanked by a mm-bright outer ring (Ring24) with a sharp inner edge at 24\,au.
@@
 Among the main recent findings of resolved observations of discs is the discovery of substructures in the form of gaps, rings, cavities, and spirals, to name a few \citep[see,][and references there in]{Andrews_2020_aug}.
-***EXPAND on rings as radial dust traps***.
-
-The focus of resolved imaging with the Atacama Large Millimeter/submillimeter Array (ALMA) or with the current generation of high-contrast cameras has mainly been towards the brighter sources.
+However, the focus of resolved imaging with the Atacama Large Millimeter/submillimeter Array (ALMA) or with the current generation of high-contrast cameras has mainly been towards the brighter sources.
 It is to address this bias that the ``Discs Around T Tauri Stars with SPHERE'' (DARTTS-S) programme collected differential polarization imaging (DPI) data with the Spectro-Polarimeter High-contrast Exoplanet REsearch \citep[SPHERE][]{2019A&A...631A.155B} for a total of 29 solar-type stars \citep[][]{Avenhaus_2018,Garufi2020}.
@@
 
-Finding a parametric model that simultaneously fits the near-IR scattered light and millimetre continuum emission is challenging and has been attempted in a few previous studies \citep[e.g.][]{Dong_2018,2019MNRAS.486..304B, Ru_z_Rodr_guez_2019}.
-Such model can provide a way to link the observations to the structures in the underlying dust and gas density distributions, and shed light on the complex processes that shaped them.
-
-In this paper, we present new ALMA observations of the continuum emission at 1.3\,mm of V4046\,Sgr which reveal previously undiscovered structures.
-This work also aims to reproduce these observations with a 3D parametric model that fits all available data, including the polarized scattered light SPHERE image, the spectral energy distribution (SED), as well as the new high definition 1.3\,mm continuum map.
+Building  a parametric model that simultaneously fits the near-IR scattered light and millimetre continuum emission  can provide a way to link the observations to the structures in the underlying dust and gas density distributions, and shed light on the complex processes that shaped them.
+In this paper, we present new ALMA observations of the continuum emission at 1.3\,mm of V4046\,Sgr, which reveal a new inner ring in the disc.
+We also reproduce these observations with a 3D parametric model that fits all available data, including the polarized scattered light SPHERE image, the spectral energy distribution (SED), as well as the new high definition 1.3\,mm continuum map.
 Section~\ref{sec:Observations} describes the available observations that we aim to model.
@@
 The top panel of Fig.~\ref{fig:polarring} shows the positions of the obtained centroids and widths over the polar decomposition of the ALMA image.
-On average, we obtained a FWHM of 2.83$\pm$0.16\,au, and a stellocentric radius of 13.15$\pm$0.42\,au.
+On average, we obtained a FWHM of 2.83$\pm$0.50\,au, and a stellocentric radius of 13.15$\pm$0.42\,au.
 As the {\tt uvmem} model image has an approximate {\tt uvmem} beam of $\sim$0$\farcs021 \,\times \,\sim$0$\farcs018$, we see that Ring13 is marginally resolved.
-After subtraction of the {\tt uvmem} beam, the ring width is $\sim$2.46$\pm$0.20\,au.
+After subtraction of the {\tt uvmem} beam, the ring width is $\sim$2.46$\pm$0.56\,au.
 
@@
 Interestingly, the ALMA image also detects faint 1.3\,mm continuum emission near the stellar positions (see the inset in Fig.~\ref{fig:images_vs_simulated}).
-Since this faint central emission is larger than the angular resolution, it is probably stemming from thermal emission from large dust grains rather than directly from the stars.
+Since this central emission is larger than the angular resolution, it is probably stemming from thermal emission from large dust grains rather than directly from the stars.
 The peak intensity of this dust structure is at an estimated distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.85$\pm$0.14\,au, from the binary system, and, estimating its form as a Gaussian ellipse, it has a mean FWHM of $\sim$1.43\,au.
 \citet{Francis_2020} also did some measurements of this central emission by assuming a power--law profile for an inner disc that goes from 0.1 to 4\,au, and has a total dust mass of 0.013$\pm$0.002\,M$_{\earth}$.
-They stated that the inner radius of the disc is well beyond the sublimation radius as the system shows a low--NIR excess but a clear millimetre emission.
 
@@
 \citet{Jensen_97} concluded that these data matched that of a extended circumbinary disc truncated at $\sim$0.3\,au, as the interior would also be expected to be cleared by dynamical effects of the central binary \citep{Art_Lu}.
+
+The system present a low near--infrared (NIR) excess of 0.9$\pm$3.7\,\% \citep{Francis_2020}.
+This appears to be inconsistent with the detection of the mm-bright central emission, but the low NIR excess could be interpreted as a lack of micron-sized dust in the central blob.
+Also, from this feature (or the absence of it) \citet{Francis_2020} stated that the inner radius of the millimetre-sized dust ring that accounts for the central emission is well beyond the sublimation radius.
 
@@
 The model predictions for the millimetre-sized dust population in Ring13 are close to the measurements, with only a 0.07\,au difference in the centroid location of the ring, and a 0.46\,au difference in the width estimation.
-Since the scale height FWHM of the large grains in Ring13 is 0.25\,au, and that from the ALMA observation we can resolve a width of 2.46$\pm$0.20\,au (see sec.~\ref{subsec:ALMA}), the ring is 9.7$\pm$1.5 times more extended radially than vertically.
+Since the scale height FWHM of the large grains in Ring13 is 0.25\,au, and that from the ALMA observation we can resolve a width of 2.46$\pm$0.56\,au (see sec.~\ref{subsec:ALMA}), the ring is 9.7$\pm$1.5 times more extended radially than vertically.
 Looking at the rest of the disc, in turn, our model reproduces the observations of Ring24 with peak intensity at $\sim$30\,au, and breaks at $\sim$36\,au.
@@
 
+Discs, rings and gaps are common structures present in protoplanetary discs, each time a disc with complex geometry appears we learn something knew about planet formation or disc mechanics.
+
 Observing the same source at different wavelengths, or employing more than one instrument, will tell different stories about the same physical phenomena.
@@
 For V4046\,Sgr, there was a missing piece for an accurate representation of the system: a thin ring of millimetre-sized dust grains at a distance of $\sim$13\,au.
-We presented new ALMA 1.3\,mm continuum imaging of this circumbinary disc at an unprecedented definition ($\sim$0$\farcs021 \, \times \, \sim$0$\farcs018$) were this new ring becomes visible for the first time.
+We present new ALMA 1.3\,mm continuum imaging of this circumbinary disc at an unprecedented definition ($\sim$0$\farcs021 \, \times \, \sim$0$\farcs018$) were new features ring becomes visible for the first time.
 The new observed feature gives us some insights of the dynamics that are driving the formation of this unique morphology.
@@
   \item We report the detection of a two-ringed disc structure.
-The narrow ring in the 1.3\,mm continuum, has a radius of 13.15$\pm$0.42\,au and an estimated width of 2.46$\pm$0.20\,au.
+The narrow ring in the 1.3\,mm continuum, has a radius of 13.15$\pm$0.42\,au and an estimated width of 2.46$\pm$0.56\,au.
 The location of this ring is coincident with the inner ring observed in the scattered light image.
@@
 
-The model presented here has many degrees of freedom and each model requires a high level of computational power and time, so a MCMC optimization or similar methods of parameter exploration are impossible to acquire.
-But as a way to compute a measure of goodness of fit and to try to quantify the improvements, we did a partial exploration of the parameter space.
-We explore $\chi^2$ space in the vicinity of the model values for the scale height at $r_\circ$ ($H_\circ$), the location of Ring5 $r_5$, the width of the gas component of Ring13 $w_{\mathrm{g13}}$, the width of the gas part of Ring5 $w_{\mathrm{g5}}$, the width of the large dust portion of Ring13 $w_{\mathrm{ld13}}$ and around the lower limit of the grain sizes in the central blob.
+The parametric model presented here has many degrees of freedom and the RT calculation for each set of parameters is very intensive in computational power and time, so a MCMC optimization or similar methods of parameter exploration are impossible to carry out.
+As a way to compute a measure of goodness of fit and to try to quantify the model uncertainties, we performed a partial exploration of parameter space.
+We explore $\chi^2$ space in the vicinity of the model values (obtained by trial and error, see sec.~\ref{sec:model}) for the scale height at $r_\circ$ ($H_\circ$), the width of the gas component of Ring13 $w_{\mathrm{g13}}$, and around the lower limit of the grain sizes in the central blob.
 The parameter space exploration is shown in Fig.~\ref{fig:chi}.
@@
 
-For the first three parameters, we find that the values of the parameters in our model are almost at a minimum in each one dimensional $\chi^2$ space, so given $\chi^2_\mathrm{m}$ the total chi squared value for the model, the uncertainties (up and down) will be those with $\chi^2=\chi^2_\mathrm{m}+1$.
+For $H_\circ$ and $w_{\mathrm{g13}}$, we find that the values of the parameters in our model are almost at a minimum in each one dimensional $\chi^2$ space, so given $\chi^2_\mathrm{m}$ the local minimum value, the uncertainties (up and down) will be those with $\chi^2=\chi^2_\mathrm{m}+1$.
 As the values are around a local minimum, we can as assume a quadratic equation for the curve fitting.
 
-For the the other three parameters, we found that although our chosen values are close to a minimum, the geometries are more suggestive of different border conditions.
-These exploration allow us to support the idea of Ring5, as it is clear that the absence of it creates a great increment in the total $\chi^2$ value, but also requires the ring to be quite thin.
-For the case of the lower limit of the central blob, it is evident that there is a threshold around 500\,$\micron$ where the SED start to deviate far away from the typical value.
+For the lower grain size limit, we found that although our chosen value is at the minimum, the geometry is more suggestive of a border condition.
+It is evident that there is a threshold around 500\,$\micron$ where the SED start to deviate far away from the typical value.
 That point represent where the NIR excess becomes significant.
+
+%These exploration allow us to support the idea of Ring5, as that the absence of it creates a great increment in the total $\chi^2$ value, but also requires the ring to be quite thin.
 
@@
 	\includegraphics[width=\textwidth]{plot_chi_squared_all800.pdf}
-        \caption{one dimensional explorations of the chi squared space of our parametric model.
-Each panel display at the bottom the $\chi^2$ values for the SED and for the two images separately, and on top the total $\chi^2$ value in terms of the parameter value.
-{\it Top:} scale height at $r_\circ$=18\,au, location of Ring5, width of the gas component of Ring13.
-{\it Bottom:} Width of the gas part of Ring5, width of the large dust section of Ring13, lower limit of the grain sizes in the blob.}
+        \caption{One dimensional explorations of the chi squared space of our parametric model.
+Variation of $\chi^2$ in terms of the scale height $H_\circ$ at $r_\circ$=18\,au, the width of the gas component of Ring13 $w_{\mathrm{g13}}$, and around the lower limit of the grain size in the central blob.
+Each panel displays at the bottom the $\chi^2$ values for the SED and for the two images separately, and on top the total $\chi^2$ value in terms of the parameter value.}
     \label{fig:chi}

### 2021-05-30 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 Ring13 at 13\,au and Ring24 starting at 24\,au.
-The wide and bright Ring24 reaches its peak intensity at $\sim$30\,au, beyond which it drops steeply before breaking at $\sim$35\,au into a shallow tail.
+The wide and bright Ring24 reaches its peak intensity at $\sim$30\,au, continues relatively flat and then breaks at $\sim$35\,au into a steeper tail.
 While this is the first observation of Ring13, \citet{Ru_z_Rodr_guez_2019} did anticipate its existence as their ALMA continuum image showed a distinct excess between $\sim$10 and 17\,au.
@@
 On average, we obtained a FWHM of 2.83$\pm$0.50\,au, and a stellocentric radius of 13.15$\pm$0.42\,au.
-As the {\tt uvmem} model image has an approximate {\tt uvmem} beam of $\sim$0$\farcs021 \,\times \,\sim$0$\farcs018$, we see that Ring13 is marginally resolved.
+As the {\tt uvmem} model image has an approximate {\tt uvmem} beam of $\sim$0$\farcs021 \,\times \,\sim$0$\farcs018$ (or $\sim$1.4\,au at 71.1\,pc), we see that Ring13 is resolved.
 After subtraction of the {\tt uvmem} beam, the ring width is $\sim$2.46$\pm$0.56\,au.
@@
 
-Interestingly, the ALMA image also detects faint 1.3\,mm continuum emission near the stellar positions (see the inset in Fig.~\ref{fig:images_vs_simulated}).
+Interestingly, the ALMA image also detects 1.3\,mm continuum emission near the stellar positions (see the inset in Fig.~\ref{fig:images_vs_simulated}).
 Since this central emission is larger than the angular resolution, it is probably stemming from thermal emission from large dust grains rather than directly from the stars.
 The peak intensity of this dust structure is at an estimated distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.85$\pm$0.14\,au, from the binary system, and, estimating its form as a Gaussian ellipse, it has a mean FWHM of $\sim$1.43\,au.
-\citet{Francis_2020} also did some measurements of this central emission by assuming a power--law profile for an inner disc that goes from 0.1 to 4\,au, and has a total dust mass of 0.013$\pm$0.002\,M$_{\earth}$.
+Measurements of this central emission made by \citet{Francis_2020}, assume a power-law profile for an inner disc that goes from 0.1 to 4\,au, and has a total dust mass of 0.013$\pm$0.002\,M$_{\earth}$.
 
@@
 
-The system present a low near--infrared (NIR) excess of 0.9$\pm$3.7\,\% \citep{Francis_2020}.
-This appears to be inconsistent with the detection of the mm-bright central emission, but the low NIR excess could be interpreted as a lack of micron-sized dust in the central blob.
-Also, from this feature (or the absence of it) \citet{Francis_2020} stated that the inner radius of the millimetre-sized dust ring that accounts for the central emission is well beyond the sublimation radius.
+The SED present a low near--infrared (NIR) excess of 0.9$\pm$3.7\,\% \citep{Francis_2020}.
+This appears to be inconsistent with the detection of the mm-bright central emission, as the presence of a inner disc would generate higher NIR fluxes, but the low excess could be interpreted as a lack of micron-sized dust in the central spot.
+Also, from this feature (or the absence of it) \citet{Francis_2020} stated that the inner radius of the millimetre-sized dust ring that accounts for the central emission is well beyond the sublimation radius, around 0.1\,au.
 
@@
 The separation between the two values was set at $r = 18$\,au with $\psi_1=0.2$ for Ring5 and Ring13, and $\psi_2=0.5$ for Ring24.
-The scale height is set to $H_\circ = 0.94$\,au at $r_\circ = 18$\,au.
-This vertical structure is consistent with the measurements made by \citet{dOrazi}, as the model flaring angles are $\varphi_{\mathrm{inner}}$ = 6.5\,$\degr$ and $\varphi_{\mathrm{outer}}$ = 7.9\,$\degr$.
+The scale height is set to $H_\circ = 0.91$\,au at $r_\circ = 18$\,au.
+This vertical structure is consistent with the measurements made by \citet{dOrazi}, as the model flaring angles are $\varphi_{\mathrm{inner}}$ = 6.5\,$\degr$ and $\varphi_{\mathrm{outer}}$ = 7.8\,$\degr$.
 This is summarized in bottom panel of Fig.~\ref{fig:profiles} that shows the aspect ratio profile $h(r)=H(r)/r$.
@@
 \end{equation}
-where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring5}}=5.2$\,au, $\mu_{\mathrm{Ring13}}=14.9$\,au\}, ring widths \{$\sigma_{\mathrm{Ring5}}=0.25$\,au, $\sigma_{\mathrm{Ring13}}=2.2$\,au\}, and normalizations \{$\Sigma_{\circ,\mathrm{Ring5}}=3.3$\,$\mathrm{g\,cm^{-3}}$, $\Sigma_{\circ,\mathrm{Ring13}}=6.0 \times 10^{-1}$\,$\mathrm{g\,cm^{-3}}$\} for both components separately.
+where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring5}}=5.2$\,au, $\mu_{\mathrm{Ring13}}=14.9$\,au\}, ring widths \{$\sigma_{\mathrm{Ring5}}=0.25$\,au, $\sigma_{\mathrm{Ring13}}=2.25$\,au\}, and normalizations \{$\Sigma_{\circ,\mathrm{Ring5}}=3.3$\,$\mathrm{g\,cm^{-3}}$, $\Sigma_{\circ,\mathrm{Ring13}}=6.0 \times 10^{-1}$\,$\mathrm{g\,cm^{-3}}$\} for both components separately.
 
@@
 Nevertheless, as a way to improve and obtain a rough measure of the accuracy of our model, we made one dimensional explorations of the parameter space and found uncertainties of some relevant parameters that will be useful for the discussion (see Appendix.~\ref{sec:Appendix}).
-We can estimate confidence intervals for the scale height at $r_\circ$= 18\,au with $H_\circ = 0.92^{+0.01}_{-0.01}$\,au, for the location of Ring5 with $r=5.2^{+0.14}_{-0.36}$\,au, and for the width of gas Ring13 of $w_\mathrm{g} = 5.18^{+0.33}_{-0.20}$\,au.
+We can estimate confidence intervals for the scale height at $r_\circ$= 18\,au with $H_\circ = 0.91^{+0.01}_{-0.01}$\,au and for the width of gas Ring13 of $w_\mathrm{g} = 5.30^{+0.24}_{-0.30}$\,au.
 
@@
 Otherwise, the present small grains should quickly coagulate to form detectable grain sizes in the ALMA observation in Fig.~\ref{fig:images_vs_simulated} \citep{Drazkowska2019}.
-The central emission is also well reproduced with the inclusion of a Gaussian close ring, resulting in the observed central blob.
+The central emission is also well reproduced with the inclusion of a Gaussian close ring.
 The lack of a high NIR excess in the SED indicate that the dust in this blob must be at least bigger than 0.5\,mm (see Appendix~\ref{sec:Appendix}), but we choose to use 0.8\,mm as the lower limit for the dust population that composes this feature because this predicts a dust mass of 0.012\,M$_{\earth}$, that is in agreement with the mass estimate of \citet{Francis_2020} (0.013$\pm$0.002\,M$_{\earth}$).
@@
 
-Discs, rings and gaps are common structures present in protoplanetary discs, each time a disc with complex geometry appears we learn something knew about planet formation or disc mechanics.
-
-Observing the same source at different wavelengths, or employing more than one instrument, will tell different stories about the same physical phenomena.
-Using radiative transfer simulations let us find a common plot that may explain all this diverse results.
-For V4046\,Sgr, there was a missing piece for an accurate representation of the system: a thin ring of millimetre-sized dust grains at a distance of $\sim$13\,au.
-We present new ALMA 1.3\,mm continuum imaging of this circumbinary disc at an unprecedented definition ($\sim$0$\farcs021 \, \times \, \sim$0$\farcs018$) were new features ring becomes visible for the first time.
-The new observed feature gives us some insights of the dynamics that are driving the formation of this unique morphology.
-Together with the analysis of SPHERE--IRDIS polarized images and a well-sampled SED, the radiative transfer modeling came as a useful tool for increasing the scope of our investigation.
+Rings, spirals, cavities and gaps are common structures present in protoplanetary discs, but only recent observations have allowed us to study them in detail.
+Observing systems with solar-type stars, that are not exceptionally bright or large, has not been the main focus of high resolution imaging.
+For that reason, DARTTS-S programme, that collected DPI data for T Tauri Stars, has been so revealing, and with the counterpart of ALMA continuum maps from DARTTS-A, we can search for substructures in this systems as never before.
+Following that line, we present new ALMA 1.3\,mm continuum imaging of V4046\,Sgr, a well know circumbinary disc, at an unprecedented definition ($\sim$0$\farcs021 \, \times \, \sim$0$\farcs018$) where new features become visible.
+Together with the analysis of a SPHERE--IRDIS polarized image and a well-sampled SED, we aim to reproduce the system with radiative transfer modeling looking for a way to explain the data in terms of a physically model.
 
@@
 
-  \item The central emission present in the ALMA image might be a close inner ring made up of dust grains larger than 0.5\,mm, or it would create a NIR excess higher than the one inferred from the SED.
-Our model agrees with the mass estimation for this feature made by \citet{Francis_2020} with a mass of 0.012\,M$_{\earth}$.
+  \item The central emission present in the ALMA image suggests the existence of a close inner ring that goes in pass the sublimation radius and is made up of dust grains larger than 0.5\,mm.
+Our interpretation agrees with the mass estimation for this feature made by \citet{Francis_2020} with a mass of 0.012\,M$_{\earth}$.
+
+  \item Our parametric model, which accounts for the SED of the system, involves the existence of sub-micron dust population close to the stars (inner disc outside the sublimation radius).
+Also predicts the presence of another inner ring at $\sim$5\,au, mainly consisting of small dust grains.
+The depletion of large dust is consistent with efficient dust trapping in Ring13.
+This additional ring lies under the coronagraph of the scattered light image and is to faint to be detected by the ALMA observation.
 
@@
 
-  \item Our parametric model, which accounts for the SED of the system, involves the existence of a sub-micron dust population close to the stars (inner disc).
-Also predicts the presence of another inner ring at $\sim$5\,au, mainly consisting of small dust grains.
-The depletion of large dust is consistent with efficient dust trapping in Ring13.
-This additional ring lies under the coronagraph of the scattered light image and is to faint to be detected by the ALMA observation.
 \end{enumerate}

### 2021-05-30 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 This appears to be inconsistent with the detection of the mm-bright central emission, as the presence of a inner disc would generate higher NIR fluxes, but the low excess could be interpreted as a lack of micron-sized dust in the central spot.
-Also, from this feature (or the absence of it) \citet{Francis_2020} stated that the inner radius of the millimetre-sized dust ring that accounts for the central emission is well beyond the sublimation radius, around 0.1\,au.
+Also, from this feature (or the absence of it) \citet{Francis_2020} stated that the inner radius of the millimetre-sized dust ring that accounts for the central emission is well beyond the sublimation radius, at around 0.1\,au.
 
@@
 Consequently, our approach was to find through trial and error a set of values for the parameters that closely fit the available data, and then, improve this fit by implementing one dimensional chi squared optimizations for some key parameters (more on this in sec.~\ref{sec:results}).
-The final structure of the parametric model is summarised in Fig.~\ref{fig:profiles}, where we show on the top panel surface density profiles for gas, large and small dust grains, and in the bottom panel the respective aspect ratio profile.
+The final structure of the parametric model is summarised in Fig.~\ref{fig:profiles}, where we show on the top panel surface density profiles for gas and the dust grains population, and in the bottom panel the respective aspect ratio profile for each specie.
 
@@
 We built the model in terms of the gas distribution, and with two main dust populations: larger grains that are vertically settled and dominate the total dust mass, and a population of smaller grains that are uniformly mixed with the gas and reach higher regions above the mid-plane.
-And we also added a third dust population of large grains and with a tightly confined distribution and a special size range just to account for the central emission.
+We also added a third dust population of large grains with a tightly confined distribution and a special size range just to account for the central emission.
 
@@
 We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =3.3\times10^{-4}$\,$\mathrm{g\,cm^{-3}}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
-Our model extends from 0.3\,au outwards, consistent with the inner edge radius inferred from the SED data (See sec.~\ref{subsec:SED}).
+The gas in our model extends from $R_{sub}$ = 0.3\,au outwards, consistent with the inner edge radius inferred from the SED data (See sec.~\ref{subsec:SED}).
 
@@
 
-The simulated 1.3\,mm continuum image reproduces the two observed rings: the faint Ring13 and the brighter Ring24.
+The simulated 1.3\,mm continuum image reproduces the two observed rings: the thin Ring13 and the brighter Ring24.
 The introduced Ring5 is not visible in the simulated image as its predicted peak intensity is around two times the noise in the ALMA image ($\sim$1$\times10^{-7}$\,Jy\,$\mathrm{beam}^{-1}$).
@@
 The central emission is also well reproduced with the inclusion of a Gaussian close ring.
-The lack of a high NIR excess in the SED indicate that the dust in this blob must be at least bigger than 0.5\,mm (see Appendix~\ref{sec:Appendix}), but we choose to use 0.8\,mm as the lower limit for the dust population that composes this feature because this predicts a dust mass of 0.012\,M$_{\earth}$, that is in agreement with the mass estimate of \citet{Francis_2020} (0.013$\pm$0.002\,M$_{\earth}$).
+The lack of a high-NIR excess in the SED indicate that the dust in this ring must be at least bigger than 0.5\,mm (see Appendix~\ref{sec:Appendix}), but our decision to implement 0.8\,mm as the lower limit for the dust population that composes this feature is well justified, as this predicts a dust mass of 0.012\,M$_{\earth}$, that is in agreement with the mass estimate of \citet{Francis_2020} (0.013$\pm$0.002\,M$_{\earth}$).
 
@@
 The model predictions for the millimetre-sized dust population in Ring13 are close to the measurements, with only a 0.07\,au difference in the centroid location of the ring, and a 0.46\,au difference in the width estimation.
-Since the scale height FWHM of the large grains in Ring13 is 0.25\,au, and that from the ALMA observation we can resolve a width of 2.46$\pm$0.56\,au (see sec.~\ref{subsec:ALMA}), the ring is 9.7$\pm$1.5 times more extended radially than vertically.
+Since the scale height FWHM of the large grains in Ring13 is 0.25\,au, and that from the ALMA observation we can resolve a width of 2.46$\pm$0.56\,au (see sec.~\ref{subsec:ALMA}), the ring is 9.8$\pm$1.6 times more extended radially than vertically.
 Looking at the rest of the disc, in turn, our model reproduces the observations of Ring24 with peak intensity at $\sim$30\,au, and breaks at $\sim$36\,au.
@@
 The observed SED is compared with the model in Fig.~\ref{fig:SED}.
-From the similarity with the data, we propose that there has to be a small-grain population close to the stars down to 0.3\,au, i.e.
+From the similarity with the data, we propose that there has to be a small-grain population close to the stars down to 0.3\,au ($R_{}$), i.e.
 an inner disc, as it was crucial to fit the 5--10\,$\micron$ range.

### 2021-05-30 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 Computing a high-resolution radiative transfer model that succeeds in the reproduction of multi-frequency imaging and the SED, is finding a solution to a highly degenerative problem, so obtaining an ideal model with a full parameter exploration requires a level of computation and time that exceeds our capabilities and the scope of this paper.
-Consequently, our approach was to find through trial and error a set of values for the parameters that closely fit the available data, and then, improve this fit by implementing one dimensional chi squared optimizations for some key parameters (more on this in sec.~\ref{sec:results}).
+Consequently, our approach was to find through trial and error a set of values for the parameters that closely fit the available data, and then, improve this fit by implementing one dimensional chi squared optimizations for some key parameters (more on this in Sec.~\ref{sec:results}).
 The final structure of the parametric model is summarised in Fig.~\ref{fig:profiles}, where we show on the top panel surface density profiles for gas and the dust grains population, and in the bottom panel the respective aspect ratio profile for each specie.
@@
 Although both ALMA and SPHERE--IRDIS images display two-ringed morphologies, we propose a three-ringed structure plus an inner disc to reproduce the observations.
-This bold decision is due the major fit improvement in the SED and the polarize image (more on this in sec.~\ref{sec:results}).
+This bold decision is due the major fit improvement in the SED and the polarize image (more on this in Sec.~\ref{sec:results}).
 We separate the disc into four individual regions: the inner disc, Ring5, Ring13, and Ring24.
@@
 We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =3.3\times10^{-4}$\,$\mathrm{g\,cm^{-3}}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
-The gas in our model extends from $R_{sub}$ = 0.3\,au outwards, consistent with the inner edge radius inferred from the SED data (See sec.~\ref{subsec:SED}).
+The gas in our model extends from $R_{sub}$ = 0.3\,au outwards, consistent with the inner edge radius inferred from the SED data (See Sec.~\ref{subsec:SED}).
 
@@
 This dust population has grains with radii ranging from 0.8 to 10\,mm, same upper limit as the large dust but is depleted of small grains.
-This different size range is a way to avoid creating excess NIR in the SED and to be consistent with previous mass estimates (see Appendix~\ref{sec:Appendix}).
+This different size range is a way to avoid creating excess NIR in the SED and to be consistent with previous mass estimates (see Appendix~\ref{sec:Appendix} and Sec.~\ref{sec:results}).
 As the ring is extremely proximate to the binary system the dust will not have any traces of ice, so we used a composition mix of 70\% silicate and 30\% graphite.
@@
 The model predictions for the millimetre-sized dust population in Ring13 are close to the measurements, with only a 0.07\,au difference in the centroid location of the ring, and a 0.46\,au difference in the width estimation.
-Since the scale height FWHM of the large grains in Ring13 is 0.25\,au, and that from the ALMA observation we can resolve a width of 2.46$\pm$0.56\,au (see sec.~\ref{subsec:ALMA}), the ring is 9.8$\pm$1.6 times more extended radially than vertically.
+Since the scale height FWHM of the large grains in Ring13 is 0.25\,au, and that from the ALMA observation we can resolve a width of 2.46$\pm$0.56\,au (see Sec.~\ref{subsec:ALMA}), the ring is 9.8$\pm$1.6 times more extended radially than vertically.
 Looking at the rest of the disc, in turn, our model reproduces the observations of Ring24 with peak intensity at $\sim$30\,au, and breaks at $\sim$36\,au.
@@
 The observed SED is compared with the model in Fig.~\ref{fig:SED}.
-From the similarity with the data, we propose that there has to be a small-grain population close to the stars down to 0.3\,au ($R_{}$), i.e.
+From the similarity with the data, we propose that there has to be a small-grain population close to the stars down to 0.3\,au ($R_{sub}$), i.e.
 an inner disc, as it was crucial to fit the 5--10\,$\micron$ range.
@@
 As a way to compute a measure of goodness of fit and to try to quantify the model uncertainties, we performed a partial exploration of parameter space.
-We explore $\chi^2$ space in the vicinity of the model values (obtained by trial and error, see sec.~\ref{sec:model}) for the scale height at $r_\circ$ ($H_\circ$), the width of the gas component of Ring13 $w_{\mathrm{g13}}$, and around the lower limit of the grain sizes in the central blob.
+We explore $\chi^2$ space in the vicinity of the model values (obtained by trial and error, see Sec.~\ref{sec:model}) for the scale height at $r_\circ$ ($H_\circ$), the width of the gas component of Ring13 $w_{\mathrm{g13}}$, and around the lower limit of the grain sizes in the central blob.
 The parameter space exploration is shown in Fig.~\ref{fig:chi}.
@@
 
-For $H_\circ$ and $w_{\mathrm{g13}}$, we find that the values of the parameters in our model are almost at a minimum in each one dimensional $\chi^2$ space, so given $\chi^2_\mathrm{m}$ the local minimum value, the uncertainties (up and down) will be those with $\chi^2=\chi^2_\mathrm{m}+1$.
+For $H_\circ$ and $w_{\mathrm{g13}}$, we find that the values of the parameters in our model are at a minimum in each one dimensional $\chi^2$ space, so given $\chi^2_\mathrm{m}$ the local minimum value, the uncertainties (up and down) will be those with $\chi^2=\chi^2_\mathrm{m}+1$.
 As the values are around a local minimum, we can as assume a quadratic equation for the curve fitting.
 
-For the lower grain size limit, we found that although our chosen value is at the minimum, the geometry is more suggestive of a border condition.
+For the lower grain size limit, we found that despite our chosen value minimises $\chi^2$, the geometry is more suggestive of a border condition.
 It is evident that there is a threshold around 500\,$\micron$ where the SED start to deviate far away from the typical value.
@@
         \caption{One dimensional explorations of the chi squared space of our parametric model.
-Variation of $\chi^2$ in terms of the scale height $H_\circ$ at $r_\circ$=18\,au, the width of the gas component of Ring13 $w_{\mathrm{g13}}$, and around the lower limit of the grain size in the central blob.
+We show the variation of $\chi^2$ in terms of the scale height $H_\circ$ at $r_\circ$=18\,au, the width of the gas component of Ring13 $w_{\mathrm{g13}}$, and around the lower limit of the grain size in the close inner ring.
 Each panel displays at the bottom the $\chi^2$ values for the SED and for the two images separately, and on top the total $\chi^2$ value in terms of the parameter value.}

### 2021-05-30 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 an inner disc, as it was crucial to fit the 5--10\,$\micron$ range.
-On the other hand, the observed central and compact signal in the ALMA observation cannot be explained with the hypothesis of thermal emission from large grains in the inner disc.
-Following the mass estimates in Section~\ref{sec:Observations}, the millimetre-sized dust needed reaches $\sim$18 times larger surface densities than in the gas, resulting in a large excess at 10$\,\micron$ that does not match the data.
-Meanwhile, the decision of employing the three-ringed structure (i.e.
-add Ring5 to the observed structure) relies on the fact that the SED needed a ring at a radius around 4--6\,au to have a proper fit around 10\,$\micron$, otherwise, instead of the distinct bump that is present, there would be a gap.
+Meanwhile, the decision of employing the three-ringed structure for the small dust (i.e.
+add Ring5 to the observed structure) relies on the fact that the SED needed a thin ring at a radius at $\sim$5\,au to have a proper fit around 10\,$\micron$, otherwise, instead of the distinct bump that is present, there would be a gap.
 

### 2021-05-31 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 This angular resolution is comparable to uniform or super-uniform weights in {\tt tclean}, but it preserves the natural-weights point-source sensitivity.
+The RMS noise of the {\tt uvmem} image is 26\,$\micron$Jy per resolution beam, at a frequency of 237\,GHz.
 
@@
 While this is the first observation of Ring13, \citet{Ru_z_Rodr_guez_2019} did anticipate its existence as their ALMA continuum image showed a distinct excess between $\sim$10 and 17\,au.
-The {\tt uvmem} map has a resolution of 21$\times$18\,mas and an RMS noise of 26$\micron$Jy per resolution beam, at a frequency of 237 GHz.
 
@@
 
-The ring width can be measured in polar coordinates by fitting 1-D Gaussians at each azimuth, thus obtaining a width and centroid.
-The top panel of Fig.~\ref{fig:polarring} shows the positions of the obtained centroids and widths over the polar decomposition of the ALMA image.
-On average, we obtained a FWHM of 2.83$\pm$0.50\,au, and a stellocentric radius of 13.15$\pm$0.42\,au.
-As the {\tt uvmem} model image has an approximate {\tt uvmem} beam of $\sim$0$\farcs021 \,\times \,\sim$0$\farcs018$ (or $\sim$1.4\,au at 71.1\,pc), we see that Ring13 is resolved.
-After subtraction of the {\tt uvmem} beam, the ring width is $\sim$2.46$\pm$0.56\,au.
-
 In a second optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.86$\pm$0.02\,$\degr$, with an inclination of 33.92$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 2\pm0.02$\,mas $\Delta \delta = 12\pm0.02$\,mas relative to the stars.
@@
 The curve that follows these fitted centroids for each of the optimizations goes almost entirely within the errors of the other one, leaving the window open to the discussion of if this differences are just a consequence of the pointing error or are they a real notable feature of the disc.
+
+The width of Ring13 can be measured in polar coordinates by fitting 1-D Gaussians at each azimuth, thus obtaining a width and centroid.
+The top panel of Fig.~\ref{fig:polarring} shows the positions of the obtained centroids and widths over the polar decomposition of the ALMA image.
+On average, we obtained a FWHM of 2.83$\pm$0.50\,au, and a stellocentric radius of 13.15$\pm$0.42\,au.
+As the {\tt uvmem} model image has an approximate {\tt uvmem} beam of $\sim$0$\farcs021 \,\times \,\sim$0$\farcs018$ (or $\sim$1.4\,au at 71.1\,pc), we see that Ring13 is resolved.
+After subtraction of the {\tt uvmem} beam, the ring width is $\sim$2.46$\pm$0.56\,au.
 

### 2021-05-31 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 This is summarised in the second panel of Fig.~\ref{fig:polarring}, where it shows the centroids of the Gaussian fitting at each azimuth for both optimization.
-The curve that follows these fitted centroids for each of the optimizations goes almost entirely within the errors of the other one, leaving the window open to the discussion of if this differences are just a consequence of the pointing error or are they a real notable feature of the disc.
+The curve that follows these centroids fitted for each of the optimizations goes almost entirely within the errors of the other one, leaving the window open for discussion as to whether these differences are just a consequence of the pointing error or are a true feature of the disc.
+Future imaging and further research will clarify the doubts.
 
@@
 Since this central emission is larger than the angular resolution, it is probably stemming from thermal emission from large dust grains rather than directly from the stars.
-The peak intensity of this dust structure is at an estimated distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.85$\pm$0.14\,au, from the binary system, and, estimating its form as a Gaussian ellipse, it has a mean FWHM of $\sim$1.43\,au.
+The peak intensity of this dust structure is at an estimated distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.85$\pm$0.14\,au from the binary system, and, estimating its form as a Gaussian ellipse, it has a mean FWHM of $\sim$1.43\,au.
 Measurements of this central emission made by \citet{Francis_2020}, assume a power-law profile for an inner disc that goes from 0.1 to 4\,au, and has a total dust mass of 0.013$\pm$0.002\,M$_{\earth}$.
@@
 The SED present a low near--infrared (NIR) excess of 0.9$\pm$3.7\,\% \citep{Francis_2020}.
-This appears to be inconsistent with the detection of the mm-bright central emission, as the presence of a inner disc would generate higher NIR fluxes, but the low excess could be interpreted as a lack of micron-sized dust in the central spot.
-Also, from this feature (or the absence of it) \citet{Francis_2020} stated that the inner radius of the millimetre-sized dust ring that accounts for the central emission is well beyond the sublimation radius, at around 0.1\,au.
+This appears to be inconsistent with the detection of the mm-bright central emission, as the presence of a inner disc would generate higher NIR fluxes, but the low excess could be interpreted as a lack of micron-sized dust in the central ring.
+Also, \citet{Francis_2020} stated that the inner radius of the millimetre-sized dust ring that accounts for the central emission is well beyond the sublimation radius, at around 0.1\,au.
 
@@
 Consequently, our approach was to find through trial and error a set of values for the parameters that closely fit the available data, and then, improve this fit by implementing one dimensional chi squared optimizations for some key parameters (more on this in Sec.~\ref{sec:results}).
-The final structure of the parametric model is summarised in Fig.~\ref{fig:profiles}, where we show on the top panel surface density profiles for gas and the dust grains population, and in the bottom panel the respective aspect ratio profile for each specie.
+The final structure of the parametric model is summarised in Fig.~\ref{fig:profiles}, where we show on the top panel the surface density profiles for gas and dust grains populations, and in the lower panel the respective aspect ratio profile.
 
@@
 We built the model in terms of the gas distribution, and with two main dust populations: larger grains that are vertically settled and dominate the total dust mass, and a population of smaller grains that are uniformly mixed with the gas and reach higher regions above the mid-plane.
-We also added a third dust population of large grains with a tightly confined distribution and a special size range just to account for the central emission.
+We also added a third dust population of larger grains with a tightly confined distribution and a special size range just to account for the central emission.
 
@@
 where $H_\circ$ is the scale height at $r$ = $r_\circ$, $\psi$ is the flaring index and $\chi$ is a scaling factor (in the range $0-1$) that mimics dust settling.
-In hydrostatical equilibrium dust diffusion and settling are expected to balance each other, leading to a settling factor of $\chi = \sqrt{D_{\rm d}/(D_{\rm d} + St)}$ \citep{Dubrulle1995}.
-Here, $D_{\rm d}$ is a dimensionless parameter that informs about the level of diffusivity (it is typically assumed to be similar to the level of turbulence for the particle sizes regarded here \citep{2007Icar..192..588Y}.
+In hydrostatical equilibrium, dust diffusion and settling are expected to balance each other, leading to a settling factor of $\chi = \sqrt{D_{\rm d}/(D_{\rm d} + St)}$ \citep{Dubrulle1995}.
+Here, $D_{\rm d}$ is a dimensionless parameter that informs about the level of diffusivity \citep[it is typically assumed to be similar to the level of turbulence for the particle sizes regarded here][]{2007Icar..192..588Y}.
 The Stokes number,
@@
 \end{equation}
-summarises a particle's dynamical behaviour in a given environment (where $\rho_{\rm mat}$ represents a dust particle's material density).
+summarises the dynamical behaviour of a particle in a given environment (where $\rho_{\rm mat}$ represents a dust particle's material density).
 By definition, the gas has no settling, and the small dust grains settling is negligible, so that $\chi_{\rm gas}=\chi_{\rm sd}=1$.
@@
 We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =3.3\times10^{-4}$\,$\mathrm{g\,cm^{-3}}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
-The gas in our model extends from $R_{sub}$ = 0.3\,au outwards, consistent with the inner edge radius inferred from the SED data (See Sec.~\ref{subsec:SED}).
+The gas in our model extends from $R_{\mathrm{sub}}$ = 0.3\,au outwards, consistent with the inner edge radius inferred from the SED data (see Sec.~\ref{subsec:SED}).
 
@@
 \end{equation}
-where
+where for the smoothing factor $\epsilon(r)$ we used $R_\mathrm{in,ld}$ = 24.2\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$. In an effort to recreate the break seen in the outer ring, we used
 \begin{equation}
@@
   3.2 \times10^{4} & 27.9 < r < 35.3\text{\,au} \\
-  2.7 \times10^{5} & 35.3 < r < 64\text{\,au.} \\
+  2.7 \times10^{5} & 35.3 < r < 64\text{\,au,} \\
   \end{cases}
 \end{equation}
-and for the smoothing factor $\epsilon(r)$ we used $R_\mathrm{in,ld}$ = 24.2\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$. In an effort to recreate the break seen in the outer ring, we used
+and
 \begin{equation}
@@
   3.5 & 27.9\text{\,au} < r < 35.3\text{\,au} \\
-    1                 &  {\rm elsewhere} \\
+    1                 &  {\rm elsewhere.} \\
   \end{cases}
@@
 The observed asymmetry between the near side and the far side of the disc in the DPI image is suggestive of a strongly forward-scattering phase function.
-In order to reproduce a similar asymmetry, we used much larger grains than typically used in the RT modelling of such NIR data \citep[e.g.,][]{2018MNRAS.477.5104C}.
-
-The simulated DPI image at 1.65\,$\micron$ in Fig.~\ref{fig:images_vs_simulated} was obtained with the scattering matrix calculated by the {\tt makeopac.py} script provided in the \textsc{radmc3d} package.
-As a way of reproducing the \textit{H}-band image, we used a different grain size distribution, where we centred a Gaussian at $\mathrm{a}$ = 0.4\,$\micron$ with $\sigma_{\mathrm{a}}$ = 0.12\,$\micron$ (smeared out by 30\%), and distributed the dust over 20 bins within the range of $\pm \sigma$.
+In order to reproduce a similar asymmetry in the \textit{H}-band image, we used much larger grains than typically used in the RT modelling of such NIR data \citep[e.g.,][]{2018MNRAS.477.5104C}.
+We implemented a different grain size distribution, where we centred a Gaussian at $\mathrm{a}$ = 0.4\,$\micron$ with $\sigma_{\mathrm{a}}$ = 0.12\,$\micron$ (smeared out by 30\%), and distributed the dust over 20 bins within the range of $\pm \sigma$.
 This distribution applies only to generate the NIR $Q_\phi$ image and not the ALMA image or the SED.
 To produce this $Q_\phi$ image we performed a linear combination of the two orthogonal linear polarizations \textit{U} and \textit{Q}, following \citet{Avenhaus_2017}, which gives a representation of an unbiased estimate of the polarized intensity image.
+The simulated DPI image at 1.65\,$\micron$ in Fig.~\ref{fig:images_vs_simulated} was obtained with the scattering matrix calculated by the {\tt makeopac.py}, script provided in the \textsc{radmc3d} package.
 
@@
 This dust population has grains with radii ranging from 0.8 to 10\,mm, same upper limit as the large dust but is depleted of small grains.
-This different size range is a way to avoid creating excess NIR in the SED and to be consistent with previous mass estimates (see Appendix~\ref{sec:Appendix} and Sec.~\ref{sec:results}).
+This different size range is a way to avoid creating a NIR excess in the SED, and to be consistent with previous mass estimates (see Appendix~\ref{sec:Appendix} and Sec.~\ref{sec:results}).
 As the ring is extremely proximate to the binary system the dust will not have any traces of ice, so we used a composition mix of 70\% silicate and 30\% graphite.
@@
 
-While certainly not unique, our parametric model is fairly successful in reproducing the available data, so it became a useful tool to discuss the real disc.
+While certainly not unique, our parametric model is fairly successful in reproducing the available data, so it is a useful tool to discuss the real system.
 The simulated images and the SED of the model are shown in Fig.~\ref{fig:images_vs_simulated} and Fig.~\ref{fig:SED} respectively.
@@
 As mentioned before, the model presented here gives a solution to a highly degenerative problem.
-Nevertheless, as a way to improve and obtain a rough measure of the accuracy of our model, we made one dimensional explorations of the parameter space and found uncertainties of some relevant parameters that will be useful for the discussion (see Appendix.~\ref{sec:Appendix}).
-We can estimate confidence intervals for the scale height at $r_\circ$= 18\,au with $H_\circ = 0.91^{+0.01}_{-0.01}$\,au and for the width of gas Ring13 of $w_\mathrm{g} = 5.30^{+0.24}_{-0.30}$\,au.
+Nevertheless, as a way to improve it and obtain a rough measure of the accuracy of our model, we made one dimensional explorations of the parameter space and found uncertainties of some relevant parameters that will be useful for the discussion (see Appendix.~\ref{sec:Appendix}).
+We can estimate errors for the scale height at $r_\circ$= 18\,au with $H_\circ = 0.91^{+0.01}_{-0.01}$\,au and for the width of the gas in Ring13 with $w_\mathrm{g} = 5.30^{+0.24}_{-0.30}$\,au.
 
@@
 The central emission is also well reproduced with the inclusion of a Gaussian close ring.
-The lack of a high-NIR excess in the SED indicate that the dust in this ring must be at least bigger than 0.5\,mm (see Appendix~\ref{sec:Appendix}), but our decision to implement 0.8\,mm as the lower limit for the dust population that composes this feature is well justified, as this predicts a dust mass of 0.012\,M$_{\earth}$, that is in agreement with the mass estimate of \citet{Francis_2020} (0.013$\pm$0.002\,M$_{\earth}$).
+The lack of a high-NIR excess in the SED indicates that the dust in this ring must be at least bigger than 0.5\,mm (see Appendix~\ref{sec:Appendix}), but our decision to implement 0.8\,mm as the lower limit for the dust population that composes this feature is well justified, as this predicts a dust mass of 0.012\,M$_{\earth}$, that is in agreement with the mass estimate of \citet{Francis_2020} (0.013$\pm$0.002\,M$_{\earth}$).
 
 As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.~\ref{fig:radprofiles}), we can assume that the model provides a possible approximation of the disc structure, including the dimensions of Ring13.
-The FWHM of the gas in Ring13 in the RT model corresponds to $w_\mathrm{g} = 5.18^{+0.32}_{-0.20}$\,au, but the  large dust grains have to be radially converged to explain the ALMA image.
-Accordingly, taking the parametric model values for the large dust in Ring13, it has a FWHM of 2.00\,au, a radius of 13.22\,au, and a scale height FWHM of the millimetre-sized dust of 0.25\,au.
+The FWHM of the gas and micron-sized dust in Ring13 in the RT model corresponds to $w_\mathrm{g} = 5.30^{+0.24}_{-0.30}$\,au, as well as a radius of 14.9\,au, and a scale height FWHM of 0.63\,au.
+Meanwhile, the millimetre-sized dust in Ring13 has a FWHM of 2.00\,au, a radius of 13.22\,au, and a scale height FWHM of 0.25\,au.
 The total dust mass of Ring13 would be about 0.7\,M$_{\earth}$.
@@
 Since the scale height FWHM of the large grains in Ring13 is 0.25\,au, and that from the ALMA observation we can resolve a width of 2.46$\pm$0.56\,au (see Sec.~\ref{subsec:ALMA}), the ring is 9.8$\pm$1.6 times more extended radially than vertically.
-Looking at the rest of the disc, in turn, our model reproduces the observations of Ring24 with peak intensity at $\sim$30\,au, and breaks at $\sim$36\,au.
-It contains a total dust mass of $\sim$45\,M$_{\earth}$.%, that stands under the lower limit of 60\,M$_{\earth}$ inferred by \citet{Ru_z_Rodr_guez_2019} from a previous 860\,$\micron$ continuum ALMA image.
+Looking at the rest of the disc, in turn, our model reproduces the observations of Ring24 with peak intensity at $\sim$30\,au, and the break at $\sim$36\,au.
+The whole disc contains a total dust mass of $\sim$45\,M$_{\earth}$.
+%, that stands under the lower limit of 60\,M$_{\earth}$ inferred by \citet{Ru_z_Rodr_guez_2019} from a previous 860\,$\micron$ continuum ALMA image.
 
@@
 The observed SED is compared with the model in Fig.~\ref{fig:SED}.
-From the similarity with the data, we propose that there has to be a small-grain population close to the stars down to 0.3\,au ($R_{sub}$), i.e.
+From the similarity with the data, we propose that there has to be a small-grain population close to the stars down to 0.3\,au ($R_{\mathrm{sub}}$), i.e.
 an inner disc, as it was crucial to fit the 5--10\,$\micron$ range.

### 2021-05-31 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 Meanwhile, the decision of employing the three-ringed structure for the small dust (i.e.
-add Ring5 to the observed structure) relies on the fact that the SED needed a thin ring at a radius at $\sim$5\,au to have a proper fit around 10\,$\micron$, otherwise, instead of the distinct bump that is present, there would be a gap.
+add Ring5 to the observed structure) relies on the fact that the SED needs a thin dust ring at a radius of $\sim$5\,au to have a proper fit around 15\,$\micron$, otherwise, instead of the distinct bump that is present, there would be a valley.
 
@@
 Rings, spirals, cavities and gaps are common structures present in protoplanetary discs, but only recent observations have allowed us to study them in detail.
-Observing systems with solar-type stars, that are not exceptionally bright or large, has not been the main focus of high resolution imaging.
-For that reason, DARTTS-S programme, that collected DPI data for T Tauri Stars, has been so revealing, and with the counterpart of ALMA continuum maps from DARTTS-A, we can search for substructures in this systems as never before.
+In the past years, observing systems with solar-type stars, that are not exceptionally bright or large, has not been the main focus of high resolution imaging.
+For that reason, DARTTS-S programme, that collected DPI data for T Tauri Stars, has been so revealing, and with the counterpart of ALMA continuum maps from DARTTS-A, we can search for substructures in that kind of systems as never before.
 Following that line, we present new ALMA 1.3\,mm continuum imaging of V4046\,Sgr, a well know circumbinary disc, at an unprecedented definition ($\sim$0$\farcs021 \, \times \, \sim$0$\farcs018$) where new features become visible.
@@
   \item The central emission present in the ALMA image suggests the existence of a close inner ring that goes in pass the sublimation radius and is made up of dust grains larger than 0.5\,mm.
-Our interpretation agrees with the mass estimation for this feature made by \citet{Francis_2020} with a mass of 0.012\,M$_{\earth}$.
+Our interpretation agrees with the mass estimation of this feature made by \citet{Francis_2020} with a mass of 0.012\,M$_{\earth}$.
 
-  \item Our parametric model, which accounts for the SED of the system, involves the existence of sub-micron dust population close to the stars (inner disc outside the sublimation radius).
-Also predicts the presence of another inner ring at $\sim$5\,au, mainly consisting of small dust grains.
+  \item Our parametric model, which accounts for the SED of the system, involves the existence of sub-micron dust inner disc.
+Also predicts the presence of a undetected inner ring at $\sim$5\,au, mainly consisting of small dust grains.
 The depletion of large dust is consistent with efficient dust trapping in Ring13.
@@
 The parametric model presented here has many degrees of freedom and the RT calculation for each set of parameters is very intensive in computational power and time, so a MCMC optimization or similar methods of parameter exploration are impossible to carry out.
-As a way to compute a measure of goodness of fit and to try to quantify the model uncertainties, we performed a partial exploration of parameter space.
+As a way to compute a measure of goodness of fit and to try to quantify the model uncertainties, we performed a partial exploration of the parameter space.
+
 We explore $\chi^2$ space in the vicinity of the model values (obtained by trial and error, see Sec.~\ref{sec:model}) for the scale height at $r_\circ$ ($H_\circ$), the width of the gas component of Ring13 $w_{\mathrm{g13}}$, and around the lower limit of the grain sizes in the central blob.
@@
 
-For the lower grain size limit, we found that despite our chosen value minimises $\chi^2$, the geometry is more suggestive of a border condition.
-It is evident that there is a threshold around 500\,$\micron$ where the SED start to deviate far away from the typical value.
+For the lower grain size limit, we found that despite our chosen value seems to minimise $\chi^2$, the geometry is more suggestive of a border condition.
+So it is evident that there is a threshold around 500\,$\micron$ where the SED starts to deviate strongly from the typical value.
 That point represent where the NIR excess becomes significant.
@@
         \caption{One dimensional explorations of the chi squared space of our parametric model.
-We show the variation of $\chi^2$ in terms of the scale height $H_\circ$ at $r_\circ$=18\,au, the width of the gas component of Ring13 $w_{\mathrm{g13}}$, and around the lower limit of the grain size in the close inner ring.
+The first panel shows the variation of $\chi^2$ in terms of the scale height $H_\circ$ at $r_\circ$=18\,au, the second one for the width of the gas component of Ring13 $w_{\mathrm{g13}}$, and the third one around the lower limit of the grain size in the close inner ring.
 Each panel displays at the bottom the $\chi^2$ values for the SED and for the two images separately, and on top the total $\chi^2$ value in terms of the parameter value.}

### 2021-06-13 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 Sebasti\'an P\'erez,$^{2}$
-Antonio Hales,$^{3,4}$
+Antonio Hales,$^{4,5}$
 Philipp Weber, $^{1,2}$ \newauthor
-Miguel Carcamo,$^{5,6}$
+Miguel Carcamo,$^{6,7}$
 Carla Arce-Tord,$^{1}$
-Lucas Cieza,$^{7}$
-Antonio Garufi,$^{8}$
-Sebasti\'an Marino,$^{9}$
-Alice Zurlo$^{7,10,11}$
+Lucas Cieza,$^{8}$
+Antonio Garufi,$^{9}$
+Sebasti\'an Marino,$^{10}$
+Alice Zurlo$^{8,11,12}$
 \\
@@
 $^{2}$Departamento de F\'isica, Universidad de Santiago de Chile, Av. Ecuador 3659, Santiago\\
-$^{3}$Joint ALMA Observatory, Avenida Alonso de C\'ordova 3107, Vitacura 7630355, Santiago, Chile \\
-$^{4}$National Radio Astronomy Observatory, 520 Edgemont Road, Charlottesville, VA 22903-2475, United States of America \\
-$^{5}$Departamento de Ingenier\'ia Inform´atica, Universidad de Santiago de Chile, Av. Ecuador, 3659, Santiago, Chile\\
-$^{6}$Jodrell Bank Centre for Astrophysics, Alan Turing Building, Department of Physics and Astronomy, Alan Turing Building,\\ University of Manchester, Oxford Road, Manchester, M13 9PL, UK \\
-$^{7}$N\'ucleo de Astronom\'ia, Facultad de Ingenier\'ia y Ciencias, Universidad Diego Portales, Av. Ejercito 441, Santiago, Chile\\
-$^{8}$INAF, Osservatorio Astrofisico di Arcetri, Largo Enrico Fermi 5, I-50125, Firenze, Italy\\
-$^{9}$Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
-$^{10}$Escuela de Ingenier\'ia Industrial, Facultad de Ingenier\'ia y Ciencias, Universidad Diego Portales, Av. Ejercito 441, Santiago, Chile \\
-$^{11}$Aix Marseille Universit\'e, CNRS, LAM - Laboratoire d'Astrophysique de Marseille, UMR 7326, 13388, Marseille, France  \\
+$^{3}$ Center for Interdisciplinary Research in Astrophysics and Space Exploration (CIRAS), Universidad de Santiago de Chile, Estaci\'on Central, Chile \\
+$^{4}$Joint ALMA Observatory, Avenida Alonso de C\'ordova 3107, Vitacura 7630355, Santiago, Chile \\
+$^{5}$National Radio Astronomy Observatory, 520 Edgemont Road, Charlottesville, VA 22903-2475, United States of America \\
+$^{6}$Departamento de Ingenier\'ia Inform´atica, Universidad de Santiago de Chile, Av. Ecuador, 3659, Santiago, Chile\\
+$^{7}$Jodrell Bank Centre for Astrophysics, Alan Turing Building, Department of Physics and Astronomy, Alan Turing Building,\\ University of Manchester, Oxford Road, Manchester, M13 9PL, UK \\
+$^{8}$N\'ucleo de Astronom\'ia, Facultad de Ingenier\'ia y Ciencias, Universidad Diego Portales, Av. Ejercito 441, Santiago, Chile\\
+$^{9}$INAF, Osservatorio Astrofisico di Arcetri, Largo Enrico Fermi 5, I-50125, Firenze, Italy\\
+$^{10}$Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
+$^{11}$Escuela de Ingenier\'ia Industrial, Facultad de Ingenier\'ia y Ciencias, Universidad Diego Portales, Av. Ejercito 441, Santiago, Chile \\
+$^{12}$Aix Marseille Universit\'e, CNRS, LAM - Laboratoire d'Astrophysique de Marseille, UMR 7326, 13388, Marseille, France  \\
 }
@@
 \textit{Bottom right panel:} synthetic image at 1.3\,mm convolved with the {\tt uvmem} beam.
-For all the images in the figure the colour scale is linear.}
+For all the images in the figure the colour scale is linear, and the color bar on the right applies only to the right images.}
   \label{fig:images_vs_simulated}
@@
 The SED describe the characteristic “dip” near 10 $\micron$, a common element of transition disc, as described by \citet{Rosenfeld_2013}.
-\citet{Jensen_97} concluded that these data matched that of a extended circumbinary disc truncated at $\sim$0.3\,au, as the interior would also be expected to be cleared by dynamical effects of the central binary \citep{Art_Lu}.
+\citet{Jensen_97} concluded that these data matched that of a extended circumbinary disc truncated at $\sim$0.2\,au, as the interior would also be expected to be cleared by dynamical effects of the central binary \citep{Art_Lu}.
 
-The SED present a low near--infrared (NIR) excess of 0.9$\pm$3.7\,\% \citep{Francis_2020}.
-This appears to be inconsistent with the detection of the mm-bright central emission, as the presence of a inner disc would generate higher NIR fluxes, but the low excess could be interpreted as a lack of micron-sized dust in the central ring.
-Also, \citet{Francis_2020} stated that the inner radius of the millimetre-sized dust ring that accounts for the central emission is well beyond the sublimation radius, at around 0.1\,au.
+The SED reveals a small near--infrared (NIR) excess of 0.9$\pm$3.7\,\% \citep{Francis_2020}.
+The mm-bright central emission, on the other hand, suggests a much more massive inner dust disc.
+The lack of correlation between the excess of NIR fluxes and mm emission could point to a lack of micron-sized dust in this central ring.
+This could be due to efficient dust growth or, as proposed by \citet{Francis_2020}, due to an incongruity between the sublimation radius and the inner boundary of the disc.
 
@@
 The separation between the two values was set at $r = 18$\,au with $\psi_1=0.2$ for Ring5 and Ring13, and $\psi_2=0.5$ for Ring24.
-The scale height is set to $H_\circ = 0.91$\,au at $r_\circ = 18$\,au.
-This vertical structure is consistent with the measurements made by \citet{dOrazi}, as the model flaring angles are $\varphi_{\mathrm{inner}}$ = 6.5\,$\degr$ and $\varphi_{\mathrm{outer}}$ = 7.8\,$\degr$.
+The scale height is set to $H_\circ = 0.89$\,au at $r_\circ = 18$\,au.
+This vertical structure is consistent with the measurements made by \citet{dOrazi}, as the model flaring angles are $\varphi_{\mathrm{inner}}$ = 6.4\,$\degr$ and $\varphi_{\mathrm{outer}}$ = 7.6\,$\degr$.
 This is summarized in bottom panel of Fig.~\ref{fig:profiles} that shows the aspect ratio profile $h(r)=H(r)/r$.
@@
 where $R_c$ is a characteristic radius and $\gamma$ is the surface density power-law index.
-We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =3.3\times10^{-4}$\,$\mathrm{g\,cm^{-3}}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
-The gas in our model extends from $R_{\mathrm{sub}}$ = 0.3\,au outwards, consistent with the inner edge radius inferred from the SED data (see Sec.~\ref{subsec:SED}).
+We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =1.3\times10^{-4}$\,$\mathrm{g\,cm^{-3}}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
+The gas in our model extends from $R_{\mathrm{in}}$ = 0.2\,au outwards, consistent with the inner edge radius inferred from the SED data (see Sec.~\ref{subsec:SED}).
 
@@
 \end{equation}
-where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring5}}=5.2$\,au, $\mu_{\mathrm{Ring13}}=14.9$\,au\}, ring widths \{$\sigma_{\mathrm{Ring5}}=0.25$\,au, $\sigma_{\mathrm{Ring13}}=2.25$\,au\}, and normalizations \{$\Sigma_{\circ,\mathrm{Ring5}}=3.3$\,$\mathrm{g\,cm^{-3}}$, $\Sigma_{\circ,\mathrm{Ring13}}=6.0 \times 10^{-1}$\,$\mathrm{g\,cm^{-3}}$\} for both components separately.
+where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring5}}=5.2$\,au, $\mu_{\mathrm{Ring13}}=14.9$\,au\}, ring widths \{$\sigma_{\mathrm{Ring5}}=0.25$\,au, $\sigma_{\mathrm{Ring13}}=2.26$\,au\}, and normalizations \{$\Sigma_{\circ,\mathrm{Ring5}}=3.3$\,$\mathrm{g\,cm^{-3}}$, $\Sigma_{\circ,\mathrm{Ring13}}=6.0 \times 10^{-1}$\,$\mathrm{g\,cm^{-3}}$\} for both components separately.
 
@@
 \end{equation}
-with $\delta_{\mathrm{sd}}(r) = 4.2\times 10^4$ for $r > 18$\,au and zero for lower radii, and
+with $\delta_{\mathrm{sd}}(r) = 1.0\times 10^5$ for $r > 18$\,au and zero for lower radii, and
 %\begin{equation}
@@
   0                 & r < 24.6\text{\,au} \\
-  7.2 \times10^{4} & 24.6 < r < 27.9\text{\,au} \\
-  3.2 \times10^{4} & 27.9 < r < 35.3\text{\,au} \\
-  2.7 \times10^{5} & 35.3 < r < 64\text{\,au,} \\
+  1.8 \times10^{5} & 24.6 < r < 27.9\text{\,au} \\
+  8.4 \times10^{4} & 27.9 < r < 35.3\text{\,au} \\
+  7.1 \times10^{5} & 35.3 < r < 64\text{\,au,} \\
   \end{cases}
@@
   \begin{cases}
-  3.5 & 27.9\text{\,au} < r < 35.3\text{\,au} \\
+  -3.8 & 27.9\text{\,au} < r < 35.3\text{\,au} \\
     1                 &  {\rm elsewhere.} \\
@@
 
-For the reproduction of central emission we introduce a special dust population that is distributed only on a very close Gaussian ring parameterized by $\mu_{\mathrm{central\,blob}}=1.1$\,au, $\sigma_{\mathrm{central\,blob}}=0.4$\,au and $\Sigma_{\circ,\mathrm{central\,blob}}=58.8\,\mathrm{g\,cm^{-3}}$, and following the argument of \citet{Francis_2020}, it goes in past the sublimation radius until it reaches the grid boundary.
+For the reproduction of central emission we introduce a special dust population that is distributed only on a very close Gaussian ring parameterized by $\mu_{\mathrm{central\,blob}}=1.1$\,au, $\sigma_{\mathrm{central\,blob}}=0.4$\,au and $\Sigma_{\circ,\mathrm{central\,blob}}=58.8\,\mathrm{g\,cm^{-3}}$.
 This dust population has grains with radii ranging from 0.8 to 10\,mm, same upper limit as the large dust but is depleted of small grains.
@@
 Nevertheless, as a way to improve it and obtain a rough measure of the accuracy of our model, we made one dimensional explorations of the parameter space and found uncertainties of some relevant parameters that will be useful for the discussion (see Appendix.~\ref{sec:Appendix}).
-We can estimate errors for the scale height at $r_\circ$= 18\,au with $H_\circ = 0.91^{+0.01}_{-0.01}$\,au and for the width of the gas in Ring13 with $w_\mathrm{g} = 5.30^{+0.24}_{-0.30}$\,au.
+We can estimate errors for the scale height at $r_\circ$= 18\,au with $H_\circ = 0.89\pm0.01$\,au and for the width of the gas in Ring13 with $w_\mathrm{g} = 5.30\pm0.27$\,au.
 
@@
 The central emission is also well reproduced with the inclusion of a Gaussian close ring.
-The lack of a high-NIR excess in the SED indicates that the dust in this ring must be at least bigger than 0.5\,mm (see Appendix~\ref{sec:Appendix}), but our decision to implement 0.8\,mm as the lower limit for the dust population that composes this feature is well justified, as this predicts a dust mass of 0.012\,M$_{\earth}$, that is in agreement with the mass estimate of \citet{Francis_2020} (0.013$\pm$0.002\,M$_{\earth}$).
+The lack of a high-NIR excess in the SED indicates that the dust in this ring must be at least bigger than 0.3\,mm (see Appendix~\ref{sec:Appendix}), but our decision to implement 0.8\,mm as the lower limit for the dust population that composes this feature is well justified, as this predicts a dust mass of 0.012\,M$_{\earth}$, that is in agreement with the mass estimate of \citet{Francis_2020} (0.013$\pm$0.002\,M$_{\earth}$).
 
@@
 The model predictions for the millimetre-sized dust population in Ring13 are close to the measurements, with only a 0.07\,au difference in the centroid location of the ring, and a 0.46\,au difference in the width estimation.
-Since the scale height FWHM of the large grains in Ring13 is 0.25\,au, and that from the ALMA observation we can resolve a width of 2.46$\pm$0.56\,au (see Sec.~\ref{subsec:ALMA}), the ring is 9.8$\pm$1.6 times more extended radially than vertically.
+Since the scale height FWHM of the large grains in Ring13 is 0.25\,au, and that from the ALMA observation we can resolve a width of 2.46$\pm$0.56\,au (see Sec.~\ref{subsec:ALMA}), the ring is 10.0$\pm$1.6 times more extended radially than vertically.
 Looking at the rest of the disc, in turn, our model reproduces the observations of Ring24 with peak intensity at $\sim$30\,au, and the break at $\sim$36\,au.
-The whole disc contains a total dust mass of $\sim$45\,M$_{\earth}$.
+The whole disc contains a total dust mass of $\sim$48\,M$_{\earth}$.
 %, that stands under the lower limit of 60\,M$_{\earth}$ inferred by \citet{Ru_z_Rodr_guez_2019} from a previous 860\,$\micron$ continuum ALMA image.
@@
 As \citet{Ru_z_Rodr_guez_2019} suggest, the putative planet between Ring13 and Ring24 may be a giant planet with a mass within the range of 0.3$-$1.5\,$\mathrm{M}_{\mathrm{Jup}}$.
-This idea is supported by the similarity to the structure around HD\,169142 which \citet{2020arXiv200711565B} reproduced by including several giant planets.
+This idea is supported by a dedicated study (Weber et al.
+submitted) which qualitatively reproduces the observations of this system with a hydrodynamical simulation including several giant planets.
 
@@
 The observed SED is compared with the model in Fig.~\ref{fig:SED}.
-From the similarity with the data, we propose that there has to be a small-grain population close to the stars down to 0.3\,au ($R_{\mathrm{sub}}$), i.e.
-an inner disc, as it was crucial to fit the 5--10\,$\micron$ range.
+The SED requires the extent of the inner cavity to significantly exceed both the sublimation radius ($\sim$0.05-0.1\,au) and the zone that is expected to be cleared by dynamical binary-disc interaction \citep[][$\lesssim$0.1\,au]{Art_Lu}, insinuating the presence of an additional effect of truncation.
 Meanwhile, the decision of employing the three-ringed structure for the small dust (i.e.
@@
 
-  \item The central emission present in the ALMA image suggests the existence of a close inner ring that goes in pass the sublimation radius and is made up of dust grains larger than 0.5\,mm.
+  \item The central emission present in the ALMA image suggests the existence of a close inner ring made up of dust grains larger than 0.5\,mm.
 Our interpretation agrees with the mass estimation of this feature made by \citet{Francis_2020} with a mass of 0.012\,M$_{\earth}$.
@@
 acknowledges support from the Joint Committee of ESO and the Government of Chile and FONDECYT grant 1191934.
+P.W.
+acknowledges support from ALMA-ANID postdoctoral fellowship 31180050.
 A.Z.
@@
 For the lower grain size limit, we found that despite our chosen value seems to minimise $\chi^2$, the geometry is more suggestive of a border condition.
-So it is evident that there is a threshold around 500\,$\micron$ where the SED starts to deviate strongly from the typical value.
+So it is evident that there is a threshold around 300\,$\micron$ where the SED starts to deviate strongly from the typical value.
 That point represent where the NIR excess becomes significant.
@@
 \begin{figure*}
-	\includegraphics[width=\textwidth]{plot_chi_squared_all800.pdf}
+	\includegraphics[width=\textwidth]{plot_chi_squared_all.pdf}
         \caption{One dimensional explorations of the chi squared space of our parametric model.
-The first panel shows the variation of $\chi^2$ in terms of the scale height $H_\circ$ at $r_\circ$=18\,au, the second one for the width of the gas component of Ring13 $w_{\mathrm{g13}}$, and the third one around the lower limit of the grain size in the close inner ring.
+The first panel shows the variation of $\chi^2$ in terms of the scale height $H_\circ$ at $r_\circ$=18\,au, the second one for the width of the gas component of Ring13 ($w_{\mathrm{g13}}$), and the third one around the lower limit of the grain size in the close inner ring.
 Each panel displays at the bottom the $\chi^2$ values for the SED and for the two images separately, and on top the total $\chi^2$ value in terms of the parameter value.}

### 2021-06-22 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
     The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc known for its wide cavity and dusty ring.
-We present high resolution ($\sim$20\,mas or 1.4\,au) ALMA observations of the 1.3\,mm continuum of V4046\,Sgr which, combined with SPHERE--IRDIS polarized images and well-sampled spectral energy distribution (SED), allow us to propose a physical model using radiative transfer (RT) predictions.
+We present high resolution ($\sim$20\,mas or 1.4\,au) ALMA observations of the 1.3\,mm continuum of V4046\,Sgr which, combined with SPHERE--IRDIS polarized images and a well-sampled spectral energy distribution (SED), allow us to propose a physical model using radiative transfer (RT) predictions.
 The new ALMA data reveal a thin ring at a radius of 13.15$\pm$0.42\,au (Ring13), with a radial width of 2.46$\pm$0.56\,au.
@@
 Between 25 and $\sim$35\,au the brightness of Ring24 is relatively flat and then breaks into a steeper tail that reaches out to $\sim$60\,au.
-In addition, central emission is detected close to the star which we interpret as a tight ring made of dust grains with a lower size limit of 0.5\,mm.
-In order to reproduce the SED, the model also requires an inner ring at $\sim$5\,au (Ring5) composed mainly of small dust grains, hiding under the IRDIS coronagraph, and surrounding an inner circumbinary disc.
+In addition, central emission is detected close to the star which we interpret as a tight circumbinary ring made of dust grains with a lower size limit of 0.8\,mm at 1.1\,au.
+In order to reproduce the SED, the model also requires an inner ring at $\sim$5\,au (Ring5) composed mainly of small dust grains, hiding under the IRDIS coronagraph, and surrounding the inner circumbinary disc.
 The surprisingly thin Ring13 is nonetheless roughly 10 times wider than its expected vertical extent.
@@
 
-Building  a parametric model that simultaneously fits the near-IR scattered light and millimetre continuum emission  can provide a way to link the observations to the structures in the underlying dust and gas density distributions, and shed light on the complex processes that shaped them.
+Building a parametric model that simultaneously fits the NIR scattered light and millimetre continuum emission  can provide a way to link the observations to the structures in the underlying dust and gas density distributions, and shed light on the complex processes that shaped them.
 In this paper, we present new ALMA observations of the continuum emission at 1.3\,mm of V4046\,Sgr, which reveal a new inner ring in the disc.
@@
 
-The resulting {\tt uvmem} image shown in the top right panel of Fig.~\ref{fig:images_vs_simulated} exhibits previously unseen substructure of the disc.
-This image reveals that the disc features two rings of large dust grains with a broad gap between them, i.e.
+The resulting {\tt uvmem} image shown in the top right panel of Fig.~\ref{fig:images_vs_simulated} reveals new substructure of the disc, in the form of two rings of large dust grains with a broad gap between them, i.e.
 Ring13 at 13\,au and Ring24 starting at 24\,au.
 The wide and bright Ring24 reaches its peak intensity at $\sim$30\,au, continues relatively flat and then breaks at $\sim$35\,au into a steeper tail.
-While this is the first observation of Ring13, \citet{Ru_z_Rodr_guez_2019} did anticipate its existence as their ALMA continuum image showed a distinct excess between $\sim$10 and 17\,au.
+While this is the first observation of Ring13, \citet{Ru_z_Rodr_guez_2019} anticipated its existence as their ALMA continuum image showed a distinct excess between $\sim$10 and 17\,au.
 
 Ring13 is surprisingly narrow and seems to be off-centred relative to the Gaia stellar position, at the origin of coordinates in Fig.~\ref{fig:images_vs_simulated}.
-We determined the ring's centre and orientation by minimising the dispersion of the disc radial profiles from 6 to 18\,au, by using the {\tt MPolarMaps} package described in Casassus et al.
-(2021, in prep).
-The resulting disc orientation is set at a position angle (PA) of 77.31$\pm$0.03\,$\degr$ (east of north), with an inclination of 32.96$\pm$0.02\,$\degr$, and the optimal ring centre is at $\Delta \alpha = -4\pm0.02$\,mas $\Delta \delta = 13\pm0.05$\,mas relative to the Gaia position of the stars.
-The offset of the center of the cavity and the nominal stellar positions is entirely consistent with a pointing error, since the pointing accuracy of ALMA is $\sim$5\,mas for the signal to noise ratio of our image (calculated using the ALMA Technical Handbook).
+We determined the ring's centre and orientation using the {\tt MPolarMaps} package described in \citep{2021arXiv210408379C}, which minimises the dispersion of the intensity radial profiles from 6 to 18\,au.
+The resulting disc orientation is set at a position angle (PA) of 77.31$\pm$0.03\,deg (east of north), with an inclination of 32.96$\pm$0.02\,deg, and the optimal ring centre is at $\Delta \alpha = -4\pm0.02$\,mas $\Delta \delta = 13\pm0.05$\,mas relative to the Gaia position of the stars.
+The offset of the center of the cavity and the nominal stellar positions are coincident within the pointing accuracy of ALMA, which  is $\sim$5\,mas for the signal to noise ratio of our image (calculated using the ALMA Technical Handbook).
 
-In a second optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.86$\pm$0.02\,$\degr$, with an inclination of 33.92$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 2\pm0.02$\,mas $\Delta \delta = 12\pm0.02$\,mas relative to the stars.
-We see that both Ring13 and Ring24 share a very similar orientation and centre, given the errors and the pointing error.
-However, quite likely due to the joint effect of all these small differences, we can see that there are some hints for a somewhat different orientation.
-This is summarised in the second panel of Fig.~\ref{fig:polarring}, where it shows the centroids of the Gaussian fitting at each azimuth for both optimization.
-The curve that follows these centroids fitted for each of the optimizations goes almost entirely within the errors of the other one, leaving the window open for discussion as to whether these differences are just a consequence of the pointing error or are a true feature of the disc.
-Future imaging and further research will clarify the doubts.
+In a second optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.86$\pm$0.02\,deg, with an inclination of 33.92$\pm$0.01\,deg and a centre at $\Delta \alpha = 2\pm0.02$\,mas $\Delta \delta = 12\pm0.02$\,mas relative to the stars.
+We see that both Ring13 and Ring24 share a very similar orientation and centre, given the errors and the pointing accuracy.
+However, see that there are some hints for a somewhat different orientation in the azimuthal profiles for the ring radii, which may nonetheless be accounted for by the joint effect of all these small differences in disc orientation.
+This is summarised in Fig.~\ref{fig:polarring}b, which characterises the radial position and width of Ring13 as a function of azimuth by using radial Gaussian fits at each azimuth.
+The radial centroids  for both disc orientation overlap within the errors, but there is a systematic trend for the difference between the two.
+It may be that this small difference reflects a finite  intrinsic eccentricity of one or both rings.
+Deeper imaging is required to progress on this question.
 
-The width of Ring13 can be measured in polar coordinates by fitting 1-D Gaussians at each azimuth, thus obtaining a width and centroid.
-The top panel of Fig.~\ref{fig:polarring} shows the positions of the obtained centroids and widths over the polar decomposition of the ALMA image.
-On average, we obtained a FWHM of 2.83$\pm$0.50\,au, and a stellocentric radius of 13.15$\pm$0.42\,au.
+On average, we obtained a radial FWHM for Ring13 of 2.83$\pm$0.50\,au, and a stellocentric radius of 13.15$\pm$0.42\,au.
 As the {\tt uvmem} model image has an approximate {\tt uvmem} beam of $\sim$0$\farcs021 \,\times \,\sim$0$\farcs018$ (or $\sim$1.4\,au at 71.1\,pc), we see that Ring13 is resolved.
@@
 The peak intensity of this dust structure is at an estimated distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.85$\pm$0.14\,au from the binary system, and, estimating its form as a Gaussian ellipse, it has a mean FWHM of $\sim$1.43\,au.
-Measurements of this central emission made by \citet{Francis_2020}, assume a power-law profile for an inner disc that goes from 0.1 to 4\,au, and has a total dust mass of 0.013$\pm$0.002\,M$_{\earth}$.
 
@@
 \textit{Bottom right panel:} synthetic image at 1.3\,mm convolved with the {\tt uvmem} beam.
-For all the images in the figure the colour scale is linear, and the color bar on the right applies only to the right images.}
+For all the images in the figure the colour scale is linear, and the color bar on the right applies only to the images on the right-hand panel.}
   \label{fig:images_vs_simulated}
@@
 
-The binary phase reported by \citet{dOrazi} in the scattered light observation is at a PA of 265\,$\degr$, east of north.
-Using this measurement, the binary phase was calculated at the time of the ALMA observation at a PA of $\sim$80\,$\degr$.
-There is no hint of radio decrements in either Ring13 nor in Ring24 that would match shadowing at this PA.
-This could be explained by inefficient disc cooling compared to the speed of the illumination pattern \citep[see ][ for estimates of this cooling timescale]{Casassus2019MNRAS.486L..58C}.
+The binary phase reported by \citet{dOrazi} in the scattered light observation is at a PA of 265\,deg, east of north.
+Using this measurement, the binary phase was calculated at the time of the ALMA observation at a PA of $\sim$80\,deg.
 
@@
 We also used archival \textit{Spitzer} IRS spectroscopic data available in the CASSIS database \citep{Lebouteiller_2015} (see Fig.~\ref{fig:SED}).
-The SED describe the characteristic “dip” near 10 $\micron$, a common element of transition disc, as described by \citet{Rosenfeld_2013}.
+The SED exhibits the dip near 10\,$\micron$ characteristic of transition discs, as described by \citet{Rosenfeld_2013}.
 \citet{Jensen_97} concluded that these data matched that of a extended circumbinary disc truncated at $\sim$0.2\,au, as the interior would also be expected to be cleared by dynamical effects of the central binary \citep{Art_Lu}.
-
-The SED reveals a small near--infrared (NIR) excess of 0.9$\pm$3.7\,\% \citep{Francis_2020}.
-The mm-bright central emission, on the other hand, suggests a much more massive inner dust disc.
-The lack of correlation between the excess of NIR fluxes and mm emission could point to a lack of micron-sized dust in this central ring.
-This could be due to efficient dust growth or, as proposed by \citet{Francis_2020}, due to an incongruity between the sublimation radius and the inner boundary of the disc.
 
@@
 The general framework of the parametric model that we developed is similar to that in \citet{2018MNRAS.477.5104C} for DoAr\,44, and the initial model values were inspired from those in \citet{Rosenfeld_2013}, \citet{Ru_z_Rodr_guez_2019} and \citet{2019ApJ...882..160Q}.
-Computing a high-resolution radiative transfer model that succeeds in the reproduction of multi-frequency imaging and the SED, is finding a solution to a highly degenerative problem, so obtaining an ideal model with a full parameter exploration requires a level of computation and time that exceeds our capabilities and the scope of this paper.
-Consequently, our approach was to find through trial and error a set of values for the parameters that closely fit the available data, and then, improve this fit by implementing one dimensional chi squared optimizations for some key parameters (more on this in Sec.~\ref{sec:results}).
+A high-resolution radiative transfer model that reproduces multi-frequency imaging and the SED, is a solution to a highly degenerate problem, so a full parameter exploration requires a level of computation and time that exceeds our capabilities and the scope of this paper.
+Consequently, our approach was to find through trial and error a set of values for the parameters that closely fit the available data, and then, improve this fit by implementing one dimensional least squared optimizations for some key parameters (more on this in Sec.~\ref{sec:results}).
 The final structure of the parametric model is summarised in Fig.~\ref{fig:profiles}, where we show on the top panel the surface density profiles for gas and dust grains populations, and in the lower panel the respective aspect ratio profile.
@@
 The stars were placed at a mutual separation of 0.041\,au, so that their centre of mass coincides with the origin.
-Their PA was set to 250\,$\degr$, so that the secondary lies to the NW from the primary, thus casting the same shadow as observed by \citet{dOrazi}.
+Their PA was set to 250\,deg, so that the secondary lies to the NW from the primary, thus casting the same shadow as observed by \citet{dOrazi}.
 
@@
 We built the model in terms of the gas distribution, and with two main dust populations: larger grains that are vertically settled and dominate the total dust mass, and a population of smaller grains that are uniformly mixed with the gas and reach higher regions above the mid-plane.
-We also added a third dust population of larger grains with a tightly confined distribution and a special size range just to account for the central emission.
+We also added a third dust population of larger grains with a  distribution tightly confined to the stellar vicinity, within 2\,au, and a special size range meant to account for the central emission.
 
@@
 \begin{equation}
-    {\rm St} := \frac{1}{2} \,\frac{\pi a \rho_{\rm mat}}{\Sigma_{\rm gas}}, 
+    {\rm St} = \frac{1}{2} \,\frac{\pi a \rho_{\rm mat}}{\Sigma_{\rm gas}}, 
 \end{equation}
@@
 For the vertical structure, \citet{dOrazi} found flaring angles (i.e.
-height of the ring over the disc midplane divided by the radius of the ring), of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one.
+height of the ring over the disc midplane divided by the radius of the ring), of $\varphi$ = 6.2$\pm$0.6\,deg for the inner ring and $\varphi$ = 8.5$\pm$1.0\,deg for the outer one.
 Our model aims to reproduce those values by using two different flaring indices, $\psi_1$ and $\psi_2$.
@@
 The scale height is set to $H_\circ = 0.89$\,au at $r_\circ = 18$\,au.
-This vertical structure is consistent with the measurements made by \citet{dOrazi}, as the model flaring angles are $\varphi_{\mathrm{inner}}$ = 6.4\,$\degr$ and $\varphi_{\mathrm{outer}}$ = 7.6\,$\degr$.
-This is summarized in bottom panel of Fig.~\ref{fig:profiles} that shows the aspect ratio profile $h(r)=H(r)/r$.
+This vertical structure is consistent with the measurements made by \citet{dOrazi}, as the model flaring angles are $\varphi_{\mathrm{inner}}$ = 6.4\,deg and $\varphi_{\mathrm{outer}}$ = 7.6\,deg.
+This is summarized in the bottom panel of Fig.~\ref{fig:profiles} that shows the aspect ratio profile $h(r)=H(r)/r$.
 
@@
 \begin{equation}
-  \Sigma_{\mathrm{gas}}(r) = \Sigma_{\mathrm{inner\,disc}} + \Sigma_{\mathrm{Ring5}} + \Sigma_{\mathrm{Ring13}} + \Sigma_{\mathrm{Ring24}}
+  \Sigma_{\mathrm{gas}}(r) = \Sigma_{\mathrm{inner\,disc}}(r) + \Sigma_{\mathrm{R5}}(r) + \Sigma_{\mathrm{R13}}(r) + \Sigma_{\mathrm{R24}}(r)
 \end{equation}
@@
 \end{equation}
-where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring5}}=5.2$\,au, $\mu_{\mathrm{Ring13}}=14.9$\,au\}, ring widths \{$\sigma_{\mathrm{Ring5}}=0.25$\,au, $\sigma_{\mathrm{Ring13}}=2.26$\,au\}, and normalizations \{$\Sigma_{\circ,\mathrm{Ring5}}=3.3$\,$\mathrm{g\,cm^{-3}}$, $\Sigma_{\circ,\mathrm{Ring13}}=6.0 \times 10^{-1}$\,$\mathrm{g\,cm^{-3}}$\} for both components separately.
+where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{R5}}=5.2$\,au, $\mu_{\mathrm{R13}}=14.9$\,au\}, ring widths \{$\sigma_{\mathrm{R5}}=0.25$\,au, $\sigma_{\mathrm{R13}}=2.26$\,au\}, and normalizations \{$\Sigma_{\circ,\mathrm{R5}}=3.3$\,$\mathrm{g\,cm^{-3}}$, $\Sigma_{\circ,\mathrm{R13}}=6.0 \times 10^{-1}$\,$\mathrm{g\,cm^{-3}}$\} for both components separately.
 
@@
 \begin{equation}
-  \Sigma_{\mathrm{Ring24}}(r) = \Sigma_{\mathrm{inner\,disc}}(r)\, \delta_{\mathrm{sd}}(r)\,\epsilon(r),
+  \Sigma_{\mathrm{R24}}(r) = \Sigma_{\mathrm{inner\,disc}}(r)\, \delta_{\mathrm{sd}}(r)\,\epsilon(r),
 \end{equation}
@@
 \begin{equation}
-\rho_{\mathrm{small-dust}}(r,z)=\rho_{\mathrm{gas}}(r,z)\, f_{\mathrm{sd}} \: \zeta .
+\rho_{\mathrm{small dust}}(r,z)=\rho_{\mathrm{gas}}(r,z)\, f_{\mathrm{sd}} \: \zeta .
 \end{equation}
@@
 \begin{equation}
-  \Sigma_{\mathrm{ld}}(r) = \Sigma_{\mathrm{Ring5,ld}} + 
-  \Sigma_{\mathrm{Ring13,ld}} + \Sigma_{\mathrm{Ring24,ld}}.
+  \Sigma_{\mathrm{ld}}(r) = \Sigma_{\mathrm{R5,ld}} + 
+  \Sigma_{\mathrm{R13,ld}} + \Sigma_{\mathrm{R24,ld}}.
 \end{equation}
 
-For Ring5 and Ring13, we chose Gaussian profiles parameterized with centroid radii $\mu_{\mathrm{Ring5, ld}}=5.2$\,au and $\mu_{\mathrm{Ring13, ld}}=13.22$\,au, ring widths of $\sigma_{\mathrm{Ring5,ld}}=0.1$\,au and $\sigma_{\mathrm{Ring13,ld}}=0.85$\,au, and normalizations $\Sigma_{\circ,\mathrm{Ring5,ld}}=1.3\times10^{-4}\,\mathrm{g\,cm^{-3}}$ and $\Sigma_{\circ,\mathrm{Ring13,ld}}=2.3\,\mathrm{g\,cm^{-3}}$.
+For Ring5 and Ring13, we chose Gaussian profiles parameterized with centroid radii $\mu_{\mathrm{R5, ld}}=5.2$\,au and $\mu_{\mathrm{R13, ld}}=13.22$\,au, ring widths of $\sigma_{\mathrm{R5,ld}}=0.1$\,au and $\sigma_{\mathrm{R13,ld}}=0.85$\,au, and normalizations $\Sigma_{\circ,\mathrm{R5,ld}}=1.3\times10^{-4}\,\mathrm{g\,cm^{-3}}$ and $\Sigma_{\circ,\mathrm{R13,ld}}=2.3\,\mathrm{g\,cm^{-3}}$.
 For Ring24 we used a similar profile as for the gas (a power-law function).
@@
 \begin{equation}
-    \Sigma_{\mathrm{Ring24,ld}}(r) = \Sigma_{\mathrm{c}} \left(\frac{r}{R_{\mathrm{c}}(r)}\right)^{-\gamma_{\mathrm{ld}}} \exp\left[-\left(\frac{r}{R_{\mathrm{c}}(r)}\right)^{2-\gamma_{\mathrm{ld}}}\right]\,\delta_{\mathrm{ld}}(r) \,\epsilon(r),
+    \Sigma_{\mathrm{R24,ld}}(r) = \Sigma_{\mathrm{c}} \left(\frac{r}{R_{\mathrm{c}}(r)}\right)^{-\gamma_{\mathrm{ld}}} \exp\left[-\left(\frac{r}{R_{\mathrm{c}}(r)}\right)^{2-\gamma_{\mathrm{ld}}}\right]\,\delta_{\mathrm{ld}}(r) \,\epsilon(r),
 \end{equation}
@@
 The inner radius of the model grid was set to 0.1\,au, and the outer radius to 100\,au, which is large enough for the dust disc to be undetectable.
-We set the values of the inclination and disc position angle to the same as obtained from the ALMA observation in Section~\ref{sec:Observations}, such that the model has an inclination of i = 32.96\,$\degr$ and a P.A.
-= 77.31\,$\degr$.
+We set the values of the inclination and disc position angle to the same as obtained from the ALMA observation in Section~\ref{sec:Observations}, such that the model has an inclination of i = 32.96\,deg and a P.A.
+= 77.31\,deg.
 Finally, the distance is set to d = 71.48\,pc \citep{gaiacollaboration2020gaia}.
+
+As mentioned before, the model presented here gives a solution to a highly degenerative problem, and the RT calculation for each set of parameters is very intensive in computational power and time, so a MCMC optimization or similar methods of parameter exploration are impossible to carry out.
+Nevertheless, as a way to improve the fit and obtain a rough measure of the accuracy of our model, we made one dimensional explorations of the parameter space and found uncertainties of some relevant parameters that will be useful for the discussion (see Appendix.~\ref{sec:Appendix}).
+We can estimate uncertainties for the scale height at $r_\circ$= 18\,au with $H_\circ = 0.89\pm0.01$\,au and for the width of the gas in Ring13 with $w_\mathrm{g} = 5.30\pm0.27$\,au.
 
@@
 
-While certainly not unique, our parametric model is fairly successful in reproducing the available data, so it is a useful tool to discuss the real system.
-The simulated images and the SED of the model are shown in Fig.~\ref{fig:images_vs_simulated} and Fig.~\ref{fig:SED} respectively.
-
-As mentioned before, the model presented here gives a solution to a highly degenerative problem.
-Nevertheless, as a way to improve it and obtain a rough measure of the accuracy of our model, we made one dimensional explorations of the parameter space and found uncertainties of some relevant parameters that will be useful for the discussion (see Appendix.~\ref{sec:Appendix}).
-We can estimate errors for the scale height at $r_\circ$= 18\,au with $H_\circ = 0.89\pm0.01$\,au and for the width of the gas in Ring13 with $w_\mathrm{g} = 5.30\pm0.27$\,au.
-
-%Given those uncertainties for the width of Ring13 and the , one thought that arise is that the inner ring could be much thinner than our ALMA measurements The intrinsic error of the {\tt uvmem} correction can not be known with high accuracy, so the approximate beam may not be $1/3$ of the beam in natural weights but higher.
-Any change in this factor would translate to into a narrower Ring13.
-With a $2/5$ factor, the width of Ring13 is 2.28$\pm$0.51\,au, resulting in a marginally resolve ring.
-T
-
-The simulated image at 1.65\,$\micron$ matches the radial structure of the corresponding observation to a high degree, displaying a two ringed disc, where Ring5 hides under the artificial coronagraph.
-The visible asymmetry in the SPHERE observations is reproduced using relatively large grains, $\sim$0.4\,$\micron$, as smaller grains did not result in such strong forward scattering.
-As \citet{refId0} state, the strong forward scattering that is present in the observation may indicate that the dust grains in the disc surface are relatively large, suggesting that the disc is depleted of very small grains.
-Alternatively, it may suggest that grains are not spherical as assumed in the calculations of opacities using Mie theory.
-Interestingly, the model accurately shows the shadows described by \citet{dOrazi} that are present in the SPHERE--IRDIS image.
+The observed SED reveals a small near-infrared (NIR) excess of 0.9$\pm$3.7\,\% \citep{Francis_2020}, this low emission would be primarily emanating from micron-sized dust grains at the hot inner dust wall of a low-mass inner disc.
+On the other hand, the mm-bright central emission suggests a massive inner dust ring.
+The faint near-IR excess contrast with the bright mm emission, and could point to a lack of micron-sized dust in the central ring, that could be due to efficient dust growth or due to the ring having an inner radius well beyond the sublimation radius.
+In order to reproduce the low NIR and simultaneous bright central mm emission, we extended the radius of an inner cavity to significantly exceed both the sublimation radius ($\sim$0.05-0.1\,au) and the zone that is expected to be cleared by dynamical binary-disc interaction \citep[][$\lesssim$0.1\,au]{Art_Lu}.
+A possible explanation for this wider cavity is the presence of an additional effect of truncation, like an unseen companion planet in the very inner part of the disc \citep{Francis_2020}.
+At the same time, the central emission is also well reproduced in the ALMA image with the inclusion of a Gaussian ring at 1.1\,au.
+This inner ring produces a low near-IR excess only if it consists of dust grains larger than $\sim$0.3\,mm (see Appendix~\ref{sec:Appendix}).
+But we implement 0.8\,mm instead as the lower limit for the dust population that composes this feature, given that this predicts a dust mass of 0.012\,M$_{\earth}$, which is close to that obtained by \citet{Francis_2020} (0.013$\pm$0.002,M${\earth}$).
+They converted mm-flux into mass using the standard opacity value of $\kappa_{\nu}$=10\,$\mathrm{cm}^2 \mathrm{g}^{-1}$ at 1000\,GHz with an opacity power-law index of $\beta$=1.0.
 
@@
 
-The simulated 1.3\,mm continuum image reproduces the two observed rings: the thin Ring13 and the brighter Ring24.
-The introduced Ring5 is not visible in the simulated image as its predicted peak intensity is around two times the noise in the ALMA image ($\sim$1$\times10^{-7}$\,Jy\,$\mathrm{beam}^{-1}$).
+The decision of including Ring5 to the observed structure relies on the fact that the SED needs a thin dust ring, made mainly of small dust grains, at a radius of $\sim$5\,au to have a proper fit around 15\,$\micron$ (see Appendix.\ref{sec:Appendix}).
+The introduced Ring5 is not visible in the simulated image at 1.65\,$\micron$, where it hides under the artificial coronagraph, neither in the 1.3\,mm continuum simulated image, as its predicted peak intensity is around two times the noise in the ALMA image ($\sim$1$\times10^{-7}$\,Jy\,$\mathrm{beam}^{-1}$).
 This gives us an upper limit for the total millimetre--sized dust mass present in Ring5 of $\sim$2$\times10^{-5}$\,M$_{\earth}$.
 The depletion of large dust grains in Ring5 is consistent with efficient dust trapping in Ring13.
-A zone of radially increasing gas pressure can entirely filter out large dust grains from inner regions, while smaller grains can be able to overcome this barrier due to their strong frictional coupling to the gas accretion flow \citep[studied in the context of planetary gaps,][]{Rice2006,Zhu2012,Weber2018}.
-Still, the strong depletion of large particles demands that within Ring5 dust evolution is extremely inefficient or limited, or that large particles are rapidly removed.
-Otherwise, the present small grains should quickly coagulate to form detectable grain sizes in the ALMA observation in Fig.~\ref{fig:images_vs_simulated} \citep{Drazkowska2019}.
-The central emission is also well reproduced with the inclusion of a Gaussian close ring.
-The lack of a high-NIR excess in the SED indicates that the dust in this ring must be at least bigger than 0.3\,mm (see Appendix~\ref{sec:Appendix}), but our decision to implement 0.8\,mm as the lower limit for the dust population that composes this feature is well justified, as this predicts a dust mass of 0.012\,M$_{\earth}$, that is in agreement with the mass estimate of \citet{Francis_2020} (0.013$\pm$0.002\,M$_{\earth}$).
+A zone of radially increasing gas pressure can entirely filter out large dust grains from the inner regions, while smaller grains can be able to overcome this barrier due to their strong frictional coupling to the gas accretion flow \citep[studied in the context of planetary gaps,][]{Rice2006,Zhu2012,Weber2018}.
+Still, the strong depletion of large particles demands that within Ring5 dust growth is extremely inefficient or limited by fragmentation.
+Otherwise, the present small grains should coagulate to form detectable grain sizes in the ALMA observation in Fig.~\ref{fig:images_vs_simulated} \citep{Drazkowska2019}.
 
 As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.~\ref{fig:radprofiles}), we can assume that the model provides a possible approximation of the disc structure, including the dimensions of Ring13.
-The FWHM of the gas and micron-sized dust in Ring13 in the RT model corresponds to $w_\mathrm{g} = 5.30^{+0.24}_{-0.30}$\,au, as well as a radius of 14.9\,au, and a scale height FWHM of 0.63\,au.
-Meanwhile, the millimetre-sized dust in Ring13 has a FWHM of 2.00\,au, a radius of 13.22\,au, and a scale height FWHM of 0.25\,au.
+The FWHM of the gas and micron-sized dust in Ring13 in the RT model corresponds to $w_\mathrm{g} = 5.30\pm0.27$\,au, as well as a radius of 14.9\,au, and a scale height FWHM of 0.63\,au.
+Meanwhile, the millimetre-sized dust in Ring13 has a FWHM of 2.00\,au, a radius of 13.22\,au, and a scale height FWHM of 0.25\,au ($\sim2.355\times H(\mu_\mathrm{R13,ld})$).
 The total dust mass of Ring13 would be about 0.7\,M$_{\earth}$.
-The model predictions for the millimetre-sized dust population in Ring13 are close to the measurements, with only a 0.07\,au difference in the centroid location of the ring, and a 0.46\,au difference in the width estimation.
-Since the scale height FWHM of the large grains in Ring13 is 0.25\,au, and that from the ALMA observation we can resolve a width of 2.46$\pm$0.56\,au (see Sec.~\ref{subsec:ALMA}), the ring is 10.0$\pm$1.6 times more extended radially than vertically.
-Looking at the rest of the disc, in turn, our model reproduces the observations of Ring24 with peak intensity at $\sim$30\,au, and the break at $\sim$36\,au.
+The model predictions for the millimetre-sized dust population in Ring13 are close to the measurements, with only a 1\% difference in the centroid location of the ring, and a 19\% difference in the width estimation.
+Given that the scale height FWHM of the large grains in Ring13 is 0.25\,au, and that the width of Ring13 from the ALMA observations is 2.46$\pm$0.56\,au (see Sec.~\ref{subsec:ALMA}), we conclude that the large dust ring is 10.0$\pm$1.6 times more extended radially than vertically.
+Looking at the rest of the disc, our model reproduces the observations of Ring24 with peak intensity at $\sim$30\,au, and the break at $\sim$36\,au.
 The whole disc contains a total dust mass of $\sim$48\,M$_{\earth}$.
-%, that stands under the lower limit of 60\,M$_{\earth}$ inferred by \citet{Ru_z_Rodr_guez_2019} from a previous 860\,$\micron$ continuum ALMA image.
-
-The observed structure may point to the existence of planet-disc interactions within this system, where a giant planet depletes its orbit of gas and dust material.
-A possible constellation in this scenario is, therefore, the presence of two giant planets in the disc, one planet between the star and Ring13, and one planet between Ring13 and Ring24.
-As \citet{Ru_z_Rodr_guez_2019} suggest, the putative planet between Ring13 and Ring24 may be a giant planet with a mass within the range of 0.3$-$1.5\,$\mathrm{M}_{\mathrm{Jup}}$.
-This idea is supported by a dedicated study (Weber et al.
-submitted) which qualitatively reproduces the observations of this system with a hydrodynamical simulation including several giant planets.
 
@@
 
-The observed SED is compared with the model in Fig.~\ref{fig:SED}.
-The SED requires the extent of the inner cavity to significantly exceed both the sublimation radius ($\sim$0.05-0.1\,au) and the zone that is expected to be cleared by dynamical binary-disc interaction \citep[][$\lesssim$0.1\,au]{Art_Lu}, insinuating the presence of an additional effect of truncation.
-Meanwhile, the decision of employing the three-ringed structure for the small dust (i.e.
-add Ring5 to the observed structure) relies on the fact that the SED needs a thin dust ring at a radius of $\sim$5\,au to have a proper fit around 15\,$\micron$, otherwise, instead of the distinct bump that is present, there would be a valley.
+The visible asymmetry in the SPHERE observations is reproduced using relatively large grains, $\sim$0.4\,$\micron$, as smaller grains did not result in such strong forward scattering.
+As \citet{refId0} state, the strong forward scattering that is present in the observation may indicate that the dust grains in the disc surface are relatively large, suggesting that the disc is depleted of very small grains.
+Alternatively, it may suggest that grains are not spherical as assumed in the calculations of opacities using Mie theory.
+
+Another interesting feature of the simulated 1.65\,$\micron$ image is that the model accurately shows the shadows described by \citet{dOrazi} that are present in the SPHERE–IRDIS image.
+In contrast, there are no hints of radio decrements along Ring13 or in Ring24, in either the ALMA observations or in the simulated 1.3\,mm continuum image, that would match the shadows.
+As noted by \citet{Casassus2019MNRAS.486L..58C}, the diffusion of thermal radiation from the disk smooths out the decrements seen in scattered light, and in this case it is likely that the disk cooling timescale is much slower than the that of the illumination pattern.
+
+The general observed structure may point to the existence of planet-disc interactions within this system, where giant planets deplete their orbits of gas and dust material.
+A possible planetary constellation in this scenario is, therefore, the presence of two giant planets in the disc, one planet between the star and Ring13, and one planet between Ring13 and Ring24.
+As \citet{Ru_z_Rodr_guez_2019} suggest, the putative planet between Ring13 and Ring24 may be a giant planet with a mass within the range of 0.3$-$1.5\,$\mathrm{M}_{\mathrm{Jup}}$.
+This idea is supported by a dedicated study (Weber et al.
+submitted) which qualitatively reproduces the observations of this system with a hydrodynamical simulation including several giant planets.
 
@@
 
-Rings, spirals, cavities and gaps are common structures present in protoplanetary discs, but only recent observations have allowed us to study them in detail.
+Rings, cavities and gaps are common structures present in protoplanetary discs, but only recent observations have allowed us to study them in detail.
 In the past years, observing systems with solar-type stars, that are not exceptionally bright or large, has not been the main focus of high resolution imaging.
-For that reason, DARTTS-S programme, that collected DPI data for T Tauri Stars, has been so revealing, and with the counterpart of ALMA continuum maps from DARTTS-A, we can search for substructures in that kind of systems as never before.
-Following that line, we present new ALMA 1.3\,mm continuum imaging of V4046\,Sgr, a well know circumbinary disc, at an unprecedented definition ($\sim$0$\farcs021 \, \times \, \sim$0$\farcs018$) where new features become visible.
-Together with the analysis of a SPHERE--IRDIS polarized image and a well-sampled SED, we aim to reproduce the system with radiative transfer modeling looking for a way to explain the data in terms of a physically model.
+For that reason, using the DARTTS-S programme data, that collected DPI images for T Tauri Stars, together with the counterpart of ALMA continuum maps from DARTTS-A, we can search for substructures in that kind of systems as never before.
+Following that line, we present new ALMA 1.3\,mm continuum imaging of V4046\,Sgr, a well-known circumbinary disc, at an unprecedented definition ($\sim$0$\farcs021 \, \times \, \sim$0$\farcs018$), where new features become visible.
+Together with the analysis of a SPHERE--IRDIS polarized image and a well-sampled SED, we aim to reproduce the observations with radiative transfer modeling, looking for a way to explain the data in terms of a physically model.
 
@@
 \begin{enumerate}
+    \item The central emission in the ALMA image suggests the existence of an inner ring of dust grains larger than 0.8\,mm.
+Our interpretation agrees with the mass estimation of this feature made by \citet{Francis_2020}, with a mass of 0.012\,M$_{\earth}$.
+
+    \item Our parametric model, which accounts for the SED of the system, involves the existence of sub-micron dust inner disc.
+Also predicts the presence of a undetected inner ring at $\sim$5\,au, mainly consisting of small dust grains.
+The depletion of large dust is consistent with efficient dust trapping in Ring13.
+This additional ring lies under the coronagraph of the scattered light image and is to faint to be detected by the ALMA observation.
+
     \item We report the detection of a two-ringed disc structure.
@@
 The 1.3\,mm outer ring, that starts at $\sim$24\,au and has its peak intensity at $\sim$30\,au, presents a visible break in the surface brightness at $\sim$36\,au.
-
-  \item The central emission present in the ALMA image suggests the existence of a close inner ring made up of dust grains larger than 0.5\,mm.
-Our interpretation agrees with the mass estimation of this feature made by \citet{Francis_2020} with a mass of 0.012\,M$_{\earth}$.
-
-  \item Our parametric model, which accounts for the SED of the system, involves the existence of sub-micron dust inner disc.
-Also predicts the presence of a undetected inner ring at $\sim$5\,au, mainly consisting of small dust grains.
-The depletion of large dust is consistent with efficient dust trapping in Ring13.
-This additional ring lies under the coronagraph of the scattered light image and is to faint to be detected by the ALMA observation.
 
@@
 
-The parametric model presented here has many degrees of freedom and the RT calculation for each set of parameters is very intensive in computational power and time, so a MCMC optimization or similar methods of parameter exploration are impossible to carry out.
+\subsection{Parameter space partial exploration}
 As a way to compute a measure of goodness of fit and to try to quantify the model uncertainties, we performed a partial exploration of the parameter space.
@@
 
-For $H_\circ$ and $w_{\mathrm{g13}}$, we find that the values of the parameters in our model are at a minimum in each one dimensional $\chi^2$ space, so given $\chi^2_\mathrm{m}$ the local minimum value, the uncertainties (up and down) will be those with $\chi^2=\chi^2_\mathrm{m}+1$.
-As the values are around a local minimum, we can as assume a quadratic equation for the curve fitting.
+For $H_\circ$ and $w_{\mathrm{g13}}$, we find that the values of the parameters in our model are at a minimum in each one dimensional $\chi^2$ space, the uncertainties (up and down) will be those that correspond to $\chi^2=\chi^2_\mathrm{m}+1$, where $\chi^2_\mathrm{m}$ is the local minimum value.
+We approximated the vicinity of the local minimum in these 1D cuts with a quadratic fit.
 
-For the lower grain size limit, we found that despite our chosen value seems to minimise $\chi^2$, the geometry is more suggestive of a border condition.
-So it is evident that there is a threshold around 300\,$\micron$ where the SED starts to deviate strongly from the typical value.
-That point represent where the NIR excess becomes significant.
-
-%These exploration allow us to support the idea of Ring5, as that the absence of it creates a great increment in the total $\chi^2$ value, but also requires the ring to be quite thin.
+For the lower grain size limit, we found that despite that our chosen value seems to minimise $\chi^2$, the shape that follows the curve is more suggestive of a border condition.
+So there is a threshold around 300\,$\micron$ where the SED starts to deviate strongly from the typical value.
+That point represents where the NIR excess becomes significantly larger that the observed.
 
@@
     \label{fig:chi}
+\end{figure*}
+
+\subsection{Comparison between different models}
+
+Our model includes Ring5, a thin Gaussian ring mainly consisting of small dust grains located at 5.2\,au.
+The inclusion of this feature provides a great improvement in the SED fit, especially around the 10-30\,$\micron$ range.
+The sublimation radius of the system is expected to be at $\sim$0.05\,au \citep[$R_{sub}=0.07\sqrt{L_*(L_{\sun})}$,][]{Francis_2020}, and the edge of the zone cleared by dynamical interactions between the near-circular binary and the circumbinary disc is at 0.085\,au \citep[$r=2.08a$,][]{Art_Lu}.
+The inner radius of the disc in our best-fitting model lies outside of these two regions, at 0.2\,au.
+
+In Fig.~\ref{fig:SED_comparition} we show a side-by-side comparison between our best-fitting model and two other models, one without Ring5, and another with the inner edge of the disc at the truncation radius due to dynamical binary-disc interaction.
+Both features considerably improve the fit in the 10-100\,$\micron$ range.
+
+\begin{figure*}
+	\includegraphics[width=\columnwidth]{SED_three_model_comparision.pdf}
+        \caption{}
+    \label{fig:SED_comparition}
+
 \end{figure*}

### 2021-10-08 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 \usepackage{amsmath}	% Advanced maths commands
+\usepackage{ulem}
+\usepackage{xcolor}
+
 %% \usepackage{amssymb}	% Extra maths symbols
@@
 %\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
+\newcommand{\red}[1]{\textcolor{red}{#1}}
 
@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[R. Martinez Brunner et al.]{Rafael Martinez--Brunner,$^{1}$
+\author[R. Martinez--Brunner et al.]{Rafael Martinez--Brunner,$^{1}$
 \thanks{E-mail: rmartinezbrunner@gmail.com}
 Simon Casassus,$^{1}$
-Sebasti\'an P\'erez,$^{2}$
+Sebasti\'an P\'erez,$^{2,3}$
 Antonio Hales,$^{4,5}$
-Philipp Weber, $^{1,2}$ \newauthor
+Philipp Weber, $^{1,2,3}$ \newauthor
 Miguel Carcamo,$^{6,7}$
@@
 $^{2}$Departamento de F\'isica, Universidad de Santiago de Chile, Av. Ecuador 3659, Santiago\\
-$^{3}$ Center for Interdisciplinary Research in Astrophysics and Space Exploration (CIRAS), Universidad de Santiago de Chile, Estaci\'on Central, Chile \\
+$^{3}$Center for Interdisciplinary Research in Astrophysics and Space Exploration (CIRAS), Universidad de Santiago de Chile, Estaci\'on Central, Chile \\
 $^{4}$Joint ALMA Observatory, Avenida Alonso de C\'ordova 3107, Vitacura 7630355, Santiago, Chile \\
 $^{5}$National Radio Astronomy Observatory, 520 Edgemont Road, Charlottesville, VA 22903-2475, United States of America \\
-$^{6}$Departamento de Ingenier\'ia Inform´atica, Universidad de Santiago de Chile, Av. Ecuador, 3659, Santiago, Chile\\
+$^{6}$Departamento de Ingenier\'ia Inform\'atica, Universidad de Santiago de Chile, Av. Ecuador, 3659, Santiago, Chile\\
 $^{7}$Jodrell Bank Centre for Astrophysics, Alan Turing Building, Department of Physics and Astronomy, Alan Turing Building,\\ University of Manchester, Oxford Road, Manchester, M13 9PL, UK \\
@@
 We present high resolution ($\sim$20\,mas or 1.4\,au) ALMA observations of the 1.3\,mm continuum of V4046\,Sgr which, combined with SPHERE--IRDIS polarized images and a well-sampled spectral energy distribution (SED), allow us to propose a physical model using radiative transfer (RT) predictions.
-The new ALMA data reveal a thin ring at a radius of 13.15$\pm$0.42\,au (Ring13), with a radial width of 2.46$\pm$0.56\,au.
+The ALMA data reveal a thin ring at a radius of 13.15$\pm$0.42\,au (Ring13), with a radial width of 2.46$\pm$0.56\,au.
 Ring13 is surrounded by a $\sim$10\,au-wide gap, and it is flanked by a mm-bright outer ring (Ring24) with a sharp inner edge at 24\,au.
@@
 The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$.
-The previously reported scattered light shadow of the secondary star is also reproduced by our model.
 \end{abstract}
@@
 Among the main recent findings of resolved observations of discs is the discovery of substructures in the form of gaps, rings, cavities, and spirals, to name a few \citep[see,][and references there in]{Andrews_2020_aug}.
-However, the focus of resolved imaging with the Atacama Large Millimeter/submillimeter Array (ALMA) or with the current generation of high-contrast cameras has mainly been towards the brighter sources.
+However, the focus of resolved imaging with the Atacama Large Millimeter/submillimeter Array (ALMA) or with the current generation of high-contrast cameras has mainly been towards the brighter sources \red{\citep[e.g.,][]{2017A&A...603A..21G}}.
 It is to address this bias that the ``Discs Around T Tauri Stars with SPHERE'' (DARTTS-S) programme collected differential polarization imaging (DPI) data with the Spectro-Polarimeter High-contrast Exoplanet REsearch \citep[SPHERE][]{2019A&A...631A.155B} for a total of 29 solar-type stars \citep[][]{Avenhaus_2018,Garufi2020}.
@@
 V4046\,Sgr is a double-lined spectroscopic binary of K-type stars (K5 and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012}, on a close ($a \approx 0.041$\,au), circular ($e\leq0.01$) orbit, with an orbital period of 2.42\,days \citep{2000IAUS..200P..28Q}.
-It is a member of the $\beta$ Pictoris moving group \citep{Zuckerman_2004}, with an estimated age of 18.5$^{+2.0}_{-2.4}$\,Myr \citep{2020A&A...642A.179M}, and its distance is 71.48$\pm$0.11\,pc \citep{gaiacollaboration2020gaia}.
+It is a member of the $\beta$ Pictoris moving group \citep{Zuckerman_2004}, with an estimated age of 18.5$^{+2.0}_{-2.4}$\,Myr \citep{2020A&A...642A.179M}, and its distance is 71.48$\pm$0.11\,pc \citep{gaiacollaboration2021gaia}.
 V4046\,Sgr hosts a massive ($\sim$0.1\,M$_{\sun}$) circumbinary disc extending to $\sim$300\,au \citep{Rosenfeld_2013, Rodriguez_2010}, rich in diverse molecular lines \citep{Kastner_2018}.
@@
 
-Building a parametric model that simultaneously fits the NIR scattered light and millimetre continuum emission  can provide a way to link the observations to the structures in the underlying dust and gas density distributions, and shed light on the complex processes that shaped them.
-In this paper, we present new ALMA observations of the continuum emission at 1.3\,mm of V4046\,Sgr, which reveal a new inner ring in the disc.
-We also reproduce these observations with a 3D parametric model that fits all available data, including the polarized scattered light SPHERE image, the spectral energy distribution (SED), as well as the new high definition 1.3\,mm continuum map.
+A parametric model that simultaneously fits the NIR scattered light and millimetre continuum emission links the observations to the structures in the underlying dust and gas density distributions, and sheds light on the complex processes that shaped them.
+In this paper, we present \red{\sout{new}} ALMA observations of the continuum emission at 1.3\,mm of V4046\,Sgr, which reveal an inner ring in the disc.
+We also reproduce these observations with a 3D parametric model that fits all available data, including the polarized scattered light SPHERE image, the spectral energy distribution (SED), as well as the \red{\sout{new}} high definition 1.3\,mm continuum map.
 Section~\ref{sec:Observations} describes the available observations that we aim to model.
@@
 
-New ALMA observations of V4046\,Sgr were obtained in 2017 as part of the Cycle 5 program 2017.1.01167.S (PI: S.
+\red{\sout{New}} ALMA observations of V4046\,Sgr were obtained in 2017 as part of the Cycle 5 program 2017.1.01167.S (PI: S.
 Perez).
@@
 with a band 6 211-275\,GHz correlator setup).
-The ALMA array was in its C43-8 configuration, with baselines ranging from 92 to 8548\,m which translate into a synthesized beam of $0\farcs062 \,\times \, 0\farcs055$, in natural weights.
+A log of the observations is shown in Table~\ref{tab:Summary_ALMA}.
+The ALMA array was in its C43-8/9 configuration, with baselines ranging from 92 to 13894 \,m which translate into a synthesized beam of $0\farcs062 \,\times \, 0\farcs055$, in natural weights.
 Here we focus on the continuum observations only.
-The line data will be presented in the main DARTTS-A paper.
+\citet{Francis_2020} included a subset of this dataset, corresponding to the C43-8 configuration, as part of a large sample of transition disks, with a focus on the statistical properties of the inner disks.
+
+\begin{table*}
+ \caption{Summary of the \red{\sout{new}} ALMA observations presented in this work.
+The table shows the total number of antennas, total time on  source (ToS), target average elevation, mean precipitable water vapor column (PWV) in the atmosphere, minimum and maximum baseline lengths and maximum recoverable scale (MRS).}
+ \label{tab:Summary_ALMA}
+ \begin{tabular}{lccccccccc}
+  \hline
+  Configuration & Execution Block & N Ant. & Date & ToS & Avg. Elev. & Mean PWV & Baseline & MRS \\
+   & (uid://A002/) & & & (sec) & (deg) & (mm) & (m) & (")\\
+  \hline
+  C43-8/9  & Xc6b674/X44f & 48 & 2017-11-10 & 507 &  50.9 &  1.0  & 113.0 - 13894.4 & 0.571 \\
+  C43-8  & Xc72427/X34f2 & 43 & 2017-11-23 & 507 & 45.2 & 0.4  &91.6-8547.6 & 0.8\\
+  \hline
+ \end{tabular}
+\end{table*}
 
@@
 The resulting {\tt uvmem} image shown in the top right panel of Fig.~\ref{fig:images_vs_simulated} reveals new substructure of the disc, in the form of two rings of large dust grains with a broad gap between them, i.e.
-Ring13 at 13\,au and Ring24 starting at 24\,au.
+Ring13 at $\sim$13\,au and Ring24 starting at $\sim$24\,au.
 The wide and bright Ring24 reaches its peak intensity at $\sim$30\,au, continues relatively flat and then breaks at $\sim$35\,au into a steeper tail.
@@
 Ring13 is surprisingly narrow and seems to be off-centred relative to the Gaia stellar position, at the origin of coordinates in Fig.~\ref{fig:images_vs_simulated}.
-We determined the ring's centre and orientation using the {\tt MPolarMaps} package described in \citep{2021arXiv210408379C}, which minimises the dispersion of the intensity radial profiles from 6 to 18\,au.
-The resulting disc orientation is set at a position angle (PA) of 77.31$\pm$0.03\,deg (east of north), with an inclination of 32.96$\pm$0.02\,deg, and the optimal ring centre is at $\Delta \alpha = -4\pm0.02$\,mas $\Delta \delta = 13\pm0.05$\,mas relative to the Gaia position of the stars.
+We determined the ring's centre and orientation using the {\tt MPolarMaps} package described in \citep{2021arXiv210408379C}, which minimises the dispersion of the intensity radial profiles \red{between two given radii.
+That way we take a range that fully includes Ring13 but not Ring24, so the range goes} from 6 to 18\,au for the first optimization.
+The resulting disc orientation is set at a position angle (PA) of 257.31$\pm$0.03\,deg (east of north), with an inclination of 147.04$\pm$0.02\,deg, and the optimal ring centre is at $\Delta \alpha = -4\pm0.02$\,mas $\Delta \delta = 13\pm0.05$\,mas relative to the Gaia position of the stars.
 The offset of the center of the cavity and the nominal stellar positions are coincident within the pointing accuracy of ALMA, which  is $\sim$5\,mas for the signal to noise ratio of our image (calculated using the ALMA Technical Handbook).
 
-In a second optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.86$\pm$0.02\,deg, with an inclination of 33.92$\pm$0.01\,deg and a centre at $\Delta \alpha = 2\pm0.02$\,mas $\Delta \delta = 12\pm0.02$\,mas relative to the stars.
+In a second optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 256.86$\pm$0.02\,deg, with an inclination of 146.08$\pm$0.01\,deg and a centre at $\Delta \alpha = 2\pm0.02$\,mas $\Delta \delta = 12\pm0.02$\,mas relative to the stars.
 We see that both Ring13 and Ring24 share a very similar orientation and centre, given the errors and the pointing accuracy.
 However, see that there are some hints for a somewhat different orientation in the azimuthal profiles for the ring radii, which may nonetheless be accounted for by the joint effect of all these small differences in disc orientation.
-This is summarised in Fig.~\ref{fig:polarring}b, which characterises the radial position and width of Ring13 as a function of azimuth by using radial Gaussian fits at each azimuth.
+This is summarised in Fig.~\ref{fig:polarring}a, which characterises the radial position and width of Ring13 as a function of azimuth by using radial Gaussian fits at each azimuth.
 The radial centroids for both disc orientation overlap within the errors, but there is a systematic trend for the difference between the two.
@@
 
-On average, we obtained a radial FWHM for Ring13 of 2.83$\pm$0.50\,au, and a stellocentric radius of 13.15$\pm$0.42\,au.
-As the {\tt uvmem} model image has an approximate {\tt uvmem} beam of $\sim$0$\farcs021 \,\times \,\sim$0$\farcs018$ (or $\sim$1.4\,au at 71.1\,pc), we see that Ring13 is resolved.
+On average, we obtained a radial FWHM for Ring13 of 2.83$\pm$0.50\,au, and a stellocentric radius of 13.15$\pm$0.42\,au (see Fig.~\ref{fig:polarring}b).
+As the {\tt uvmem} model image has an approximate {\tt uvmem} beam of $\sim$0$\farcs021 \,\times \,\sim$0$\farcs018$ (or $\sim$1.4\,au at 71.48\,pc), we see that Ring13 is resolved.
 After subtraction of the {\tt uvmem} beam, the ring width is $\sim$2.46$\pm$0.56\,au.
@@
 %\end{multline}
-%where $F$ is the total flux of the blob, $d$ the distance of 71.4\,pc , $\lambda$ the wavelength, $\kappa_{1.3\,\mathrm{mm}}$ the opacity at 1.3\,mm and the temperature set at $T=500\,\mathrm{K}$.
+%where $F$ is the total flux of the blob, $d$ the distance of 71.48\,pc , $\lambda$ the wavelength, $\kappa_{1.3\,\mathrm{mm}}$ the opacity at 1.3\,mm and the temperature set at $T=500\,\mathrm{K}$.
 Then, its estimated mass would be around 0.12\,M$_{\earth}$.
@@
   \includegraphics[width=\textwidth]{hot_two_E.pdf}
-  \caption{Comparison of observations (top) and simulated images (bottom) at 1.65\,$\micron$ (left) and 1.3\,mm continuum (right) of the circumbinary disc orbiting V4046\,Sgr.
-\textit{Top left panel:} SPHERE--IRDIS \textit{H}-band image with a yellow filled circle that represents the N\_ALC\_YJH\_S coronagraph with a radius of $\sim$0$\farcs12$, or $\sim$8.6\,au at 71.48\,pc.
-\textit{Top right panel:} 1.3\,mm continuum {\tt uvmem} model image.
+  \caption{Comparison of observations (top) and simulated images (bottom) at 1.3\,mm continuum (left) and 1.65\,$\micron$ (right) of the circumbinary disc orbiting V4046\,Sgr.
+\textit{Top left panel:} 1.3\,mm continuum {\tt uvmem} model image.
 The small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim$0$\farcs021 \, \times \, \sim$0$\farcs018$).
 The inset zooms into the central emission, and the green star marks the center of the inner ring.
-\textit{Bottom left panel:} synthetic image at 1.65\,$\micron$.
-\textit{Bottom right panel:} synthetic image at 1.3\,mm convolved with the {\tt uvmem} beam.
-For all the images in the figure the colour scale is linear, and the color bar on the right applies only to the images on the right-hand panel.}
+\textit{Top right panel:} SPHERE--IRDIS \textit{H}-band image with a white filled circle that represents the N\_ALC\_YJH\_S coronagraph with a radius of $\sim$0$\farcs12$, or $\sim$8.6\,au at 71.48\,pc.
+\textit{Bottom left panel:} synthetic image at 1.3\,mm convolved with the {\tt uvmem} beam.
+\textit{Bottom right panel:} synthetic image at 1.65\,$\micron$.
+For all the images in the figure the colour scale is linear, and the color bar on the left applies only to the images on the left-hand panel.}
   \label{fig:images_vs_simulated}
@@
     \includegraphics[width=\columnwidth]{polar_ring_aprox_and_diff_inner.pdf}
-    \caption{{\bf (a)} Polar decomposition of the 1.3\,mm continuum image, using the orientation of Ring24.
-We trace Ring13 using the centroids (solid line) and width of radial Gaussian fits (blue region between the dotted lines).
-{\bf (b)} Centroid of Ring13, for two disc orientations: the orange line corresponds to the same trace as in (a), while the blue line is obtained for the inner ring orientation.}
+    \caption{{\bf (a)} Centroid of Ring13, for two disc orientations: the orange line corresponds to the same trace as in (b), while the blue line is obtained for the inner ring orientation.
+{\bf (b)} Polar decomposition of the 1.3\,mm continuum image, using the orientation of Ring24.
+We trace Ring13 using the centroids (solid line) and FWHM of radial Gaussian fits (blue region between the dotted lines).}
     \label{fig:polarring}
@@
 	\includegraphics[width=\columnwidth]{SED_.pdf}
-    \caption{The observed SED of V4046\,Sgr (black points and solid red curve) compared with the model (blue).
+    \caption{The observed SED of V4046\,Sgr (black points and solid red curve) compared with the \red{resulting SED of radiative transfer model (solid blue line)}.
 The black points represent the measured photometry and the red line shows an archival \textit{Spitzer} IRS spectrum.
@@
 
+\subsection{General setup}
+
 The stars were modeled using two Kurucz photosphere models \citep{1979ApJS...40....1K, 1997A&A...318..841C}, with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$, respectively and with an accretion rate of $\mathrm{log}(\,\dot{\mathrm{M}}/(\mathrm{M}_{\sun}\,\mathrm{yr^{-1}})) = -$9.3 for both cases to include excess UV due to stellar accretion \citep{10.1111/j.1365-2966.2011.19366.x}.
@@
 Reproducing the radial and vertical structure of the V4046\,Sgr disc turned out to be challenging.
-We built the model in terms of the gas distribution, and with two main dust populations: larger grains that are vertically settled and dominate the total dust mass, and a population of smaller grains that are uniformly mixed with the gas and reach higher regions above the mid-plane.
-We also added a third dust population of larger grains with a  distribution tightly confined to the stellar vicinity, within 2\,au, and a special size range meant to account for the central emission.
+We built the model in terms of the gas distribution, and with two main dust populations: large grains with radii from 0.3\,$\micron$ to 10\,mm that are vertically settled and dominate the total dust mass, and a population of smaller grains with radii ranging from 0.3 to 1.5\,$\micron$ that are uniformly mixed with the gas and reach higher regions above the mid-plane.% We also added a third special dust population of larger grains with a distribution tightly confined to the stellar vicinity, within 2\,au, and a special size range meant to account for the central emission present in the ALMA image.
+This last dust population has grains with radii ranging from 0.8 to 10\,mm, same upper limit as the large dust but is depleted of small grains.
 
-Assuming a three dimensional model in a cylindrical reference frame with coordinates ($r$, $\theta$, $z$), the gas density ($\rho_{\mathrm{gas}}$) distribution follows
-\begin{equation}
-  \rho_{\mathrm{gas}}(r,z) =\frac{\Sigma_{\mathrm{gas}}(r)}{\sqrt{2\pi} \, H(r)} \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{H(r)}\right)^2\right],
-\end{equation}
-where $H(r)$ is the scale height profile and $\Sigma_{\mathrm{gas}}(r)$ is the gas surface density profile.
+We take a three dimensional model in a cylindrical reference frame with coordinates ($r$, $\theta$, $z$).
+The inner radius of the model grid was set to 0.1\,au, and the outer radius to 100\,au, which is large enough for the dust disc to be undetectable.
+We set the values of the inclination and disc position angle to the same as obtained from the ALMA observation in Section~\ref{sec:Observations}, such that the model has an inclination of i = 147.04\,deg and a P.A.
+= 257.31\,deg.
+The model was set at a distance of d = 71.48\,pc \citep{gaiacollaboration2021gaia}.
+
+\subsection{Vertical structure}
 
@@
 
+\begin{figure}
+	\includegraphics[width=\columnwidth]{allprofiles.png}
+        \caption{{\bf Top:} surface density profiles for gas, large and small dust grains.
+{\bf Bottom:} Aspect ratio profile $h(r)= H(r)/r$.
+The dashed brown line depicts an upper limit for large dust grains within Ring5, inferred from its non-detection in ALMA data.
+The dotted lines crossing both panels correspond to transition radii in the parametric model.}
+    \label{fig:profiles}
+\end{figure}
+
+\subsection{Radial structure: gas \& small dust grains}
+
+Given the cylindrical coordinates ($r$, $\theta$, $z$), the gas density ($\rho_{\mathrm{gas}}$) distribution follows
+\begin{equation}
+  \rho_{\mathrm{gas}}(r,z) =\frac{\Sigma_{\mathrm{gas}}(r)}{\sqrt{2\pi} \, H(r)} \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{H(r)}\right)^2\right],
+\end{equation}
+where $H(r)$ is the scale height profile and $\Sigma_{\mathrm{gas}}(r)$ is the gas surface density profile.
+
 Although both ALMA and SPHERE--IRDIS images display two-ringed morphologies, we propose a three-ringed structure plus an inner disc to reproduce the observations.
-This bold decision is due the major fit improvement in the SED and the polarize image (more on this in Sec.~\ref{sec:results}).
-We separate the disc into four individual regions: the inner disc, Ring5, Ring13, and Ring24.
+This bold decision is due the major fit improvement in the SED and the polarize image (more on this in Sec.~\ref{sec:results} \red{and Appendix~\ref{sec:A2}}).
+We separate the gas disc into four individual regions: the inner disc, Ring5, Ring13, and Ring24.
 The combined gas surface density profile is then given by:
 \begin{equation}
-  \Sigma_{\mathrm{gas}}(r) = \Sigma_{\mathrm{inner\,disc}}(r) + \Sigma_{\mathrm{R5}}(r) + \Sigma_{\mathrm{R13}}(r) + \Sigma_{\mathrm{R24}}(r)
+  \Sigma_{\mathrm{gas}}(r) = \Sigma_{\mathrm{inner\,disc}}(r) + \Sigma_{\mathrm{R5}}(r) + \Sigma_{\mathrm{R13}}(r) + \Sigma_{\mathrm{R24}}(r).
 \end{equation}
 
-The inner disc model follows a power-law function defined by
+First, the inner disc model follows a power-law function defined by
 \begin{equation}
@@
 We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =1.3\times10^{-4}$\,$\mathrm{g\,cm^{-3}}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
-The gas in our model extends from $R_{\mathrm{in}}$ = 0.2\,au outwards, consistent with the inner edge radius inferred from the SED data (see Sec.~\ref{subsec:SED}).
+The gas in our model extends from $R_{\mathrm{in}}$ = 0.2\,au outwards, consistent with the inner edge radius inferred from the SED data (\red{see Appendix~\ref{sec:A2}}).
 
-We chose to use Gaussian profiles to parametrize Ring5 and Ring13,
+\red{Secondly, due to the thin nature of Ring5 and Ring13,} we chose to use Gaussian profiles to parametrize them,
 \begin{equation}
@@
 
-For Ring24 we used the same power-law as for the inner disc but scaled by an empirically obtained factor, $\delta_{\mathrm{sd}}(r)$ and by $\epsilon(r)$, a parameter that allows us model a smoother inner edge of the outer ring:
+Thirdly, for Ring24 we used the same power-law as for the inner disc but scaled by an empirically obtained factor, $\delta_{\mathrm{sd}}(r)$ and by $\epsilon(r)$, a parameter that allows us model a smoother inner edge of the outer ring:
 \begin{equation}
@@
 where $R_\mathrm{in}$ and $R_\mathrm{peak}$ respectively mark the inner edge and the location of maximum density of the outer ring.
-We used $R_\mathrm{in,gas}$ = 18.0\,au and $R_\mathrm{peak,gas}$ = 26.4\,au.
+We used $R_\mathrm{in,gas}$ = 18\,au and $R_\mathrm{peak,gas}$ = 26.4\,au.
 
-The total dust-to-gas mass ratio is taken to be $\zeta = 0.047$ \citep[as in][]{Rosenfeld_2013}.
+Finally, the total dust-to-gas mass ratio is taken to be $\zeta = 0.047$ \citep[as in][]{Rosenfeld_2013}.
 The small dust grains are assumed to only make up for a fraction of $f_\mathrm{sd}=1\%$ of the total dust mass.
@@
 
-Since the large dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a larger inner cavity, a larger gap between Ring13 and Ring24, and a break in the outer ring.
+\subsection{Radial structure: large dust grains}
+
+Since the large dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, such as a larger inner cavity, a larger gap between Ring13 and Ring24, and a break in the outer ring.
 We only included a low density of large grains within Ring5, just underneath the detection limit of the ALMA observation, as it does not show any visible signature.
-We also truncated the profile of large dust grains at 63\,au.
-It is then defined by the sum of its three components
+The surface density profile of the large dust grains is then defined by the sum of its three components
 \begin{equation}
@@
 \end{equation}
-where for the smoothing factor $\epsilon(r)$ we used $R_\mathrm{in,ld}$ = 24.2\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$. In an effort to recreate the break seen in the outer ring, we used
+where for the smoothing factor $\epsilon(r)$ we used $R_\mathrm{in,ld}$ = 24.2\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$, resulting in a inner wall of Ring24 at larger radii but a peak at the same location.
+In an effort to recreate the break seen in the outer ring, we used
 \begin{equation}
@@
 \end{equation}
+Following the observation, this profile is truncated at 63\,au.
 
-These two different populations of dust grains correspond to small grains, with radii ranging from 0.3 to 1.5\,$\micron$, and large dust grains, with radii from 0.3\,$\micron$ to 10\,mm.
-We computed the dust opacities using the {\tt bhmie} code provided in the \textsc{radmc3d} package, with a mix composed of 60\% silicate, 20\% graphite and 20\% ice.
+\subsubsection{Reproducing the central emission}
+For whole purpose of reproducing the central emission in the ALMA image, we introduce a third and special dust population of larger grains with a distribution tightly confined to the stellar vicinity.
+This dust is distributed only on a very close-in Gaussian ring parameterized by $\mu_{\mathrm{central\,blob}}=1.1$\,au, $\sigma_{\mathrm{central\,blob}}=0.4$\,au and $\Sigma_{\circ,\mathrm{central\,blob}}=58.8\,\mathrm{g\,cm^{-3}}$, and it is composed of grains with radii ranging from 0.8 to 10\,mm, same upper limit as the large dust but is depleted of small grains.
+With this distinctive size range we avoid creating a NIR excess in the SED, and we can be consistent with previous mass estimates (see Appendix~\ref{sec:A1} and Sec.~\ref{sec:results}).
 
-The observed asymmetry between the near side and the far side of the disc in the DPI image is suggestive of a strongly forward-scattering phase function.
-In order to reproduce a similar asymmetry in the \textit{H}-band image, we used much larger grains than typically used in the RT modelling of such NIR data \citep[e.g.,][]{2018MNRAS.477.5104C}.
-We implemented a different grain size distribution, where we centred a Gaussian at $\mathrm{a}$ = 0.4\,$\micron$ with $\sigma_{\mathrm{a}}$ = 0.12\,$\micron$ (smeared out by 30\%), and distributed the dust over 20 bins within the range of $\pm \sigma$.
+\subsection{Image synthesis and SED computation}
+
+To take the simulated images we computed the dust opacities using the {\tt bhmie} code provided in the \textsc{radmc3d} package.
+The two main populations are taken to be composed by a mix of 60\% silicate, 20\% graphite and 20\% ice.
+Differently, for the special population of larger grains, as the ring is extremely proximate to the binary system, the dust will not have any traces of ice, so we used a composition mix of 70\% silicate and 30\% graphite.
+
+For the reproduction of the ALMA observation, we create an image using ray-tracing preceded by a Monte Carlo run that gives the simulated image at 1250\,$\micron$, the rest wavelength of the real observation.
+This image is then convolved with Gaussian blur using the uvmem beam of 0$\farcs021 \, \times \, $0$\farcs018$ to syntesize the final image displayed in Fig.~\ref{fig:images_vs_simulated}.
+The SED is computed in a similar manner by taking the spectra at 200 wavelengths between 0.1 and 2000\,$\micron$.
+
+In order to reproduce the \textit{H}-band image, we take a different approach.
+As the observed asymmetry between the near side and the far side of the disc in the DPI image is suggestive of a strongly forward-scattering phase function, we used much larger grains than typically used in the RT modelling of such NIR data \citep[e.g.,][]{2018MNRAS.477.5104C}.
+For the computation of this particular image, we implemented a different grain size distribution, where we centred a Gaussian at $\mathrm{a}$ = 0.4\,$\micron$ with $\sigma_{\mathrm{a}}$ = 0.12\,$\micron$ (smeared out by 30\%), and distributed the dust over 20 bins within the range of $\pm \sigma$.
 This distribution applies only to generate the NIR $Q_\phi$ image and not the ALMA image or the SED.
@@
 
-For the reproduction of central emission we introduce a special dust population that is distributed only on a very close Gaussian ring parameterized by $\mu_{\mathrm{central\,blob}}=1.1$\,au, $\sigma_{\mathrm{central\,blob}}=0.4$\,au and $\Sigma_{\circ,\mathrm{central\,blob}}=58.8\,\mathrm{g\,cm^{-3}}$.
-This dust population has grains with radii ranging from 0.8 to 10\,mm, same upper limit as the large dust but is depleted of small grains.
-This different size range is a way to avoid creating a NIR excess in the SED, and to be consistent with previous mass estimates (see Appendix~\ref{sec:Appendix} and Sec.~\ref{sec:results}).
-As the ring is extremely proximate to the binary system the dust will not have any traces of ice, so we used a composition mix of 70\% silicate and 30\% graphite.
-
-\begin{figure}
-	\includegraphics[width=\columnwidth]{allprofiles.png}
-        \caption{{\bf Top:} surface density profiles for gas, large and small dust grains.
-{\bf Bottom:} Aspect ratio profile $h(r)= H(r)/r$.
-The dashed brown line depicts an upper limit for large dust grains within Ring5, inferred from its non-detection in ALMA data.
-The dotted lines crossing both panels correspond to transition radii in the parametric model.}
-    \label{fig:profiles}
-\end{figure}
-
-The inner radius of the model grid was set to 0.1\,au, and the outer radius to 100\,au, which is large enough for the dust disc to be undetectable.
-We set the values of the inclination and disc position angle to the same as obtained from the ALMA observation in Section~\ref{sec:Observations}, such that the model has an inclination of i = 32.96\,deg and a P.A.
-= 77.31\,deg.
-Finally, the distance is set to d = 71.48\,pc \citep{gaiacollaboration2020gaia}.
-
-As mentioned before, the model presented here gives a solution to a highly degenerative problem, and the RT calculation for each set of parameters is very intensive in computational power and time, so a MCMC optimization or similar methods of parameter exploration are impossible to carry out.
-Nevertheless, as a way to improve the fit and obtain a rough measure of the accuracy of our model, we made one dimensional explorations of the parameter space and found uncertainties of some relevant parameters that will be useful for the discussion (see Appendix.~\ref{sec:Appendix}).
+Finally, as mentioned before, the model presented here gives a solution to a highly degenerative problem, and the RT calculation for each set of parameters is very intensive in computational power and time, so a MCMC optimization or similar methods of parameter exploration are impossible to carry out.
+Nevertheless, as a way to improve the fit and obtain a rough measure of the accuracy of our model, we made one dimensional explorations of the parameter space and found uncertainties of some relevant parameters that will be useful for the discussion (see Appendix~\ref{sec:A1}).
 We can estimate uncertainties for the scale height at $r_\circ$= 18\,au with $H_\circ = 0.89\pm0.01$\,au and for the width of the gas in Ring13 with $w_\mathrm{g} = 5.30\pm0.27$\,au.
@@
 The faint near-IR excess contrast with the bright mm emission, and could point to a lack of micron-sized dust in the central ring, that could be due to efficient dust growth or due to the ring having an inner radius well beyond the sublimation radius.
-In order to reproduce the low NIR and simultaneous bright central mm emission, we extended the radius of an inner cavity to significantly exceed both the sublimation radius ($\sim$0.05-0.1\,au) and the zone that is expected to be cleared by dynamical binary-disc interaction \citep[][$\lesssim$0.1\,au]{Art_Lu}.
+In order to reproduce the low NIR and simultaneous bright central mm emission, we extended the radius of an inner cavity to significantly exceed both the sublimation radius \red{\sout{($\sim$0.05\,au)}} and the zone that is expected to be cleared by dynamical binary-disc interaction \red{\sout{\citep[][$\lesssim$0.1\,au]{Art_Lu}} (see Appendix~\ref{sec:A2})}.
 A possible explanation for this wider cavity is the presence of an additional effect of truncation, like an unseen companion planet in the very inner part of the disc \citep{Francis_2020}.
 At the same time, the central emission is also well reproduced in the ALMA image with the inclusion of a Gaussian ring at 1.1\,au.
-This inner ring produces a low near-IR excess only if it consists of dust grains larger than $\sim$0.3\,mm (see Appendix~\ref{sec:Appendix}).
+This inner ring produces a low near-IR excess only if it consists of dust grains larger than $\sim$0.3\,mm (see Appendix.~\ref{sec:A1}).
 But we implement 0.8\,mm instead as the lower limit for the dust population that composes this feature, given that this predicts a dust mass of 0.012\,M$_{\earth}$, which is close to that obtained by \citet{Francis_2020} (0.013$\pm$0.002,M${\earth}$).
-They converted mm-flux into mass using the standard opacity value of $\kappa_{\nu}$=10\,$\mathrm{cm}^2 \mathrm{g}^{-1}$ at 1000\,GHz with an opacity power-law index of $\beta$=1.0.
-
+They converted mm-flux into mass using the standard opacity value of $\kappa_{\nu}$=10\,$\mathrm{cm}^2 \mathrm{g}^{-1}$ at 1000\,GHz with an opacity power-law index of $\beta$=1.0\red{, on the other hand, our mass estimations are made directly from the values extracted from the RT model.
+}
 \begin{figure}
@@
 
-The decision of including Ring5 to the observed structure relies on the fact that the SED needs a thin dust ring, made mainly of small dust grains, at a radius of $\sim$5\,au to have a proper fit around 15\,$\micron$ (see Appendix.\ref{sec:Appendix}).
+The decision of including Ring5 to the observed structure relies on the fact that the SED needs a thin dust ring, made mainly of small dust grains, at a radius of $\sim$5\,au to have a proper fit between 6 and 300\,$\micron$ (see Appendix~\ref{sec:A2}).
 The introduced Ring5 is not visible in the simulated image at 1.65\,$\micron$, where it hides under the artificial coronagraph, neither in the 1.3\,mm continuum simulated image, as its predicted peak intensity is around two times the noise in the ALMA image ($\sim$1$\times10^{-7}$\,Jy\,$\mathrm{beam}^{-1}$).
@@
 
+\red{The expected age of >20\,Myr of V4046\,Sgr suggests that its gas-rich disc is unconventionally old in comparison to typical circumstellar examples \citep[e.g.][]{Fedele2010, Williams2011}.
+The dispersal of such gas discs is typically assumed to be set by photo-evaporation \citep{Alexander2006,Gorti2009}.
+While the dynamical origin of the disc's longevity is not subject of the study at hand, we would like to mention that its occurrence around such a close binary might not be coincidental.
+\citet{Alexander2012} predicted that disc lifetimes should show a sharp increase around binaries separated by $\lesssim 0.3-1.0\,$au.
+It still has to be seen whether a trend towards longer disc lifetimes in compact multiple-star systems (as recently proposed by \citealp{Ronco2021}) turns out to be prevalent.}
+
 \section{Conclusions} \label{sec:Conclusions}
 
-Rings, cavities and gaps are common structures present in protoplanetary discs, but only recent observations have allowed us to study them in detail.
+%Rings and gaps are common structures present in protoplanetary discs, but only recent observations have allowed us to study them in detail.
 In the past years, observing systems with solar-type stars, that are not exceptionally bright or large, has not been the main focus of high resolution imaging.
 For that reason, using the DARTTS-S programme data, that collected DPI images for T Tauri Stars, together with the counterpart of ALMA continuum maps from DARTTS-A, we can search for substructures in that kind of systems as never before.
-Following that line, we present new ALMA 1.3\,mm continuum imaging of V4046\,Sgr, a well-known circumbinary disc, at an unprecedented definition ($\sim$0$\farcs021 \, \times \, \sim$0$\farcs018$), where new features become visible.
+Following that line,
+We present \red{\sout{new}} ALMA 1.3\,mm continuum imaging of V4046\,Sgr, a well-known circumbinary disc, at an unprecedented definition ($\sim$0$\farcs021 \, \times \, \sim$0$\farcs018$), where new features become visible.
 Together with the analysis of a SPHERE--IRDIS polarized image and a well-sampled SED, we aim to reproduce the observations with radiative transfer modeling, looking for a way to explain the data in terms of a physically model.
-
-The key conclusions of this multi-layered analysis are as follows.
+The key conclusions of this analysis are as follows.
 \begin{enumerate}
@@
 
-    \item Our parametric model, which accounts for the SED of the system, involves the existence of sub-micron dust inner disc.
-Also predicts the presence of a undetected inner ring at $\sim$5\,au, mainly consisting of small dust grains.
-The depletion of large dust is consistent with efficient dust trapping in Ring13.
-This additional ring lies under the coronagraph of the scattered light image and is to faint to be detected by the ALMA observation.
+    \item Our parametric model, which accounts for the SED of the system, predicts the presence of an inner ring at $\sim$5\,au, mainly consisting of small dust grains.
+This additional ring lies under the coronagraph of the scattered light image and is too faint to be detected by the ALMA observation.
+The depletion of large dust in this ring is consistent with efficient dust trapping at larger radii, as can be expected in Ring13.
 
-    \item We report the detection of a two-ringed disc structure.
-The narrow ring in the 1.3\,mm continuum, has a radius of 13.15$\pm$0.42\,au and an estimated width of 2.46$\pm$0.56\,au.
+    \item The narrow ring in the 1.3\,mm continuum, has a radius of 13.15$\pm$0.42\,au and an estimated width of 2.46$\pm$0.56\,au.
 The location of this ring is coincident with the inner ring observed in the scattered light image.
-From our RT modeling we can predict that the ring includes around 0.7\,M$_{\earth}$ of millimetre-sized grains.
-Using the parametric model scale height FWHM value for the large grains ($H=$ 0.25\,au at 13.15\,au) we find that the ring width is roughly 10 times its estimated height.
-The 1.3\,mm outer ring, that starts at $\sim$24\,au and has its peak intensity at $\sim$30\,au, presents a visible break in the surface brightness at $\sim$36\,au.
+From our RT modeling we can predict that this ring includes around 0.7\,M$_{\earth}$ of millimetre-sized grains.
+Using the parametric model scale height FWHM value for the large grains ($H_{\mathrm{ld}}=$ 0.25\,au at 13.15\,au) we find that the ring width is roughly 10 times its estimated height.
 
-    \item The resolved radial width of Ring13 speaks for the presence of a considerable level of turbulent viscosity.
+    \item The 1.3\,mm outer ring, that starts at $\sim$24\,au and has its peak intensity at $\sim$30\,au, presents a visible break in the surface brightness at $\sim$36\,au.
+
+    \item While we can not get an exact value for $\alpha_{\rm turb}$, the resolved radial width of Ring13 speaks for the presence of a considerable level of turbulent viscosity.
 
@@
 S.C.
-acknowledges support from FONDECYT grant 1171624.
+acknowledges support from FONDECYT grant 1211496.
 S.P.
@@
 acknowledges support from the FONDECYT Iniciaci\'on en investigaci\'on project number 11190837.
-MC acknowledges support from ANID PFCHA/DOCTORADO BECAS CHILE/2018-72190574.
+M.C.
+acknowledges support from ANID PFCHA/DOCTORADO BECAS CHILE/2018-72190574.
 This paper makes use of the following ALMA data: ADS/JAO.ALMA \#2017.0.01167.S.
@@
 
-\subsection{Parameter space partial exploration}
+\subsection{Parameter space partial exploration} \label{sec:A1}
 As a way to compute a measure of goodness of fit and to try to quantify the model uncertainties, we performed a partial exploration of the parameter space.
@@
 
-\subsection{Comparison between different models}
+\subsection{Comparison between different models}\label{sec:A2}
 
-Our model includes Ring5, a thin Gaussian ring mainly consisting of small dust grains located at 5.2\,au.
-The inclusion of this feature provides a great improvement in the SED fit, especially around the 10-30\,$\micron$ range.
-The sublimation radius of the system is expected to be at $\sim$0.05\,au \citep[$R_{sub}=0.07\sqrt{L_*(L_{\sun})}$,][]{Francis_2020}, and the edge of the zone cleared by dynamical interactions between the near-circular binary and the circumbinary disc is at 0.085\,au \citep[$r=2.08a$,][]{Art_Lu}.
-The inner radius of the disc in our best-fitting model lies outside of these two regions, at 0.2\,au.
+\red{The inner radius of the disc is usually defined by one of two phenomena, photo-evaporation or dynamical interaction with the central stars.
+The sublimation radius of the system is expected to be at $\sim$0.05\,au \citep[$R_{\mathrm{sub}}=0.07\sqrt{L_*(L_{\sun})}$,][]{Francis_2020}, and the edge of the zone cleared by dynamical interactions between the near-circular binary and the circumbinary disc is at 0.085\,au \citep[$r=2.08a$,][]{Art_Lu}.
+On the other hand, \citet{Jensen_97} concluded from the SED that the system matched that of a disc truncated at $\sim$0.2\,au.
+For our model we have found that following the latter value gives a significant improvement in the SED fit (see Fig.~\ref{fig:SED_comparition}), therefore, the inner radius of the disc in our best-fitting model lies at 0.2\,au.}
 
-In Fig.~\ref{fig:SED_comparition} we show a side-by-side comparison between our best-fitting model and two other models, one without Ring5, and another with the inner edge of the disc at the truncation radius due to dynamical binary-disc interaction.
-Both features considerably improve the fit in the 10-100\,$\micron$ range.
+\red{The final structure of our proposed disc also include some nontrivial features that were necessary in order to fit the SED and the images simultaneously.
+Those were the inner large-dust ring at 1.1\,au responsible for the central emission, and the thin Gaussian ring made mainly of small dust grains at 5.2\,au (Ring5).
+The first one is visible in the ALMA image so we are forced to include it, but Ring5 was added as its contribution to the SED is substantial.}
+
+\red{Fig.~\ref{fig:SED_comparition} works as a summary as it shows a comparison between our best-fitting model and five models with changes on their structures: one without Ring5, one without the inner large-dust disc, one without both of those structures, another with an inner edge of the disc at 0.085\,au, and a last one with an inner edge of the disc at 0.05\,au.
+All these models drift away from the SED data somewhere in the 6-300\,$\micron$ range.
+This noticeable offset led us to propose the presented model structure, where we found that adding Ring5 and the inner large-dust ring, and setting the inner edge of the disc at 0.2\,au improved the SED fit considerably.}
 
@@
 	\includegraphics[width=\columnwidth]{SED_three_model_comparision.pdf}
-        \caption{}
+        \caption{\red{Side-to-side comparison between spectral energy distributions of our model versus five other models with differences in their dust structure.
+Every model drift away from the best-fitting SED somewhere between 6 and 300\,$\micron$.
+The figure shows the impact that removing or changing one of them would have on the SED.
+The dotted lines represent the models with different inner radius while the dashed lines represent the models without Ring5 or the inner large-dust disc.}}
+        %the truncation radius due to dynamical binary-disc interaction.
     \label{fig:SED_comparition}

### 2021-10-09 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

@@
 Ring13 is surrounded by a $\sim$10\,au-wide gap, and it is flanked by a mm-bright outer ring (Ring24) with a sharp inner edge at 24\,au.
-Between 25 and $\sim$35\,au the brightness of Ring24 is relatively flat and then breaks into a steeper tail that reaches out to $\sim$60\,au.
+Between 25 and $\sim$35\,au the brightness of Ring24 is relatively flat and then breaks into a steep tail that reaches out to $\sim$60\,au.
 In addition, central emission is detected close to the star which we interpret as a tight circumbinary ring made of dust grains with a lower size limit of 0.8\,mm at 1.1\,au.
@@
 A parametric model that simultaneously fits the NIR scattered light and millimetre continuum emission links the observations to the structures in the underlying dust and gas density distributions, and sheds light on the complex processes that shaped them.
-In this paper, we present \red{\sout{new}} ALMA observations of the continuum emission at 1.3\,mm of V4046\,Sgr, which reveal an inner ring in the disc.
+In this paper, we present new ALMA observations of the continuum emission at 1.3\,mm of V4046\,Sgr with unprecedented angular resolution in this source, which reveal an inner ring in the disc.
 We also reproduce these observations with a 3D parametric model that fits all available data, including the polarized scattered light SPHERE image, the spectral energy distribution (SED), as well as the \red{\sout{new}} high definition 1.3\,mm continuum map.
@@
 The resulting {\tt uvmem} image shown in the top right panel of Fig.~\ref{fig:images_vs_simulated} reveals new substructure of the disc, in the form of two rings of large dust grains with a broad gap between them, i.e.
-Ring13 at $\sim$13\,au and Ring24 starting at $\sim$24\,au.
+Ring13 at \red{$\sim$}13\,au and Ring24 starting at \red{$\sim$}24\,au.
 The wide and bright Ring24 reaches its peak intensity at $\sim$30\,au, continues relatively flat and then breaks at $\sim$35\,au into a steeper tail.
@@
 Ring13 is surprisingly narrow and seems to be off-centred relative to the Gaia stellar position, at the origin of coordinates in Fig.~\ref{fig:images_vs_simulated}.
-We determined the ring's centre and orientation using the {\tt MPolarMaps} package described in \citep{2021arXiv210408379C}, which minimises the dispersion of the intensity radial profiles \red{between two given radii.
-That way we take a range that fully includes Ring13 but not Ring24, so the range goes} from 6 to 18\,au for the first optimization.
-The resulting disc orientation is set at a position angle (PA) of 257.31$\pm$0.03\,deg (east of north), with an inclination of 147.04$\pm$0.02\,deg, and the optimal ring centre is at $\Delta \alpha = -4\pm0.02$\,mas $\Delta \delta = 13\pm0.05$\,mas relative to the Gaia position of the stars.
+We determined the ring's centre and orientation using the {\tt MPolarMaps} package described in \citep{10.1093/mnras/stab2359}, which minimises the dispersion of the intensity radial profiles \red{between two given radii.
+In an initial optimization we focus on the orientation of Ring13, and choose a radial range from from 6 to 18\,au, which covers Ring13 but excludes Ring24.} The resulting disc orientation is set at a position angle (PA) of 257.31$\pm$0.03\,deg (east of north), with an inclination of 147.04$\pm$0.02\,deg, and the optimal ring centre is at $\Delta \alpha = -4\pm0.02$\,mas $\Delta \delta = 13\pm0.05$\,mas relative to the Gaia position of the stars.
 The offset of the center of the cavity and the nominal stellar positions are coincident within the pointing accuracy of ALMA, which  is $\sim$5\,mas for the signal to noise ratio of our image (calculated using the ALMA Technical Handbook).
 
-In a second optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 256.86$\pm$0.02\,deg, with an inclination of 146.08$\pm$0.01\,deg and a centre at $\Delta \alpha = 2\pm0.02$\,mas $\Delta \delta = 12\pm0.02$\,mas relative to the stars.
+In a second optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au \red{(fully including Ring24 and excluding Ring13)}, we obtained a PA of 256.86$\pm$0.02\,deg, with an inclination of 146.08$\pm$0.01\,deg and a centre at $\Delta \alpha = 2\pm0.02$\,mas $\Delta \delta = 12\pm0.02$\,mas relative to the stars.
 We see that both Ring13 and Ring24 share a very similar orientation and centre, given the errors and the pointing accuracy.
@@
 The scattered light image in the top left panel of Fig.~\ref{fig:images_vs_simulated} also shows a double ring structure in the micron-sized dust distribution.
-The observed morphology presents an inner cavity of $\sim$10\,au in radius and two rings located at 14.10$\pm$0.01\,au, coincident with Ring13, and 24.62$\pm$0.08\,au, coincident with Ring24, with a small gap between them at $\sim$20\,au.
-The observed second ring matches the inner wall of the 1.3\,mm continuum emission outer ring \citep{Ru_z_Rodr_guez_2019}.
+The observed morphology presents an inner cavity of $\sim$10\,au in radius and two rings located at 14.10$\pm$0.01\,au, coincident with Ring13, and 24.62$\pm$0.08\,au, coincident with Ring24, with a small gap between them at $\sim$20\,au \red{\citep{Ru_z_Rodr_guez_2019}}.
 Two other important features that are present in the image are: the near-far brightness asymmetry, and the shadows projected on the disc by the close binary system as they eclipse each other, discovered by \citet{dOrazi}.
@@
 The observed SED was collected from data in the literature \citep{1988iras....7.....H, 1990A&A...234..230H, Jensen_97, 2000A&A...355L..27H, 2001KFNT...17..409K, 2003yCat.2246....0C, 2007PASJ...59S.369M, 2008PASP..120.1128O, 2010A&A...514A...1I, 2012yCat.2311....0C}, available online in \textsc{vizier}.
-We also used archival \textit{Spitzer} IRS spectroscopic data available in the CASSIS database \citep{Lebouteiller_2015} (see Fig.~\ref{fig:SED}).
+We also used archival \textit{Spitzer} IRS spectroscopic data available in the CASSIS database \citep{Lebouteiller_2015}.
+\red{The data is displayed in Fig.~\ref{fig:SED} along with the resulting SED of the radiative transfer model presented in the next section (more on the SED in Sec.~\ref{sec:results})}.
 The SED exhibits the dip near 10\,$\micron$ characteristic of transition discs, as described by \citet{Rosenfeld_2013}.
@@
 	\includegraphics[width=\columnwidth]{SED_.pdf}
-    \caption{The observed SED of V4046\,Sgr (black points and solid red curve) compared with the \red{resulting SED of radiative transfer model (solid blue line)}.
+    \caption{The observed SED of V4046\,Sgr (black points and solid red curve) compared with the \red{model SED resulting from the RT model (solid blue line)}.
 The black points represent the measured photometry and the red line shows an archival \textit{Spitzer} IRS spectrum.
@@
 A high-resolution radiative transfer model that reproduces multi-frequency imaging and the SED, is a solution to a highly degenerate problem, so a full parameter exploration requires a level of computation and time that exceeds our capabilities and the scope of this paper.
-Consequently, our approach was to find through trial and error a set of values for the parameters that closely fit the available data, and then, improve this fit by implementing one dimensional least squared optimizations for some key parameters (more on this in Sec.~\ref{sec:results}).
+Consequently, our approach was to find through trial and error a set of values for the 3parameters that closely fit the available data, and then, improve this fit by implementing one dimensional least squared optimizations for some key parameters (more on this in Sec.~\ref{sec:results}).
 The final structure of the parametric model is summarised in Fig.~\ref{fig:profiles}, where we show on the top panel the surface density profiles for gas and dust grains populations, and in the lower panel the respective aspect ratio profile.
@@
 But we implement 0.8\,mm instead as the lower limit for the dust population that composes this feature, given that this predicts a dust mass of 0.012\,M$_{\earth}$, which is close to that obtained by \citet{Francis_2020} (0.013$\pm$0.002,M${\earth}$).
-They converted mm-flux into mass using the standard opacity value of $\kappa_{\nu}$=10\,$\mathrm{cm}^2 \mathrm{g}^{-1}$ at 1000\,GHz with an opacity power-law index of $\beta$=1.0\red{, on the other hand, our mass estimations are made directly from the values extracted from the RT model.
-}
+They converted mm-flux into mass using the standard opacity value of $\kappa_{\nu}$=10\,$\mathrm{cm}^2 \mathrm{g}^{-1}$ at 1000\,GHz with an opacity power-law index of $\beta$=1.0\red{, while our mass estimates are  extracted from the RT model.}
 \begin{figure}
@@
 The dispersal of such gas discs is typically assumed to be set by photo-evaporation \citep{Alexander2006,Gorti2009}.
-While the dynamical origin of the disc's longevity is not subject of the study at hand, we would like to mention that its occurrence around such a close binary might not be coincidental.
+While the dynamical origin of the disc’s longevity is not the subject of the present study, we would like to mention that its occurrence around such a close binary might not be coincidental.
 \citet{Alexander2012} predicted that disc lifetimes should show a sharp increase around binaries separated by $\lesssim 0.3-1.0\,$au.
@@
 \subsection{Parameter space partial exploration} \label{sec:A1}
+
+\begin{figure*}
+	\includegraphics[width=\textwidth]{plot_chi_squared_all.pdf}
+        \caption{One dimensional explorations of the chi squared space of our parametric model.
+The first panel shows the variation of $\chi^2$ in terms of the scale height $H_\circ$ at $r_\circ$=18\,au, the second one for the width of the gas component of Ring13 ($w_{\mathrm{g13}}$), and the third one around the lower limit of the grain size in the close inner ring.
+Each panel displays at the bottom the $\chi^2$ values for the SED and for the two images separately, and on top the total $\chi^2$ value in terms of the parameter value.}
+    \label{fig:chi}
+\end{figure*}
+
 As a way to compute a measure of goodness of fit and to try to quantify the model uncertainties, we performed a partial exploration of the parameter space.
@@
 
-\begin{figure*}
-	\includegraphics[width=\textwidth]{plot_chi_squared_all.pdf}
-        \caption{One dimensional explorations of the chi squared space of our parametric model.
-The first panel shows the variation of $\chi^2$ in terms of the scale height $H_\circ$ at $r_\circ$=18\,au, the second one for the width of the gas component of Ring13 ($w_{\mathrm{g13}}$), and the third one around the lower limit of the grain size in the close inner ring.
-Each panel displays at the bottom the $\chi^2$ values for the SED and for the two images separately, and on top the total $\chi^2$ value in terms of the parameter value.}
-    \label{fig:chi}
-\end{figure*}
-
 \subsection{Comparison between different models}\label{sec:A2}
 
-\red{The inner radius of the disc is usually defined by one of two phenomena, photo-evaporation or dynamical interaction with the central stars.
-The sublimation radius of the system is expected to be at $\sim$0.05\,au \citep[$R_{\mathrm{sub}}=0.07\sqrt{L_*(L_{\sun})}$,][]{Francis_2020}, and the edge of the zone cleared by dynamical interactions between the near-circular binary and the circumbinary disc is at 0.085\,au \citep[$r=2.08a$,][]{Art_Lu}.
-On the other hand, \citet{Jensen_97} concluded from the SED that the system matched that of a disc truncated at $\sim$0.2\,au.
-For our model we have found that following the latter value gives a significant improvement in the SED fit (see Fig.~\ref{fig:SED_comparition}), therefore, the inner radius of the disc in our best-fitting model lies at 0.2\,au.}
+\red{A compact inner hole in the dust distribution around a binary can typically be produced by sublimation of solids or dynamical clearing of the central stars.
+The sublimation radius of the system is expected to be at $\sim$0.05\,au \citep[$R_{\mathrm{sub}}=0.07\sqrt{L_*(L_{\sun})}$\,au,][]{Francis_2020}, and the edge of the zone cleared by dynamical interactions between the near-circular binary and the circumbinary disc is estimated to be at 0.085\,au \citep[$r=2.08a$,][]{Art_Lu}.
+On the other hand, for V4046 Sgr, \citet{Jensen_97} required to implement a cavity to 0.2\,au to fit the SED flux around the silicate feature at 10\,$\micron$.
+We find that the latter value significantly improves the SED fit when compared to a disc extending to the inner radius predicted by dynamical clearing in the SED fit (see Fig.~\ref{fig:SED_comparition}), therefore, the inner radius of the disc in our best-fitting model lies at 0.2\,au.}
 
-\red{The final structure of our proposed disc also include some nontrivial features that were necessary in order to fit the SED and the images simultaneously.
-Those were the inner large-dust ring at 1.1\,au responsible for the central emission, and the thin Gaussian ring made mainly of small dust grains at 5.2\,au (Ring5).
-The first one is visible in the ALMA image so we are forced to include it, but Ring5 was added as its contribution to the SED is substantial.}
+\red{The final structure of our proposed disc also includes additional features that are necessary to fit both the SED and the images.
+These features are a cut-off of the inner density accumulation of large dust grains outside of 1.1\,au (to fit the central emission in the ALMA image), and the thin Gaussian ring made mainly of small dust grains at 5.2\,au (Ring5, demanded by mid-infrared excess in the SED).
+The first one is visible in the ALMA image so we are forced to include it, but Ring5 is not detected in the ALMA continuum and was included because of its contribution to the 10$\micron$ flux is required by the SED.
+Fig.~\ref{fig:SED_comparition} works as a summary as it shows a comparison between our best-fitting model and five models with changes on their structures: one without Ring5, one without the inner large-dust disc, one without both of those structures, another with an inner edge of the disc at 0.085\,au, and a last one with an inner edge of the disc at 0.05\,au.
+All these models diverge from the SED data somewhere in the 6-300\,$\micron$ range.}
 
-\red{Fig.~\ref{fig:SED_comparition} works as a summary as it shows a comparison between our best-fitting model and five models with changes on their structures: one without Ring5, one without the inner large-dust disc, one without both of those structures, another with an inner edge of the disc at 0.085\,au, and a last one with an inner edge of the disc at 0.05\,au.
-All these models drift away from the SED data somewhere in the 6-300\,$\micron$ range.
-This noticeable offset led us to propose the presented model structure, where we found that adding Ring5 and the inner large-dust ring, and setting the inner edge of the disc at 0.2\,au improved the SED fit considerably.}
-
-\begin{figure*}
+\begin{figure}
 	\includegraphics[width=\columnwidth]{SED_three_model_comparision.pdf}
-        \caption{\red{Side-to-side comparison between spectral energy distributions of our model versus five other models with differences in their dust structure.
-Every model drift away from the best-fitting SED somewhere between 6 and 300\,$\micron$.
-The figure shows the impact that removing or changing one of them would have on the SED.
+        \caption{\red{Comparison between the SEDs of best-fitting model versus five other models with differences in the dust structure.
 The dotted lines represent the models with different inner radius while the dashed lines represent the models without Ring5 or the inner large-dust disc.}}
@@
 
-\end{figure*}
+\end{figure}
 
